---
title: "Untitled"
author: "helio"
date: "2026-01-22"
output: html_document
---


```{r}
```{r}
dta_mfa_part4_wide<- dta_mfa_part4_wide%>%
  left_join(dta_emo_dmg)

dta_mfa_part4_wide
dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(tas20_total<80)%>%
  ggplot(aes(tas20_total, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

# northing in tas and pcs coord

# now tas and contrib
dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(tas20_total, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(tas20_total<80)%>%
  ggplot(aes(tas20_total, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)
  # tas effect on PC 3 
```


only tas effect on PC3

now aq

```{r}


# dta_mfa_part4_wide<- dta_mfa_part4_wide%>%
#   left_join(dta_emo_dmg [,c("participant", "aq28_scale_sum_cont")])

dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(aq28_scale_sum_cont<80)%>%
  ggplot(aes(aq28_scale_sum_cont, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

# northing in aq and pcs coord

# now aq and contrib
dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(aq28_scale_sum_cont, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(aq28_scale_sum_cont<80)%>%
  ggplot(aes(aq28_scale_sum_cont, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)
 
```
nothing in aq


dass dep
```{r}
# dta_mfa_part4_wide
dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(dass21_dep<80)%>%
  ggplot(aes(dass21_dep, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

# northing in tas and pcs coord

# now tas and contrib
dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(dass21_dep, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(dass21_dep<80)%>%
  ggplot(aes(dass21_dep, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)



```

dass depression has an efect in PC contrinbution (coherence)


anx
```{r}

# dta_mfa_part4_wide
dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(dass21_anx<80)%>%
  ggplot(aes(dass21_anx, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

# northing in tas and pcs coord

# now tas and contrib
dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(dass21_anx, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(dass21_anx<80)%>%
  ggplot(aes(dass21_anx, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)



```

some trends nothingnof note


```{r}
dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, mfa_pc1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, mfa_pc2))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(dass21_total<80)%>%
  ggplot(aes(dass21_total, mfa_pc3))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

# northing in tas and pcs coord

# now tas and contrib
dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, log1p(mfa_pc1_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, log1p(mfa_pc2_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4_wide%>%
  ggplot(aes(dass21_total, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()
  

dta_mfa_part4_wide%>%
  # subset(dass21_total<80)%>%
  ggplot(aes(dass21_total, log1p(mfa_pc3_contrib+.01)))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

```


```{r}
dta_mfa_part4<- dta_mfa_part4%>%
  left_join(dta_emo_dmg)
 
dta_mfa_part



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp1.2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp1.2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp2.2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp2.2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp3.2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp3.2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)
  
# contrib

dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp1.2^2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp1.2^2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp2.2^2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp2.2^2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)


dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp3.2^2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()



dta_mfa_part4%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(tas20_total, pc_comp3.2^2))+
  geom_point()+
  geom_smooth(method = "lm")+
  # geom_jitter(width = .1, alpha = .2)+
  # stat_summary(geom = "pointrange")+
  ggpubr::stat_cor()+
  facet_grid(~social_nonsocial)

```


```{r}
# variables  mixed models
dta_mfa_part4$tas20_total_z<- scale(dta_mfa_part4$tas20_total)[,1]
mod_res$pc_comp1.2.lmer_tas <- lmer(pc_comp1.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*tas20_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp2.2.lmer_tas <- lmer(pc_comp2.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*tas20_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp3.2.lmer_tas <- lmer(pc_comp3.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*tas20_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

anova(mod_res$pc_comp1.2.lmer_tas)
anova(mod_res$pc_comp2.2.lmer_tas)
anova(mod_res$pc_comp3.2.lmer_tas)
```
<!-- Nothing here --> for tas


```{r}
dta_mfa_part4$aq28_scale_sum_cont_z<- scale(dta_mfa_part4$aq28_scale_sum_cont)[,1]
                                            
mod_res$pc_comp1.2.lmer_aq <- lmer(pc_comp1.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*aq28_scale_sum_cont_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp2.2.lmer_aq <- lmer(pc_comp2.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*aq28_scale_sum_cont_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp3.2.lmer_aq <- lmer(pc_comp3.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*aq28_scale_sum_cont_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

anova(mod_res$pc_comp1.2.lmer_aq)
anova(mod_res$pc_comp2.2.lmer_aq)
anova(mod_res$pc_comp3.2.lmer_aq)


```
nothing here


```{r}

# dta_mfa_part4$dass21_dep_z<- scale(dta_mfa_part4$dass21_dep)[,1]

mod_res$pc_comp1.2.lmer_das <- lmer(pc_comp1.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*dass21_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp2.2.lmer_das <- lmer(pc_comp2.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*dass21_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp3.2.lmer_das <- lmer(pc_comp3.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*dass21_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

anova(mod_res$pc_comp1.2.lmer_das)
anova(mod_res$pc_comp2.2.lmer_das)
anova(mod_res$pc_comp3.2.lmer_das)


mod_res$pc_comp1.2.lmer_das_dep <- lmer(pc_comp1.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*dass21_dep_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp2.2.lmer_das_dep <- lmer(pc_comp2.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*dass21_dep_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$pc_comp3.2.lmer_das_dep <- lmer(pc_comp3.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb*dass21_dep_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

anova(mod_res$pc_comp1.2.lmer_das_dep)
anova(mod_res$pc_comp2.2.lmer_das_dep)
anova(mod_res$pc_comp3.2.lmer_das_dep)


```

nothingof note

```{r}

dta_mfa_part4
mod_res$hr_mean_diff_tas_lmer <- lmer(hr_mean_diff ~ 1+ social_nonsocial * subj_emo_lab_no_amb*tas20_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$hr_mean_diff_aq_lmer <- lmer(hr_mean_diff ~ 1+ social_nonsocial * subj_emo_lab_no_amb*aq28_scale_sum_cont_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)


mod_res$logscr_mean_diff_tas_lmer <- lmer(log_cda_iscr ~ 1+ social_nonsocial * subj_emo_lab_no_amb*tas20_total_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

mod_res$logscr_mean_diff_aq_lmer <- lmer(log_cda_iscr ~ 1+ social_nonsocial * subj_emo_lab_no_amb*aq28_scale_sum_cont_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)


anova(mod_res$hr_mean_diff_tas_lmer)
anova(mod_res$hr_mean_diff_aq_lmer)
anova(mod_res$logscr_mean_diff_tas_lmer)
anova(mod_res$logscr_mean_diff_aq_lmer)
```