---
title: "Emotion Physio Mixed Models"
author: "Jay Davies"
date: "2025-09-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Mixed Models Analysis

Research Questions
RQ1. Does social context have a differential impact on affective modalities?

Variables: 
Subjective responses (valence, intensity and emotion sliders)
Autonomic responses (galvanic skin response and cardiac activity)
Behavioural responses (Eye tracking and facial movements)

```{r load libraries, results='hide', message=FALSE, warning=FALSE}
require(tidyverse)
require(readr)
require(lmerTest)
require(jtools)
require(merTools)
require(dplyr)
require(broom.mixed)
require(purrr)
require(ggplot2)
require(forcats)
library(emmeans)
require(cowplot)
options(scipen=999)
```

## Subjective and autonomic mixed models--------------------------------------------------------
```{r load data}
## Read in the data (we are working with 'dta_original_trial_exclusions')
## participants 101, 102, 201, 202, 203 and 204 excluded entirely due to missing face data
## Note here that we will first run models on all available data. Later on, we will create sub-sets for each signal

load("/Users/jaydavies/Library/CloudStorage/OneDrive-UniversityofBristol/Desktop/Jay_AffexLab/EmotionPhysio/Mixed Models Analysis/Helio_data.RData")

full_dta <- dta_original_trial_exclusions
colnames(full_dta)
```

```{r derive emotion ratings, warning=FALSE}

#Prepare subjective emotion columns derived from emotion ratings
  
## 1.Define which columns contain emotion slider ratings
emotion_cols <- c(
  "happy_slide_response",
  "sad_slide_response",
  "fear_slide_response",
  "disgust_slide_response",
  "anger_slide_response"
)

## 2. For each trial, create a single subjective emotion label based on the slider values
full_dta <- full_dta %>%
  rowwise() %>%
  mutate(
    # Handle where all emotion sliders are NA (e.g., rest trials)
    subj_emotion_label = if (all(is.na(c_across(all_of(emotion_cols))))) {
      NA_character_
    } else {
      max_score <- max(c_across(all_of(emotion_cols)), na.rm = TRUE)
      n_tied <- sum(c_across(all_of(emotion_cols)) == max_score, na.rm = TRUE)
      
      case_when(
        max_score < 4.5 ~ "neutral",
        n_tied > 1 ~ "ambiguous",
        TRUE ~ {
          best_idx <- which.max(c_across(all_of(emotion_cols)))
          sub("_slide_response$", "", emotion_cols[best_idx])
        }
      )
    }
  ) %>%
  ungroup()
 
unique(full_dta$subj_emotion_label)
  

## 3. Compute an aggregated label for each image (across participants)
agg_labels <- full_dta %>%
  group_by(stim_iaps) %>%
  summarise(
    across(all_of(emotion_cols), ~ mean(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    subj_emo_label_agg = if (all(is.na(c_across(all_of(emotion_cols))))) {
      NA_character_
    } else {
      max_avg <- max(c_across(all_of(emotion_cols)), na.rm = TRUE)
      n_tied <- sum(c_across(all_of(emotion_cols)) == max_avg, na.rm = TRUE)
      
      subj_emo_label_agg= case_when(
        max_avg < 4            ~ "neutral",
        n_tied  >  1           ~ "tie",
        TRUE                   ~ {
          best_idx <- which.max(c_across(all_of(emotion_cols)))
          sub("_slide_response$", "", emotion_cols[best_idx])
        }
      )
    }
  ) %>%
  ungroup()%>%
  dplyr::select(stim_iaps, subj_emo_label_agg)#emotion_cols

unique(agg_labels$subj_emo_label_agg)

# join data together
full_dta <- full_dta %>%
  left_join(agg_labels, by = "stim_iaps")


## 4. Visualise the distributions
full_dta %>%
  pivot_longer(
    cols      = emotion_cols,
    names_to  = "emotion",
    values_to = "emo_slider"
  ) %>%
  ggplot(aes(emo_slider, colour = emotion)) +
  geom_histogram() +
  facet_grid(subj_emo_label_agg ~ emotion) +  # or subj_emo_label_agg
  geom_vline(xintercept = 4.5)


unique(full_dta$subj_emotion_label)
full_dta$subj_emo_lab_no_amb<- if_else(full_dta$subj_emotion_label == "ambiguous", full_dta$subj_emo_label_agg, full_dta$subj_emotion_label)

unique(full_dta$subj_emo_lab_no_amb)
table(full_dta$emotioncategory)
table(full_dta$subj_emo_lab_no_amb)
table(full_dta$subj_emo_label_agg)

```

```{r raw data, message=FALSE, warning=FALSE, echo=FALSE}
# plot some raw data
# colorblind-friendly palette:
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73",  "#0072B2", "#CC79A7")

valence_social <- 
  full_dta%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, val_slider_response, color = social_nonsocial))+
    labs(
    x = "Manipulation",
    y = "Valence Ratings (mean)",
    color = "",
  )+
  ylim(0,7)+
  scale_colour_manual(values=cbbPalette)+
  theme_cowplot()+
  ggtitle("Social effects on Subjective Ratings") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  stat_summary(geom = "pointrange")


intensity_social<-
  full_dta%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, int_slider_response, color = social_nonsocial))+
  labs(
    x = "Manipulation",
    y = "Intensity Ratings (mean)",
    color = "",
  )+
  ylim(0,7)+
  scale_colour_manual(values=cbbPalette)+
  theme_cowplot()+
  theme(legend.position = "none")+
  stat_summary(geom = "pointrange")

val_int_social_plot <- plot_grid(valence_social, intensity_social, ncol = 1)
#ggsave('val_int_social_plot.tiff', plot = val_int_social_plot,bg="white")

val_int_social_plot

valence_emotion <-
  full_dta%>%
  group_by(participant,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(subj_emo_lab_no_amb, val_slider_response, color = subj_emo_lab_no_amb))+
  labs(
    x = "Emotion",
    y = "Valence Ratings (mean)",
    color = "",
  )+
  ylim(0,7)+
  scale_colour_manual(values=cbbPalette)+
  theme_cowplot()+
  ggtitle("Emotion effects on Subjective Ratings") +
  theme(plot.title = element_text(hjust = 0.5))+
  stat_summary(geom = "pointrange")

intensity_emotion<-
  full_dta%>%
  group_by(participant,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(subj_emo_lab_no_amb, int_slider_response, color = subj_emo_lab_no_amb))+
  labs(
    x = "Emotion",
    y = "Intensity Ratings (mean)",
    color = "",
  )+
  ylim(0,7)+
  scale_colour_manual(values=cbbPalette)+
  theme_cowplot()+
  stat_summary(geom = "pointrange")

val_int_emotion_plot <- plot_grid(valence_emotion, intensity_emotion, ncol = 1)
#ggsave('val_int_emotion_plot.tiff', plot = val_int_emotion_plot,bg="white")
val_int_emotion_plot


hr_social <-
  full_dta%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(social_nonsocial, hr_mean_diff, colour = social_nonsocial))+
  labs(
    x = "Manipulation",
    y = "Heart Rate (mean difference)",
    color = "",
  )+
  scale_colour_manual(values=cbbPalette)+
  theme_cowplot()+
  ggtitle("Social Manipulation x Autonomic Responses") +
  theme(plot.title = element_text(hjust = 0.5))+
  stat_summary(geom = "pointrange")

ibi_social <- full_dta%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(social_nonsocial, ibi_mean_diff, colour = social_nonsocial))+
  labs(
    x = "Manipulation",
    y = "Interbeat Interval (mean difference)",
    color = "",
  )+
  theme_cowplot()+
  scale_colour_manual(values=cbbPalette)+
  stat_summary(geom = "pointrange")

scr_social <- full_dta%>%
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(social_nonsocial, log_cda_phasic_max, colour = social_nonsocial))+
  labs(
    x = "Manipulation",
    y = "Skin Conductance (CDA)",
    color = "",
  )+
  theme_cowplot()+
  scale_colour_manual(values=cbbPalette)+
  stat_summary(geom = "pointrange")

social_autonomic_plots <- plot_grid(hr_social, ibi_social, scr_social, ncol = 1)
#ggsave('social_autonomic_plots.tiff', plot = social_autonomic_plots,bg="white")

social_autonomic_plots

hr_emotion<-
  full_dta%>%
  group_by(participant, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(subj_emo_lab_no_amb, hr_mean_diff, colour = subj_emo_lab_no_amb))+
  labs(
    x = "",
    y = "Heart Rate (mean difference)",
    color = "",
  )+
  theme_cowplot()+
  scale_colour_manual(values=cbbPalette)+
  stat_summary(geom = "pointrange")+
  ggtitle("Emotion x Autonomic Responses") +
  theme(plot.title = element_text(hjust = 0.5))

ibi_emotion <- 
  full_dta%>%
  group_by(participant, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(subj_emo_lab_no_amb, ibi_mean_diff, color = subj_emo_lab_no_amb))+
  labs(
    x = "",
    y = "Interbeat Interval (mean difference)",
    color = "",
  )+
  theme_cowplot()+
  scale_colour_manual(values=cbbPalette)+
  stat_summary(geom = "pointrange")

scr_emotion <- 
  full_dta%>%
  group_by(participant, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(subj_emo_lab_no_amb, log_cda_phasic_max, color = subj_emo_lab_no_amb))+
  labs(
    x = "Emotion",
    y = "Skin Conductance (CDA)",
    color = "",
  )+ 
  theme_cowplot()+
  scale_colour_manual(values=cbbPalette)+
  stat_summary(geom = "pointrange")

emotion_autonomic_plots <- plot_grid(hr_emotion, ibi_emotion,scr_emotion, ncol = 1)
#ggsave('emotion_autonomic_plots.tiff', plot = emotion_autonomic_plots,bg="white")

emotion_autonomic_plots


```

```{r create subjective ratings subset}
# 1. Create data subset of the subjective ratings (valence, intensity, emotion ratings) 
subjective_data<-subset(full_dta, select= c(1:55, 133:135))
```

```{r effects of objective emotion category and social manipulation on subjective ratings}

# Subjective ratings: 
#   "val_slider_response" - Valence
#   "int_slider_response" - Intensity
#   "happy_slide_response" - Happy
#   "sad_slide_response" - Sad
#   "fear_slide_response" - Fear
#   "disgust_slide_response" - Disgust
#   "anger_slide_response" - Anger

# set sum contrasts
# what does this do? avoids comparing effects to a 'baseline' variable and instead tests whether any levels differ from the grand mean 
options(contrasts =c("contr.sum", "contr.sum"))

# # set neutral as the reference level  
#options(contrasts = c("contr.treatment", "contr.poly"))
#subjective_data$emotioncategory <- relevel(subjective_data$emotioncategory, ref = "neutral")

# Subjective rating models:
subjratings_x_social_objemotion<- list()

# Valence
subjratings_x_social_objemotion$Valence<-lmer(val_slider_response ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + 
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = subjective_data)

# Intensity
subjratings_x_social_objemotion$Intensity<- lmer(int_slider_response ~ 1+ social_nonsocial * emotioncategory + 
                           (1|participant) + 
                           (1|stim_iaps), 
                         REML = FALSE,
                         data = subjective_data)
subjratings_x_social_objemotion$Intensity
library(lmerTest)
anova(subjratings_x_social_objemotion$Valence, type = 3)
anova(subjratings_x_social_objemotion$Intensity, type = 3)

# run a post hoc for the intensity model

intensity_emm <- emmeans(subjratings_x_social_objemotion$Intensity, ~ social_nonsocial + emotioncategory, infer = c(TRUE, TRUE))
valence_emm <- emmeans(subjratings_x_social_objemotion$Valence,~ social_nonsocial + emotioncategory,  infer = c(TRUE, TRUE))

valence_df   <- as.data.frame(valence_emm)   %>% mutate(model = "Valence")
intensity_df <- as.data.frame(intensity_emm) %>% mutate(model = "Intensity")


posthoc_social <- pairs(intensity_emm, by = "emotioncategory", adjust = "tukey")
posthoc_emotion <- pairs(intensity_emm, by = "social_nonsocial", adjust = "tukey")

# #plot social manipulation only - 

subjratings_x_social_objemotion_df <- map_dfr(subjratings_x_social_objemotion, tidy, effects = "fixed", conf.int = TRUE, .id = "model")
# Filter
social_effects1 <- subjratings_x_social_objemotion_df %>%
  filter(term == "social_nonsocial1" | term == "social_nonsocial") %>%
  mutate(term = "Social vs Non-Social")  # optional cleaner label

plot1<-
  ggplot(social_effects1, aes(x = estimate, y = model)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_text(aes(label = paste0("p = ", signif(p.value, 2))),
            hjust = -0.1, vjust = 1.2, size = 3.5) +
  labs(x = "Estimate (95% CI)", y = "Model",
       title = "Social vs Non-Social Effect on Subjective Ratings") +
  theme_minimal(base_size = 14)

#ggsave('subjratings_x_social_objemo.tiff', plot = plot1,bg="white")
plot1

# we want all 6 emotion category predictors in our plot, so we need to extra them using emmeans
# valence_emm<- emmeans(subjratings_x_social_objemotion$Valence, ~ emotioncategory)
# intensity_emm<- emmeans(subjratings_x_social_objemotion$Intensity, ~ emotioncategory)

valence_emm <- emmeans(subjratings_x_social_objemotion$Valence, ~ emotioncategory, infer = c(TRUE, TRUE))
intensity_emm <- emmeans(subjratings_x_social_objemotion$Intensity, ~ emotioncategory, infer = c(TRUE, TRUE))

emmeans_df <- bind_rows(
  as.data.frame(valence_emm) %>% mutate(model = "Valence"),
  as.data.frame(intensity_emm) %>% mutate(model = "Intensity")
)

plot2 <- ggplot(emmeans_df, aes(x = emmean, y = fct_rev(model), color = emotioncategory)) +
  geom_point(position = position_dodge(width = 0.7), size = 3) +
  geom_errorbarh(aes(xmin = asymp.LCL, xmax = asymp.UCL),
                 position = position_dodge(width = 0.7), height = 0.2) +
  geom_text(aes(label = ifelse(p.value < 0.001, "p < .001",
                             paste0("p = ", signif(p.value, 2)))),
          position = position_dodge(width = 0.7),
          hjust = -0.2, vjust = -0.5, size = 3.5)+
  geom_vline(xintercept = 0, linetype = "dashed") +
  # Add horizontal separator line
  geom_hline(yintercept = 1.5, linetype = "solid", color = "black", linewidth = 0.5) +
  labs(x = "Estimate (95% CI)", y = "Model",
       title = "Objective Emotion Category Effects",
       color = "Emotion") +
  theme_minimal(base_size = 14)
#ggsave('subjratings_x_objemotion.tiff', plot = plot2, bg = "white")

plot1
plot2
```


```{r effects of subjective emotion ratings and social manip on subjective ratings}
options(contrasts =c("contr.sum", "contr.sum"))

# Subjective rating models:
subjratings_x_social_subjemotion<- list()

# Valence
subjratings_x_social_subjemotion$Valence<-lmer(val_slider_response ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                (1|participant) + 
                                                (1|stim_iaps), 
                                              REML = FALSE,
                                              data = subjective_data)

# Intensity
subjratings_x_social_subjemotion$Intensity<- lmer(int_slider_response ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = subjective_data)

anova(subjratings_x_social_subjemotion$Valence, type = 3)
anova(subjratings_x_social_subjemotion$Intensity, type = 3)

```

Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF  F value              Pr(>F)    
social_nonsocial                        0.01    0.01     1  102.5   0.0064              0.9362    
subj_emo_lab_no_amb                  1974.60  394.92     5 5439.0 244.9644 <0.0000000000000002 ***
social_nonsocial:subj_emo_lab_no_amb    8.71    1.74     5 5435.7   1.0810              0.3686    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF  F value               Pr(>F)    
social_nonsocial                        5.28    5.28     1   94.2   1.4586              0.23018    
subj_emo_lab_no_amb                  2825.28  565.06     5 5274.8 155.9683 < 0.0000000000000002 ***
social_nonsocial:subj_emo_lab_no_amb   67.16   13.43     5 5402.5   3.7074              0.00237 ** 
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


breakdown the interaction effect above

```{r posthoc for intensity x subjective ratings, message = FALSE}
valence_emm2 <- emmeans(subjratings_x_social_subjemotion$Valence, ~ social_nonsocial + subj_emo_lab_no_amb)
valence_posthoc <-pairs(valence_emm2, adjust = "tukey")
valence_posthoc

intensity_emm2 <- emmeans(subjratings_x_social_subjemotion$Intensity, ~ social_nonsocial + subj_emo_lab_no_amb, infer = c(TRUE, TRUE))
intensity_posthoc <- pairs(intensity_emm2, adjust = "tukey")
intensity_posthoc


intensity_emm3 <- emmeans(subjratings_x_social_subjemotion$Intensity, pairwise~  social_nonsocial| subj_emo_lab_no_amb)
intensity_emm3
intensity_interaction <- pairs(intensity_emm3, adjust = "tukey")
intensity_interaction
```
 contrast                              estimate    SE  df z.ratio p.value
 nonsocial anger - social anger          0.1865 0.292 Inf   0.639  1.0000
 nonsocial anger - nonsocial disgust     0.3801 0.175 Inf   2.173  0.5691
 nonsocial anger - social disgust        0.5714 0.268 Inf   2.133  0.5989
 nonsocial anger - nonsocial fear        0.3461 0.181 Inf   1.911  0.7524
 nonsocial anger - social fear           0.6855 0.275 Inf   2.489  0.3465
 nonsocial anger - nonsocial happy       1.3075 0.183 Inf   7.129  <.0001
 nonsocial anger - social happy          1.9140 0.273 Inf   7.006  <.0001
 nonsocial anger - nonsocial neutral     3.0017 0.188 Inf  15.942  <.0001
 nonsocial anger - social neutral        3.2565 0.272 Inf  11.994  <.0001
 nonsocial anger - nonsocial sad         0.6106 0.176 Inf   3.467  0.0264
 nonsocial anger - social sad            0.5461 0.268 Inf   2.040  0.6656
 social anger - nonsocial disgust        0.1936 0.278 Inf   0.697  0.9999
 social anger - social disgust           0.3850 0.194 Inf   1.982  0.7057
 social anger - nonsocial fear           0.1596 0.283 Inf   0.564  1.0000
 social anger - social fear              0.4991 0.206 Inf   2.426  0.3878
 social anger - nonsocial happy          1.1210 0.285 Inf   3.935  0.0047
 social anger - social happy             1.7275 0.204 Inf   8.470  <.0001
 social anger - nonsocial neutral        2.8152 0.285 Inf   9.861  <.0001
 social anger - social neutral           3.0700 0.202 Inf  15.204  <.0001
 social anger - nonsocial sad            0.4241 0.279 Inf   1.520  0.9355
 social anger - social sad               0.3597 0.195 Inf   1.847  0.7918
 nonsocial disgust - social disgust      0.1913 0.227 Inf   0.842  0.9995
 nonsocial disgust - nonsocial fear     -0.0340 0.151 Inf  -0.225  1.0000
 nonsocial disgust - social fear         0.3054 0.256 Inf   1.191  0.9897
 nonsocial disgust - nonsocial happy     0.9274 0.148 Inf   6.284  <.0001
 nonsocial disgust - social happy        1.5339 0.250 Inf   6.124  <.0001
 nonsocial disgust - nonsocial neutral   2.6216 0.152 Inf  17.216  <.0001
 nonsocial disgust - social neutral      2.8763 0.250 Inf  11.499  <.0001
 nonsocial disgust - nonsocial sad       0.2304 0.145 Inf   1.594  0.9119
 nonsocial disgust - social sad          0.1660 0.248 Inf   0.669  1.0000
 social disgust - nonsocial fear        -0.2253 0.253 Inf  -0.890  0.9992
 social disgust - social fear            0.1141 0.162 Inf   0.705  0.9999
 social disgust - nonsocial happy        0.7361 0.251 Inf   2.932  0.1296
 social disgust - social happy           1.3426 0.153 Inf   8.796  <.0001
 social disgust - nonsocial neutral      2.4303 0.253 Inf   9.589  <.0001
 social disgust - social neutral         2.6850 0.153 Inf  17.508  <.0001
 social disgust - nonsocial sad          0.0391 0.249 Inf   0.157  1.0000
 social disgust - social sad            -0.0253 0.149 Inf  -0.169  1.0000
 nonsocial fear - social fear            0.3394 0.251 Inf   1.352  0.9721
 nonsocial fear - nonsocial happy        0.9614 0.149 Inf   6.451  <.0001
 nonsocial fear - social happy           1.5679 0.251 Inf   6.235  <.0001
 nonsocial fear - nonsocial neutral      2.6556 0.155 Inf  17.174  <.0001
 nonsocial fear - social neutral         2.9104 0.250 Inf  11.652  <.0001
 nonsocial fear - nonsocial sad          0.2645 0.154 Inf   1.715  0.8619
 nonsocial fear - social sad             0.2000 0.254 Inf   0.788  0.9998
 social fear - nonsocial happy           0.6220 0.255 Inf   2.437  0.3806
 social fear - social happy              1.2285 0.159 Inf   7.723  <.0001
 social fear - nonsocial neutral         2.3162 0.257 Inf   9.025  <.0001
 social fear - social neutral            2.5709 0.160 Inf  16.063  <.0001
 social fear - nonsocial sad            -0.0750 0.258 Inf  -0.291  1.0000
 social fear - social sad               -0.1394 0.164 Inf  -0.851  0.9995
 nonsocial happy - social happy          0.6065 0.224 Inf   2.705  0.2237
 nonsocial happy - nonsocial neutral     1.6942 0.135 Inf  12.532  <.0001
 nonsocial happy - social neutral        1.9489 0.239 Inf   8.171  <.0001
 nonsocial happy - nonsocial sad        -0.6969 0.152 Inf  -4.575  0.0003
 nonsocial happy - social sad           -0.7614 0.253 Inf  -3.012  0.1050
 social happy - nonsocial neutral        1.0877 0.242 Inf   4.489  0.0004
 social happy - social neutral           1.3424 0.134 Inf  10.027  <.0001
 social happy - nonsocial sad           -1.3035 0.253 Inf  -5.145  <.0001
 social happy - social sad              -1.3679 0.156 Inf  -8.785  <.0001
 nonsocial neutral - social neutral      0.2548 0.245 Inf   1.038  0.9968
 nonsocial neutral - nonsocial sad      -2.3911 0.156 Inf -15.312  <.0001
 nonsocial neutral - social sad         -2.4556 0.255 Inf  -9.642  <.0001
 social neutral - nonsocial sad         -2.6459 0.252 Inf -10.488  <.0001
 social neutral - social sad            -2.7103 0.155 Inf -17.519  <.0001
 nonsocial sad - social sad             -0.0644 0.240 Inf  -0.268  1.0000

Degrees-of-freedom method: asymptotic 
P value adjustment: tukey method for comparing a family of 12 estimates 

```{r plot}
#combined plots 
#raw data points per ppt
valence_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb) %>%
   summarise(
    mean = mean(val_slider_response, na.rm = TRUE),
    sd   = sd(val_slider_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop"
  )

#summary stats 
valence_agg_means2 <- subjective_data %>%
  group_by(social_nonsocial, subj_emo_lab_no_amb) %>%
  summarise(
    mean = mean(val_slider_response, na.rm = TRUE),
    sd   = sd(val_slider_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)


valence_df2   <- as.data.frame(valence_emm2)   %>% mutate(model = "Valence")
intensity_df2 <- as.data.frame(intensity_emm2) %>% mutate(model = "Intensity")

social_x_valence <- ggplot(valence_agg_means, aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 0.8, alpha = 0.15) +
  # summary mean points
  geom_point(data = valence_agg_means2, aes(x = social_nonsocial, y = mean, colour = social_nonsocial),
             size = 1.5, inherit.aes = FALSE) +
  # summary error bars
  geom_errorbar(data = valence_agg_means2, aes(x = social_nonsocial, y = mean, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ subj_emo_lab_no_amb, nrow = 1) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Valence (Mean)", colour = "") +
  theme_classic(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size =14 ),
    axis.title.x = element_text(face = "bold", size = 14),
    axis.title.y = element_text(face = "bold", size = 14),
    axis.text.y = element_text(size =14),
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )

social_x_valence

ggsave(filename = "valence.tiff", plot = social_x_valence, width = 7, height = 7, dpi = 300, compression = "lzw", bg = "white")

intensity_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb) %>%
  summarise(mean = mean(int_slider_response, na.rm = TRUE), .groups = "drop")


#summary stats 
intensity_agg_means2 <- subjective_data %>%
  group_by(social_nonsocial, subj_emo_lab_no_amb) %>%
  summarise(
    mean = mean(int_slider_response, na.rm = TRUE),
    sd   = sd(int_slider_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)


social_x_intensity <- ggplot(intensity_agg_means, aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 0.8, alpha = 0.15) +
  # summary mean points
  geom_point(data = intensity_agg_means2, aes(x = social_nonsocial, y = mean, colour = social_nonsocial),
             size = 1.5, inherit.aes = FALSE) +
  # summary error bars
  geom_errorbar(data = intensity_agg_means2, aes(x = social_nonsocial, y = mean, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ subj_emo_lab_no_amb, nrow = 1) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Intensity (Mean)", colour = "") +
  theme_classic(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size =14 ),
    axis.title.x = element_text(face = "bold", size = 14),
    axis.title.y = element_text(face = "bold", size = 14),
    axis.text.y = element_text(size =14),
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )

social_x_intensity

ggsave(filename = "intensity_model.tiff", plot = social_x_intensity, width = 7, height = 7,dpi = 300,compression = "lzw", bg = "white")

```
Linear mixed-effects models were fitted to examine the effects of social context (social vs. nonsocial) and emotion category on subjective ratings of valence and intensity.

For valence ratings, there was no significant main effect of social context, F(1, 102.5) = 0.01, p = .936, and no significant interaction between social context and emotion category, F(5, 5436) = 1.08, p = .369. Yet, valence ratings were significantly impacted by the type of emotion presented (F(5, 5439) = 244.96, p < .001).Post-hoc comparisons of estimated marginal means (Tukey-adjusted) showed that valence ratings differed reliably between most emotions. Happy and neutral stimuli received the highest valence ratings overall, while anger, fear, sad and disgust were rated lower in valence (see Figure X)

For intensity ratings, there was no main effect of social context, (F(1, 94.2 = 1.46, p = .23). As for valence, intensity ratings were significantly impacted by the emotion presented (F(5, 5274.8) = 155.968, p < .001). Importantly, the interaction between social context and emotion category was significant, F(5, 5369) = 3.92, p = .001, indicating that the influence of social context on intensity ratings differed across emotions. Post-hoc comparisons (tukey adjusted) revealed that that neutral images were consistently rated lower in intensity than all other emotions across both social and nonsocial contexts (p < .001). Anger, disgust, and fear were rated as the most intense, with no reliable modulation by social context. The interaction was driven by differences in happy and sad ratings: happy stimuli were rated as more intense in social compared to nonsocial contexts, whereas sad stimuli were rated as less intense in social compared to nonsocial contexts.

```{r social context effects on emotion ratings}
subjratings_x_social_subjemotion$Happy<- lmer(happy_slide_response ~ 1+ social_nonsocial + 
                          (1|participant) + 
                          (1|stim_iaps), 
                        REML = FALSE,
                        data = subjective_data)

subjratings_x_social_subjemotion$Sad<- lmer(sad_slide_response ~ 1+ social_nonsocial  + 
                          (1|participant) + 
                          (1|stim_iaps), 
                        REML = FALSE,
                        data = subjective_data)

subjratings_x_social_subjemotion$Fear<- lmer(fear_slide_response ~ 1+ social_nonsocial  + 
                           (1|participant) + 
                           (1|stim_iaps), 
                         REML = FALSE,
                         data = subjective_data)

subjratings_x_social_subjemotion$Disgust<- lmer(disgust_slide_response ~ 1+ social_nonsocial  + 
                           (1|participant) + 
                           (1|stim_iaps), 
                         REML = FALSE,
                         data = subjective_data)

subjratings_x_social_subjemotion$Anger<- lmer(anger_slide_response ~ 1+ social_nonsocial +
                          (1|participant) + 
                          (1|stim_iaps), 
                        REML = FALSE,
                        data = subjective_data)

anova(subjratings_x_social_subjemotion$Happy, type = 3)
anova(subjratings_x_social_subjemotion$Sad, type = 3)
anova(subjratings_x_social_subjemotion$Fear, type = 3)
anova(subjratings_x_social_subjemotion$Disgust, type = 3)
anova(subjratings_x_social_subjemotion$Anger, type = 3)
```

Type III Analysis of Variance Table with Satterthwaite's method
                 Sum Sq Mean Sq NumDF  DenDF F value Pr(>F)
social_nonsocial 3.3658  3.3658     1 91.113  1.3004 0.2571
Type III Analysis of Variance Table with Satterthwaite's method
                 Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial 12.163  12.163     1 91.238  3.1779 0.07797 .
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                 Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial  12.11   12.11     1 91.404  2.7905 0.09825 .
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                 Sum Sq Mean Sq NumDF  DenDF F value Pr(>F)
social_nonsocial 7.6614  7.6614     1 91.142  1.8902 0.1725
Type III Analysis of Variance Table with Satterthwaite's method
                 Sum Sq Mean Sq NumDF  DenDF F value Pr(>F)
social_nonsocial 9.8804  9.8804     1 91.373  2.2542 0.1367


Linear mixed-effects models were also fitted to examine the effects of social context on emotion ratings. 

Social context had no significant on how participants rated images for happy (F(1, 91.1) = 1.30, p = 0.25), sad (F(1, 91.2 ) = 3.18, p =.08.), fear (F(1, 91.4 ) = 2.79, p = .09), disgust (F(1, 91.1) = 1.89, p = .17) or anger (F(1, 91.4) = 2.25, p = .14) emotions. Note that for these models, emotion category was not included as a predictor as using the presented emotion to predict corresponding emotion ratings offers little explanatory value (i.e., images from the “happy” category are expected to elicit higher happy ratings by design). Instead, these analyses were interested solely in whether social context modulated participants’ subjective emotional responses.

```{r plot emotion ratings x social/nonsocial}
# happy_emm <- emmeans(subjratings_x_social_subjemotion$Happy, ~ social_nonsocial)
# happy_df   <- as.data.frame(happy_emm)   %>% mutate(model = "Happy")
# 
# sad_emm <- emmeans(subjratings_x_social_subjemotion$Sad, ~ social_nonsocial) 
# sad_df   <- as.data.frame(sad_emm)   %>% mutate(model = "Sad")
# 
# anger_emm<- emmeans(subjratings_x_social_subjemotion$Anger, ~ social_nonsocial) 
# anger_df   <- as.data.frame(anger_emm)   %>% mutate(model = "Angry")
# 
# disgust_emm<- emmeans(subjratings_x_social_subjemotion$Disgust, ~ social_nonsocial) 
# disgust_df   <- as.data.frame(disgust_emm)   %>% mutate(model = "Disgust")
# 
# fear_emm<- emmeans(subjratings_x_social_subjemotion$Fear, ~ social_nonsocial) 
# fear_df   <- as.data.frame(fear_emm)   %>% mutate(model = "Fear")


happy_agg_means <- subjective_data %>%
  group_by(participant, social_nonsocial) %>%   
  summarise(
    mean = mean(happy_slide_response),
    .groups = "drop"
  )

#summary stats 
happy_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(happy_slide_response, na.rm = TRUE),
    sd   = sd(happy_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

sad_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(sad_slide_response, , na.rm = TRUE), .groups = "drop")

sad_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(sad_slide_response, na.rm = TRUE),
    sd   = sd(sad_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

anger_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(anger_slide_response, , na.rm = TRUE), .groups = "drop")

anger_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(anger_slide_response, na.rm = TRUE),
    sd   = sd(anger_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

disgust_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(disgust_slide_response, , na.rm = TRUE), .groups = "drop")

disgust_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(disgust_slide_response, na.rm = TRUE),
    sd   = sd(disgust_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

fear_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(fear_slide_response, , na.rm = TRUE), .groups = "drop")

fear_summary <- subjective_data %>%  
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(fear_slide_response, na.rm = TRUE),
    sd   = sd(fear_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

#plot separately
plot_happy <- ggplot(happy_agg_means %>% mutate(emotion = "Happy"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 0.8, alpha = 0.15) +
  # condition means
  geom_point(data = happy_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial),
             size = 1.5, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = happy_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (Mean)") +
  theme_classic(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.background = element_rect(fill = "white", colour = "black")
  )

plot_happy


plot_sad <- ggplot(sad_agg_means %>% mutate(emotion = "Sad"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 0.8, alpha = 0.15) +
  # condition means
  geom_point(data = sad_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial),
             size = 1.5, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = sad_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (emm)") +
  theme_classic(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.background = element_rect(fill = "white", colour = "black")
  )

plot_sad

plot_angry <- ggplot(anger_agg_means %>% mutate(emotion = "Angry"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 0.8, alpha = 0.15) +
  # condition means
  geom_point(data = anger_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial),
             size = 1.5, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = anger_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (Mean)") +
  theme_classic(base_size = 14) +
  theme(
    axis.title.y = element_text(face = "bold", size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.background = element_rect(fill = "white", colour = "black")
  )

plot_angry

plot_disgust <- ggplot(disgust_agg_means %>% mutate(emotion = "Disgust"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 0.8, alpha = 0.15) +
  # condition means
  geom_point(data = disgust_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial),
             size = 1.5, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = disgust_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (emm)") +
  theme_classic(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.background = element_rect(fill = "white", colour = "black")
  )

plot_disgust

plot_fear <- ggplot(fear_agg_means %>% mutate(emotion = "Fear"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 0.8, alpha = 0.15) +
  # condition means
  geom_point(data = fear_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial),
             size = 1.5, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = fear_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (Mean)") +
  theme_classic(base_size = 14) +
  theme(
    axis.title.x = element_text(face = "bold", size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.background = element_rect(fill = "white", colour = "black")
  )

plot_fear

library(patchwork)

plot_angry <- plot_angry + labs(x = "")
plot_disgust <- plot_disgust + labs(x = "", y= "")
plot_fear <- plot_fear + labs(x = "Condition", y= "") # Keep label in middle
plot_happy <- plot_happy + labs(x = "", y= "")
plot_sad <- plot_sad + labs(x = "", y= "")


# The combined emotion plot gets one tag
plot_angry+geom_boxplot(alpha = .01, colour = "black", notch = TRUE) 

emotion_x_social <- (plot_angry + plot_disgust + plot_fear + 
                     plot_happy + plot_sad +
                     plot_layout(nrow = 1, guides = "collect"))



#ggsave(filename = "social_x_emotions.tiff",
    #plot = emotion_x_social, width = 15, height = 4,dpi = 300, compression = "lzw", bg = "white")

emotion_x_social
```

```{r plot all subj ratings}

subj_ratings_plot <- (social_x_valence | social_x_intensity) / emotion_x_social+
  plot_layout(heights = c(1.5, 0.5))
subj_ratings_plot
ggsave(filename = "subjective_ratings.tiff",
    plot = subj_ratings_plot, width = 17, height = 15,dpi = 300, compression = "lzw", bg = "white")
```

```{r pool emotion ratings}
# Overall effect of social manip on pooled emotion ratings 
# Pooling + Z-test (Equations 1–2)
pool_effect <- function(betas, ses) {
  beta_pool <- sqrt(sum(betas^2))
  se_pool   <- sqrt(sum(ses^2))
  Z_stat    <- beta_pool / se_pool
  p_value   <- 2 * pnorm(-abs(Z_stat))
  c(beta = beta_pool, se = se_pool, Z = Z_stat, p = p_value)
}

subjratings_x_social_subjemotion_df <- map_dfr(subjratings_x_social_subjemotion, tidy, effects = "fixed", conf.int = TRUE, .id = "model")

# Pool social manipulation effect
social_pool_subjratings <- subjratings_x_social_subjemotion_df %>%
  filter(term == "social_nonsocial1") %>%
  # keep only rows where model is not valence or intensity
  filter(!model %in% c("Valence", "Intensity")) %>%
  # turn into data frame for plotting
  summarise(pooled = list(pool_effect(estimate, std.error))) %>%  
  unnest_wider(pooled) %>%  
  mutate(effect = "Social vs Non-Social")
require(cowplot)

social_pool_subjratings<-
  ggplot(social_pool_subjratings, aes(x = beta, y = effect)) +
  geom_point(size = 4) +
  geom_errorbarh(aes(xmin = beta - se, xmax = beta + se), height = 0.2) +
  geom_text(aes(label = ifelse(p < 0.001, "p < .001",
                             paste0("p = ", signif(p, 2)))),
          position = position_dodge(width = 0.7),
          hjust = -0.2, vjust = -0.5, size = 3.5)+
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(x = "Pooled Beta (±SE)", y = "",) +
  theme_minimal(base_size = 14)+
  ggtitle("Fixed effect of Social Manipulation on Emotion Ratings (pooled)") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme_cowplot()

social_pool_subjratings
#ggsave('pooled_subjratings_x_social.tiff',dpi = 300,plot = social_pool_subjratings, bg="white")

```  

Estimates from each of the emotion slider models were also pooled to account for that fact that some emotions have opposite scoring directions (e.g., higher happy ratings indicate positive affect, whereas higher sad ratings indicate negative affect). Pooling across emotions therefore removes the influence of valence direction and allows for Pooling across emotions removes the influence of valence direction and allows for a general assessment of the effect of social manipulation on subjective emotional responses. Pooled ratings confirmed no effect of social manipulation on emotion ratings (beta = 0.42, p = .12)

```{r plot main effects, message = FALSE}

# # Filter
# social_effects2 <- subjratings_x_social_subjemotion_df %>%
#   filter(term == "social_nonsocial1" | term == "social_nonsocial") %>%
#   mutate(term = "Social vs Non-Social")  # optional cleaner label
# 
# plot3<-
#   ggplot(social_effects2, aes(x = estimate, y = model)) +
#   geom_point(size = 3) +
#   geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
#   geom_vline(xintercept = 0, linetype = "dashed") +  
#   labs(x = "Estimate (95% CI)", y = "Model", 
#        title = "Fixed effects of Social Manipulation on Subjective Ratings")+
#       theme_minimal(base_size = 14)
# #ggsave('subjratings_x_social_subjemo.tiff', plot = plot3, bg="white")
# plot3
# 
# 
# emotion_effectstest <- subjratings_x_social_subjemotion_df %>%
#   filter(term %in% c("subj_emo_lab_no_amb1",
#                      "subj_emo_lab_no_amb2",
#                      "subj_emo_lab_no_amb3",
#                      "subj_emo_lab_no_amb4",
#                      "subj_emo_lab_no_amb5")) %>%
# 
#   # Clean up term names for plotting
#   mutate(term = gsub("subj_emo_lab_no_amb", "", term))
# 
# # we want all 6 emotion category predictors in our plot, so we need to extra them using emmeans
# valence_emm2<- emmeans(subjratings_x_social_subjemotion$Valence, ~ subj_emo_lab_no_amb, infer = c(TRUE, TRUE))
# intensity_emm2<- emmeans(subjratings_x_social_subjemotion$Intensity, ~ subj_emo_lab_no_amb, infer = c(TRUE, TRUE))
# 
# emmeans_df2 <- bind_rows(
#   as.data.frame(valence_emm2) %>% mutate(model = "Valence"),
#   as.data.frame(intensity_emm2) %>% mutate(model = "Intensity")
# )
# 
# 
# # extract grand mean for plotting
# grand_means <- emmeans_df2 %>%
#   group_by(model) %>%
#   summarise(grand_mean = mean(emmean, na.rm = TRUE)) %>%
#   mutate(ymin = as.numeric(factor(model)) - 0.5,  # vertical start of segment
#          ymax = as.numeric(factor(model)) + 0.5)
# 
# plot4 <- ggplot(emmeans_df2, aes(x = emmean, y = model, color = subj_emo_lab_no_amb)) +
#   geom_point(position = position_dodge(width = 0.7), size = 3) +
#   geom_errorbarh(aes(xmin = asymp.LCL, xmax = asymp.UCL),
#                  position = position_dodge(width = 0.7), height = 0.2) +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   xlim(0, 8)+
#   geom_segment(data = grand_means, 
#                aes(x = grand_mean, xend = grand_mean, y = ymin, yend = ymax),
#                color = "black", linetype = "dotted", size = 0.8) +
#   # Add horizontal separator line
#   geom_hline(yintercept = 1.5, linetype = "solid", color = "black", linewidth = 0.5) +
#   labs(x = "Estimated Marginal Mean (95% CI)", y = "Model",
#        title = "Estimated Marginal Means of Subjective Ratings by Emotion",
#        color = "Emotion") +
#   scale_colour_manual(values=cbbPalette)+
#   theme_minimal(base_size = 14)+
#   theme(plot.title = element_text(hjust = 0.5))
# 
# #ggsave('subjratings_x_subjemotion.tiff', plot = plot4, bg = "white")
# plot4

```

```{r create physio signal subsets}
#Ruth's exclusions:
# b) Create columns flagging whether trials fall outside the thresholds
# dta_original_trial_exclusions <- dta_original_trial_exclusions%>%
#   group_by(participant)%>%
#   mutate(face_exclusion = if_else(success >= "0.8" & confidence >= "0.8", "TRUE", "FALSE"),
#          gaze_exclusion = if_else(gaze_valid_prop >= "0.8", "TRUE", "FALSE"),
#          hr_range_exclusion = if_else(hr_mean_bpm>=30 & hr_mean_bpm<201, "TRUE", "FALSE"),
#          z_hr_mean = scale(hr_mean_bpm)[, 1],
#          hr_z_exclusion = abs(z_hr_mean) <= 3,
#          z_log_cda_scr = scale(log_cda_scr)[, 1],
#          scr_z_exclusion = abs(z_log_cda_scr) <= 3
#   )%>%
#   select(-c(z_hr_mean, z_log_cda_scr))%>%
#   ungroup()%>%
#   relocate(128:132, .after = 2)

full_dta %>% count(face_exclusion)# TRUE = 5488, FALSE = 32
full_dta %>% count(gaze_exclusion)# TRUE = 5233, FALSE = 252, NA = 35
full_dta %>% count(hr_range_exclusion)# TRUE = 5507, NA = 13
full_dta %>% count(hr_z_exclusion)# TRUE = 5474, FALSE = 33, NA = 13
full_dta %>% count(scr_z_exclusion)# TRUE = 5454, FALSE = 66


# see where the overlaps are
chk_exclusions <- full_dta%>%
  count(face_exclusion, gaze_exclusion, hr_range_exclusion, hr_z_exclusion, scr_z_exclusion) # 5108 all TRUE

# create subsets for each signal
signals <- list(
  hr   = list(signal_col = "hr_mean_diff", excl_col = "hr_range_exclusion"),
  ibi   = list(signal_col = "ibi_mean_diff", excl_col = "hr_range_exclusion"),
  scr  = list(signal_col = "log_cda_phasic_max", excl_col = "scr_z_exclusion"),
  fix = list(signal_col = "mean_fix_dur_stim_aoi", excl_col = "gaze_exclusion"),
  saccade = list(signal_col = "mean_sac_amp_stim_aoi", excl_col = "gaze_exclusion"),
  entropy = list(signal_col ="mean_stat_entropy_maxnorm", excl_col = "gaze_exclusion"),
  inner_brow_raise = list(signal_col ="au01_inner_brow_raise", excl_col = "face_exclusion"),
  outer_brow_raise = list(signal_col ="au02_outer_brow_raise", excl_col = "face_exclusion"),
  brow_lower = list(signal_col ="au_04_brow_lower", excl_col = "face_exclusion"),
  lid_raise = list(signal_col ="au05_eye_lid_raise", excl_col = "face_exclusion"),                                     
  cheek_raise = list(signal_col ="au06_cheek_raise", excl_col = "face_exclusion"),
  lid_tighten = list(signal_col ="au07_eye_lid_tighten", excl_col = "face_exclusion"),
  nose_wrinkle = list(signal_col ="au09_nose_wrinkle", excl_col = "face_exclusion"),
  upper_lip_raise = list(signal_col ="au10_upper_lip_raise", excl_col = "face_exclusion"),
  lip_pull = list(signal_col ="au12_lip_corner_pull", excl_col = "face_exclusion"),
  dimpler = list(signal_col ="au14_dimpler", excl_col = "face_exclusion"),
  lip_corner_depress = list(signal_col ="au15_lip_corner_depress", excl_col = "face_exclusion"),
  chin_raise = list(signal_col ="au17_chin_raise", excl_col = "face_exclusion"),
  lip_stretch = list(signal_col ="au20_lip_stretch", excl_col = "face_exclusion"),
  lip_tighten = list(signal_col ="au23_lip_tighten", excl_col = "face_exclusion"),
  lips_apart = list(signal_col ="au25_lips_apart", excl_col = "face_exclusion"),
  jaw_drop = list(signal_col ="au26_jaw_drop", excl_col = "face_exclusion"),
  eye_blink = list(signal_col ="au45_eye_blink", excl_col = "face_exclusion"))


# Define which columns to keep for each signal or group
# Corrected column indices for each signal
signal_keep_cols <- list(
  hr = c(1,2,8:19,42:65,133:135),       
  ibi = c(1,2,8:19,42:65,133:135),  
  scr = c(1,2,8:19,42, 45,55,121:135),
  fix = c(1,2,8:19,42,45,55,66:99,133:135),
  saccade = c(1,2,8:19,42,45,55, 66:99,133:135),
  entropy = c(1,2,8:19,42,45,55, 66:99,133:135),
  inner_brow_raise = c(1,2,8:42, 45,55,100:120,133:135),
  outer_brow_raise = c(1,2,8:42, 45,55,100:120,133:135),
  brow_lower =  c(1,2,8:42, 45,55,100:120,133:135),
  lid_raise =  c(1,2,8:2, 45,55,100:120,133:135),
  cheek_raise =  c(1,2,8:2, 45,55,100:120,133:135),
  lid_tighten =  c(1,2,8:42, 45,55,100:120,133:135),
  nose_wrinkle =  c(1,2,8:42, 45,55,100:120,133:135),
  upper_lip_raise =  c(1,2,8:42, 45,55,100:120,133:135),
  lip_pull =  c(1,2,8:42, 45,55,100:120,133:135),
  dimpler =  c(1,2,8:42, 45,55,100:120,133:135),
  lip_corner_depress = c(1,2,8:12, 45,55,100:120,133:135),
  chin_raise =  c(1,2,8:42, 45,55,100:120,133:135),
  lip_stretch =  c(1,2,8:42, 45,55,100:120,133:135),
  lip_tighten =  c(1,2,8:42, 45,55,100:120,133:135),
  lips_apart =  c(1,2,8:42, 45,55,100:120,133:135),
  jaw_drop =  c(1,2,8:42,42, 45,55,100:120,133:135),
  eye_blink =  c(1,2,8:42, 45,55,100:120,133:135)
)

# Create subsets for each signal
signal_subsets <- lapply(names(signals), function(sig) {
  
  signal_col <- signals[[sig]]$signal_col
  excl_col   <- signals[[sig]]$excl_col
  
  # Get column names to keep for this signal
  cols_to_keep <- names(full_dta)[signal_keep_cols[[sig]]]
  
  full_dta %>%
    # Filter rows where exclusion column is TRUE
    filter(!!sym(excl_col) == TRUE) %>%
    # Select the signal column + chosen columns
    dplyr::select(all_of(cols_to_keep), !!sym(signal_col))
})

# Name the list elements
names(signal_subsets) <- names(signals)

heart_data <- signal_subsets$hr
skin_data <- signal_subsets$scr
eye_data <- signal_subsets$saccade
face_data <- signal_subsets$inner_brow_raise
```

```{r aggregate some means for later plotting}
library(dplyr)

hr_agg_means <- heart_data %>%
  group_by(participant, social_nonsocial, subj_emo_lab_no_amb) %>%
  summarise(mean = mean(hr_mean_diff, na.rm = TRUE),.groups = "drop")

ibi_agg_means <- heart_data %>%
  group_by(participant,social_nonsocial,subj_emo_lab_no_amb) %>%
  summarise(mean = mean(ibi_mean_diff, na.rm = TRUE),.groups = "drop")

scr_agg_means <- skin_data %>%
  group_by(participant, social_nonsocial,subj_emo_lab_no_amb) %>%
  summarise( mean = mean(log_cda_phasic_max, na.rm = TRUE),.groups = "drop")
```

```{r autonomic models}
# # set neutral as the reference level again 
# options(contrasts = c("contr.treatment", "contr.poly"))
# heart_data$emotioncategory <- factor(heart_data$emotioncategory, 
#                                   levels = c("neutral", "anger", "disgust", "fear", "happy", "sad"))

options(contrasts =c("contr.sum", "contr.sum"))

autonomic_results<- list()
autonomic_results$Heart_Rate<-lmer(hr_mean_diff ~ 1+ social_nonsocial* subj_emo_lab_no_amb +#* int_slider_response +
                                                (1|participant) + 
                                                (1|stim_iaps), 
                                              REML = FALSE,
                                              data = heart_data)

# ibi 
autonomic_results$Interbeat_Interval<-lmer(ibi_mean_diff ~ 1+ social_nonsocial * subj_emo_lab_no_amb +#* #int_slider_response+
                                                (1|participant) + 
                                                (1|stim_iaps), 
                                              REML = FALSE,
                                              data = heart_data)

# options(contrasts = c("contr.treatment", "contr.poly"))
# skin_data$emotioncategory <- factor(skin_data$emotioncategory, 
#                                   levels = c("neutral", "anger", "disgust", "fear", "happy", "sad"))
# skin conductance 
skin_data$
autonomic_results$skin_conductance<-lmer(log_cda_phasic_max ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                (1|participant) + 
                                                (1|stim_iaps), 
                                              REML = FALSE,
                                              data = skin_data)
anova(autonomic_results$skin_conductance)
# thuis is the sxr metric
autonomic_results$skin_conductance_iscr<-lmer(log_cda_scr ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                (1|participant) + 
                                                (1|stim_iaps), 
                                              REML = FALSE,
                                              data = skin_data)

anova(autonomic_results$skin_conductance_iscr)
message("ANOVA: Heart rate")
anova(autonomic_results$Heart_Rate, type = 3)
message("ANOVA: Interbeat Interval")
anova(autonomic_results$Interbeat_Interval, type = 3)
message("ANOVA: Skin conductance")
anova(autonomic_results$skin_conductance, type = 3)
```

```{r posthocs, message = FALSE, warning = FALSE}
heartrate_emm1 <- emmeans(autonomic_results$Heart_Rate, ~ social_nonsocial)
heartrate_emm1
pairs(heartrate_emm1)   # gives nonsocial vs social difference

heartrate_emm2 <- emmeans(autonomic_results$Heart_Rate, ~ subj_emo_lab_no_amb)
heartrate_emm2
pairs(heartrate_emm2, adjust = "tukey")   # gives nonsocial vs social difference

ibi_emm1 <-emmeans(autonomic_results$Interbeat_Interval, ~ social_nonsocial)
ibi_emm1
pairs(ibi_emm1)

ibi_emm2 <-emmeans(autonomic_results$Interbeat_Interval, ~ subj_emo_lab_no_amb)
ibi_emm2
pairs(ibi_emm2, adjust = "tukey")
```

```{r plot social effects on autonomic signals, message = FALSE}
autonomic_results_df <- map_dfr(autonomic_results, tidy, effects = "fixed", conf.int = TRUE, .id = "model")

# # Filter
social_effects3 <- autonomic_results_df %>%
   filter(term == "social_nonsocial1" | term == "social_nonsocial") %>%
   mutate(term = "Social vs Non-Social")  # optional cleaner label

# this is plotting the results directly from the mixed models
plot5<-
  ggplot(social_effects3, aes(x = estimate, y = model)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed") +  
  labs(x = "Estimate (95% CI)", y = "Model", 
       title = "Fixed Effects of Social Manipulation on Autonomic Responses")+
      theme_minimal(base_size = 14)+
      theme(plot.title = element_text(size = 14))

#ggsave('autonomic_x_social.tiff', plot = plot5, bg="white")
plot5

#plot social effects - these ones are slightly more in depth and show the effect of social and non social 
hr_social_emm <- emmeans(autonomic_results$Heart_Rate, ~ social_nonsocial + subj_emo_lab_no_amb)
ibi_social_emm<- emmeans(autonomic_results$Interbeat_Interval, ~ social_nonsocial + subj_emo_lab_no_amb)
scr_social_emm<- emmeans(autonomic_results$skin_conductance, ~ social_nonsocial + subj_emo_lab_no_amb)
emmeans(autonomic_results$skin_conductance, pairwise~ social_nonsocial | subj_emo_lab_no_amb)
hr_social_emmean <- as.data.frame(hr_social_emm) %>% mutate(model = "Heart_Rate")
ibi_social_emmean <- as.data.frame(ibi_social_emm) %>% mutate(model = "Interbeat_Interval")
scr_social_emmean <- as.data.frame(scr_social_emm) %>% mutate(model = "Skin Conductance")

# extract grand mean for plotting
hr_social_grand_mean <- mean(hr_social_emmean$emmean)
ibi_social_grand_mean <- mean(ibi_social_emmean$emmean)
scr_social_grand_mean <- mean(scr_social_emmean$emmean)

```

```{r combined plots}

hr_summary <- heart_data %>%
  group_by(subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise(
    mean = mean(hr_mean_diff, na.rm = TRUE),
    sd   = sd(hr_mean_diff, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

social_x_hr <- ggplot(
  hr_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  ## raw participant means (background)
  geom_jitter(
    data = hr_agg_means,
    aes(x = social_nonsocial, y = mean, colour = social_nonsocial), width = 0.15, size = 0.8, alpha = 0.15) +
  ## model estimated means
  geom_point(size = 1.5, position = position_dodge(width = 0.4)) +
  ## model CI
  geom_errorbar(
    aes(ymin = ci_lower, ymax = ci_upper),
    width = 0.15, size = 1, position = position_dodge(width = 0.4)) +
  facet_grid(~ subj_emo_lab_no_amb) +
  labs(x = "Condition", y = expression(bold("Heart Rate Mean "*Delta*"")), colour = "") +
  coord_cartesian(ylim = c(-10, 10))+
  scale_colour_brewer(palette = "Dark2") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.text.y = element_text(size = 14),
    axis.title.y = element_text(size = 14, face = "bold"),
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )

ggsave(filename = "heart_rate.tiff", plot = social_x_hr, width =7, height = 7, dpi = 300, compression = "lzw", bg = "white")


ibi_summary <- heart_data %>%
  group_by(subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise(
    mean = mean(ibi_mean_diff, na.rm = TRUE),
    sd   = sd(ibi_mean_diff, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

social_x_ibi <- ggplot(
  ibi_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial)) +
  ## raw participant means (background)
  geom_jitter(
    data = ibi_agg_means, 
    aes(x = social_nonsocial, y = mean, colour = social_nonsocial),width = 0.15, size = 0.8, alpha = 0.15) +
 ## model estimated means
  geom_point(size = 1.5, position = position_dodge(width = 0.4)) +
  ## model CI
  geom_errorbar(
    aes(ymin = ci_lower, ymax = ci_upper), width = 0.15, size = 1, position = position_dodge(width = 0.4)) +
  facet_grid(~ subj_emo_lab_no_amb) +
  labs(x = "Condition", y = expression(bold("Interbeat Interval Mean "*Delta* "")), colour = "") +
  scale_colour_brewer(palette = "Dark2") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.text.y = element_text(size = 14),
    axis.title.y = element_text(size = 14, face = "bold"),
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )

ggsave(filename = "ibi_model.tiff", plot = social_x_ibi, width =7, height = 7, dpi = 300, compression = "lzw", bg = "white")


scr_summary <- skin_data %>%
  group_by(subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise(
    mean = mean(log_cda_phasic_max, na.rm = TRUE),
    sd   = sd(log_cda_phasic_max, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

social_x_scr 

ggplot(scr_summary, aes( x = social_nonsocial,y = mean, colour = social_nonsocial)) +
  ## raw participant means (background)
  geom_jitter(data = scr_agg_means, 
              aes(x = social_nonsocial, y = mean, colour = social_nonsocial),width = 0.15, size = 0.8, alpha = 0.15) +
  ## model estimated means
  # geom_point(size = 1.5, position = position_dodge(width = 0.4)) +
  ## model CI
  geom_errorbar(aes( ymin = ci_lower, ymax = ci_upper), width = 0.15, size = 1, position = position_dodge(width = 0.4))+
  facet_grid(~ subj_emo_lab_no_amb) +
  labs(x = "Condition", y = expression(bold("Skin Conductance")), colour = "") +
  scale_colour_brewer(palette = "Dark2") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 14),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.text.y = element_text(size = 14),
    axis.title.y = element_text(size = 14, face = "bold"),
    strip.text = element_text(face = "bold"),
    legend.position = "top")

#ggsave(filename = "scr_model.tiff", plot = social_x_scr, width =7, height = 7, dpi = 300, compression = "lzw",bg = "white")

social_x_hr
social_x_ibi
social_x_scr

autonomic_plots <- social_x_hr + social_x_scr
ggsave(filename = "autonomic_plots.tiff", plot = autonomic_plots, width =12, height = 6, dpi = 300, compression = "lzw",bg = "white")

```


Heart Rate. A linear mixed model revealed a significant main effect of social context on heart rate, F(1, 96.8) = 8.49, p = .004, such that heart rate was lower in the social (M = -2.05, SE = .28) compared to the nonsocial condition (M = -.97, SE= .26). There was also a significant main effect of emotion rating (F(5, 714.0) = 2.28, p = .045). Although post-hoc comparisons of estimated marginal means (with Tukey correction) did not reveal significant pairwise differences between emotions, the 95% CI bars around the estimated marginal means suggest that heart rate responses varied across emotions relative to the grand mean, with some emotions eliciting slightly stronger (e.g. happy or netural) or weaker heart rate response (e.g., anger fear; Figure X). In line with this, the interaction between social context and emotion category was not significant (F(5, 5424.9) = 0.78, p = .56).

The model results for Interbeat Interval (IBI) complement these heart rate findings: IBI was significantly longer in the social condition (M = .02, SE = .003) compared to the non-social condition (M = .01, SE = .003;F(1, 96.5) = 4.44, p = .038). As with heart rate, although there was a significant main effect of emotion (F(5, 706.7) = 2.26, p = .047), post-hoc comparisons of estimated marginal means (with TUkey correction) did not highlight any significant pairwise comparisons. There was no significant interaction between social context and emotion (F(5, 5422.7) = 1.19, p = .31).

Skin Conductance. No significant effects were observed for social context, F(1, 92.3) = 2.27, p = .14, emotion category, F(5, 1258.9) = 0.23, p = .95, or their interaction, F(5, 5322.1) = 1.72, p = .13.

```{r eye movement models}
options(contrasts =c("contr.sum", "contr.sum"))
eye_results<- list()

eye_results$Fixation_duration<-lmer(mean_fix_dur_stim_aoi ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                 (1|participant) + 
                                                 (1|stim_iaps), 
                                               REML = FALSE,
                                               data = eye_data)

eye_results$Saccade_amplitude<-lmer(mean_sac_amp_stim_aoi ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                (1|participant) + 
                                                (1|stim_iaps), 
                                              REML = FALSE,
                                              data = eye_data)

eye_results$Entropy<-lmer(mean_stat_entropy_maxnorm ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                (1|participant) + 
                                                (1|stim_iaps), 
                                              REML = FALSE,
                                              data = eye_data)
message("ANOVA: Fixation duration")
anova(eye_results$Fixation_duration, type = 3)
message("ANOVA: Saccade amplitude")
anova(eye_results$Saccade_amplitude, type = 3)
message("ANOVA: Entropy")
anova(eye_results$Entropy, type = 3)
```

Neither social context or emotion had any impact upon fixation duration, saccade amplitude or entropy, where neither of these main effects reached significance (p >.05).

## FAU mixed models - excluding time
```{r z score face signals}
# z score each facial action unit 
face_z_scored <- face_data %>%
  mutate(across(starts_with("au"), scale))
face_z_scored
```

```{r run models on z scores}
face_results<- list()
face_results$Inner_brow<-lmer(au01_inner_brow_raise~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                          (1|participant) + 
                                                          (1|stim_iaps), 
                                                        REML = FALSE,
                                                        data = face_z_scored)

face_results$Outer_brow<-lmer(au02_outer_brow_raise~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)


face_results$Brow_lower<-lmer(au_04_brow_lower~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)


face_results$eyelid_raise<-lmer(au05_eye_lid_raise~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)


face_results$cheek_raise<-lmer(au06_cheek_raise~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)


face_results$eyelid_tighten<-lmer(au07_eye_lid_tighten~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)


face_results$nose_wrinkle<-lmer(au09_nose_wrinkle~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)


face_results$upper_lip_raise<-lmer(au10_upper_lip_raise~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)


face_results$lip_corner_pull<-lmer(au12_lip_corner_pull~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)

face_results$dimpler<-lmer(au14_dimpler~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                  (1|participant) + 
                                                  (1|stim_iaps), 
                                                REML = FALSE,
                                                data = face_z_scored)

face_results$lip_corner_depress<-lmer(au15_lip_corner_depress~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                  (1|participant) + 
                                                  (1|stim_iaps), 
                                                REML = FALSE,
                                                data = face_z_scored)

face_results$chin_raise<-lmer(au17_chin_raise~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                           (1|participant) + 
                                                           (1|stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_z_scored)

face_results$lip_stretch<-lmer(au20_lip_stretch~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                           (1|participant) + 
                                                           (1|stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_z_scored)

face_results$lip_tighten<-lmer(au23_lip_tighten~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                           (1|participant) + 
                                                           (1|stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_z_scored)

face_results$lips_apart<-lmer(au25_lips_apart~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                           (1|participant) + 
                                                           (1|stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_z_scored)

face_results$jaw_drop<-lmer(au26_jaw_drop~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                   (1|participant) + 
                                                   (1|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_z_scored)

face_results$eye_blink<-lmer(au45_eye_blink~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                                                 (1|participant) + 
                                                 (1|stim_iaps), 
                                               REML = FALSE,
                                               data = face_z_scored)

#face_results <- map_dfr(face_results, tidy, effects = "fixed", conf.int = TRUE, .id="model")
```

```{r print face signal results}
anova(face_results$Inner_brow, type = 3)
anova(face_results$Outer_brow, type = 3)
anova(face_results$Brow_lower, type = 3)
anova(face_results$eyelid_raise, type = 3)
anova(face_results$cheek_raise, type = 3)
anova(face_results$eyelid_tighten, type = 3)
anova(face_results$nose_wrinkle, type = 3)
anova(face_results$upper_lip_raise, type = 3)
anova(face_results$lip_corner_pull, type = 3)
anova(face_results$dimpler, type = 3)
anova(face_results$lip_corner_depress, type = 3)
anova(face_results$chin_raise, type = 3)
anova(face_results$lip_stretch, type = 3)
anova(face_results$lip_tighten, type = 3)
anova(face_results$lips_apart, type = 3)
anova(face_results$jaw_drop, type = 3)
anova(face_results$eye_blink, type = 3)

test <-emmeans(face_results$Inner_brow, ~ subj_emo_lab_no_amb)
test
pairs(test)
```
emotion category was significant for multiple AUs, including Inner brow, brow lower, eye lid raise, cheek raise, eye lid tighten, nose wrinkle, upper lip raise,  lip corner depress, and lips apart, indicating that facial responses differed reliably across emotions (all p < .05). For example, Lip Corner Pull showed increased activity for happy expressions relative to other emotions, F(5, 5402.0) = 4.89, p < .001.

A significant main effect of social context was observed for eyelid tighten, F(1, 92.2) = 4.53, p = .036, with greater activity in the nonsocial condition (M = 0.19, SE = 0.13) than the social condition (M = -0.20, SE = 0.13).”No other AUs were significantly influenced by social context, suggesting that social conditions had minimal impact on facial expressions overall.

The interaction between social context and emotion category was generally non-significant, indicating that emotion-driven facial responses were largely consistent across social and nonsocial settings. A notable exception was Eye Blink, where the interaction was significant, F(5, 5362.2) = 4.89, p < .001, suggesting that blinking varied across emotions depending on the social context. However, pairwise comparisons did not reveal any differences between emotions across social contexts, 
Overall, facial expressions were primarily driven by emotion category, with limited modulation by social context and only isolated evidence for social × emotion interactions.

```{r plot model results face signals }

face_emmeans <- map_dfr(face_results, ~ {
  as.data.frame(emmeans(.x, ~ subj_emo_lab_no_amb, infer = c(TRUE, TRUE)))
}, .id = "model")  # .id adds model name (e.g., AU01, AU02)
face_emmeans$model <- dplyr::recode(face_emmeans$model,
  "Inner_brow"= "Inner brow",
  "Outer_brow" = "Outer brow",
  "Brow_lower"="Brow lower",
  "eyelid_raise" = "Eyelid raise",
  "cheek_raise" = "Cheek raise",
  "eyelid_tighten" = "Eyelid tighten",
  "nose_wrinkle" = "Nose wrinkle",
  "upper_lip_raise" = "Upper lip raise",
  "lip_corner_pull" = "Lip corner pull" ,
  "dimpler" ="Dimpler",
  "lip_corner_depress" = "Lip corner depress",
  "chin_raise" = "Chin raise" ,
  "lip_stretch" = "Lip stretch",
 "lip_tighten" =  "Lip tighten" ,
  "lips_apart" = "Lips apart",
  "jaw_drop" = "Jaw drop",
  "eye_blink" = "Eye blink"
)
au_order <- c(
  "Inner brow", "Outer brow", "Brow lower", "Eyelid raise", "Cheek raise",
  "Eyelid tighten", "Nose wrinkle", "Upper lip raise", "Lip corner pull",
  "Dimpler", "Lip corner depress", "Chin raise", "Lip stretch", "Lip tighten",
  "Lips apart", "Jaw drop", "Eye blink"
)

face_emmeans$model <- factor(face_emmeans$model, levels = au_order)

```

```{r pool and plot face signals}
# pool the betas for all facial units and plot pooled effects
# Pooling + Z-test (Equations 1–2)
pool_effect <- function(betas, ses) {
  beta_pool <- sqrt(sum(betas^2))
  se_pool   <- sqrt(sum(ses^2))
  Z_stat    <- beta_pool / se_pool
  p_value   <- 2 * pnorm(-abs(Z_stat))
  c(beta = beta_pool, se = se_pool, Z = Z_stat, p = p_value)
}

# Pool social manipulation effect
social_pool_faces<- face_results_df %>%
  filter(term == "social_nonsocial1") %>%
  #turn into data frame for plotitng: 
  summarise(pooled = list(pool_effect(estimate, std.error))) %>%  
  unnest_wider(pooled) %>%  
  mutate(effect = "Social vs Non-Social") 

social_pool_faces_plot<-
  ggplot(social_pool_faces, aes(x = beta, y = effect)) +
  geom_point(size = 4) +
  geom_errorbarh(aes(xmin = beta - se, xmax = beta + se), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(x = "Pooled Beta (±SE)", y = "", title = "Fixed Effect of Social Manipulation on Face Behaviour (pooled)") +
  theme_minimal(base_size = 14)

social_pool_faces_plot 
  
#ggsave('pooled_faces_x_social.tiff', plot = social_pool_faces_plot, bg="white")

# Pool emotion effects 
emotion_pool_faces <- face_emmeans %>%
  group_by(subj_emo_lab_no_amb) %>% 
  summarise(pooled = list(pool_effect(emmean, SE))) %>%
  tidyr::unnest_wider(pooled) %>%
  mutate(effect = subj_emo_lab_no_amb)

emotion_pool_faces_plot<-
  ggplot(emotion_pool_faces, aes(x = beta, y = effect, colour = subj_emo_lab_no_amb)) +
  geom_point(size = 4) +
  geom_errorbarh(aes(xmin = beta - se, xmax = beta + se), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_colour_manual(values=cbbPalette)+
  labs(x = "Pooled Beta (±SE)", y = "Emotion", title = "Fixed Effects of Emotion on Face Behaviour (pooled)") +
  theme_minimal(base_size = 14)
#ggsave('pooled_faces_x_emotion.tiff', plot = emotion_pool_faces_plot, bg="white")

emotion_pool_faces_plot + theme(legend.position = "none")
```
social manipulation increases AU activity by 0.236 units - non significant 
no significant effects of subjective rated emotion on action units when pooled 

```{r Face PCAs}
#	Run a multilevel PCA (see mixOmics r package for this kind of PCA) → extract component scores → run mixed models on these component scores. – face only 

#logic:
# We want to test the effects of social manipulation (social vs. nonsocial) and emotion category (anger, #fear, happy, etc.) on facial behavior.
# We have 17 facial AUs per trial, per participant. Thats a lot and makes interpretation tricky
# Theoretically as well, action units work together 
# Why PCA? PCA reduces these 17 AUs into a few principal components (PCs).
# Each PC is a linear combination of AUs that explains the most variance in facial behavior.
# e.g. perhaps its the case that au01, au02, au03 are grouped and = smile, for example
# extract the pcc scores for each trial and each participant
# then we can run mixed models on each PC and ask does social manip affect this 

# ## install BiocManager if not installed 
# if (!requireNamespace("BiocManager", quietly = TRUE))    
# install.packages("BiocManager")
# ## then install mixOmics
# BiocManager::install("mixOmics")
library(mixOmics)
require(Factoshiny)
require(factoextra)

pca_multil_design <- data.frame(sample = face_data$participant) # set the multilevel design

# note this is not the z scored data, mixOmics will scale when performing the PCA 
pca_multil_omix_face <- mixOmics::pca(face_data[42:58], 
                            scale = TRUE, 
                            center = TRUE, 
                            multilevel = pca_multil_design, ncomp = 3)
pca_multil_omix_face

# plot the scores. do they cluster differently depending on emotion rating? 
plotIndiv(pca_multil_omix_face , group = face_data$subj_emo_lab_no_amb,
          ind.names = face_data$participant,
          legend = TRUE)

# do scores cluster differently for nonsocial and social conditions?
plotIndiv(pca_multil_omix_face , group = face_data$social_nonsocial, 
          ind.names = face_data$participant,
          legend =TRUE)

plotVar(pca_multil_omix_face , var.names = TRUE, cutoff = 0.4, pch = 16)

# Extract all PCs 
components <- data.frame(pca_multil_omix_face$variates$X)
# attach back to main data frame
pc_data <- cbind(face_data[, c("participant", "stim_iaps","social_nonsocial", "subj_emo_lab_no_amb")],
                   components) # we want this data frame for our mixed models


# Extract loadings for AUs onto each PC so we can see what goes where
au_loadings <- as.data.frame(pca_multil_omix_face$loadings$X)
au_loadings$AU <- rownames(au_loadings)
# Reorder so AU is first column
au_loadings<- au_loadings[, c("AU", colnames(au_loadings)[1:3])]

au_loadings_ranked <- au_loadings %>%
  pivot_longer(cols = -AU, names_to = "PC", values_to = "loading") %>%
  mutate(abs_loading = abs(loading)) %>%
  group_by(PC) %>%
  arrange(desc(abs_loading), .by_group = TRUE) %>%
  ungroup()

top5_per_pc <- au_loadings_ranked %>%
  group_by(PC) %>%
  slice_head(n = 5)

top5_per_pc

```

```{r extract metrics}
# Extract proportion of variance explained per component
pca_multil_omix_face[["prop_expl_var"]]

var_explained <- unlist(pca_multil_omix_face$prop_expl_var$X)

var_explained_df <- data.frame(
  PC = paste0("PC", 1:length(var_explained)),
  Variance_Explained = var_explained,
  Cumulative_Variance = cumsum(var_explained)
)

var_explained_df

```

What is the PCA telling us? 
The AUs loaded onto PC1 could reflect a surprised/open-mouth/tense expression
The AUs loaded onto PC2 could reflect a positive facial expression/smile pattern
The AUs loaded onto PC3 could reflect surprise (e.g. eyebrow raises)

```{r run mixed models on the principle components}
# add stimulus as random effect instead of participant 
pc1 <- lmer(PC1 ~ social_nonsocial * subj_emo_lab_no_amb +(1|stim_iaps), data = pc_data)
pc2 <- lmer(PC2 ~ social_nonsocial * subj_emo_lab_no_amb + (1|stim_iaps),data = pc_data)
pc3 <- lmer(PC3 ~ social_nonsocial * subj_emo_lab_no_amb + (1|stim_iaps),data = pc_data)

# multiple comparisons are tukey-adjusted
anova(pc1, type = 3)
anova(pc2, type = 3)
anova(pc3, type = 3)
```

For all principle components, there was no significant main effect of social manipulation. 
For PC1, there was a significant main effect of emotion category (p=.008 respectively).
No main effects for PC3. 

```{r pairwise comparisons, message = FALSE}
emm_PC1 <- emmeans(pc1, ~ subj_emo_lab_no_amb, adjust = "tukey")
pairs(emm_PC1)
```

PC1 seems to distinguish disgust from other emotions. That is, images rated as disgusting predict facial movements for this PC. 
Ties in with the AUs loaded on this factor? 

PC2 has fewer significant differences overall, but happy and neutral are both higher than disgust. Ties in somewhat with the AUs for PC2 reflecting positive expression? 

Results show that findings are not down to methodological/analytical limitations 

## FAU mixed models - including time - report these ones
```{r linear mixed models on FAUs over time}
# 1. use the face data that includes time series
# can we predict effects across the 6 seconds for each action unit 
# z-score time as a predictor + covariate + random effect
#so replicate the existing models per AU, just adding time to the models 

#prepare the data 
library(arrow)
face_time_raw <- read_parquet("face_time_data.parquet", show_col_types = FALSE)

head(face_time_raw)

#filter to columns we want : raw smoothed aus e.g. au01_r_smt
face_time<- face_time_raw[,-c(5:39, 58:110)]

#filter out rest and example stimuli trials
face_time <- face_time%>%
  filter(!grepl("example|rest", source_file, ignore.case = TRUE))

#extract participant id from source_file column
library(stringr)

# Extract the participant number at the start of the source file
face_time <- face_time %>%
  mutate(participant = str_extract(source_file, "^\\d+"))
#rename ppt 103103 to 103
face_time <- face_time %>%
  mutate(participant = substr(participant, 1, 3))

# extract whether participant was in social or nonsocial 
ppt_conditions <- dta_original %>% 
  dplyr::select(participant, social_nonsocial) %>% 
  distinct()

# Join it to face_time data
face_time <- face_time %>%
  left_join(ppt_conditions, by = "participant")

# extract subj_emo_lab_no_amb
ppt_images <- full_dta %>% 
  dplyr::select(stim_iaps, subj_emo_lab_no_amb, participant)%>% 
  distinct()

# Extract the image name from filename
face_time <- face_time %>%
  mutate(source_file = str_extract(source_file, "\\d+\\.jpg"))

#rename column in ppt_images
face_time <- face_time %>%
  rename(stim_iaps = source_file)

face_time <- face_time %>%
  left_join(ppt_images, by = c("stim_iaps", "participant"))

#check how many frames were recorded for each ppt
frame_counts <- face_time %>%
  group_by(participant, filename) %>%
  summarise(frame = n())
frame_counts

frame_counts  <- frame_counts %>%
  filter (frame < 100)
frame_counts

#exclude participants where they had too few frames
#participants excluded = 103, 104, 105,106,107,108
#before exclusions we had 1190285 rows, after we have 1139465
face_time_clean <- face_time %>%
  filter(!participant %in% c(103:108, 201:205))

#also check data quality using open face confidence
# first, look at trials that have an average confidence of less than 75%
low_confidence_trials <- face_time_clean %>%
  group_by(filename)%>%
  summarise(avg_confidence = mean(confidence, na.rm =TRUE))%>%
  filter(avg_confidence < 0.75)
low_confidence_trials

#remove these trials 
face_time_clean <- face_time_clean %>%
  filter(!filename %in% low_confidence_trials$filename)

#check confidence per ppt per trial
participant_confidence <- face_time_clean %>%
  group_by(participant, filename) %>%
  summarise(avg_confidence = mean(confidence, na.rm = TRUE))%>%
  filter(avg_confidence < 0.75)

participant_confidence 
#no further trials to remove
# 1134770 trials left after exclusions 

#finally, downsample. keep every 3rd frame. gives around 76 samples per trial
face_time_downsampled <- face_time_clean %>%
  group_by(participant, filename)%>%
  slice(seq(1, n(), by = 3))%>%
  ungroup()
face_time_downsampled
```

```{r mixed models}
# z score each facial action unit 
face_time_z_scored <- face_time_downsampled %>%
  mutate(across(starts_with("au"), scale))
face_time_z_scored

#z score time
face_time_z_scored$timestamp_z<- scale(face_time_z_scored$timestamp)
face_time_z_scored
saveRDS(face_time_z_scored, file = "face_time_z_scored.rds")
```

```{r visualise some time data}
library(dplyr)
library(ggplot2)

# Get all AU column names
au_columns <- names(face_time_z_scored)[grepl("^au.*_smt$", names(face_time_z_scored))]

bin_size <- 0.01

# Create directory for plots if it doesn't exist
dir.create("au_time_plots", showWarnings = FALSE)

# Loop through each AU and save
for(au in au_columns) {
  
  summary_data <- face_time_z_scored %>%
    mutate(time_bin = floor(timestamp / bin_size) * bin_size) %>%
    group_by(subj_emo_lab_no_amb, participant, time_bin) %>%
    summarise(mean_au_participant = mean(.data[[au]], na.rm = TRUE),
              .groups = 'drop') %>%
    group_by(subj_emo_lab_no_amb, time_bin) %>%
    summarise(
      mean_au = mean(mean_au_participant, na.rm = TRUE),
      se_au = sd(mean_au_participant, na.rm = TRUE) / sqrt(n()),
      .groups = 'drop'
    )
  
  p <- ggplot(summary_data, aes(x = time_bin, y = mean_au,
                                 color = subj_emo_lab_no_amb,
                                 fill = subj_emo_lab_no_amb)) +
    geom_ribbon(aes(ymin = mean_au - se_au, 
                    ymax = mean_au + se_au), 
                alpha = 0.2, color = NA) +
    geom_line(linewidth = 1) +
    labs(
      x = "Time (seconds)",
      y = "Intensity (z-scored)",
      title = au,
      color = "Emotion",
      fill = "Emotion"
    ) +
    theme_minimal()+
    theme(
      legend.position = "bottom",
      plot.background = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "white", color = NA)
    )
  
  # Save as TIFF
  ggsave(
    filename = paste0("au_time_plots/", au, ".tiff"),
    plot = p,
    width = 8,
    height = 6,
    dpi = 300,
    compression = "lzw"  # lossless compression
  )
  
  print(paste("Saved:", au))
}

print("All plots saved to au_time_plots/ directory")

```
Facial action unit intensities were averaged within 100-ms time bins to reduce high-frequency noise while preserving meaningful temporal dynamics across the 6 second stimulus presentation.

Note: the plots were returning some NAs, which was weird. After looking at the data
 na_rows <- face_time_z_scored %>%
     filter(is.na(subj_emo_lab_no_amb))
all of the NAs are for trials that had 0 confidence from open face. all of the FAUs are also 0. so, i think these trials were excluded from full_dta, hence the join is returning NAs.

```{r run models on z scores}
#check convergence warnings - if results is lower than the tolerance stated in the warning, then the model did converge 
#relgrad <- with(face_time_results$Inner_brow@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

face_time_results<- list()

library(lmerTest)
face_time_results$Inner_brow <-lmer(au01_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z +
                                                          (1 + timestamp_z | participant)+
                                                          (1 + timestamp_z |stim_iaps), 
                                                        REML = FALSE,
                                                        data = face_time_z_scored)

face_time_results$Outer_brow<-lmer(au02_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z + 
                                                   (1 + timestamp_z|participant) + 
                                                   (1 + timestamp_z|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$Brow_lower<-lmer(au04_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                   (1 + timestamp_z|participant) + 
                                                   (1+ timestamp_z|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$eyelid_raise<-lmer(au05_r_smt~  social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                   (1 + timestamp_z|participant) + 
                                                   (1+ timestamp_z|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$cheek_raise<-lmer(au06_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                   (1 + timestamp_z|participant) + 
                                                   (1 + timestamp_z|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$eyelid_tighten<-lmer(au07_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z + 
                                                   (1 + timestamp_z|participant) + 
                                                   (1 + timestamp_z|stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$nose_wrinkle<-lmer(au09_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                   (1 + timestamp_z |participant) + 
                                                   (1 + timestamp_z |stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$upper_lip_raise<-lmer(au10_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                   (1 + timestamp_z |participant) + 
                                                   (1 + timestamp_z |stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$lip_corner_pull<-lmer(au12_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                   (1 + timestamp_z |participant) + 
                                                   (1 + timestamp_z |stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$dimpler<-lmer(au14_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                  (1 + timestamp_z |participant) + 
                                                  (1 + timestamp_z |stim_iaps), 
                                                REML = FALSE,
                                                data = face_time_z_scored)

face_time_results$lip_corner_depress<-lmer(au15_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z + 
                                                  (1 + timestamp_z |participant) + 
                                                  (1 + timestamp_z |stim_iaps), 
                                                REML = FALSE,
                                                data = face_time_z_scored)

face_time_results$chin_raise<-lmer(au17_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                           (1 + timestamp_z |participant) + 
                                                           (1 + timestamp_z |stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_time_z_scored)

face_time_results$lip_stretch<-lmer(au20_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z + 
                                                           (1 + timestamp_z |participant) + 
                                                           (1 + timestamp_z |stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_time_z_scored)

face_time_results$lip_tighten<-lmer(au23_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                           (1 + timestamp_z |participant) + 
                                                           (1 + timestamp_z |stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_time_z_scored)

face_time_results$lips_apart<-lmer(au25_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                           (1 + timestamp_z |participant) + 
                                                           (1 + timestamp_z |stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_time_z_scored)

face_time_results$jaw_drop<-lmer(au26_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z+ 
                                                   (1 + timestamp_z |participant) + 
                                                   (1 + timestamp_z |stim_iaps), 
                                                 REML = FALSE,
                                                 data = face_time_z_scored)

face_time_results$eye_blink<-lmer(au45_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z + 
                                                 (1 + timestamp_z |participant) + 
                                                 (1 + timestamp_z |stim_iaps), 
                                               REML = FALSE,
                                               data = face_time_z_scored)

```

```{r display model results}
message("ANOVA: Inner Brow")
anova(face_time_results$Inner_brow, type = 3)
message("ANOVA: Outer Brow")
anova(face_time_results$Outer_brow, type = 3)
message("ANOVA: Brow lower")
anova(face_time_results$Brow_lower, type = 3)
message("ANOVA: Eyelid raise")
anova(face_time_results$eyelid_raise, type = 3)
message("ANOVA: Cheek raise")
anova(face_time_results$cheek_raise, type = 3)
message("ANOVA: Eyelid tighten")
anova(face_time_results$eyelid_tighten, type = 3)
message("ANOVA: Nose wrinkle")
anova(face_time_results$nose_wrinkle, type = 3)
message("ANOVA: Lip raise")
anova(face_time_results$upper_lip_raise, type = 3)
message("ANOVA: Lip corner pull")
anova(face_time_results$lip_corner_pull, type = 3)
message("ANOVA: Dimpler")
anova(face_time_results$dimpler, type = 3)
message("ANOVA: Lip corner depress")
anova(face_time_results$lip_corner_depress, type = 3)
message("ANOVA: Chin raise")
anova(face_time_results$chin_raise, type = 3)
message("ANOVA: Lip stretch")
anova(face_time_results$lip_stretch, type = 3)
message("ANOVA: Lip tighten")
anova(face_time_results$lip_tighten, type = 3)
message("ANOVA: Lips apart")
anova(face_time_results$lips_apart, type = 3)
message("ANOVA: Jaw drop")
anova(face_time_results$jaw_drop, type = 3)
message("ANOVA: Eye blink")
anova(face_time_results$eye_blink, type = 3)

eyelid_emm <- emmeans(face_time_results$eyelid_tighten, ~ social_nonsocial)
eyelid_emm
eyelid_posthoc <-pairs(eyelid_emm, adjust = "tukey")
eyelid_posthoc
```

```{r model tests}
model_tests <- list()
model_tests$model1 <-lmer(au01_r_smt~ 1 +
                                                           (1 + timestamp_z | participant)+
                                                           (1 + timestamp_z |stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_time_z_scored)


model_tests$model2 <-lmer(au01_r_smt~ 1 + (1 + subj_emo_lab_no_amb* timestamp_z | participant)+                                                                       (1 + timestamp_z |stim_iaps), 
                                              REML = FALSE,
                                              data = face_time_z_scored)

model_tests$model3 <-lmer(au01_r_smt~ social_nonsocial * subj_emo_lab_no_amb * timestamp_z +
                                                           (1 + subj_emo_lab_no_amb * timestamp_z | participant)+
                                                           (1 +  social_nonsocial * timestamp_z |stim_iaps), 
                                                         REML = FALSE,
                                                         data = face_time_z_scored)

anova(model1, model2, model3)

```

```{r}
face_time_results_2 <- map_dfr(face_time_results, tidy, effects = "fixed", conf.int = TRUE, .id="model")

all_au_plots<-ggplot(
  filter(face_time_results_2, term == "social_nonsocialsocial"),
  aes(x = estimate, y = model, colour=model)
) +
  geom_point() +
  geom_errorbarh(
    aes(xmin = estimate - std.error,
        xmax = estimate + std.error),
    height = 0.2
  ) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    x = "Beta (± SE)",
    y = "Action Unit",
    title = "Effect of Social Manipulation on Facial Action Units"
  ) + 
  theme_minimal(base_size = 13)+
  theme(legend.position = "none")
all_au_plots

au_x_time <-ggplot(
  filter(face_time_results_2, term == "timestamp_z"),
  aes(x = estimate, y = model, colour = model)
) +
  geom_point() +
  geom_errorbarh(
    aes(xmin = estimate - std.error,
        xmax = estimate + std.error),
    height = 0.2
  ) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    x = "Beta (± SE)",
    y = "Action Unit",
    title = "Effect of Time on Facial Action Units"
  ) +
  theme_minimal(base_size = 13)+
  theme(legend.position = "none")
au_x_time
```

```{r pool face time models}

# pool the betas for all facial units and plot pooled effects

# Pooling + Z-test (Equations 1–2)
pool_effect <- function(betas, ses) {
  beta_pool <- sqrt(sum(betas^2))
  se_pool   <- sqrt(sum(ses^2))
  Z_stat    <- beta_pool / se_pool
  p_value   <- 2 * pnorm(-abs(Z_stat))
  c(beta = beta_pool, se = se_pool, Z = Z_stat, p = p_value)
}

# Pool social manipulation effect
social_pool_faces <- face_time_results_2 %>%
  filter(term == "social_nonsocialsocial") %>%
  summarise(pooled = list(pool_effect(estimate, std.error))) %>%
  unnest_wider(pooled) %>%
  mutate(effect = "Social vs Non-Social")

social_pool_faces_plot<-
  ggplot(social_pool_faces, aes(x = beta, y = effect)) +
  geom_point(size = 4) +
  geom_errorbarh(aes(xmin = beta - se, xmax = beta + se), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(x = "Pooled Beta (±SE)", y = "", title = "Fixed Effect of Social Manipulation on Face Behaviour (pooled)") +
  theme_minimal(base_size = 14)
social_pool_faces_plot 
  
#ggsave('pooled_faces_x_social.tiff', plot = social_pool_faces_plot, bg="white")

# Pool emotion effects 
emotion_pool_faces <- face_emmeans %>%
  group_by(subj_emo_lab_no_amb) %>% 
  summarise(pooled = list(pool_effect(emmean, SE))) %>%
  tidyr::unnest_wider(pooled) %>%
  mutate(effect = subj_emo_lab_no_amb)

emotion_pool_faces_plot<-
  ggplot(emotion_pool_faces, aes(x = beta, y = effect, colour = subj_emo_lab_no_amb)) +
  geom_point(size = 4) +
  geom_errorbarh(aes(xmin = beta - se, xmax = beta + se), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_colour_manual(values=cbbPalette)+
  labs(x = "Pooled Beta (±SE)", y = "Emotion", title = "Fixed Effects of Emotion on Face Behaviour (pooled)") +
  theme_minimal(base_size = 14)
#ggsave('pooled_faces_x_emotion.tiff', plot = emotion_pool_faces_plot, bg="white")

emotion_pool_faces_plot + theme(legend.position = "none")
```

```{r NMF stuff}
# 2. also do mixed models on features derived from the face data 
# on Helio's github, see 'expression only nmf' for feature extraction
# here we're just measuring overall change 
```

Non-negative Matrix Factorization (NMF) is used in psychology and machine vision to model facial expressions by decomposing images or data into a set of constituent, localized facial features or "parts" that are then used for recognition and analysis. This approach aligns with psychological and neurological theories of part-based object recognition in the brain. 






