---
title: "pre-process_pup"
output: html_document
date: "2025-12-17"
---

note originally we only did complete processing for gaze, not pupil

so this script will take over the initial processing of pupil from pre_process_eytr, and finalise processing for pupildata


Pupil



```{r}
load("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/dta_gaze_env.RData")
# in pre_process_eyetrk we want dta_eytr_rpx
# from here you cna do the stanard pupil processinh



```


```{r}
dta_socemophys_pup<- select(dta_eytr_rpx, 
                                      c("participant", "session_id", "event_id", "ssid", 
                                        "text","trialunq","screencontent",
                                        "screencontent_no_na","pratice_vs_trial",                           "stimnopath",
                                        "stimnopath_no_na",
                            "time", "timerezero","time_backward",
                            
                            "pupil",
                            "pupil_d", "trackloss", "gaze_loss_prop", "gaze_valid_prop"))


saveRDS(dta_socemophys_pup, "dta_socemophys_pup.rds")
```

to do


```{r}
dta_socemophys_pup <- readRDS("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/2022_2023_Analyses/Data/2025 - autism and alexithymia/dta_socemophys_pup.rds")

```

```{r}

# remotes::install_github("dmirman/gazer")
library(gazer)

colnames(dta_gaze_clean_10s_nodup)

```

```{r}

dta_pupil<- dta_gaze_clean_10s_nodup%>%
  select(screencontent, pratice_vs_trial,
 isfake_or_real,stimnopath,text,filename,bris_vs_birm,ssid_bris_birm,time,
 timerezero, time_backward,
 trial,
         trackloss,gaze_valid_prop, pupil, pupil_d)

range(dta_pupil$pupil, na.rm = TRUE)
range(dta_pupil$pupil_d, na.rm = TRUE)
max(dta_pupil$pupil, na.rm = TRUE)

```

```{r}

dta_pupil%>%
  ggplot(aes(pupil))+
  geom_histogram()


dta_pupil%>%
  ggplot(aes(pupil_d))+
  geom_histogram()


```




```{r}

dta_pupil$pupil<- if_else(dta_pupil$pupil> 7, dta_pupil$pupil, NA)

dta_pupil$pupil<- if_else(dta_pupil$pupil< 45, dta_pupil$pupil, NA)
range(dta_pupil$pupil, na.rm = T)
range(dta_pupil$pupil_d, na.rm = T)
# 1.30 27.91
# 


# note that smothing and interpolating is order dependent so order by ssid, trial and time
dta_pupil

options(digits=10)


dta_pupil<- dta_pupil %>%
    group_by(ssid_bris_birm)%>%
  arrange(ssid_bris_birm,time)

# dta_pupil<- dta_pupil%>%
#   group_by(ssid)%>%
#   mutate(duplicated_event_id = duplicated(event_id),
#          duplicated_time = duplicated(time))

# dta_pupil_nodup<-subset(dta_pupil,
#                                 duplicated_event_id == FALSE)
         
# 
# table(dta_pupil$duplicated_event_id)
# table(dta_pupil$duplicated_time)



```


```{r}

dta_pupil<- dta_pupil%>%
  group_by(ssid_bris_birm)%>%
   arrange(ssid_bris_birm,time)%>%
  group_by(ssid_bris_birm,screencontent)%>%
  mutate(trial_no = cumsum(text != lag(text, default = first(text))) + 1)

range(dta_pupil$trial_no)
# dta_pupil$trial_no<- NULL

# unique(dta_pupil$screencontent)
      
dta_pupil <- dta_pupil%>%
  group_by(ssid_bris_birm, text,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=50, fillforward=50, hz=150))%>%
  mutate(extendpupil_d=gazer::extend_blinks(pupil_d, fillback=50, fillforward=50, hz=150))

range(dta_pupil$extendpupil, na.rm = TRUE)
range(dta_pupil$extendpupil_d, na.rm = TRUE)
range(dta_pupil$pupil, na.rm = TRUE)

```

# let's check

```{r}
dta_pupil%>%
  subset(ssid_bris_birm == "bris_30" & trial_no == 15)%>%
  # ssid = 010 & s
  # subset(trialUnq == " stimuli 22_23__walking_outside_cafe_disgusted__J8JK3NBV.mp4" )%>%
ggplot(aes(x = time_backward, y= extendpupil))+
      geom_line()+
  geom_line(aes(y = pupil), colour = "red", linetype = "dashed", size = .1) 




```

```{r}
dta_pupil%>%
  subset(trial_no == 15)%>%
  # ssid = 010 & s
  # subset(trialUnq == " stimuli 22_23__walking_outside_cafe_disgusted__J8JK3NBV.mp4" )%>%
ggplot(aes(x = time_backward, y= extendpupil , colour = as.factor(ssid_bris_birm)))+
      geom_line()+
  theme(legend.position = "none")+
  geom_vline(xintercept = 0, linetype = "dashed")

# range(dta_pupil$pupil,na.rm = T)
# range(dta_pupil$pupil_d,na.rm = T)
# 
# range(dta_pupil$extendpupil,na.rm = T)
# range(dta_pupil$extendpupil_d,na.rm = T)
```

# Smooth and Interpolate
```{r}

dta_pupil$subject<- dta_pupil$ssid_bris_birm


# ?smooth_interpolate_pupil

#  order dependent


dta_pupil$trial_unq<- paste0(dta_pupil$trial_no, paste0(dta_pupil$text))

dta_pupil<- dta_pupil %>%
  group_by(ssid_bris_birm, trial_unq,screencontent) %>%
  gazer::smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE,
                           step.first= 'smooth',
                                    maxgap=Inf,
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

dta_pupil$pup_interp_pix<- dta_pupil$pup_interp

# diameter
dta_pupil2<- dta_pupil %>%
  select(-pupil,-extendpupil)%>%
  mutate(pupil = pupil_d, extendpupil = extendpupil_d)%>%
 group_by(ssid_bris_birm, trial_unq,screencontent) %>%
  gazer::smooth_interpolate_pupil(pupil="pupil_d", 
                           extendpupil="extendpupil_d",
                                    extendblinks=TRUE,
                           step.first= 'smooth',
                                    maxgap=Inf,
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

dta_pupil$pup_interp_d <- dta_pupil2$pup_interp

range(dta_pupil$pup_interp, na.rm =T)
range(dta_pupil$pup_interp,na.rm = T)
range(dta_pupil$pup_interp_d,na.rm = T)



```

```{r}
cor.test(dta_pupil$pup_interp_pix, dta_pupil$pupil)
cor.test(dta_pupil$pup_interp_d, dta_pupil$pupil_d)



range(dta_pupil$pup_interp_pix, na.rm = TRUE)
range(dta_pupil$pup_interp_d, na.rm = TRUE)

# subset(dta_pupil, tNo == 20 & ssid == 357)%>%


dta_pupil%>%
  subset(ssid_bris_birm == "bris_30" & trial_no == 15)%>%
  # ssid = 010 & s
  # subset(trialUnq == " stimuli 22_23__walking_outside_cafe_disgusted__J8JK3NBV.mp4" )%>%
ggplot(aes(x = time_backward, y= pup_interp_pix ))+

  geom_line(colour = "blue")+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'black', alpha = 1)


```







```{r}

# takes a lot of time
# dta_pupil%>%
#   subset(screencontent == "stimuli")%>%
#   ggplot(aes(time_backward, pup_interp_pix, colour = isfake_or_real))+
#   geom_smooth()
```

# pupil baseline correction

```{r}

#  Subtractive baseline correction 

# Count the samples in each trial section
# ?gazer::baseline_correction_pupil()
# ?gazer::baseline_correction_pupil_msg

min(dta_pupil$time_backward, na.rm = T)

# make baseline about half a second
dta_pupil_1<-

dta_pupil%>%
  subset(time_backward>-.5)%>%
  group_by(ssid_bris_birm)%>%
  arrange(ssid_bris_birm, trial_no,screencontent, time,time_backward)
  # subset(ssid_bris_birm == "bris_10" & trial_no < 3 & time_backward< 1)




# remove outliers to do
dta_pupil_1<-dta_pupil_1  %>%
  dplyr::group_by(ssid_bris_birm, trial_no) %>%
  dplyr::mutate(pup_speed=gazer::speed_pupil(pup_interp_pix,timerezero)) %>%
  dplyr::mutate(pup_mad=gazer::calc_mad(pup_speed)) %>%
  mutate(pup_interp_pix_mad = if_else(pup_speed < pup_mad, pup_interp_pix, NA_real_))

dta_pupil_1$pup_interp_pix_mad
dta_pupil_1$pup_interp_pix
#onset to stimulus



dta_pupil_1$baseline<- if_else(dta_pupil_1$time_backward< .2, "baseline", "trial")


# create baseline
dta_pupil_1<-dta_pupil_1 %>%
  group_by(ssid_bris_birm,trial_no)%>%
  mutate(pup_bas_med = median(pup_interp_pix_mad[baseline == "baseline"], na.rm = T))

# temp_test<- dta_pupil_1 %>%subset(ssid_bris_birm == "bris_20" & trial_no == 1)
# 
# temp_test<- temp_test%>%
#   group_by(baseline)%>%
#   mutate(test_value = mean(pup_interp_pix))
```

 
# Push these values down 20 steps so that all the samples needed to compute the median will always fall within the trial where they will be used

  
```{r}
dta_pupil_1


# Subtract pupil size from median pupil size during the baseline period
dta_pupil_1<- dta_pupil_1 %>%
  # arrange(ssid, text, time) %>%
  group_by(ssid_bris_birm, trial_no) %>%
  mutate(pup_interp_pix_bas_cor = pup_interp_pix_mad - pup_bas_med)


dta_pupil_1%>%
  subset(ssid_bris_birm == "bris_35" & trial_no == 25)%>%

ggplot(aes(x = time_backward, y= pupil ))+

  geom_line(colour = "blue")+
   geom_line(aes(y = pup_interp_pix), color = 'red')+
   geom_line(aes(y = pup_interp_pix_bas_cor), color = 'green')+ 
  geom_line(aes(y = pupil), colour = 'gray', alpha = .1)



```


```{r}
dta_pupil_1%>%
  subset(ssid_bris_birm == "bris_30" )%>%

ggplot(aes(x = time_backward, y= pup_interp_pix, group = trial_no ))+

  geom_line(colour = "blue")+
   # geom_line(aes(y = extendpupil), color = 'red')+
   geom_line(aes(y = pup_interp_pix_bas_cor), color = 'green')
  # geom_line(aes(y = pupil), colour = 'gray', alpha = .1)

```

```{r}
dta_pupil_1%>%
  subset(ssid_bris_birm == "bris_33" )%>%

ggplot(aes(x = time_backward, y= pup_interp_pix, group = trial_no ))+

  # geom_line(colour = "blue")+
   # geom_line(aes(y = extendpupil), color = 'red')+
   geom_line(aes(y = pup_interp_pix_bas_cor), color = 'green')

dta_pupil_1$stimnopath



```


```{r}


dta_pupil_1%>%
  subset(stimnopath == "14_03__walking_down_street_outside_angry__PLCQJM81.mp4" )%>%

ggplot(aes(x = time_backward, y= pup_interp_pix_bas_cor, group = ssid_bris_birm ))+

  geom_line(colour = "blue")
   # geom_line(aes(y = extendpupil), color = 'red')
   # geom_point(aes(y = pup_interp_pix_bas_cor), color = 'green')
   # 

dta_pupil_1$pup_loss_true = is.na(dta_pupil_1$pup_interp_pix_mad)
  
colnames(dta_pupil_1)


dta_pupil_1_agg<- dta_pupil_1%>%
  group_by(ssid_bris_birm, trial_no)%>%
  mutate(pup_loss_prop = mean(pup_loss_true, na.rm. =T))%>%
  # drop screen content
  subset(screencontent == "stimuli")%>%
  group_by(ssid_bris_birm, pratice_vs_trial, isfake_or_real,
           stimnopath, text, filename, bris_vs_birm, trial, trial_no, trial_unq, subject)%>%
  summarise_if(is.numeric, mean, na.rm = T)
  
  
  
  dta_pupil_1_agg%>%
  ggplot(aes(pup_loss_prop))+
  geom_histogram()

  
  # 89*Ntrials
  
  
  
  
  unique(dta_pupil_1_agg$ssid_bris_birm)
  
  
```

Combine pupil gaze and behaviour and questionnaires

```{r}

unique(dta_pupil_1_agg$ssid_bris_birm)
dta_pupil_1_agg


dta_pupil_1_agg_bris_23_24_birm_22_23<-dta_pupil_1_agg




  dta_pupil_1_agg_bris_23_24_birm_22_23%>%
    ggplot(aes(pupil, pup_interp_pix_bas_cor))+
    geom_point(alpha = .1)+
    geom_smooth(aes(group = ssid_bris_birm), method = lm, se = F)
  
  
    dta_pupil_1_agg_bris_23_24_birm_22_23%>%
    ggplot(aes(pup_interp_pix, pupil))+
    geom_point(alpha = .1)+
    geom_smooth(aes(group = ssid_bris_birm), method = lm, se = F)
    
    
 table(dta_pupil_1_agg_bris_23_24_birm_22_23$ssid_bris_birm)   
    
```


```{r}

table(dta_gp_all_fix_sacc_entr_agg$ssid_bris_birm)
dta_gp_all_fix_sacc_entr_agg_bris_23_24_birm_22_23<-dta_gp_all_fix_sacc_entr_agg

unique(dta_gp_all_fix_sacc_entr_agg_bris_23_24_birm_22_23$ssid_bris_birm)
unique(dta_pupil_1_agg_bris_23_24_birm_22_23$ssid_bris_birm)



dta_dfst_bris_23_24_birm_22_23_eytr_behv_quest1 <- read_csv("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/Deepfakes/Deepfake_RProject/Data/2022_birm_2024_bristol/dta_dfst_bris_23_24_birm_22_23_eytr_behv_quest1.csv")
View(dta_dfst_bris_23_24_birm_22_23_eytr_behv_quest1)



dta_pupil_1_agg_bris_23_24_birm_22_23$trial_no<-as.character(dta_pupil_1_agg_bris_23_24_birm_22_23$trial_no)
dta_gp_all_fix_sacc_entr_agg_bris_23_24_birm_22_23$filename<-NULL
dta_pupil_1_agg_bris_23_24_birm_22_23$filename<-NULL


unique(dta_gp_all_fix_sacc_entr_agg_bris_23_24_birm_22_23$trial)
unique(dta_pupil_1_agg_bris_23_24_birm_22_23$trial)




 
dta_dfst_bris_23_24_birm_22_23_eytr_behv_quest


dta_bhv_quest_bris_23_24_birm_22_23%>%subset(pratice_vs_trial == "Trial")

dta_df_plf_eyetrak<- 
  dta_pupil_1_agg_bris_23_24_birm_22_23%>%
              select(-subject,-gaze_valid_prop, -trackloss)%>%
              subset(pratice_vs_trial == "Trial")%>%
  left_join(dta_gp_all_fix_sacc_entr_agg_bris_23_24_birm_22_23%>%
  select(-subject)%>%
  subset(pratice_vs_trial == "Trial"))



# combine with behavioral data
# dta_dfplf_bris_23_24_birm_22_23_behav_quest

unique(dta_df_plf_eyetrak$pratice_vs_trial)
dta_dfplf_bris_23_24_birm_22_23_behav_quest

table(dta_dfplf_bris_23_24_birm_22_23_behav_quest$ssid_bris_birm)

table(dta_df_plf_eyetrak$ssid_bris_birm)
# note gaze data may have been lost due to gazepath fixation fio

unique(dta_dfplf_bris_23_24_birm_22_23_behav_quest$pratice_vs_trial)



dta_dfplf_bris_23_24_birm_22_23_behav_quest_trial<- dta_dfplf_bris_23_24_birm_22_23_behav_quest%>%subset(dta_dfplf_bris_23_24_birm_22_23_behav_quest$pratice_vs_trial == "Trial")


dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest

dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest<-left_join(dta_dfplf_bris_23_24_birm_22_23_behav_quest_trial,
          dta_df_plf_eyetrak,
          by = join_by(ssid_bris_birm, bris_vs_birm, 
                       stimnopath, pratice_vs_trial, 
                       isfake_or_real))




dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest

colnames(dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest)

dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest
```


```{r}

colnames(dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest)


dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest1<-dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest[,c(1:119,121,127,131)]

tmp_cnames <-colnames(dta_dfst_bris_23_24_birm_22_23_eytr_behv_quest1)

tmp_cnames<- gsub("dfs_", "dplf_", tmp_cnames)


# desired_order <- c(1:17, 82:87, 25:28)
# total_cols <- ncol(dta_dfst_bris_23_24_birm_22_23_eytr_behv_quest1)

# Append the remaining columns (preserving their original order)
# remaining <- setdiff(seq_len(total_cols), desired_order)

# Create the new column order
# new_order <- c(desired_order, remaining)

colnames(dta_dfst_bris_23_24_birm_22_23_eytr_behv_quest1)

dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest1 <-
dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest%>%
  select(tmp_cnames)

colnames(dta_dfplf_bris_23_24_birm_22_23_eytrk_behav_quest1)

```