---
title: "pre-process_pup"
output: html_document
date: "2025-12-17"
---

note originally we only did complete processing for gaze, not pupil

so this script will take over the initial processing of pupil from pre_process_eytr, and finalise processing for pupildata


Pupil



```{r}
load("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/dta_gaze_env.RData")
# in pre_process_eyetrk we want dta_eytr_rpx
# from here you cna do the stanard pupil processinh



```


```{r}
dta_socemophys_pup<- select(dta_eytr_rpx, 
                                      c("participant", "session_id", "event_id", "ssid", 
                                        "text","trialunq","screencontent",
                                        "screencontent_no_na","pratice_vs_trial",                           "stimnopath",
                                        "stimnopath_no_na",
                            "time", "timerezero","time_backward",
                            
                            "pupil",
                            "pupil_d", "trackloss", "gaze_loss_prop", "gaze_valid_prop"))


saveRDS(dta_socemophys_pup, "dta_socemophys_pup.rds")
```

to do


```{r}
dta_socemophys_pup <- readRDS("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/2022_2023_Analyses/Data/2025 - autism and alexithymia/dta_socemophys_pup.rds")

```

```{r}

remotes::install_github("dmirman/gazer")
install.packages("remotes")
install.packages("gazer")
library(gazer)

colnames(dta_socemophys_pup)
unique(dta_socemophys_pup$trialunq)

```

```{r}

dta_pupil<- dta_socemophys_pup

range(dta_pupil$pupil, na.rm = TRUE)
range(dta_pupil$pupil_d, na.rm = TRUE)
max(dta_pupil$pupil, na.rm = TRUE)

```

```{r}

dta_pupil%>%
  ggplot(aes(pupil))+
  geom_histogram()


dta_pupil%>%
  ggplot(aes(pupil_d))+
  geom_histogram()


```




```{r}

dta_pupil$pupil<- if_else(dta_pupil$pupil> 7, dta_pupil$pupil, NA)

dta_pupil$pupil<- if_else(dta_pupil$pupil< 45, dta_pupil$pupil, NA)
range(dta_pupil$pupil, na.rm = T)
range(dta_pupil$pupil_d, na.rm = T)
# 1.30 27.91
# 


# note that smothing and interpolating is order dependent so order by ssid, trial and time
dta_pupil$time

options(digits=10)

dta_pupil$ssid

dta_pupil<- dta_pupil %>%
    group_by(participant, ssid)%>%
  arrange(ssid,time)





```


```{r}

dta_pupil<- dta_pupil%>%
  group_by(participant)%>%
   arrange(ssid,time)%>%
  group_by(participant,screencontent_no_na)%>%
  mutate(trial_no = cumsum(text != lag(text, default = first(text))) + 1)

range(dta_pupil$trial_no)
# dta_pupil$trial_no<- NULL

# unique(dta_pupil$screencontent)
require(gazer)
      
dta_pupil <- dta_pupil%>%
  group_by(participant, text,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=50, fillforward=50, hz=150))%>%
  mutate(extendpupil_d=gazer::extend_blinks(pupil_d, fillback=50, fillforward=50, hz=150))

range(dta_pupil$extendpupil, na.rm = TRUE)
range(dta_pupil$extendpupil_d, na.rm = TRUE)
range(dta_pupil$pupil, na.rm = TRUE)

```

# let's check

```{r}
unique(dta_pupil$participant)
dta_pupil%>%
  subset(ssid == "130" & trial_no == 15)%>%
  # ssid = 010 & s
  # subset(trialUnq == " stimuli 22_23__walking_outside_cafe_disgusted__J8JK3NBV.mp4" )%>%
ggplot(aes(x = time_backward, y= extendpupil))+
      geom_line()+
  geom_line(aes(y = pupil), colour = "red", linetype = "dashed", size = .5) 




```

```{r}

unique(dta_pupil$stimnopath)
dta_pupil%>%
  subset(stimnopath == "4599.jpg")%>%
  # ssid = 010 & s
  # subset(trialUnq == " stimuli 22_23__walking_outside_cafe_disgusted__J8JK3NBV.mp4" )%>%
ggplot(aes(x = time_backward, y= extendpupil , colour = as.factor(ssid)))+
      geom_line()+
  theme(legend.position = "none")+
  geom_vline(xintercept = 0, linetype = "dashed")

# range(dta_pupil$pupil,na.rm = T)
# range(dta_pupil$pupil_d,na.rm = T)
# 
# range(dta_pupil$extendpupil,na.rm = T)
# range(dta_pupil$extendpupil_d,na.rm = T)
```

# Smooth and Interpolate
```{r}

dta_pupil$subject<- dta_pupil$participant


# ?smooth_interpolate_pupil

#  order dependent


dta_pupil$trialunq
dta_pupil$screencontent_no_na
dta_pupil$trial<- dta_pupil$trialunq

dta_pupil<- dta_pupil %>%
  group_by(participant, trialunq,screencontent_no_na) %>%
  gazer::smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE,
                           step.first= 'smooth',
                                    maxgap=Inf,
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

dta_pupil$pup_interp_pix<- dta_pupil$pup_interp

# diameter
dta_pupil2<- dta_pupil %>%
  select(-pupil,-extendpupil)%>%
  mutate(pupil = pupil_d, extendpupil = extendpupil_d)%>%
 group_by(participant, trialunq,screencontent_no_na) %>%
  gazer::smooth_interpolate_pupil(pupil="pupil_d", 
                           extendpupil="extendpupil_d",
                                    extendblinks=TRUE,
                           step.first= 'smooth',
                                    maxgap=Inf,
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

dta_pupil$pup_interp_d <- dta_pupil2$pup_interp

range(dta_pupil$pup_interp, na.rm =T)
range(dta_pupil$pup_interp,na.rm = T)
range(dta_pupil$pup_interp_d,na.rm = T)



```

```{r}
cor.test(dta_pupil$pup_interp_pix, dta_pupil$pupil)
cor.test(dta_pupil$pup_interp_d, dta_pupil$pupil_d)



range(dta_pupil$pup_interp_pix, na.rm = TRUE)
range(dta_pupil$pup_interp_d, na.rm = TRUE)

# subset(dta_pupil, tNo == 20 & ssid == 357)%>%


dta_pupil%>%
  subset(participant == "130" & trial_no == 15)%>%
  # ssid = 010 & s
  # subset(trialUnq == " stimuli 22_23__walking_outside_cafe_disgusted__J8JK3NBV.mp4" )%>%
ggplot(aes(x = time_backward, y= pup_interp_pix ))+

  geom_line(colour = "blue")+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'black', alpha = 1)


```









# pupil baseline correction

```{r}

#  Subtractive baseline correction 

# Count the samples in each trial section
# ?gazer::baseline_correction_pupil()
# ?gazer::baseline_correction_pupil_msg

min(dta_pupil$time_backward, na.rm = T)

# make baseline about half a second
dta_pupil_1<-

dta_pupil%>%
  subset(time_backward>-.5)%>%
  group_by(participant)%>%
  arrange(ssid, trial_no,screencontent_no_na, time,time_backward)
  # subset(ssid_bris_birm == "bris_10" & trial_no < 3 & time_backward< 1)




# remove outliers to do
dta_pupil_1<-dta_pupil_1  %>%
  dplyr::group_by(participant, trial_no) %>%
  dplyr::mutate(pup_speed=gazer::speed_pupil(pup_interp_pix,timerezero)) %>%
  dplyr::mutate(pup_mad=gazer::calc_mad(pup_speed)) %>%
  mutate(pup_interp_pix_mad = if_else(pup_speed < pup_mad, pup_interp_pix, NA_real_))

dta_pupil_1$pup_interp_pix_mad
dta_pupil_1$pup_interp_pix
#onset to stimulus



dta_pupil_1$baseline<- if_else(dta_pupil_1$time_backward< .2, "baseline", "trial")


# create baseline
dta_pupil_1<-dta_pupil_1 %>%
  group_by(participant,trial_no)%>%
  mutate(pup_bas_med = median(pup_interp_pix_mad[baseline == "baseline"], na.rm = T))

# temp_test<- dta_pupil_1 %>%subset(ssid_bris_birm == "bris_20" & trial_no == 1)
# 
# temp_test<- temp_test%>%
#   group_by(baseline)%>%
#   mutate(test_value = mean(pup_interp_pix))
```

 
# Push these values down 20 steps so that all the samples needed to compute the median will always fall within the trial where they will be used

  
```{r}
dta_pupil_1


# Subtract pupil size from median pupil size during the baseline period
dta_pupil_1<- dta_pupil_1 %>%
  # arrange(ssid, text, time) %>%
  group_by(participant, trial_no) %>%
  mutate(pup_interp_pix_bas_cor = pup_interp_pix_mad - pup_bas_med)


dta_pupil_1%>%
  subset(participant == "130" & trial_no == 15)%>%

ggplot(aes(x = time_backward, y= pupil ))+

  geom_line(colour = "blue")+
   geom_line(aes(y = pup_interp_pix), color = 'red')+
   geom_line(aes(y = pup_interp_pix_bas_cor), color = 'green')+ 
  geom_line(aes(y = pupil), colour = 'gray', alpha = .1)



```
```{r}

dta_pupil_1$pup_loss_true = is.na(dta_pupil_1$pup_interp_pix_mad)
  
colnames(dta_pupil_1)
dta_pupil_1
unique(dta_pupil_1$screencontent_no_na)

dta_pupil_1_agg<- dta_pupil_1%>%
  group_by(participant, trial_no)%>%
  mutate(pup_loss_prop = mean(pup_loss_true, na.rm. =T))%>%
  # drop screen content
  subset(screencontent_no_na == "stimuli")%>%
  group_by(participant,ssid, pratice_vs_trial,
           stimnopath,stimnopath_no_na, text, trial, trial_no, trialunq, subject)%>%
  summarise_if(is.numeric, mean, na.rm = T)
  
  


  
  # 89*Ntrials
  
  
  
  
  unique(dta_pupil_1_agg$participant)
  
  
```

Combine pupil gaze and behaviour and questionnaires

```{r}


dta_pupil_1_agg_soc_emophys<-dta_pupil_1_agg

saveRDS(dta_pupil_1_agg_soc_emophys, "final_pupil_to_merge.Rds")

#     setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/merged_data_august24")
# > saveRDS(dta_pupil_1_agg_soc_emophys, "final_pupil_to_merge.Rds")
# > save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/dta_socemophys_pup_env.RData")
```
