---
title: "pre_process_ecg"
author: "Helio"
date: "2024-03-09"
output: html_document
---




ECG signals



Set-up: where I load libraries and create objects for later use (such as color schemes etc).
```{r setup, include=FALSE}
# Load necessary libraries
require(tidyverse)
require(data.table)
library(janitor)
library(purrr)
require(readr)


```


Load files check how many we have on sd vs PC
# Handling file imports from PC and SD sources:
# - This process primarily relies on PC files, but switches to SD files in the absence of a corresponding PC file.
# - A notable discrepancy has been observed in the export formats: PC exports contain "sync" within the timestamps, unlike SD exports. This difference may affect how filenames are generated and could imply variations in how data synchronization is handled or represented between the two sources.
# - It is essential to consider this variation during data processing to ensure consistent naming conventions and to investigate the synchronization status of SD data.
# - The custom function is applied to each file to adjust for these discrepancies, and the results are subsequently combined.


```{r}

setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Consensys-physio/Calibrated")

# List of .csv files, assuming you've already created 'tmp_files' with list.files()
# tmp_files <- list.files(pattern = "\\._PCcsv$", recursive = FALSE, full.names = TRUE)
tmp_files_pc <- list.files(pattern = "ECG.*PC\\.csv$", recursive = FALSE, full.names = TRUE)

tmp_files_sd <- list.files(pattern = "ECG.*SD\\.csv$", recursive = FALSE, full.names = TRUE)


# Extract identifiers

# Regular expression to capture the pattern before "_" and after "./"
pattern <- "\\./([0-9]+)_.*"

# Extract the pattern

identifiers_tmp_files_pc <- sub(pattern, "\\1",  tmp_files_pc)
identifiers_tmp_files_sd <- sub(pattern, "\\1", tmp_files_sd)

# Compare and find common identifiers
tmp_common_identifiers <- intersect(identifiers_tmp_files_pc, identifiers_tmp_files_sd)

# Display the common identifiers
tmp_common_identifiers
# length(tmp_common_identifiers) # 51

# Identifiers unique to PC files
tmp_unique_identifiers_pc <- setdiff(identifiers_tmp_files_pc, identifiers_tmp_files_sd)
# "101" "102" "106" ADDED DB 103
# Identifiers unique to SD files
tmp_unique_identifiers_sd <- setdiff(identifiers_tmp_files_sd, identifiers_tmp_files_pc)
# "105" "108" "110" "111" "113" "114" "201" "204" "205" "208" "209" "213" "220"
# 220 noted missing in logbook
# way more ECG files didn load to PC than GSR


# now we want to create a list that contains tmp_files_pc plus the tmp_unique_identifiers_sd

# Assuming tmp_unique_identifiers_sd contains unique identifiers like c("101", "102", "106")
# Create a regular expression pattern that matches any of these identifiers
pattern_unique_sd <- paste(tmp_unique_identifiers_sd, collapse = "|")

# Use grep to select files from tmp_files_sd that match the unique identifiers
tmp_selected_files_sd <- tmp_files_sd[grep(pattern_unique_sd, tmp_files_sd)]

# Display the selected files
tmp_selected_files_sd

# Combine selected_files_sd with tmp_files_pc
tmp_combined_list <- c(tmp_files_pc,tmp_selected_files_sd)

# Display the combined vector

tmp_combined_list
# remember to update 000_Session1_ECG_Calibrated_PC to 2176?
```


select col names
```{r}
###################################################

tmp_combined_list
# do we actually want to store all of thes efiles here, or just load each adjut then save it back due to memory issues
setDT(dta_psypy1)
# dta_psypy1$orig_unixtime_start_psypy<- dta_psypy1$unixtime_start



# Predefined column names
column_names <- c( "ecg_timestamp_sync_unix_cal_ms", "ecg_battery_cal_m_v",
                  "ecg_ecg_emg_status1_cal_no_units", "ecg_ecg_emg_status2_cal_no_units",
                  "ecg_ecg_ibi_ll_ra_cal_ms", "ecg_ecg_ibi_vx_rl_cal_ms",
                  "ecg_ecg_la_ra_24bit_cal_m_v", "ecg_ecg_ll_la_24bit_cal_m_v",
                  "ecg_ecg_ll_ra_24bit_cal_m_v", "ecg_ecg_vx_rl_24bit_cal_m_v",
                  "ecg_ec_gto_hr_ll_ra_cal_bpm", "ecg_ec_gto_hr_vx_rl_cal_bpm",
                  "ecg_pressure_bmp280_cal_k_pa", "ecg_temperature_bmp280_cal_degrees_celsius")



# Assuming participant_ids and other necessary data are already defined

participant_ids <- unique(dta_psypy1$participant)
participant_ids
tmp_combined_list




```

skip this
```{r eval=FALSE, include=FALSE}

library(data.table)
library(dplyr)
library(stringr)

# Helper function to extract participant ID and session from filename
extract_info <- function(filename) {
  parts <- str_match(filename, ".*/(\\d+)_Session(\\d+)_ECG_Calibrated_.*\\.csv$")
  return(list(participant_id = parts[, 2], session = parts[, 3]))
}

# Create a dataframe to map participant IDs and sessions to file paths
file_info <- sapply(tmp_combined_list, function(x) extract_info(x), simplify = FALSE)
file_df <- do.call(rbind, lapply(file_info, function(x) data.frame(participant_id = x$participant_id, session = x$session, stringsAsFactors = FALSE)))
file_df$filepath <- tmp_combined_list


# Loop through each participant ID
participant_id = 136
for (participant_id in participant_ids) {
  # Find all files for this participant
  participant_files <- file_df[file_df$participant_id == participant_id, ]
  
  for (i in 1:nrow(participant_files)) {
    # Load and process each file
    filepath <- participant_files$filepath[i]
    session <- participant_files$session[i]

  # Assuming tmp_combined_list is correctly defined earlier as a list of file paths
  
  # Read the CSV file, skip the first 3 rows
  tmp_ecg <- fread(filepath, skip = 3, header = FALSE) # Adjust the index as necessary
  
  # Check if there's an extra empty column and remove it if necessary
  if (ncol(tmp_ecg) > length(column_names)) {
    tmp_ecg <- tmp_ecg[, -ncol(tmp_ecg), with = FALSE]
  }
  
  setnames(tmp_ecg, old = names(tmp_ecg), new = column_names)
  
  # Add a new column with the filename
  tmp_ecg[, filename := basename(tmp_combined_list[participant_id])] # Adjust the index as necessary
  
  # Parse participant and session from filename
  tmp_ecg[, participant := sub("_.*", "", filename)]
  tmp_ecg[, session := gsub(".*_(Session\\d+)_.*", "\\1", filename)]
  
  # Correct original timestamp column name
  tmp_ecg[, orig_timestamp_ecg := ecg_timestamp_sync_unix_cal_ms]
  
  # Perform operations with dta_psypy1 data
  # Assuming dta_psypy1 is already defined
  
  # Merge timestamps and other operations
  tmp_psypy <- dta_psypy1[participant == participant_id, .(participant, social_nonsocial, stim_iaps, trial_no_all, unixtime_start, orig_unixtime_start_psypy)]
  tmp_psypy[, next_unixtime_start := shift(unixtime_start, type = "lead", fill = Inf)]
  tmp_psypy[, unixtime_end := next_unixtime_start - 1]
  
  # Initialize missing columns in tmp_ecg
  tmp_ecg[, `:=` (social_nonsocial = as.character(NA), 
                  stim_iaps = as.character(NA), 
                  trial_no_all = as.integer(NA), 
                  psypy_unixtime_start = as.numeric(NA),
                  orig_unixtime_start_psypy = as.numeric(NA))]
  
  # Perform the non-equi join and update
  tmp_ecg[tmp_psypy, on = .(ecg_timestamp_sync_unix_cal_ms >= unixtime_start, 
                            ecg_timestamp_sync_unix_cal_ms <= unixtime_end), 
          `:=` (social_nonsocial = i.social_nonsocial, 
                stim_iaps = i.stim_iaps, 
                trial_no_all = i.trial_no_all, 
                psypy_unixtime_start = i.unixtime_start,
                orig_unixtime_start_psypy = i.orig_unixtime_start_psypy), 
          by = .EACHI]
  
  # Converting data.table to tibble for dplyr operations
  tmp_ecg <- as_tibble(tmp_ecg)
  
  # dplyr operations
  tmp_ecg <- tmp_ecg %>%
    arrange(ecg_timestamp_sync_unix_cal_ms) %>%
    mutate(start_true = !duplicated(trial_no_all) & !is.na(trial_no_all),
           trigger = case_when(
             trial_no_all == 1 & start_true == TRUE ~ 1, 
             start_true == FALSE ~ 0, 
             TRUE ~ as.numeric(trial_no_all)),
           ecg_timerezero_sync_unix_cal_ms = ecg_timestamp_sync_unix_cal_ms - first(ecg_timestamp_sync_unix_cal_ms))
  
  # Save the updated dataframe to a CSV file
  fwrite(as.data.table(tmp_ecg), paste0(participant_id, "_dta_ecg_trig.csv"), row.names = FALSE)

  
      
    # Your file processing code here, using fread(filepath) to load the file
    # Example: tmp_ecg <- fread(filepath, skip = 3, header = FALSE)
    # Make sure to include session handling in your processing
    
    # Continue with your existing data processing steps, adapted for each file
  }
}



```



load merge triggers and export - so this will still be rawish - i.e no procesing
```{r}
setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Consensys-physio/Calibrated/ecg_wtriggers")

# Ensure that file_df is correctly created and available before this script runs.

 # Helper function to extract participant ID and session from filename
extract_info <- function(filename) {
  parts <- str_match(filename, ".*/(\\d+)_Session(\\d+)_ECG_Calibrated_.*\\.csv$")
  return(list(participant_id = parts[, 2], session = parts[, 3]))
}

# Create a dataframe to map participant IDs and sessions to file paths
file_info <- sapply(tmp_combined_list, function(x) extract_info(x), simplify = FALSE)
file_df <- do.call(rbind, lapply(file_info, function(x) data.frame(participant_id = x$participant_id, session = x$session, stringsAsFactors = FALSE)))
file_df$filepath <- tmp_combined_list

# participant_id = 134
# rm(participant_id)
# participant_ids
for (participant_id in participant_ids) {
  # Find all files for this participant
  participant_files <- file_df[file_df$participant_id == participant_id, ]
  
  # rm(i)
  for (i in 1:nrow(participant_files)) {
    # Load and process each file
    filepath <- participant_files$filepath[i]
    session <- participant_files$session[i] # This line captures the session info directly

    # Read the CSV file, skip the first 3 rows
    tmp_ecg <- fread(filepath, skip = 3, header = FALSE)
    
    # Check if there's an extra empty column and remove it if necessary
    if (ncol(tmp_ecg) > length(column_names)) {
      tmp_ecg <- tmp_ecg[, -ncol(tmp_ecg), with = FALSE]
    }
    
    # Assign predefined column names
    setnames(tmp_ecg, old = names(tmp_ecg), new = column_names)
    
    # Add a new column with the filename
    filename <- basename(filepath)
    tmp_ecg[, filename := filename]
    
    # Correct original timestamp column name if necessary
    tmp_ecg[, orig_timestamp_ecg := ecg_timestamp_sync_unix_cal_ms] 

    
    # Merge timestamps and other operations from dta_psypy1

    tmp_psypy <- dta_psypy1[participant == participant_id, 
                            .(participant, social_nonsocial, 
                              stim_iaps, trial_no_all, unixtime_start, 
                              orig_unixtime_start_psypy)]
    tmp_psypy[, next_unixtime_start := shift(unixtime_start, type = "lead", fill = Inf)]
    tmp_psypy[, unixtime_end := next_unixtime_start - 1]
    
    # Initialize missing columns in tmp_ecg
    tmp_ecg[, `:=` (social_nonsocial = as.character(NA), 
                    stim_iaps = as.character(NA), 
                    trial_no_all = as.integer(NA), 
                    psypy_unixtime_start = as.numeric(NA),
                    orig_unixtime_start_psypy = as.numeric(NA))]
    
    # Perform the non-equi join and update
    tmp_ecg[tmp_psypy, on = .(ecg_timestamp_sync_unix_cal_ms >= unixtime_start, 
                              ecg_timestamp_sync_unix_cal_ms <= unixtime_end), 
            `:=` (social_nonsocial = i.social_nonsocial, 
                  stim_iaps = i.stim_iaps, 
                  trial_no_all = i.trial_no_all, 
                  psypy_unixtime_start = i.unixtime_start,
                  orig_unixtime_start_psypy = i.orig_unixtime_start_psypy), 
            by = .EACHI]
    
    # Convert data.table to tibble for further dplyr operations if necessary
    tmp_ecg <- as_tibble(tmp_ecg)
    
    # dplyr operations
    tmp_ecg <- tmp_ecg %>%
      arrange(ecg_timestamp_sync_unix_cal_ms) %>%
      mutate(start_true = !duplicated(trial_no_all) & !is.na(trial_no_all),
             trigger = case_when(
               trial_no_all == 1 & start_true == TRUE ~ 1, 
               start_true == FALSE ~ 0, 
               TRUE ~ as.numeric(trial_no_all)),
             ecg_timerezero_sync_unix_cal_ms = ecg_timestamp_sync_unix_cal_ms - first(ecg_timestamp_sync_unix_cal_ms))
    
    # table(tmp_ecg$trigger)
    
    # Save the updated dataframe to a CSV file
    fwrite(as.data.table(tmp_ecg), paste0(participant_id, "_Session", session, "_dta_ecg_trig.csv"), row.names = FALSE)
  }
}


```
note 103 is mising ecg data but this is present in database so we need to load up manualy from sql
quick checks

```{r}
# Load necessary libraries
# install.packages("RSQLite")
# install.packages("DBI")
library(RSQLite)
library(DBI)

setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Consensys-physio/103/Raw data/1706540442")

# Specify the path to your SQLite database file
db_path <- "~Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Consensys-physio/103/Raw data/1706540442/1706540442.db" # Replace with your actual file path

# Establish a connection to the SQLite database
conn <- dbConnect(RSQLite::SQLite(), dbname = db_path)

# Specify the table you want to download
table_name <- "Calibrated_BT_fc0fe7b56da3"

# Read the table into a data frame
data <- dbReadTable(conn, table_name)

# Specify the path where you want to save the CSV file
csv_path <- "path/to/where/you/want/Calibrated_BT_fc0fe7b56da3.csv" # Replace with your actual save path

# Write the data frame to a CSV file
write.csv(data, csv_path, row.names = FALSE)

# Close the connection
dbDisconnect(conn)
```



```{r}
colnames(tmp_ecg)
 tmp_ecg %>%
    arrange(ecg_timestamp_sync_unix_cal_ms) %>%
  group_by(trial_no_all) %>%
  mutate(start_true = !duplicated(trial_no_all) & !is.na(trial_no_all)) %>%
  
  mutate(time = ifelse(start_true, ecg_timestamp_sync_unix_cal_ms, NA)) %>%
  # Use `fill` to propagate the first timestamp down the group
  fill(time, .direction = "down")%>%
  ungroup()%>%
  arrange(ecg_timestamp_sync_unix_cal_ms)%>%
  # subset(trial_no_all>15 & trial_no_all<20)%>%
  mutate(time_diff_psypy_gsr = orig_unixtime_start_psypy-orig_unixtime_start_psypy)%>%
  ggplot( aes(x = ecg_timestamp_sync_unix_cal_ms, 
                         y = ecg_ec_gto_hr_ll_ra_cal_bpm)) +
  geom_line() +
  # Add red vertical lines at 'time' for the start of each trial
  geom_vline(aes(xintercept = time), color = "red") 
 
 
  tmp_ecg %>%
    arrange(ecg_timestamp_sync_unix_cal_ms) %>%
  group_by(trial_no_all) %>%
  # mutate(start_true = !duplicated(trial_no_all) & !is.na(trial_no_all)) %>%
  
  mutate(time = ifelse(start_true, ecg_timestamp_sync_unix_cal_ms, NA)) %>%
  # Use `fill` to propagate the first timestamp down the group
  fill(time, .direction = "down")%>%
  ungroup()%>%
  arrange(ecg_timestamp_sync_unix_cal_ms)%>%
  # subset(trial_no_all>15 & trial_no_all<20)%>%
  mutate(time_diff_psypy_gsr = orig_unixtime_start_psypy-orig_unixtime_start_psypy)%>%
  ggplot( aes(x = ecg_timestamp_sync_unix_cal_ms, 
                         y = ecg_ec_gto_hr_ll_ra_cal_bpm)) +
  geom_line() +
  # Add red vertical lines at 'time' for the start of each trial
  geom_vline(aes(xintercept = time), color = "red") 
 
 
 
 
 # IBI
 unique( tmp_ecg$ecg_ecg_ibi_ll_ra_cal_ms)
 
 
 tmp_ecg %>%
    arrange(ecg_timestamp_sync_unix_cal_ms) %>%
  group_by(trial_no_all) %>%
  mutate(start_true = !duplicated(trial_no_all) & !is.na(trial_no_all)) %>%


  mutate(time = ifelse(start_true, ecg_timestamp_sync_unix_cal_ms, NA)) %>%

  # Use `fill` to propagate the first timestamp down the group
  fill(time, .direction = "down")%>%
  ungroup()%>%
  arrange(ecg_timestamp_sync_unix_cal_ms)%>%
         subset(ecg_ecg_ibi_ll_ra_cal_ms> 0 )%>%
  subset(trial_no_all>15 & trial_no_all<20)%>%
  mutate(time_diff_psypy_gsr = orig_unixtime_start_psypy-orig_unixtime_start_psypy)%>%
  ggplot( aes(x = ecg_timestamp_sync_unix_cal_ms, 
                         y = ecg_ecg_ibi_ll_ra_cal_ms)) +
  geom_point(size = .00001) +
   geom_line(size = .1)+
  # Add red vertical lines at 'time' for the start of each trial
  geom_vline(aes(xintercept = time), color = "red") 

 options(scipen = 999)
 
 tmp_gsr$filename
 tmp_ecg$filename
 
# tmp_ecg$orig_timestamp_ecg[tmp_ecg$start_true == TRUE]-
# tmp_gsr$orig_timestamp_gsr[tmp_gsr$start_true == TRUE]
 
 # this difference should be pretty small and it is close to 1 ms, which is great
```

[1] -1.38330078  1.89526367 -4.51904297 -2.84741211  2.70336914  3.34204102 -3.37255859
 [8] -0.88989258 -2.88159180  0.59008789 -0.29345703  0.04248047 -2.20581055 -5.65771484
[15] -1.18432617 -4.25805664  0.17578125 -4.96362305 -0.14355469 -6.34448242  1.48095703
[22] -4.22753906 -1.11303711 -4.90869141 -4.12866211 -0.66748047 -4.19775391  0.46020508
[29] -5.09057617 -3.11108398  0.88183594 -1.17407227 -3.05859375 -5.82446289 -0.14453125
[36] -6.11572266 -4.53393555  0.69726562  1.80908203  0.38989258 -0.66479492 -0.09057617
[43] -4.64746094  0.43823242 -6.83593750 -1.65405273 -3.28808594  0.71997070 -0.89892578
[50] -1.68627930 -1.86425781 -4.26074219 -0.76806641  0.58715820  1.12573242 -4.09643555
[57] -1.47729492  3.52734375  2.04956055 -5.97534180  2.72998047  0.77148438  1.63110352
[64] -0.84375000 -1.84399414
to do in ECG
smooth check artifacts and interpolate

to do later
- compare peak detecion 

```{r}



# Step 1: Read the first two rows to get column names and units


# read_delim("110_Session1_GSRPulse_Calibrated_PC.csv", 
#     delim = "\t", escape_double = FALSE, 


dta_ecg_header_info <-  read_delim("116_Session1_ECG_Calibrated_PC.csv", 
                                    # nrows = 2, 
                                    skip = 1,
                                    escape_double = FALSE, 
                                    delim = "\t")

dta_ecg <-  read_delim("116_Session1_ECG_Calibrated_PC.csv", 
                                    # nrows = 2, 
                                    skip = 2,
                                    escape_double = FALSE, 
                                    delim = "\t")

colnames(dta_ecg)


names(dta_ecg)<- paste0(colnames(dta_ecg_header_info),"_", paste0(dta_ecg_header_info[1,]))


dta_ecg$...15_NA<-NULL


# make clean names
dta_ecg<- dta_ecg%>%
  janitor::clean_names()


colnames(dta_ecg)

# ECG heart rate
dta_ecg%>%
  mutate(time_rezero = ecg_timestamp_sync_unix_cal_ms-ecg_timestamp_sync_unix_cal_ms[1])%>%
  ggplot(aes(time_rezero,
             ecg_ec_gto_hr_ll_ra_cal_bpm))+
  geom_line()
  # geom_point()


# just ECG
dta_physio$gsr_pulse_timestamp_sync_unix_cal_ms-lag(dta_physio$gsr_pulse_timestamp_sync_unix_cal_ms)
dta_ecg$ecg_timestamp_sync_unix_cal_ms-lag(dta_ecg$ecg_timestamp_sync_unix_cal_ms)


# Calculate the sample rate given the sampling interval in seconds
# sampling_interval_seconds = 0.003998047
# sample_rate = 1 / sampling_interval_seconds
# 
# sample_rate

dta_ecg$ecg_ecg_emg_status1_cal_no_units
dta_ecg$ecg_ecg_emg_status2_cal_no_units

# ecg_ecg_ll_ra_24bit_cal_m_v = ECG signa;
# ecg_ec_gto_hr_ll_ra_cal_bpm = heart rate
# ecg_ecg_ibi_ll_ra_cal_ms = IBI



dta_ecg%>%
  mutate(time_rezero = ecg_timestamp_sync_unix_cal_ms-ecg_timestamp_sync_unix_cal_ms[1])%>%
  ggplot(aes(time_rezero,
             ecg_ecg_ll_ra_24bit_cal_m_v))+
  geom_line()


dta_ecg%>%
  mutate(time_rezero = ecg_timestamp_sync_unix_cal_ms-ecg_timestamp_sync_unix_cal_ms[1])%>%
  ggplot(aes(time_rezero,
             ecg_ecg_ll_ra_24bit_cal_m_v))+
  geom_line()



# IBI
dta_ecg%>%
  subset(ecg_ecg_ibi_ll_ra_cal_ms!=-1)%>%
  mutate(time_rezero = ecg_timestamp_sync_unix_cal_ms-ecg_timestamp_sync_unix_cal_ms[1])%>%
  ggplot(aes(time_rezero,
             ecg_ecg_ibi_ll_ra_cal_ms))+
  geom_line()


# expected cavare plot of R to R interval
dta_ecg%>%
  subset(ecg_ecg_ibi_ll_ra_cal_ms!=-1)%>%
  mutate(ecg_ecg_ibi_ll_ra_cal_ms_lag = lag(ecg_ecg_ibi_ll_ra_cal_ms))%>%
  ggplot(aes(ecg_ecg_ibi_ll_ra_cal_ms,
             ecg_ecg_ibi_ll_ra_cal_ms_lag))+
  geom_point()



dta_ecg%>%
  mutate(time_rezero = ecg_timestamp_sync_unix_cal_ms-ecg_timestamp_sync_unix_cal_ms[1])%>%
  ggplot(aes(time_rezero,
             ecg_temperature_bmp280_cal_degrees_celsius))+
  geom_line()


# EGG ecg_ecg_vx_rl_24bit_cal_m_v

dta_ecg%>%
  mutate(time_rezero = ecg_timestamp_sync_unix_cal_ms-ecg_timestamp_sync_unix_cal_ms[1])%>%
  ggplot(aes(time_rezero,
             ecg_ecg_vx_rl_24bit_cal_m_v))+
  geom_line()


```