---
title: "eyetracking pre-procesing - social vs non social modualtion of emotion response and physilogy"
author: "Helio"
date: "2024-03-07"
output: html_document
---



# Overview 
In this file I aim to process all the gaze data, essentially read, clean and combines multiple files with gaze data and their metadata

# Conventions
For data: dta_
Temporary files: tmp_
Statistical summaries: sum_
Models (such as lm models): mod_
Custom functions: fn_
Plots and visualization: plt_
Lookup and referecne tables: lkp_
Results and Analysis: rlt_
Consistency and accuracy checks: chk_

Set-up: where I load libraries and create objects for later use (such as color schemes etc).

4. Check gaze data




Set-up: where I load libraries and create objects for later use (such as color schemes etc).

```{r setup, include=FALSE}
# store date
current_date<- Sys.Date()

# libraries
require(tidyverse)
require(data.table)
require(readr)

# for reading hdf5 files
# if (!requireNamespace("BiocManager", quietly = TRUE))
# install.packages("BiocManager")
# BiocManager::install(version = "3.18")
# 
# BiocManager::install("rhdf5")
library(rhdf5)



```

Data Import / Cleaning: where datasets are imported and cleaned.
```{r}

setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking")

# get hdf files in 
hdf5_file_path<-"~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking"
  

  setwd(hdf5_file_path)
fn_gp.extractor = function(hdf5_file_path) {
  

  hdf_files_list = list.files(hdf5_file_path, pattern = "\\.hdf5$")
  
  if (length(hdf_files_list) == 0){
    
    return(message('No HDF5 files found in the directory provided.'))
  }
  
  
  # pb <- txtProgressBar(min = 0, max = length(hdf_files_list), style = 3)

  for (f in 1:length(hdf_files_list)) {
    # f = 1
    message(sprintf("Extracting file %i / %i - %s", f, length(hdf_files_list), hdf_files_list[f]))
    
    #note this sometimes fails because e are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdf_files_list[f], '/data_collection/events/experiment/MessageEvent')

    # check tstop or tend
    tmp.events$keep_drop<- if_else(grepl(c('tStart'), tmp.events$text), "keep",
                                   if_else(grepl(c('tEnd'), tmp.events$text), "keep",
                                            if_else(tmp.events$category == "VALIDATION", "keep",
                                           "drop")))
    
    tmp.events<- subset(tmp.events, keep_drop == "keep")
  
  
    # load the eye tracking data
    tmp.eyetr  = h5read(hdf_files_list[f], '/data_collection/events/eyetracker/GazepointSampleEvent') # note this is updated to GazepointSampleEvent whereas before it was BinocularEyeSampleEvent
    

    # Get subejct id from Events
    ssid = sub("_.*", "", hdf_files_list[f])
      # substr(hdf_files_list[f], 1,3)
    # update the string before the data
    date = gsub('^.*Interostudy_\\s*|\\s*.hdf5*$', '', hdf_files_list[f])
    
  
    session = unique(tmp.events$session_id)

    
    # Create DF for trials data
    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
    names(tmp.df) = names(tmp.eyetr)
    colnames(tmp.df)
    
    # Prepare Events, keep only start/end messages
    phrases = c('tStart', 'tEnd')

    
    # unique(tmp.events$category)
    tmp.events_calib = subset(tmp.events, category == "VALIDATION")
    
    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))
# tmp.events    
    # we should have a total of XX stimuli multiplied by 4 (start and t end for stim and fix) 
    # 4 pratice + 48 trials = 52
    # 52*4 = we should should 208 rows
    # Create start/end references
    tmp.events$t_start   = NA
    tmp.events$t_end     = NA
    
    # Trial number extraction 
    tmp.events$t_no      = NA
    
    # Space for subject id
    tmp.df$ssid         = NA
    tmp.df$text<-NA
    
    for (l in 1:nrow(tmp.events)) {
      
      message(sprintf("Grabing start messages %s", tmp.events$text[l]))
      
      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
        tmp.events$t_start[l] = tmp.events$time[l]
        
        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
          tmp.events$t_end[l] = tmp.events$time[l+1]
        }
        
        else {
          message('trial start/end structure not valid')
        }
      }
      
    }
    
    message(sprintf("done grabbing messages"))
    # readline(prompt="Press [enter] to continue")
    
     message(sprintf("making screencontent"))
     # unique(tmp.events$text)
    tmp.events$screencontent <- if_else(grepl('fix', tmp.events$text), 'fixation',
                                       if_else(grepl('stim', tmp.events$text), 'stimuli', NA))
    
    
    # first let's do condition
    # update the names
    tmp.events$pratice_vs_trial<- if_else(grepl('Example', tmp.events$text), 'Pratice',
                                   if_else(grepl('IAPS', tmp.events$text), 'Trial', NA))
    
 
    # store stim code here -0 we need the content between "_" and ".jpg
    tmp.events$stimnopath<-   paste0(sub(".*_(.*?)\\.jpg.*", "\\1", tmp.events$text), ".jpg")
      
      
    
    # tmp.events$emotion_yes_no_new<- 
    
    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
 

    tmp.df$screencontent<- NA
    tmp.df$pratice_vs_trial <- NA
    # tmp.df$isfakeOrReal <- NULL
    tmp.df$stimnopath <- NA
    
    # e=10
        message(sprintf("subsetting eyetracking data"))
    
        tmp.events1$ssid<- ssid
        
        # why?
tmp.eyetr<-tmp.eyetr%>%
  mutate_if(is.raw, as.double)

for(e in 1:nrow(tmp.events1)) {
      # e = 1
      # Subset the EyeTracking data based on start/end
      tmp.raw.trial = subset(tmp.eyetr, 
                             tmp.eyetr$time >= tmp.events1$t_start[e] & tmp.eyetr$time <= tmp.events1$t_end [e]+.5)
      
      # tmp.raw.trial$tNo = tmp.events1$tNo[e]
      # tmp.events1$tNo<-NULL
      
      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
      tmp.raw.trial$pratice_vs_trial = tmp.events1$pratice_vs_trial[e]
      # tmp.raw.trial$isfakeOrReal = tmp.events1$isfakeOrReal[e]
      tmp.raw.trial$stimnopath = tmp.events1$stimnopath[e]
      # tmp.raw.trial$stim = tmp.events1$[e]
      tmp.raw.trial$ssid = ssid
      tmp.raw.trial$text = tmp.events1$text[e]
       message(sprintf("binding tmp.df"))
       
      tmp.df<- rbind(tmp.raw.trial,tmp.df)

}

        
     message(sprintf("done binding"))
    
    # Add ssid
    # tmp.df$ssID = ssid[e]
    tmp.df<- tmp.df%>%
      arrange(time)
    
     ###########################
    # Save file
    
    name = sprintf("%s_",ssid)
    message(sprintf("saving data"))
    write.csv(tmp.df, paste0(name,Sys.Date(), paste0("_gp_data.csv")))#
    # write.csv(tmp.df, paste0(name,Sys.Date(), paste0(".csv")))#
    
    ###########################
    # write calibration cali
    name2 = sprintf("%s_", ssid)
    write.csv(tmp.events_calib, paste0(name2,Sys.Date(), paste0("_gp_data_cali.csv")))#
      
    #   sprintf("ss%s_GPdata_cali", ssid)
    # write.csv(tmp.events_calib, paste0(name2,Sys.Date(), paste0(".csv")))#
    
  }
  

  message("Processing Completed.")
  tmp.df
  # close(pb)
}

# tmp.df%>%
#   group_by(text)%>%
#   mutate(diff_time = time-lag(time))%>%
#   mutate(cum_diff = sum(abs(diff_time), na.rm = T))%>%
#   ggplot(aes(cum_diff))+
#   geom_histogram()+
#   facet_grid(~screencontent)
# 
# table(is.na(tmp.df$screencontent))


```

run the fn_gp.extractor

```{r }

# not this throws ann error on problematic participants
tmp_full<- fn_gp.extractor(hdf5_file_path)

```




Now some basic cleaning 

```{r, cleaning}
# setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking/preprocessed")

# reads all individual gaze exported files into one big file

library(readr)
colnames(X101_2024_03_07_gp_data)


read_plus <- function(flnm) {
  data.table::fread(flnm, select = c( "ssid", "session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1",
                                     "left_pupil_measure2",
                                     "right_pupil_measure2",
                                     "status", 
                                     "screencontent",
                                     "pratice_vs_trial",
                                     "stimnopath",
                                     
                                     "text")) %>% 
    mutate(filename = flnm)
}


# read all clean data 

dta_eytr <-
  list.files(pattern = "*data.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))%>%
  janitor::clean_names()%>%
  subset(!is.na(ssid))

# three digits?
# Regular expression to capture the pattern before "_" and after "./"
pattern <- "\\./([0-9]+)_.*"

# Extract the pattern

dta_eytr$participant<-  sub(pattern, "\\1", dta_eytr$filename)





dta_eyetrack
unique(dta_eyetrack$screencontent)

dta_eytr$screencontent_no_na <- if_else(is.na(dta_eytr$screencontent), "rest", dta_eytr$screencontent)

dta_eytr$stimnopath_no_na <- if_else(is.na(dta_eytr$stimnopath), "rest", 
                                   if_else(dta_eytr$stimnopath == "tStart_rest1_cross", "rest",       
                                           dta_eytr$stimnopath))
  
```




#####################################################################################
# gp preprocessing funtion, checks for losses, averages gaze, pupil and pixelate
#####################################################################################

```{r, gppreprocessing}

unique(dta_eytr$status)

fn_gp_preprocessing = function(dta_eytr) {
  
  message(sprintf("step1 left gaze validity"))
  
  # transform invalid gaze into NA based on validity codes
  # to do: link the conventions file
  
#   status - https://psychopy.org/api/iohub/device/eyetracker_interface/GazePoint_Implementation_Notes.html
# Indicates if eye sample contains ‘valid’ data for left and right eyes. 
  # 0 = Eye sample is OK. 2 = Right eye data is likely invalid. 20 = Left #eye data is likely invalid. 22 = Eye sample is likely invalid.
  dta_eytr$left_gaze_x_cor<- if_else(dta_eytr$status != '20', dta_eytr$left_gaze_x, NA)
  dta_eytr$left_gaze_x_cor<- if_else(dta_eytr$status != '22', dta_eytr$left_gaze_x_cor, NA)
  dta_eytr$left_gaze_y_cor<- if_else(dta_eytr$status != '20', dta_eytr$left_gaze_y, NA)
  dta_eytr$left_gaze_y_cor<- if_else(dta_eytr$status != '22', dta_eytr$left_gaze_y_cor, NA)
  
  message(sprintf("step2 right gaze validity"))
  
  dta_eytr$right_gaze_x_cor<- if_else(dta_eytr$status != '2', dta_eytr$right_gaze_x, NA)
  #
  dta_eytr$right_gaze_x_cor<- if_else(dta_eytr$status != '22', dta_eytr$right_gaze_x_cor, NA)
  dta_eytr$right_gaze_y_cor<- if_else(dta_eytr$status != '2', dta_eytr$right_gaze_y, NA)
  dta_eytr$right_gaze_y_cor<- if_else(dta_eytr$status != '22', dta_eytr$right_gaze_y_cor, NA)

  # pupil validity
  
  message(sprintf("step3 pupil validity"))
  # pupil pixels
  dta_eytr$left_pupil_measure1<- if_else(dta_eytr$status != '20', dta_eytr$left_pupil_measure1, NA)
  dta_eytr$left_pupil_measure1<- if_else(dta_eytr$status != '22', dta_eytr$left_pupil_measure1, NA)
  
  dta_eytr$right_pupil_measure1<- if_else(dta_eytr$status != '2', dta_eytr$right_pupil_measure1, NA)
  dta_eytr$right_pupil_measure1<- if_else(dta_eytr$status != '22', dta_eytr$right_pupil_measure1, NA)
  table(is.na(dta_eytr$right_pupil_measure1))
  
  # pupil diameter
  
   dta_eytr$left_pupil_measure2<- if_else(dta_eytr$status != '20', dta_eytr$left_pupil_measure2, NA)
  dta_eytr$left_pupil_measure2<- if_else(dta_eytr$status != '22', dta_eytr$left_pupil_measure2, NA)
  
  dta_eytr$right_pupil_measure2<- if_else(dta_eytr$status != '2', dta_eytr$right_pupil_measure2, NA)
  dta_eytr$right_pupil_measure2<- if_else(dta_eytr$status != '22', dta_eytr$right_pupil_measure2, NA)
  table(is.na(dta_eytr$right_pupil_measure2))
  
  # check gazepoint out of bounds and repixelate 
  
  # screen=1, size=array([1920, 1080]) # update here accordingly
  
  # (1920/2 = 960 by 1080/2 = 540 add half to normalised coordinates from psychopy)
  # update according to setup
  
  message(sprintf("step 4 cutting off screen in points and repixelate"))
  
  dta_eytr$left_gaze_x_cor<- if_else(dta_eytr$left_gaze_x_cor >= -960 & dta_eytr$left_gaze_x_cor <= 960, dta_eytr$left_gaze_x_cor, NA)
  dta_eytr$right_gaze_x_cor<- if_else(dta_eytr$right_gaze_x_cor >= -960 & dta_eytr$right_gaze_x_cor <= 960, dta_eytr$right_gaze_x_cor, NA)
  
  dta_eytr$left_gaze_y_cor<- if_else(dta_eytr$left_gaze_y_cor >= -540 & dta_eytr$left_gaze_y_cor <= 540, dta_eytr$left_gaze_y_cor, NA)
  dta_eytr$right_gaze_y_cor<- if_else(dta_eytr$right_gaze_y_cor >= -540 & dta_eytr$right_gaze_y_cor <= 540, dta_eytr$right_gaze_y_cor, NA)
  
  dta_eytr$left_gaze_x_cor_pix<- dta_eytr$left_gaze_x_cor+960
  dta_eytr$right_gaze_x_cor_pix<- dta_eytr$right_gaze_x_cor+960
  
  dta_eytr$left_gaze_y_cor_pix<- dta_eytr$left_gaze_y_cor+540
  dta_eytr$right_gaze_y_cor_pix<- dta_eytr$right_gaze_y_cor+540
  
  # is left or right an NA
  
  dta_eytr$left_na<- is.na(dta_eytr$left_gaze_x_cor) 
  dta_eytr$right_na<- is.na(dta_eytr$right_gaze_x_cor)
  dta_eytr$both_na<- if_else(dta_eytr$left_na == TRUE & dta_eytr$right_na == TRUE, TRUE, FALSE)
  
  message(sprintf("step5 gaze x  means"))
  # create gaze means betwenn left and right eye
  
  dta_eytr$gaze_x_cor<-if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_gaze_x_cor,
                              if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_gaze_x_cor,
                                      ((dta_eytr$left_gaze_x_cor + dta_eytr$right_gaze_x_cor)/2)))
  message(sprintf("step6 gaze y means"))
  
  dta_eytr$gaze_y_cor<-if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_gaze_y_cor,
                              if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_gaze_y_cor,
                                      ((dta_eytr$left_gaze_y_cor + dta_eytr$right_gaze_y_cor)/2)))
  
  message(sprintf("step6 repixelate gaze means"))
  
  dta_eytr$gaze_x_cor_pix<- dta_eytr$gaze_x_cor + 960
  # min(dta_eytr$gaze_x_cor_pix, na.rm = TRUE)
  
  dta_eytr$gaze_y_cor_pix<- dta_eytr$gaze_y_cor+540
  # min(dta_eytr$gaze_y_cor_pix, na.rm = TRUE)
  
  # clean_pupil
  
  message(sprintf("cleaning pupil"))
  
  # max(dta_eytr$left_pupil_measure1)
  
  dta_eytr$pupil<- if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_pupil_measure1,
                          if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_pupil_measure1,
                                  ((dta_eytr$left_pupil_measure1 + dta_eytr$right_pupil_measure1)/2)))
  
  
  # diameter
  dta_eytr$pupil_d<- if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_pupil_measure2,
                          if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_pupil_measure2,
                                  ((dta_eytr$left_pupil_measure2 + dta_eytr$right_pupil_measure2)/2)))
  
  
  # dta_eytr$trackloss<- if_else(dta_eytr$status > 0, TRUE, FALSE)
  dta_eytr$trialunq<- paste0(dta_eytr$pratice_vs_trial,"_",paste0(dta_eytr$screencontent,"_", paste0(dta_eytr$stim)))
  dta_eytr$distance_mm = 600
  
  # min(dta_eytr$pupil, na.rm = TRUE)
  # max(dta_eytr$pupil, na.rm = TRUE)
  # colnames(dta_eytr)
  dta_eytr<- dta_eytr%>%
    # group_by(ssid)
    arrange(ssid,time)
}

```

repixelated and minimally processed (e.g. deleting invalid samples), merging left and right eye
```{r}
rm(gp_preprocessing)
dta_eytr_rpx<- fn_gp_preprocessing(dta_eytr)


colnames(dta_eytr_rpx) 
 
options(scipen = 999)
range(dta_eytr_rpx$pupil, na.rm = TRUE)
range(dta_eytr_rpx$pupil_d, na.rm = TRUE)
range(dta_eytr_rpx$gaze_y_cor_pix, na.rm = TRUE)
range(dta_eytr_rpx$gaze_x_cor_pix, na.rm = TRUE) 

# split and export per participant

colnames(dta_eytr_rpx)

dta_eytr_rpx<- dta_eytr_rpx%>%
  group_by(participant)%>%
  arrange(time)


# Split the dataframe based on 'group_column'
list_of_dfs <- split(dta_eytr_rpx, dta_eytr_rpx$participant)

colnames(dta_eytr_rpx)

# Iterate over the list to write each dataframe to a CSV file
lapply(names(list_of_dfs), function(x) {
  csv_filename <- paste0(x, "_dta_eytr_rpx.csv")
  write.csv(list_of_dfs[[x]], csv_filename, row.names = FALSE)
})

```
quick checks
```{r}
dta_eytr_rpx%>%
  group_by(participant)%>%
  arrange(time)%>%
  
  mutate(tmp_group = paste0(stimnopath_no_na,screencontent_no_na))%>%
  group_by(tmp_group)%>%
 
  subset(participant == 117& screencontent_no_na != "rest")%>%
   mutate(time_rezero = time - first(time)) %>%
  ggplot(aes(time_rezero, gaze_x_cor_pix))+
    geom_line()+
    geom_line(aes(y = gaze_y_cor_pix), colour = "blue")+
  facet_grid(~screencontent_no_na)+
  geom_vline(xintercept = 6.6, linetype = "dashed", colour ="red")+
  ylab("gaze coordinates")



dta_eytr_rpx%>%
  group_by(participant)%>%
  arrange(time)%>%
  
  mutate(tmp_group = paste0(stimnopath_no_na,screencontent_no_na))%>%
  group_by(tmp_group)%>%
 
  subset(participant == 117& screencontent_no_na != "rest")%>%
   mutate(time_rezero = time - first(time)) %>%
  ggplot(aes(time_rezero, pupil))+
    geom_smooth(aes(group = stimnopath_no_na), se = F)+
    # geom_line(aes(y = gaze_y_cor_pix), colour = "blue")+
  facet_grid(~screencontent_no_na)+
  geom_vline(xintercept = 6.6, linetype = "dashed", colour ="red")+
  ylab("gaze coordinates")



```



######################
TO ADAPT CODE BELOW
To DO
# rezeroing times by trial, by participants
Continue here

```{r}
# create start at every screen content
# Preview unique screen contents and dataset structure
print(unique(dta_gaze_clean$text))
print(colnames(dta_gaze_clean))

# only run this is the previous processing code is not fixed where trialunq includes pratice vs trial
# dta_gaze_clean$trialunq<- paste0(dta_gaze_clean$pratice_vs_trial,"_",paste0(dta_gaze_clean$screencontent,"_", paste0(dta_gaze_clean$stimnopath)))

# Arrange data by participant ID and time, then identify the first occurrence of each trial

dta_gaze_clean$trialunq

dta_gaze_clean <- dta_gaze_clean %>%
  arrange(ssid, time) %>%
  group_by(ssid, screencontent) %>%
  mutate(is_firststart = !duplicated(trialunq)) # Use '!' to correctly identify the first start

# Preview the data to ensure the above operation worked as intended
print(head(dta_gaze_clean))

# Create a zero-time column where the first occurrence of each trial is marked with its time, others as NA
dta_gaze_clean <- dta_gaze_clean %>%
  mutate(zero = if_else(is_firststart, time, NA_real_)) # Use NA_real_ for consistency in numeric columns

# Propagate the zero times down each group to fill in the NAs
dta_gaze_clean <- dta_gaze_clean %>%
  group_by(ssid, screencontent, trialunq) %>%
  fill(zero, .direction = "down")%>% # Explicitly mention direction for clarity
  ungroup()

# Calculate the time relative to zero for each trial
dta_gaze_clean <- dta_gaze_clean %>%
  mutate(timerezero = time - zero)

# Arrange by time for final organization, if necessary
dta_gaze_clean <- dta_gaze_clean %>%
  arrange(ssid,time)

# Optionally, print unique zero times to verify the operation
print(unique(dta_gaze_clean$zero))

# Results stored in 'dta_gaze_clean' with 'timerezero' reflecting time since trial start



# let's check to see if it looks fine
range(dta_gaze_clean$timerezero, na.rm = TRUE)
max(dta_gaze_clean$timerezero, na.rm = TRUE) # `
# now this looks about right ~10~11sec

dta_gaze_clean%>%
subset(ssid == 1 & dta_gaze_clean$screencontent == "stimuli") %>%
ggplot( aes(timerezero, pupil ))+
  geom_smooth(aes(group = stimnopath), se = F, size = .1)


```

debug abnormally long timerezero
```{r eval=FALSE, include=FALSE}



tmp_test<- dta_gaze_clean%>%
subset(ssid == 1 & dta_gaze_clean$screencontent == "stimuli"&
         stimnopath == "10_22__kitchen_still__8YQ2EUQP.mp4")

the issue smees to be because thios sgtimuli is used in pratice and stimuli, so the timerezero is not treatign this trial as unique


debug
tmp_toolong<- dta_gaze_clean%>%
  subset(timerezero>10)

tmp_less10<- dta_gaze_clean%>%
  subset(timerezero<10)

# why do we have some abnormally high trials duration randomly

tmpsd5<- tmp_toolong%>%subset(ssid == 38)
tmpsd5_full<- dta_gaze_clean%>%subset(ssid == 38)

# data from one participant that is too long
tmpsd5%>%
  ggplot(aes(gaze_x_cor_pix, gaze_y_cor_pix))+
  geom_point()+
  facet_grid(~screencontent)


tmpsd5_full%>%
  ggplot(aes(gaze_x_cor_pix, gaze_x_cor_pix))+
  geom_point()+
  facet_grid(~screencontent)

tmpsd5%>%
  ggplot(aes(time, gaze_x_cor_pix))+
  geom_point(size = .1)
tmpsd5_full%>%
  ggplot(aes(time, gaze_x_cor_pix))+
  geom_point(size = .1)

table(tmpsd5$stimnopath)

 

```




# create a new time rezero where before stim start, time is negative
```{r}

dta_gaze_clean_10s<- dta_gaze_clean%>%
  subset(timerezero <=10)

library(dplyr)

dta_gaze_clean_10s 

dta_gaze_clean_10s<- dta_gaze_clean_10s %>%
  group_by(ssid, stimnopath) %>%
  arrange(ssid, time) %>%
  mutate(general_time = row_number() - 1) %>% # This assumes your data starts from 0 and increments
  group_by(ssid, stimnopath, screencontent, .add = TRUE) %>%
  mutate(
    backward_time = max(timerezero) - timerezero, # Calculate backward time for fixation
    time_backward = case_when(
      screencontent == "stimuli" ~ timerezero, # Use timezero directly for forward time in stimuli
      screencontent == "fixation" ~ -backward_time, # Use negative backward time for fixation
      TRUE ~ NA_real_ # Fallback case
    )
  ) %>%
  ungroup()



dta_gaze_clean_10s%>%
subset(ssid == 1) %>%
ggplot( aes(timerezero, pupil ))+
  geom_smooth(aes(group = stimnopath), se = F, size = .1)+
  geom_vline(xintercept = 0, linetype = "dashed")+
    facet_grid(~screencontent)+
  ylim(15,30)+
  xlim(-2,10)


dta_gaze_clean_10s%>%
subset(ssid == 1) %>%
ggplot( aes(time_backward, pupil ))+
  geom_smooth(aes(group = stimnopath), se = F, size = .1)+
    geom_vline(xintercept = 0, linetype = "dashed")+
    facet_grid(~screencontent)+
    ylim(15,30)+
   xlim(-2,10)

# gaze quick check
dta_gaze_clean_10s%>%
subset(ssid == 1) %>%
ggplot( aes(time_backward, gaze_ ))+
  geom_smooth(aes(group = stimnopath), se = F, size = .1)+
    geom_vline(xintercept = 0, linetype = "dashed")+
    facet_grid(~screencontent)+
    ylim(15,30)+
   xlim(-2,10)
  

```


check for an issue where the gazepoint would store duplicat times within each participant

```{r}

library(dplyr)

# Detect and flag duplicates based on event_id and time within each ssid
dta_gaze_clean_10s <- dta_gaze_clean_10s %>%
  group_by(ssid) %>%
  mutate(duplicated_event_id = duplicated(event_id) | duplicated(event_id, fromLast = TRUE),
         duplicated_time = duplicated(time) | duplicated(time, fromLast = TRUE)) %>%
  ungroup()


dta_gaze_clean_10s$event_id
table(dta_gaze_clean_10s$duplicated_event_id)
table(dta_gaze_clean_10s$duplicated_time)

# tmp_test<- subset(dta_gaze_clean_10s,duplicated_event_id == TRUE )
dta_gaze_clean_10s$screencontent

# tmp_test_stim<- dta_gaze_clean_10s%>%subset(screencontent == "stimuli" & ssid == 10)


table(tmp_test_stim$trialunq)
dta_gaze_clean_10s$pratice_vs_trial

dta_gaze_clean_10s%>%
  subset(pratice_vs_trial!= "Pratice"& screencontent!= "fixation") %>%
  group_by(ssid,stimnopath)%>%
  mutate(nrows_tmp = n())%>%
  ggplot(aes(ssid, stimnopath, fill = nrows_tmp))+
  geom_tile()
  # facet_grid(~screencontent)


# 1500 is what we would expectfor 15-0 hz,

dta_gaze_clean_10s%>%
  subset(pratice_vs_trial!= "Pratice"& screencontent!= "fixation") %>%
  group_by(ssid,stimnopath)%>%
  mutate(nrows_tmp = n())%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(ssid, nrows_tmp))+
  geom_point()+
  geom_bar(stat = "identity", width = .1) 


options(scipen = 999)
dta_gaze_clean_10s%>%
  # subset(pratice_vs_trial!= "Pratice"& screencontent!= "fixation") %>%
  group_by(ssid)%>%
  mutate(sampling_iti = time-lag(time))%>% #0.0062870 this is the expected for 150hz
    mutate(event_iti = event_id-lag(event_id))%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(event_iti))+
  geom_histogram(nbin = 300)


# no need to exclude duplicates
# i gues the question is wether when rem,oving duplciates do we get normal ranges or abnormally longeoneway.test(




dta_gaze_clean_10s%>%
subset(duplicated_event_id == FALSE)%>%
  group_by(ssid)%>%
  mutate(sampling_iti = time-lag(time))%>% #0.0062870 this is the expected for 150hz
    mutate(event_iti = event_id-lag(event_id))%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(sampling_iti))+
  geom_histogram(nbins = 300)+
    xlim(-.01,.01)
  


dta_gaze_clean_10s%>%
  subset(duplicated_event_id == FALSE)%>%
  subset(pratice_vs_trial!= "Pratice"& screencontent!= "fixation") %>%
  group_by(ssid,stimnopath)%>%
  mutate(nrows_tmp = n())%>%
  ggplot(aes(ssid, stimnopath, fill = nrows_tmp))+
  geom_tile()
  # facet_grid(~sc

```

# Filter out rows where either event_id or time is duplicated within each ssid

```{r}
nrow(dta_gaze_clean_10s_nodup )/nrow(dta_gaze_clean_10s)


dta_gaze_clean_10s_nodup <- dta_gaze_clean_10s %>%
  filter(!duplicated_event_id & !duplicated_time)



         

```



select variables for gazepath
```{r}
dta_gaze_clean_10s_nodup$subject<- dta_gaze_clean_10s_nodup$ssid
dta_gaze_clean_10s_nodup$trial <- dta_gaze_clean_10s_nodup$trialUnq


colnames(dta_gaze_clean_10s_nodup)
# range(dta_gaze_clean_10s_nodup$pup_interp)

colnames(dta_gaze_clean_10s_nodup)

dta_gaze_clean_10s_nodup$distance<- 600



dta_gaze_clean_10s_nodup$trackloss<- if_else(is.na(dta_gaze_clean_10s_nodup$gaze_x_cor_pix) == TRUE, 0, 
                         if_else(is.na(dta_gaze_clean_10s_nodup$gaze_y_cor_pix) == TRUE, 0, 1))
unique(dta_gaze_clean_10s_nodup$trackloss)

# compute proportion of lost data

dta_gaze_clean_10s_nodup$trialunq

dta_gaze_clean_10s_nodup <- dta_gaze_clean_10s_nodup %>%
  group_by(ssid, trialunq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
  ungroup()


# check to see this is right

dta_gaze_clean_10s_nodup%>%
  ggplot(aes(gaze_loss_prop))+
  geom_histogram()

dta_gaze_clean_10s_nodup%>%
  ggplot(aes(gaze_valid_prop))+
  geom_histogram()
```
