---
title: "pre_process_of"
author: "Helio"
date: "2024-03-11"
output: html_document
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, include = FALSE)

# Set working directory to the folder containing subfolders with CSV files
setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/OpenFace Processed")
# Get a list of all CSV files within subfolders using list.files() and recursive = TRUE
# file_list <- list.files(pattern = "\\.csv$", recursive = FALSE)




# get a list of all the CSV files in your folder and its subfolders
file_list <- list.files(pattern = "\\.csv$", recursive = FALSE, full.names = TRUE)

# read the CSV files into a list of data frames, and store the filename as a new column in each data frame
library(dplyr)

install.packages("pbapply")

library(pbapply)
library(dplyr)
library(janitor)

# fix 103103
tmp_data_of_list <- lapply(file_list, function(file) {
   print(paste("Processing file", file))
  data <- read.csv(file) %>%
    select(frame, timestamp, confidence, success, matches("_r")) %>%
    janitor::clean_names()
  
  # Modification here: Create a new data frame with the filename column
  data <- mutate(data, filename = file)
  
  # Now group and summarize
  data %>%
    group_by(filename) %>%
    summarise_if(is.numeric, mean, na.rm = TRUE)
}) # You can customize the type of progress bar with the progress argument


# Combine the data frames into a single data frame
dta_of_agg <- bind_rows(tmp_data_of_list)

saveRDS(dta_of_agg, "dta_of_agg.rds")
dta_of_agg<- dta_of_agg%>%
  select(!matches(c("pose", "p_")))

rm(all_sessions_data, tmp_split_df)
```
# explore this for readign specific co;lumsn from the getgo
library(readr)
library(dplyr)

# Function to read CSV with specific and pattern-based columns
read_csv_with_pattern <- function(file, static_cols, pattern) {
  # Read the header to get column names
  header <- read_csv(file, n_max = 0)
  
  # Identify columns that match the pattern
  pattern_cols <- names(header)[grepl(pattern, names(header))]
  
  # Combine static columns and pattern-matched columns, remove duplicates
  cols_to_read <- unique(c(static_cols, pattern_cols))
  
  # Read only the selected columns from the CSV
  data <- read_csv(file, col_select = cols_to_read)
  
  # Optionally, perform further data processing here
  data <- mutate(data, filename = file)
  
  return(data)
}

# Example usage
file_list <- c("path/to/your/file1.csv", "path/to/your/file2.csv")
static_cols <- c("frame", "timestamp", "confidence", "success")
pattern <- "_r"

# Apply the function to each file in the list
tmp_data_of_list <- lapply(file_list, function(file) {
  read_csv_with_pattern(file, static_cols, pattern)
})

# Combine the data frames into a single data frame, if needed
data_combined <- bind_rows(tmp_data_of_list)


```{r}
dta_of_agg

```

unique(dta_off_agg$filename)


```{r}

dta_of_agg$participant<-  sub("./(.+?)_.*", "\\1", dta_of_agg$filename)

unique(dta_of_agg$participant)                             
dta_of_agg$participant<- substr(dta_of_agg$participant,1,3)

# create variables

dta_of_agg<- dta_of_agg%>%
  mutate(
  stim_iaps = sub(".*tStart_([^_]*).IAPS.*", "\\1", filename),
  condition= if_else(grepl('Example', filename), 'Pratice',
                                   if_else(grepl('IAPS', filename), 'Trial', "rest")),
  social_nonsocial = if_else(participant<200,"nonsocial", "social"))%>%
    mutate(trial_no_all = sub(".*IAPS_([^.]*).csv", "\\1", filename))



dta_of_agg<- dta_of_agg[,c(1:26,28)]
colnames(dta_of_agg)

dta_of_agg<- dta_of_agg%>%
mutate(trial_no_all = if_else(grepl("rest", filename),1,
                                         if_else(grepl("Stimuli_0.csv", trial_no_all),2,
                                         if_else(grepl("Stimuli_1.csv", trial_no_all),3,   
                                                 if_else(grepl("Stimuli_2.csv", trial_no_all),4, 
                                                 if_else(grepl("Stimuli_3.csv", trial_no_all),5,         
                                                          if_else(condition == "Trial", 
                                                            as.numeric(trial_no_all)+6, NA)))))))


unique(dta_of_agg$trial_no_all)

colnames(dta_of_agg)


# average across austres

library(dplyr)

# Assuming 'data' is your dataframe

# Step 1: Dynamically identify AU variables
au_columns <- names(dta_of_agg)[grepl("au\\d+_r$", names(dta_of_agg))]

# Step 2 and 3: Compute row-wise mean for AU variables and group by desired variables
dta_of_agg<- dta_of_agg %>%
  rowwise() %>%
  mutate(au_average = mean(c_across(all_of(au_columns)), na.rm = TRUE))
  # ungroup() %>%
  # group_by(participant, condition, ... ) %>%
  # Step 4: Summarize to compute the mean of AU averages for each group
  # summarise(au_mean = mean(au_average, na.rm = TRUE))

dta_of_agg$au_average

```

combine with psychpopy

```{r}
dta_gsr

saveRDS(dta_gsr, "dta_gsr.rds")

rm(dta_gsr, X126_dta_gsr_trig , X126_dta_gsr_trig_before_trigger_2, X126_dta_gsr_trig_filtered,
   X136_Session1_GSRPulse_Calibrated_PC, X136_Session1_GSRPulse_Calibrated_SD)

```


dta_of_agg











```{r eval=FALSE, include=FALSE}
dta_OF_combined_tmp<- dta_OF_combined [,c(680:717, 719:721,1,3)]%>%
  # subset(condition == "IAPS")%>%
  gather(key,au_value, - filename,-ssid,-frame, - timestamp, -stim_iaps, -trial_no_pract_and_test, -pratice_vs_trial, -condition)%>%
  # mutate(start+time = if_else(timestamp == 2, timestamp))
  mutate(AU_c_r = substr(key ,6,6))%>%
  subset(AU_c_r == "r")


data_psypy1$participant

dta_psypy1

unique(dta_OF_combined_tmp$trial_no_pract_and_test)
dta_OF_combined_tmp%>%
  group_by( filename,ssid, stim_iaps, trial_no_pract_and_test, pratice_vs_trial, condition,key)%>%
  summarise_if(is.numeric, mean)%>%
  left_join(data_psypy1%>%subset(participant == 116), by = c("trial_no_pract_and_test",
                                                             "stim_iaps",
                                                            "condition"))%>%
  group_by(key)%>%
  # mutate(au_value = scale(au_value))%>%
  group_by(trial_no_pract_and_test, emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(val_slider_response, au_value))+
  geom_point()



dta_OF_combined_tmp%>%
  group_by( filename,ssid, stim_iaps, trial_no_pract_and_test, pratice_vs_trial, condition,key)%>%
  summarise_if(is.numeric, mean)%>%
  left_join(data_psypy1%>%subset(participant == 116), by = c("trial_no_pract_and_test",
                                                             "stim_iaps",
                                                            "condition"))%>%
  group_by(key)%>%
  mutate(au_value = scale(au_value))%>%
  group_by(trial_no_pract_and_test, emotioncategory)%>%
  subset(!is.na(emotioncategory))%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(emotioncategory, au_value))+
  # geom_point()+
  stat_summary(geom = "pointrange")



dta_OF_combined_tmp%>%
  group_by( filename,ssid, stim_iaps, trial_no_pract_and_test, pratice_vs_trial, condition,key)%>%
  summarise_if(is.numeric, mean)%>%
  left_join(data_psypy1%>%subset(participant == 116), by = c("trial_no_pract_and_test",
                                                             "stim_iaps",
                                                            "condition"))%>%
  group_by(key)%>%
  # mutate(au_value = scale(au_value))%>%
  group_by(trial_no_pract_and_test, emotioncategory,key)%>%
  subset(!is.na(emotioncategory) & au_value>.3)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(key, au_value))+
  # geom_point()+
  stat_summary(geom = "pointrange")+
  facet_grid(~emotioncategory)
  

```
  


dta_OF_combined_select_stimuli_agg<- dta_OF_combined_select_stimuli%>%
  group_by(ssid, practice_stim,stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = T)

colnames(as.data.frame(dta_OF_combined_select_stimuli_agg))
length(colnames(dta_OF_combined_select_stimuli_agg))

tmp_AUnames

tmp_AUnames<- c("ssid" ,         
                "practice_stim", 
                "stimIAPS"   ,   
                "frame"    ,     
                "face_id"      , 
                "timestamp"   ,  
                "confidence" ,   
                "success",
 "AU01_r_Inner_brow_raiser",   
 "AU02_r_Outer_brow_raiser",   
 "AU04_r_Brow_lowerer",       
"AU05_r_Upper_lid_raiser",    
"AU06_r_Cheek_raiser",        
"AU07_r_Lid_tightener",       
"AU09_r_Nose_wrinkler",      
 "AU10_r_Upper_lip_raiser",    
"AU12_r_Lip_corner_puller",   
"AU14_r_Dimpler",             
"AU15_r_Lip_corner_depressor",
 "AU17_r_Chin_raiser",         
"AU20_r_Lip_stretcher",       
"AU23_r_Lip_tightener",      
"AU25_r_Lips_part",          
"AU26_r_Jaw_drop",            
"AU45_r_Blink",               
"AU01_c_Inner_brow_raiser",   
"AU02_c_Outer_brow_raiser",  
"AU04_c_Brow_lowerer",        
"AU05_c_Upper_lid_raiser",    
"AU06_c_Cheek_raiser",        
"AU07_c_Lid_tightener",      
"AU09_c_Nose_wrinkler",      
"AU10_c_Upper_lip_raiser",    
"AU12_c_Lip_corner_puller",   
"AU14_c_Dimpler",            
 "AU15_c_Lip_corner_depressor",
"AU17_c_Chin_raiser",        
"AU20_c_Lip_stretcher",       
"AU23_c_Lip_tightener",      
"AU25_c_Lips_part",          
"AU26_c_Jaw_drop",    
"AU28_c_Lip_suck",    
"AU45_c_Blink")
tmp_AUnames

dta_OF_combined_select_stimuli_agg<- dta_OF_combined_select_stimuli_agg2
dta_OF_combined_select_stimuli_agg2<- dta_OF_combined_select_stimuli_agg
colnames(dta_OF_combined_select_stimuli_agg)<- tmp_AUnames

dta_OF_combined_select_stimuli_agg
# AU names

# merge with the rest of the data
dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze

dta_OF_combined_select_stimuli_agg$stimIAPS<-as.character(dta_OF_combined_select_stimuli_agg$stimIAPS)
dta_OF_combined_select_stimuli_agg$ssid<- as.double(dta_OF_combined_select_stimuli_agg$ssid)
unique(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze$stimIAPS)


