---
title: "pre_process_of"
author: "Helio"
date: "2024-03-11"
output: html_document
---

to do
1. read files
2. do some processing (here)
- potentially a basic smoothing to reduce jitter
3. aggregate (mean per participant and stimuli)

note also aggregate                 "confidence" ,   and  "success", sop we can know how well the stim did


```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, include = FALSE)


# Set working directory to the folder containing subfolders with CSV files
setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/OpenFace Processed")
# Get a list of all CSV files within subfolders using list.files() and recursive = TRUE
# file_list <- list.files(pattern = "\\.csv$", recursive = FALSE)

# get a list of all the CSV files in your folder and its subfolders
file_list <- list.files(pattern = "\\.csv$", recursive = FALSE, full.names = TRUE)

# Load necessary libraries
library(dplyr)
library(janitor)
library(zoo) # For rollmean
library(stringr) # For str_remove

# Sample rate and fixed window size
fs <- 30 # Sample rate of face data in Hz
window_size_ms <- 500 # Fixed window size in milliseconds for all files

# Define smoothing function
fn_smooth_of <- function(signal, sampling_rate, window_size_ms) {
  # Calculate window size in samples
  # Ensure window size is at least 3 samples and odd for symmetry
  window_size <- max(3, round(window_size_ms / 1000 * sampling_rate))
  if (window_size %% 2 == 0) window_size <- window_size + 1
  
  # Add zero padding on both sides to handle edge effects
  padded_signal <- c(rep(0, window_size), signal, rep(0, window_size))
  
  # Apply mean smoothing using a rolling window
  smoothed_signal <- rollmean(padded_signal, window_size, fill = NA, align = "center")
  
  # Remove padding to match original signal length
  smoothed_signal <- smoothed_signal[(window_size + 1):(length(smoothed_signal) - window_size)]
  
  # Ensure the final signal matches the original signal length
  final_signal <- smoothed_signal[1:length(signal)]
  
  return(final_signal)
}

# Define baseline correction function - might need to do soem checks
fn_baseline_correction <- function(signal, baseline_samples = 20) {
  # Calculate baseline as the mean of the first 'baseline_samples' samples
  baseline <- mean(signal[1:baseline_samples], na.rm = TRUE)
  
  # Subtract baseline from each sample in the signal
  corrected_signal <- signal - baseline
  
  return(corrected_signal)
}

# Process all files in the file list
tmp_data_of_list <- lapply(file_list, function(file) {
  print(paste("Processing file", file))
  
  # Read CSV file and select relevant columns
  data <- read.csv(file) %>%
    select(frame, timestamp, confidence, success, matches("AU")) %>%
    janitor::clean_names()
  
  # Add filename as a new column for identification
  data <- mutate(data, filename = basename(file))
  
  # Apply smoothing function to all columns containing "au" (Action Units)
  # Use the fixed window_size_ms for all files
  data <- data %>%
    mutate(across(contains("au"), 
                  .fns = list(smt = ~fn_smooth_of(., fs, window_size_ms)), 
                  .names = "{.col}_smt"))

  # Apply baseline correction to the smoothed columns
  data <- data %>%
    mutate(across(ends_with("_smt"), 
                  .fns = list(bascor = ~fn_baseline_correction(.)), 
                  .names = "{.col}_bascor"))
  
  # Generate output filename with "_smooth" suffix
  output_file <- file.path(output_directory, paste0(str_remove(basename(file), ".csv"), "_smooth.csv"))
  
  # Save processed data to new CSV file
  write.csv(data, output_file, row.names = FALSE)
  
  # Summarize numeric data, grouping by filename
  # This summary will be used to combine results from all files
  summary_data <- data %>%
    group_by(filename) %>%
    summarise(across(where(is.numeric), mean, na.rm = TRUE))
  
  return(summary_data)
})

# Combine all summary data into one data frame
dta_of_combined_summary <- bind_rows(tmp_data_of_list)

# Optionally, save the combined summary to a CSV file
summary_output_file <- file.path(output_directory, "combined_summary.csv")
write.csv(dta_of_combined_summary, summary_output_file, row.names = FALSE)

# Print or return combined_summary if needed
print(dta_of_combined_summary)


```

Save RDS and environment files (update accordingly)
```{r}

saveRDS(dta_of_combined_summary, "dta_of_agg.rds")
dta_of_agg<- dta_of_agg%>%
  select(!matches(c("pose", "p_")))

dta_of_agg<- dta_of_combined_summary
```

some checks

- load a few of the exported timersies procesed files and check how the correction differs between original; AU, smooth and baseliene corrected

unique(dta_off_agg$filename)


```{r}

dta_of_agg$participant<-  sub("./(.+?)_.*", "\\1", dta_of_agg$filename)

unique(dta_of_agg$participant)                             
dta_of_agg$participant<- substr(dta_of_agg$participant,1,3)

# create variables

dta_of_agg<- dta_of_agg%>%
  mutate(
  stim_iaps = sub(".*tStart_([^_]*).IAPS.*", "\\1", filename),
  condition= if_else(grepl('Example', filename), 'Pratice',
                                   if_else(grepl('IAPS', filename), 'Trial', "rest")),
  social_nonsocial = if_else(participant<200,"nonsocial", "social"))%>%
    mutate(trial_no_all = sub(".*IAPS_([^.]*).csv", "\\1", filename))



dta_of_agg<- dta_of_agg[,c(1:26,28)]
colnames(dta_of_agg)

dta_of_agg<- dta_of_agg%>%
mutate(trial_no_all = if_else(grepl("rest", filename),1,
                                         if_else(grepl("Stimuli_0.csv", trial_no_all),2,
                                         if_else(grepl("Stimuli_1.csv", trial_no_all),3,   
                                                 if_else(grepl("Stimuli_2.csv", trial_no_all),4, 
                                                 if_else(grepl("Stimuli_3.csv", trial_no_all),5,         
                                                          if_else(condition == "Trial", 
                                                            as.numeric(trial_no_all)+6, NA)))))))


unique(dta_of_agg$trial_no_all)

colnames(dta_of_agg)


# average across austres

library(dplyr)

# Assuming 'data' is your dataframe

# Step 1: Dynamically identify AU variables
au_columns <- names(dta_of_agg)[grepl("au\\d+_r$", names(dta_of_agg))]

# Step 2 and 3: Compute row-wise mean for AU variables and group by desired variables
dta_of_agg<- dta_of_agg %>%
  rowwise() %>%
  mutate(au_average = mean(c_across(all_of(au_columns)), na.rm = TRUE))
  # ungroup() %>%
  # group_by(participant, condition, ... ) %>%
  # Step 4: Summarize to compute the mean of AU averages for each group
  # summarise(au_mean = mean(au_average, na.rm = TRUE))

dta_of_agg$au_average

```





some checks
```{r eval=FALSE, include=FALSE}
dta_OF_combined_tmp<- dta_OF_combined [,c(680:717, 719:721,1,3)]%>%
  # subset(condition == "IAPS")%>%
  gather(key,au_value, - filename,-ssid,-frame, - timestamp, -stim_iaps, -trial_no_pract_and_test, -pratice_vs_trial, -condition)%>%
  # mutate(start+time = if_else(timestamp == 2, timestamp))
  mutate(AU_c_r = substr(key ,6,6))%>%
  subset(AU_c_r == "r")


data_psypy1$participant

dta_psypy1

unique(dta_OF_combined_tmp$trial_no_pract_and_test)
dta_OF_combined_tmp%>%
  group_by( filename,ssid, stim_iaps, trial_no_pract_and_test, pratice_vs_trial, condition,key)%>%
  summarise_if(is.numeric, mean)%>%
  left_join(data_psypy1%>%subset(participant == 116), by = c("trial_no_pract_and_test",
                                                             "stim_iaps",
                                                            "condition"))%>%
  group_by(key)%>%
  # mutate(au_value = scale(au_value))%>%
  group_by(trial_no_pract_and_test, emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(val_slider_response, au_value))+
  geom_point()



dta_OF_combined_tmp%>%
  group_by( filename,ssid, stim_iaps, trial_no_pract_and_test, pratice_vs_trial, condition,key)%>%
  summarise_if(is.numeric, mean)%>%
  left_join(data_psypy1%>%subset(participant == 116), by = c("trial_no_pract_and_test",
                                                             "stim_iaps",
                                                            "condition"))%>%
  group_by(key)%>%
  mutate(au_value = scale(au_value))%>%
  group_by(trial_no_pract_and_test, emotioncategory)%>%
  subset(!is.na(emotioncategory))%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(emotioncategory, au_value))+
  # geom_point()+
  stat_summary(geom = "pointrange")



dta_OF_combined_tmp%>%
  group_by( filename,ssid, stim_iaps, trial_no_pract_and_test, pratice_vs_trial, condition,key)%>%
  summarise_if(is.numeric, mean)%>%
  left_join(data_psypy1%>%subset(participant == 116), by = c("trial_no_pract_and_test",
                                                             "stim_iaps",
                                                            "condition"))%>%
  group_by(key)%>%
  # mutate(au_value = scale(au_value))%>%
  group_by(trial_no_pract_and_test, emotioncategory,key)%>%
  subset(!is.na(emotioncategory) & au_value>.3)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(key, au_value))+
  # geom_point()+
  stat_summary(geom = "pointrange")+
  facet_grid(~emotioncategory)


```
  



tmp_AUnames

tmp_AUnames<- c("ssid" ,         
                "practice_stim", 
                "stimIAPS"   ,   
                "frame"    ,     
                "face_id"      , 
                "timestamp"   ,  
                "confidence" ,   
                "success",
 "AU01_r_Inner_brow_raiser",   
 "AU02_r_Outer_brow_raiser",   
 "AU04_r_Brow_lowerer",       
"AU05_r_Upper_lid_raiser",    
"AU06_r_Cheek_raiser",        
"AU07_r_Lid_tightener",       
"AU09_r_Nose_wrinkler",      
 "AU10_r_Upper_lip_raiser",    
"AU12_r_Lip_corner_puller",   
"AU14_r_Dimpler",             
"AU15_r_Lip_corner_depressor",
 "AU17_r_Chin_raiser",         
"AU20_r_Lip_stretcher",       
"AU23_r_Lip_tightener",      
"AU25_r_Lips_part",          
"AU26_r_Jaw_drop",            
"AU45_r_Blink",               
"AU01_c_Inner_brow_raiser",   
"AU02_c_Outer_brow_raiser",  
"AU04_c_Brow_lowerer",        
"AU05_c_Upper_lid_raiser",    
"AU06_c_Cheek_raiser",        
"AU07_c_Lid_tightener",      
"AU09_c_Nose_wrinkler",      
"AU10_c_Upper_lip_raiser",    
"AU12_c_Lip_corner_puller",   
"AU14_c_Dimpler",            
 "AU15_c_Lip_corner_depressor",
"AU17_c_Chin_raiser",        
"AU20_c_Lip_stretcher",       
"AU23_c_Lip_tightener",      
"AU25_c_Lips_part",          
"AU26_c_Jaw_drop",    
"AU28_c_Lip_suck",    
"AU45_c_Blink")
tmp_AUnames


