---
title: "eyetracking pre-procesing - social vs non social modualtion of emotion response and physilogy"
author: "Helio"
date: "2024-03-07"
output: html_document
---



# Overview 
In this file I aim to process all the gaze data, essentially read, clean and combines multiple files with gaze data and their metadata

# Conventions
For data: dta_
Temporary files: tmp_
Statistical summaries: sum_
Models (such as lm models): mod_
Custom functions: fn_
Plots and visualization: plt_
Lookup and referecne tables: lkp_
Results and Analysis: rlt_
Consistency and accuracy checks: chk_

Set-up: where I load libraries and create objects for later use (such as color schemes etc).

4. Check gaze data




Set-up: where I load libraries and create objects for later use (such as color schemes etc).

```{r setup, include=FALSE}
# store date
current_date<- Sys.Date()

# libraries
require(tidyverse)
require(data.table)
require(readr)

# for reading hdf5 files
# if (!requireNamespace("BiocManager", quietly = TRUE))
# install.packages("BiocManager")
# BiocManager::install(version = "3.18")
# 
# BiocManager::install("rhdf5")
library(rhdf5)



```

Data Import / Cleaning: where datasets are imported and cleaned.
```{r}

setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking")

# get hdf files in 
hdf5_file_path<-"~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking"
  

  setwd(hdf5_file_path)
fn_gp.extractor = function(hdf5_file_path) {
  

  hdf_files_list = list.files(hdf5_file_path, pattern = "\\.hdf5$")
  
  if (length(hdf_files_list) == 0){
    
    return(message('No HDF5 files found in the directory provided.'))
  }
  
  
  # pb <- txtProgressBar(min = 0, max = length(hdf_files_list), style = 3)

  for (f in 1:length(hdf_files_list)) {
    # f = 1
    message(sprintf("Extracting file %i / %i - %s", f, length(hdf_files_list), hdf_files_list[f]))
    
    #note this sometimes fails because e are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdf_files_list[f], '/data_collection/events/experiment/MessageEvent')

    # check tstop or tend
    tmp.events$keep_drop<- if_else(grepl(c('tStart'), tmp.events$text), "keep",
                                   if_else(grepl(c('tEnd'), tmp.events$text), "keep",
                                            if_else(tmp.events$category == "VALIDATION", "keep",
                                           "drop")))
    
    tmp.events<- subset(tmp.events, keep_drop == "keep")
  
  
    # load the eye tracking data
    tmp.eyetr  = h5read(hdf_files_list[f], '/data_collection/events/eyetracker/GazepointSampleEvent') # note this is updated to GazepointSampleEvent whereas before it was BinocularEyeSampleEvent
    

    # Get subejct id from Events
    ssid = sub("_.*", "", hdf_files_list[f])
      # substr(hdf_files_list[f], 1,3)
    # update the string before the data
    date = gsub('^.*Interostudy_\\s*|\\s*.hdf5*$', '', hdf_files_list[f])
    
  
    session = unique(tmp.events$session_id)

    
    # Create DF for trials data
    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
    names(tmp.df) = names(tmp.eyetr)
    colnames(tmp.df)
    
    # Prepare Events, keep only start/end messages
    phrases = c('tStart', 'tEnd')

    
    # unique(tmp.events$category)
    tmp.events_calib = subset(tmp.events, category == "VALIDATION")
    
    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))
# tmp.events    
    # we should have a total of XX stimuli multiplied by 4 (start and t end for stim and fix) 
    # 4 pratice + 48 trials = 52
    # 52*4 = we should should 208 rows
    # Create start/end references
    tmp.events$t_start   = NA
    tmp.events$t_end     = NA
    
    # Trial number extraction 
    tmp.events$t_no      = NA
    
    # Space for subject id
    tmp.df$ssid         = NA
    tmp.df$text<-NA
    
    for (l in 1:nrow(tmp.events)) {
      
      message(sprintf("Grabing start messages %s", tmp.events$text[l]))
      
      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
        tmp.events$t_start[l] = tmp.events$time[l]
        
        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
          tmp.events$t_end[l] = tmp.events$time[l+1]
        }
        
        else {
          message('trial start/end structure not valid')
        }
      }
      
    }
    
    message(sprintf("done grabbing messages"))
    # readline(prompt="Press [enter] to continue")
    
     message(sprintf("making screencontent"))
     # unique(tmp.events$text)
    tmp.events$screencontent <- if_else(grepl('fix', tmp.events$text), 'fixation',
                                       if_else(grepl('stim', tmp.events$text), 'stimuli', NA))
    
    
    # first let's do condition
    # update the names
    tmp.events$pratice_vs_trial<- if_else(grepl('Example', tmp.events$text), 'Pratice',
                                   if_else(grepl('IAPS', tmp.events$text), 'Trial', NA))
    
 
    # store stim code here -0 we need the content between "_" and ".jpg
    tmp.events$stimnopath<-   paste0(sub(".*_(.*?)\\.jpg.*", "\\1", tmp.events$text), ".jpg")
      
      
    
    # tmp.events$emotion_yes_no_new<- 
    
    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
 

    tmp.df$screencontent<- NA
    tmp.df$pratice_vs_trial <- NA
    # tmp.df$isfakeOrReal <- NULL
    tmp.df$stimnopath <- NA
    
    # e=10
        message(sprintf("subsetting eyetracking data"))
    
        tmp.events1$ssid<- ssid
        
        # why?
tmp.eyetr<-tmp.eyetr%>%
  mutate_if(is.raw, as.double)

for(e in 1:nrow(tmp.events1)) {
      # e = 1
      # Subset the EyeTracking data based on start/end
      tmp.raw.trial = subset(tmp.eyetr, 
                             tmp.eyetr$time >= tmp.events1$t_start[e] & tmp.eyetr$time <= tmp.events1$t_end [e]+.5)
      
      # tmp.raw.trial$tNo = tmp.events1$tNo[e]
      # tmp.events1$tNo<-NULL
      
      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
      tmp.raw.trial$pratice_vs_trial = tmp.events1$pratice_vs_trial[e]
      # tmp.raw.trial$isfakeOrReal = tmp.events1$isfakeOrReal[e]
      tmp.raw.trial$stimnopath = tmp.events1$stimnopath[e]
      # tmp.raw.trial$stim = tmp.events1$[e]
      tmp.raw.trial$ssid = ssid
      tmp.raw.trial$text = tmp.events1$text[e]
       message(sprintf("binding tmp.df"))
       
      tmp.df<- rbind(tmp.raw.trial,tmp.df)

}

        
     message(sprintf("done binding"))
    
    # Add ssid
    # tmp.df$ssID = ssid[e]
    tmp.df<- tmp.df%>%
      arrange(time)
    
     ###########################
    # Save file
    
    name = sprintf("%s_",ssid)
    message(sprintf("saving data"))
    write.csv(tmp.df, paste0(name,Sys.Date(), paste0("_gp_data.csv")))#
    # write.csv(tmp.df, paste0(name,Sys.Date(), paste0(".csv")))#
    
    ###########################
    # write calibration cali
    name2 = sprintf("%s_", ssid)
    write.csv(tmp.events_calib, paste0(name2,Sys.Date(), paste0("_gp_data_cali.csv")))#
      
    #   sprintf("ss%s_GPdata_cali", ssid)
    # write.csv(tmp.events_calib, paste0(name2,Sys.Date(), paste0(".csv")))#
    
  }
  

  message("Processing Completed.")
  tmp.df
  # close(pb)
}

# tmp.df%>%
#   group_by(text)%>%
#   mutate(diff_time = time-lag(time))%>%
#   mutate(cum_diff = sum(abs(diff_time), na.rm = T))%>%
#   ggplot(aes(cum_diff))+
#   geom_histogram()+
#   facet_grid(~screencontent)
# 
# table(is.na(tmp.df$screencontent))


```

run the fn_gp.extractor

```{r }

# not this throws ann error on problematic participants
tmp_full<- fn_gp.extractor(hdf5_file_path)

```




Now some basic cleaning 

```{r, cleaning}
# setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking/preprocessed")

# reads all individual gaze exported files into one big file

library(readr)
colnames(X101_2024_03_07_gp_data)


read_plus <- function(flnm) {
  data.table::fread(flnm, select = c( "ssid", "session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1",
                                     "left_pupil_measure2",
                                     "right_pupil_measure2",
                                     "status", 
                                     "screencontent",
                                     "pratice_vs_trial",
                                     "stimnopath",
                                     
                                     "text")) %>% 
    mutate(filename = flnm)
}


# read all clean data 

dta_eytr <-
  list.files(pattern = "*data.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))%>%
  janitor::clean_names()%>%
  subset(!is.na(ssid))

# three digits?
# Regular expression to capture the pattern before "_" and after "./"
pattern <- "\\./([0-9]+)_.*"

# Extract the pattern
unique(dta_eytr$stimnopath)
dta_eytr$participant<-  sub(pattern, "\\1", dta_eytr$filename)





dta_eyetrack
unique(dta_eyetrack$screencontent)

dta_eytr$screencontent_no_na <- if_else(is.na(dta_eytr$screencontent), "rest", dta_eytr$screencontent)

dta_eytr$stimnopath_no_na <- if_else(is.na(dta_eytr$stimnopath), "rest", 
                                   if_else(dta_eytr$stimnopath == "tStart_rest1_cross", "rest",       
                                           dta_eytr$stimnopath))

unique(dta_eytr$text)
  
```




#####################################################################################
# gp preprocessing funtion, checks for losses, averages gaze, pupil and pixelate
#####################################################################################

```{r, gppreprocessing}

unique(dta_eytr$status)

fn_gp_preprocessing = function(dta_eytr) {
  
  message(sprintf("step1 left gaze validity"))
  
  # transform invalid gaze into NA based on validity codes
  # to do: link the conventions file
  
#   status - https://psychopy.org/api/iohub/device/eyetracker_interface/GazePoint_Implementation_Notes.html
# Indicates if eye sample contains ‘valid’ data for left and right eyes. 
  # 0 = Eye sample is OK. 2 = Right eye data is likely invalid. 20 = Left #eye data is likely invalid. 22 = Eye sample is likely invalid.
  dta_eytr$left_gaze_x_cor<- if_else(dta_eytr$status != '20', dta_eytr$left_gaze_x, NA)
  dta_eytr$left_gaze_x_cor<- if_else(dta_eytr$status != '22', dta_eytr$left_gaze_x_cor, NA)
  dta_eytr$left_gaze_y_cor<- if_else(dta_eytr$status != '20', dta_eytr$left_gaze_y, NA)
  dta_eytr$left_gaze_y_cor<- if_else(dta_eytr$status != '22', dta_eytr$left_gaze_y_cor, NA)
  
  message(sprintf("step2 right gaze validity"))
  
  dta_eytr$right_gaze_x_cor<- if_else(dta_eytr$status != '2', dta_eytr$right_gaze_x, NA)
  #
  dta_eytr$right_gaze_x_cor<- if_else(dta_eytr$status != '22', dta_eytr$right_gaze_x_cor, NA)
  dta_eytr$right_gaze_y_cor<- if_else(dta_eytr$status != '2', dta_eytr$right_gaze_y, NA)
  dta_eytr$right_gaze_y_cor<- if_else(dta_eytr$status != '22', dta_eytr$right_gaze_y_cor, NA)

  # pupil validity
  
  message(sprintf("step3 pupil validity"))
  # pupil pixels
  dta_eytr$left_pupil_measure1<- if_else(dta_eytr$status != '20', dta_eytr$left_pupil_measure1, NA)
  dta_eytr$left_pupil_measure1<- if_else(dta_eytr$status != '22', dta_eytr$left_pupil_measure1, NA)
  
  dta_eytr$right_pupil_measure1<- if_else(dta_eytr$status != '2', dta_eytr$right_pupil_measure1, NA)
  dta_eytr$right_pupil_measure1<- if_else(dta_eytr$status != '22', dta_eytr$right_pupil_measure1, NA)
  table(is.na(dta_eytr$right_pupil_measure1))
  
  # pupil diameter
  
   dta_eytr$left_pupil_measure2<- if_else(dta_eytr$status != '20', dta_eytr$left_pupil_measure2, NA)
  dta_eytr$left_pupil_measure2<- if_else(dta_eytr$status != '22', dta_eytr$left_pupil_measure2, NA)
  
  dta_eytr$right_pupil_measure2<- if_else(dta_eytr$status != '2', dta_eytr$right_pupil_measure2, NA)
  dta_eytr$right_pupil_measure2<- if_else(dta_eytr$status != '22', dta_eytr$right_pupil_measure2, NA)
  table(is.na(dta_eytr$right_pupil_measure2))
  
  # check gazepoint out of bounds and repixelate 
  
  # screen=1, size=array([1920, 1080]) # update here accordingly
  
  # (1920/2 = 960 by 1080/2 = 540 add half to normalised coordinates from psychopy)
  # update according to setup
  
  message(sprintf("step 4 cutting off screen in points and repixelate"))
  
  dta_eytr$left_gaze_x_cor<- if_else(dta_eytr$left_gaze_x_cor >= -960 & dta_eytr$left_gaze_x_cor <= 960, dta_eytr$left_gaze_x_cor, NA)
  dta_eytr$right_gaze_x_cor<- if_else(dta_eytr$right_gaze_x_cor >= -960 & dta_eytr$right_gaze_x_cor <= 960, dta_eytr$right_gaze_x_cor, NA)
  
  dta_eytr$left_gaze_y_cor<- if_else(dta_eytr$left_gaze_y_cor >= -540 & dta_eytr$left_gaze_y_cor <= 540, dta_eytr$left_gaze_y_cor, NA)
  dta_eytr$right_gaze_y_cor<- if_else(dta_eytr$right_gaze_y_cor >= -540 & dta_eytr$right_gaze_y_cor <= 540, dta_eytr$right_gaze_y_cor, NA)
  
  dta_eytr$left_gaze_x_cor_pix<- dta_eytr$left_gaze_x_cor+960
  dta_eytr$right_gaze_x_cor_pix<- dta_eytr$right_gaze_x_cor+960
  
  dta_eytr$left_gaze_y_cor_pix<- dta_eytr$left_gaze_y_cor+540
  dta_eytr$right_gaze_y_cor_pix<- dta_eytr$right_gaze_y_cor+540
  
  # is left or right an NA
  
  dta_eytr$left_na<- is.na(dta_eytr$left_gaze_x_cor) 
  dta_eytr$right_na<- is.na(dta_eytr$right_gaze_x_cor)
  dta_eytr$both_na<- if_else(dta_eytr$left_na == TRUE & dta_eytr$right_na == TRUE, TRUE, FALSE)
  
  message(sprintf("step5 gaze x  means"))
  # create gaze means betwenn left and right eye
  
  dta_eytr$gaze_x_cor<-if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_gaze_x_cor,
                              if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_gaze_x_cor,
                                      ((dta_eytr$left_gaze_x_cor + dta_eytr$right_gaze_x_cor)/2)))
  message(sprintf("step6 gaze y means"))
  
  dta_eytr$gaze_y_cor<-if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_gaze_y_cor,
                              if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_gaze_y_cor,
                                      ((dta_eytr$left_gaze_y_cor + dta_eytr$right_gaze_y_cor)/2)))
  
  message(sprintf("step6 repixelate gaze means"))
  
  dta_eytr$gaze_x_cor_pix<- dta_eytr$gaze_x_cor + 960
  # min(dta_eytr$gaze_x_cor_pix, na.rm = TRUE)
  
  dta_eytr$gaze_y_cor_pix<- dta_eytr$gaze_y_cor+540
  # min(dta_eytr$gaze_y_cor_pix, na.rm = TRUE)
  
  # clean_pupil
  
  message(sprintf("cleaning pupil"))
  
  # max(dta_eytr$left_pupil_measure1)
  
  dta_eytr$pupil<- if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_pupil_measure1,
                          if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_pupil_measure1,
                                  ((dta_eytr$left_pupil_measure1 + dta_eytr$right_pupil_measure1)/2)))
  
  
  # diameter
  dta_eytr$pupil_d<- if_else(dta_eytr$left_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$right_pupil_measure2,
                          if_else(dta_eytr$right_na == TRUE & dta_eytr$both_na == FALSE, dta_eytr$left_pupil_measure2,
                                  ((dta_eytr$left_pupil_measure2 + dta_eytr$right_pupil_measure2)/2)))
  
  
  # dta_eytr$trackloss<- if_else(dta_eytr$status > 0, TRUE, FALSE)
  dta_eytr$trialunq<- paste0(dta_eytr$pratice_vs_trial,"_",paste0(dta_eytr$screencontent,"_", paste0(dta_eytr$stim)))
  dta_eytr$distance_mm = 600
  
  # min(dta_eytr$pupil, na.rm = TRUE)
  # max(dta_eytr$pupil, na.rm = TRUE)
  # colnames(dta_eytr)
  dta_eytr<- dta_eytr%>%
    # group_by(ssid)
    arrange(ssid,time)
}

```

repixelated and minimally processed (e.g. deleting invalid samples), merging left and right eye
```{r}
rm(gp_preprocessing)
dta_eytr_rpx<- fn_gp_preprocessing(dta_eytr)


colnames(dta_eytr_rpx) 
 
options(scipen = 999)
range(dta_eytr_rpx$pupil, na.rm = TRUE)
range(dta_eytr_rpx$pupil_d, na.rm = TRUE)
range(dta_eytr_rpx$gaze_y_cor_pix, na.rm = TRUE)
range(dta_eytr_rpx$gaze_x_cor_pix, na.rm = TRUE) 

# split and export per participant

colnames(dta_eytr_rpx)

unique(dta_eytr_rpx$stimnopath)
dta_eytr_rpx<- dta_eytr_rpx%>%
  group_by(participant)%>%
  arrange(time)


# Split the dataframe based on 'group_column'
list_of_dfs <- split(dta_eytr_rpx, dta_eytr_rpx$participant)

colnames(dta_eytr_rpx)

# Iterate over the list to write each dataframe to a CSV file
lapply(names(list_of_dfs), function(x) {
  csv_filename <- paste0(x, "_dta_eytr_rpx.csv")
  write.csv(list_of_dfs[[x]], csv_filename, row.names = FALSE)
})

```
quick checks
```{r}
dta_eytr_rpx%>%
  group_by(participant)%>%
  arrange(time)%>%
  
  mutate(tmp_group = paste0(stimnopath_no_na,screencontent_no_na))%>%
  group_by(tmp_group)%>%
 
  subset(participant == 117& screencontent_no_na != "rest")%>%
   mutate(time_rezero = time - first(time)) %>%
  ggplot(aes(time_rezero, gaze_x_cor_pix))+
    geom_line()+
    geom_line(aes(y = gaze_y_cor_pix), colour = "blue")+
  facet_grid(~screencontent_no_na)+
  geom_vline(xintercept = 6.6, linetype = "dashed", colour ="red")+
  ylab("gaze coordinates")



dta_eytr_rpx%>%
  group_by(participant)%>%
  arrange(time)%>%
  
  mutate(tmp_group = paste0(stimnopath_no_na,screencontent_no_na))%>%
  group_by(tmp_group)%>%
 
  subset(participant == 117& screencontent_no_na != "rest")%>%
   mutate(time_rezero = time - first(time)) %>%
  ggplot(aes(time_rezero, pupil))+
    geom_smooth(aes(group = stimnopath_no_na), se = F)+
    # geom_line(aes(y = gaze_y_cor_pix), colour = "blue")+
  facet_grid(~screencontent_no_na)+
  geom_vline(xintercept = 6.6, linetype = "dashed", colour ="red")+
  ylab("gaze coordinates")



```



######################
TO ADAPT CODE BELOW
To DO
# rezeroing times by trial, by participants
Continue here

```{r}
dta_eytr_rpx
# create start at every screen content
# Preview unique screen contents and dataset structure
print(unique(dta_eytr_rpx$text))
print(colnames(dta_eytr_rpx))


unique(dta_eytr_rpx$trialunq)
unique(dta_eytr_rpx$pratice_vs_trial)
unique(dta_eytr_rpx$screencontent)
unique(dta_eytr_rpx$screencontent_no_na)
dta_eytr_rpx$trialunq
# only run this is the previous processing code is not fixed where trialunq includes pratice vs trial


dta_eytr_rpx$pratice_vs_trial<- ifelse(is.na(dta_eytr_rpx$pratice_vs_trial), "rest", dta_eytr_rpx$pratice_vs_trial)


dta_eytr_rpx$trialunq<- paste0(dta_eytr_rpx$pratice_vs_trial,"_",paste0(dta_eytr_rpx$screencontent,"_", paste0(dta_eytr_rpx$stimnopath)))
table(is.na(dta_eytr_rpx$trialunq))

unique(dta_eytr_rpx$trialunq)
unique(dta_eytr_rpx$text)

dta_eytr_rpx <- dta_eytr_rpx %>%
  arrange(participant, time) %>%
  group_by(ssid, screencontent_no_na) %>%
  mutate(is_firststart = !duplicated(trialunq)) %>%
  ungroup()# Use '!' to correctly identify the first start

# Preview the data to ensure the above operation worked as intended
print(head(dta_eytr_rpx))

# Create a zero-time column where the first occurrence of each trial is marked with its time, others as NA
dta_eytr_rpx <- dta_eytr_rpx %>%
  mutate(zero = if_else(is_firststart, time, NA_real_)) # Use NA_real_ for consistency in numeric columns

# Propagate the zero times down each group to fill in the NAs
dta_eytr_rpx <- dta_eytr_rpx %>%
  group_by(ssid, screencontent_no_na, trialunq) %>%
  fill(zero, .direction = "down")%>% # Explicitly mention direction for clarity
  ungroup()

# Calculate the time relative to zero for each trial
dta_eytr_rpx <- dta_eytr_rpx %>%
  mutate(timerezero = time - zero)

# Arrange by time for final organization, if necessary
dta_eytr_rpx <- dta_eytr_rpx %>%
  arrange(participant,time)

# Optionally, print unique zero times to verify the operation
print(unique(dta_eytr_rpx$zero))

# Results stored in 'dta_gaze_clean' with 'timerezero' reflecting time since trial start

# let's check to see if it looks fine
range(dta_eytr_rpx$timerezero, na.rm = TRUE)
max(dta_eytr_rpx$timerezero, na.rm = TRUE) # `
# now this looks about right ~10~11sec
# 120 seconds in 2 minutes
dta_eytr_rpx%>%
subset(ssid == 116 & dta_eytr_rpx$screencontent_no_na == "stimuli") %>%
ggplot( aes(timerezero, pupil ))+
  geom_smooth(aes(group = stimnopath_no_na), se = F, size = .1)


```

# create a new time rezero where before stim start, time is negative
```{r}


dta_eytr_rpx<- dta_eytr_rpx %>%
  group_by(participant, stimnopath_no_na) %>%
  arrange(participant, time) %>%
  mutate(general_time = row_number() - 1) %>% # This assumes your data starts from 0 and increments
  group_by(ssid, stimnopath_no_na, screencontent_no_na, .add = TRUE) %>%
  mutate(
    backward_time = max(timerezero) - timerezero, # Calculate backward time for fixation
    time_backward = case_when(
      screencontent_no_na == "stimuli" ~ timerezero, # Use timezero directly for forward time in stimuli
      screencontent_no_na == "fixation" ~ -backward_time, # Use negative backward time for fixation
      TRUE ~ NA_real_ # Fallback case
    )
  ) %>%
  ungroup()



dta_eytr_rpx%>%
subset(ssid == 116 & screencontent_no_na!= "rest") %>%
ggplot( aes(time_backward, pupil ))+
  geom_smooth(aes(group = stimnopath_no_na), se = F, size = .1)+
  geom_vline(xintercept = 0, linetype = "dashed")
    # facet_grid(~screencontent_no_na)
  



  

```



# Filter out rows where either event_id or time is duplicated within each ssid

```{r}

dta_eytr_rpx <- dta_eytr_rpx %>%
  group_by(participant) %>%
  mutate(duplicated_event_id = duplicated(event_id) | duplicated(event_id, fromLast = TRUE),
         duplicated_time = duplicated(time) | duplicated(time, fromLast = TRUE)) %>%
  ungroup()

table(dta_eytr_rpx$duplicated_event_id)



dta_eytr_rpx_nodup <- dta_eytr_rpx %>%
  filter(!duplicated_event_id & !duplicated_time)


tmp_test<-  dta_eytr_rpx %>%
  subset(duplicated_event_id & duplicated_time)
nrow(dta_eytr_rpx_nodup )/nrow(dta_eytr_rpx)         
# 0.8980762

# don'\t subset as this sems to happen at the end or start of screens and mighht cutout our isfirst start -==- TRUE
```



select variables for gazepath
```{r}
dta_eytr_rpx$subject<- dta_eytr_rpx$ssid

dta_eytr_rpx<- dta_eytr_rpx%>%
group_by(participant)%>%
  arrange(time)


dta_eytr_rpx$distance_mm<- 610



dta_eytr_rpx$trackloss<- if_else(is.na(dta_eytr_rpx$gaze_x_cor_pix) == TRUE, 0, 
                         if_else(is.na(dta_eytr_rpx$gaze_y_cor_pix) == TRUE, 0, 1))

unique(dta_eytr_rpx$trackloss)

# compute proportion of lost data

dta_gaze_clean_10s_nodup$trialunq

dta_eytr_rpx <- dta_eytr_rpx %>%
  group_by(participant, trialunq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
  group_by(participant)%>%
  arrange(time)%>%
  ungroup()


# check to see this is right

dta_eytr_rpx%>%
  ggplot(aes(gaze_loss_prop))+
  geom_histogram()

dta_eytr_rpx%>%
  ggplot(aes(gaze_valid_prop))+
  geom_histogram()
```


select for gazepath
```{r}
dta_eytr_rpx$filename

dta_4gazepath<- select(dta_eytr_rpx, 
                                      c("participant", "session_id", "event_id", "ssid", 
                                        "text","trialunq","screencontent",
                                        "screencontent_no_na","pratice_vs_trial",                           "stimnopath",
                                        "stimnopath_no_na",
                            "time", "timerezero","time_backward",
                            "status",
                            "filename",
                            "left_gaze_x_cor_pix",
                            "right_gaze_x_cor_pix",
                            "left_gaze_y_cor_pix",
                            "right_gaze_y_cor_pix",  
                            "gaze_x_cor_pix",  
                            "gaze_y_cor_pix",
                            # "pupil",
                            # "pupil_d",
                            # "pup_interp_pix",
                            "distance_mm",
                            "trackloss", "gaze_loss_prop", "gaze_valid_prop"
                            )
                            )
head(dta_4gazepath)


```
Check gaze data
```{r}
library(ggplot2)
#########################
# this can be slow if not sumamrised
dta_4gazepath %>%
  group_by(ssid,trialunq, screencontent_no_na)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(gaze_x_cor_pix, gaze_y_cor_pix, colour = timerezero))+
  # geom_contour()
  geom_point(alpha = .1)+
  facet_grid(~screencontent_no_na)+
  xlim(0,1920)+
  ylim(1080,0)+
  geom_hline(yintercept = 1080/2)+
    geom_vline(xintercept = 1920/2)


```




# for gaze parsing

```{r}

# Create a unique identifier for each combination of ssid and screencontent
dta_4gazepath <- dta_4gazepath %>%
  mutate(split_column = paste0(participant, "_", screencontent_no_na))

# Split the data frame into a list of data frames based on the unique combinations
unique(dta_4gazepath$split_column)
tmp_split_df <- split(dta_4gazepath, dta_4gazepath$split_column)

# Log message indicating the start of writing files for gazepath
message("Writing files for gazepath")


setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking/preprocessed/for_fix_sac")

# Iterate over the list of split data frames and write each to a CSV file
walk(names(tmp_split_df), function(tmp_splitcol) {
  write_csv(tmp_split_df[[tmp_splitcol]], paste0('gp_', tmp_splitcol, ".csv"))
})


# with prtogres bar

# library(pbapply)
# 
# # Assuming tmp_split_df is your list of data frames and names(tmp_split_df) gives their names
# pblapply(names(tmp_split_df), function(tmp_splitcol) {
#   write_csv(tmp_split_df[[tmp_splitcol]], paste0('gp_', tmp_splitcol, ".csv"))
# })
# 
# # Create a progress bar
# pb <- txtProgressBar(min = 0, max = length(names(tmp_split_df)), initial = 0, style = 3)
# 
# # Iterate over the list of split data frames
# walk(names(tmp_split_df), function(tmp_splitcol, index) {
#   # Update progress bar
#   setTxtProgressBar(pb, index)
#   
#   # Write to CSV
#   write_csv(tmp_split_df[[tmp_splitcol]], paste0('gp_', tmp_splitcol, ".csv"))
# }, index = seq_along(names(tmp_split_df)))
# 
# # Close the progress bar
# close(pb)


```



run gazepath to detect fioxationa nd saccades in gaze data


# cerate an emoty rscipt mor mark down then run the lines below
library(gazepath)
GUI() # 


run first stimuli files then fixcation files separately then rest fiules sepaartelly
note you need to close and restart gazepath after each processing

gazepath settings

left eye x coord: left_gaze_x_cor_pix
left eye y coord: left_gaze_y_cor_pix

didtance: distance (mm)

right eye x coord: right_gaze_x_cor_pix
right eye y coord: right_gaze_y_cor_pix
didtance: distance (mm)


sample rate: 150
screen resolution height (pix): 1080
screen resolution width (pix): 1920


stimuli height (px): 1080 
stimuli width (px): 1920
variables to keep: text, participant, pratice_vs_trial, stimnopath_no_na


<!-- bristol -->

USE SCREEN SIZE in mm (update accordinly)
stimuli height mm 275 
stimuli width mm 485

<!-- previous -->
<!-- stimuli height mm 300 -->
<!-- stimuli width mm 530 -->



load gazepath data
```{r}
# load all fix and saccades
# setwd("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/2022 - University Of Birmingham/Deepfakes/Deepfake_RProject/Data")
# Bristol data


setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Eyetracking/preprocessed/Gazepath results")

# load data
library(readr)
tmp_filelist <- list.files(pattern = ".csv")

dta_gp_all_fix_sacc <- rbindlist(sapply(tmp_filelist, fread, simplify = FALSE),
                use.names = TRUE, idcol = "filename2")%>%
  janitor::clean_names()


colnames(dta_psypy1)

dta_psypy1$stim_iaps


# Create 'screencontent' based on 'text'

unique(dta_gp_all_fix_sacc$text)

unique(dta_psypy1$condition)

library(dplyr)

dta_gp_all_fix_sacc <- dta_gp_all_fix_sacc %>%
  mutate(
    screencontent = case_when(
      grepl("fix", text) ~ "fixation_cross",
      grepl("stim", text) ~ "stimuli",
      grepl("rest", text) ~ "rest",
      TRUE ~ NA_character_ # Provides an NA value where none of the above conditions are met
    ),
    screencontent_no = case_when(
      screencontent == "rest" ~ 1,
      screencontent == "fixation_cross" ~ 2,
      screencontent == "stimuli" ~ 3,
      TRUE ~ NA_real_ # Ensures that a numeric NA is returned if none of the conditions match
    )
  )


# create pratice vs ytrial
library(stringi)
unique(dta_psypy1$stim_iaps)

unique(dta_gp_all_fix_sacc$text)

unique(dta_gp_all_fix_sacc$participant)

# dta_gp_all_fix_sacc$participant<- substr(dta_gp_all_fix_sacc$participant, 4,6)

dta_gp_all_fix_sacc$participant

dta_gp_all_fix_sacc$stim_iaps <- paste0(sub(".*_([^_]+)\\.jpg.*", "\\1", dta_gp_all_fix_sacc$text), ".jpg")
  



dta_gp_all_fix_sacc

```

now create averages for gaze


```{r}
dta_gp_all_fix_sacc
# compute means and max fixation duration

unique(dta_gp_all_fix_sacc$screencontent)

dta_gp_all_fix_sacc_stim<- dta_gp_all_fix_sacc%>%
  subset(screencontent == "stimuli")%>%
  select(-screencontent, -screencontent_no)

colnames(dta_gp_all_fix_sacc_stim)



  # First, group by the main categories
unique(dta_gp_all_fix_sacc_stim$text)


table(is.na(dta_gp_all_fix_sacc_stim$stim_iaps ))


dta_gp_all_fix_sacc_stim_agg <- dta_gp_all_fix_sacc_stim$text %>%
  group_by(participant, text, trial, stim_iaps) %>%
  summarise(
    mean_dwell_dur = mean(duration, na.rm = TRUE),
    mean_fix_dur = mean(duration[value == "f"], na.rm = TRUE),
    mean_sac_dur = mean(duration[value == "s"], na.rm = TRUE),
    sum_dwell_dur = sum(duration, na.rm = TRUE),
    sum_fix_dur = sum(duration[value == "f"], na.rm = TRUE),
    sum_sac_dur = sum(duration[value == "s"], na.rm = TRUE),
    mean_rms = mean(rms, na.rm = TRUE),
    mean_po_gsd = mean(po_gsd_sac_amp[value == "f"], na.rm = TRUE),
    mean_sac_amp = mean(po_gsd_sac_amp[value == "s"], na.rm = TRUE),
    count_fix = sum(value == "f"),
    count_sacc = sum(value == "s")
    # .groups = "drop" # This explicitly drops the grouping instead of keeping it
  )%>%

  # Optionally, ungroup if you want to remove the grouping structure
  ungroup()


dta_gp_all_fix_sacc_stim_agg
unique(dta_gp_all_fix_sacc_stim_agg$stim_iaps)

# add trackloss

colnames(dta_4gazepath)
dta_4gazepath$split_column
dta_4gazepath$screencontent_no_na

dta_4gazepath$stimnopath
trackloss<- dta_4gazepath%>%
  select(participant, screencontent_no_na,text, gaze_valid_prop)%>%
  subset(screencontent_no_na == "stimuli")%>%
  select(-screencontent_no_na)%>%
  group_by(participant, text) %>%
  summarise_at(c("gaze_valid_prop"), mean, na.rm = T)%>%
  mutate(gaze_valid_prop_ppt = mean(gaze_valid_prop, na.rm = T))


dta_gp_all_fix_sacc_stim_agg<- left_join(dta_gp_all_fix_sacc_stim_agg, 
                                                 trackloss, by = c("participant", "text"))
```


to merge

```{r}

dta_gp_all_fix_sacc_stim_agg

```