---
title: ""social emophys - pre-procesing psychopy - social vs non social modulation of emotion response and physilogy""
author: "Helio"
date: "2024-03-07"
output: html_document
---


# Overview 
  To process output of PsychoPy.

# Conventions
For data: `dta_`
Temporary files: `tmp_`
Statistical summaries: `sum_`
Models (such as lm models): `mod_`
Custom functions: `fn_`
Plots and visualization: `plt_`
Lookup and reference tables: `lkp_`
Results and Analysis: `rlt_`
Consistency and accuracy checks: `chk_`


Set-up: where I load libraries and create objects for later use (such as color schemes etc).
```{r setup, include=FALSE}
# Load necessary libraries
library(tidyverse)
library(data.table)
library(janitor)
library(purrr)

```



```{r}
setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/behavioural")

# Load behavioural data


# Read all the files and create a FileName column to store filenames

tmp_files <- list.files(pattern = ".csv")

# 99 vs 98
# exclude 208


# Load and combine all CSV files

# tmp_files<- unique(dta_psypy$filename)


# Modify the sapply call to include a function that ensures 'unixtime.Start' is always treated as 'double'
dta_psypy$filename

dta_psypy <- rbindlist(sapply(tmp_files, function(file) {
  dt <- fread(file, colClasses = list(double = "unixtime.Start")) # Ensure unixtime.Start is read as double
  return(dt)
}, simplify = FALSE), use.names = TRUE, idcol = "filename", fill = TRUE) %>%
  janitor::clean_names() %>%
  mutate(trial_order = if_else(condition == "Example Stimuli", 
                               practice_this_trial_n, test_this_trial_n),
         trial_index = if_else(condition == "Example Stimuli", 
                               practice_this_index, test_this_index)) %>%
  select(-matches("this_trial_n|this_index")) %>%
  select(-matches("v1"), -matches("v2"))
  # filter(!is.na(unixtime_start))
length(unique(dta_psypy$participant))


# fix the issues with participant

dta_psypy<- dta_psypy%>%
  subset(!is.na(participant))

dta_psypy$participant<- substr(dta_psypy$filename, 1,3)

unique(dta_psypy$participant)

table(dta_psypy$participant)

colnames(dta_psypy)

tmp_test<- dta_psypy%>%subset(participant == 101)

```



```{r}

dta_psypy <- dta_psypy%>%
  group_by(filename)%>%
  fill(obs_slider_response, .direction = "downup")%>%
   group_by(filename)%>%
  fill(belief_slider_response, .direction = "downup")

unique(dta_psypy$belief_slider_response)
# oiyur event times
dta_psypy$unixtime_start #start
dta_psypy$unixtime_end #of rest


```



```{r}
dta_psypy_obs_bel<- dta_psypy%>%
  mutate(participant = substr(filename,1,3))%>%
  select(participant, obs_slider_response, belief_slider_response)%>%
  group_by(participant)%>%
 summarise_at(c("obs_slider_response","belief_slider_response"), mean, na.rm = T)


colnames(dta_psypy)


tmp_test<- dta_psypy%>%
  subset(!is.na(unixtime_start_2))


tmp_test<- dta_psypy%>%
  subset(!is.na(unixtime_end_2))


unique(dta_psypy$unixtime_start)
unique(dta_psypy$unixtime_end)

unique(dta_psypy$unixtime_start_2)
unique(dta_psypy$unixtime_end_2)
```


```{r}
dta_psypy1<- dta_psypy%>%
  select(c(
      "filename", "participant", "session", "date", "exp_name",
      "condition", "emotion", "stim_iaps", "stim_description",
      "valence_mean", "arousal_mean", 
      "emotioncategory",
      "trial_order", "trial_index", 
      # "practice_this_trial_n", 
      # "practice_this_n",
      # "test_this_trial_n", "test_this_n",
      "et_start_started", "unixtime_start",
      "rest_started", "unixtime_end",
      "et_stop_started", "et_stop_stopped",
      "fixation_jit_started", "fixation_jit_stopped",
      "fixation_fix_p_started", "image_p_started",
      "fixation_fix_t_started", "image_t_started",
      "val_slider_response", "val_slider_rt",
      "int_slider_response", "int_slider_rt",
      "happy_slide_response", "happy_slide_rt",
      "sad_slide_response", "sad_slide_rt",
      "fear_slide_response", "fear_slide_rt",
      "disgust_slide_response", "disgust_slide_rt",
      "anger_slide_response", "anger_slide_rt",
      "obs_slider_response", "obs_slider_rt",
      
      "psychopy_version", "frame_rate"
    ))


colnames(dta_psypy1)

dta_psypy1$social_nonsocial<- if_else(dta_psypy1$participant<200,"nonsocial", "social")


dta_psypy1$condition<- if_else(!is.na(dta_psypy1$rest_started), "rest_started",
                                        dta_psypy1$condition)

# unique(dta_psypy1$condition)
# table(is.na(dta_psypy1$condition))

dta_psypy1<- dta_psypy1%>%
  subset(!is.na(participant))






dta_psypy1<- dta_psypy1%>%
  subset(condition!= "")



table(dta_psypy1$participant)
# 65
# tmp_test<- dta_psypy1%>%subset(dta_psypy1$participant == 110)


# avoid gaps
dta_psypy1$stim_iaps<- if_else(dta_psypy1$condition == "rest_started", "rest_started",
                                dta_psypy1$stim_iaps)

dta_psypy1$emotioncategory<- if_else(dta_psypy1$condition == "rest_started", "rest_started",
                                      if_else(dta_psypy1$condition == "Example Stimuli", dta_psypy1$emotion,
                                dta_psypy1$emotioncategory))

table(is.na(dta_psypy1$stim_iaps))


  
# #so that zero is rest, so 1 to 4 is pratice
# dta_psypy1$test_this_n+5 #so that it doesn't overlap with pratice

########################################
# here let's make sure the trial start at 1 and not zero, because we will need 0 as trigger for trial off in ledalab
#######################################

dta_psypy1$trial_no_all<- if_else(dta_psypy1$condition == "rest_started", 1,
                                      if_else(dta_psypy1$condition == "Example Stimuli",
                                              dta_psypy1$trial_order+2,
                                              dta_psypy1$trial_order+6))

unique(dta_psypy1$trial_no_all)





```


# Split the data frame by the specified column and then iterate over the list to write each


```{r}
# fix unix start and end fir rest period
# <115 and < 211
options(scipen = 999)
range(dta_psypy1$unixtime_start)
# 1706527409 1718377980800
# 1706527409 1718377980800


# 170652740900

# 170652740900

test<- dta_psypy1%>%
   subset(unixtime_start< 170652740900)

unique(test$participant)
  

# dta_psypy1$unixtime_start*1000
# run only once
# dta_gsr$gsr_pulse_timestamp_sync_unix_cal_ms
# 

# update the start only for # <115 and < 211
# for end update for all

dta_psypy1$unixtime_start<- if_else(dta_psypy1$unixtime_start< 170652740900,
                                           round(dta_psypy1$unixtime_start*1000),
                                           dta_psypy1$unixtime_start)


range(dta_psypy1$unixtime_start)
# 1706527409400 1718377980800
# 
# 
# 
# # test<- dta_psypy1$unixtime_start%>%
# #   subset(!is.na(unixtime_start2))
# # 
# range(dta_psypy1$unixtime_end)
# # dta_psypy1$unixtime_end
# # 
# tmp_test<- dta_psypy1%>%
#   subset(unixtime_end< 17065274090)
# unique(tmp_test$participant)

tmp_test%>%
  ggplot(aes(unixtime_start))+
  geom_histogram()


# 170652740900
range(dta_psypy1$unixtime_end)
# update just the end for rthe rets period
dta_psypy1$unixtime_end<- if_else(dta_psypy1$unixtime_end< 170652740900,
                                           round(dta_psypy1$unixtime_end*1000),
                                           dta_psypy1$unixtime_end)
# 1718377987279
# 1706527529678 < 1718377987279
range(dta_psypy1$unixtime_end)
# 1706527529678 
# 1718377987279


```


```{r}
# write out psypy clean files per person
setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/behavioural/preprocessed")

# Create a unique identifier for each combination of ssid and screencontent
table(dta_psypy1$participant)

dta_psypy1 <- dta_psypy1 %>%
  mutate(split_column = participant)

# Split the data frame into a list of data frames based on the unique combinations
tmp_split_df <- split(dta_psypy1, dta_psypy1$split_column)

# Iterate over the list of split data frames and write each to a CSV file
walk(names(tmp_split_df), function(tmp_splitcol) {
  write_csv(tmp_split_df[[tmp_splitcol]], paste0('dta_psypy_', tmp_splitcol, ".csv"))
})



setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/behavioural/preprocessed")

saveRDS(dta_psypy1, "dta_psypy1.rds")

save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/behavioural/preprocessed/dta_psypy_env.RData")


```