---
title: ""social emophys - pre-procesing psychopy - social vs non social modulation of emotion response and physilogy""
author: "Helio"
date: "2024-03-07"
output: html_document
---


# Overview 
  To process output of PsychoPy.

# Conventions
For data: `dta_`
Temporary files: `tmp_`
Statistical summaries: `sum_`
Models (such as lm models): `mod_`
Custom functions: `fn_`
Plots and visualization: `plt_`
Lookup and reference tables: `lkp_`
Results and Analysis: `rlt_`
Consistency and accuracy checks: `chk_`


Set-up: where I load libraries and create objects for later use (such as color schemes etc).
```{r setup, include=FALSE}
# Load necessary libraries
library(tidyverse)
library(data.table)
library(janitor)
library(purrr)

# Define paths
data_path <- "./Data backup/DataChecks/R code and data/feb 6"
ctrl_data_path <- file.path(data_path, "ctrl")


```

```{r}
setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/behavioural")
# Load behavioural data


# Read all the files and create a FileName column to store filenames

tmp_files <- list.files(pattern = ".csv")


# Load and combine all CSV files


# Load and preprocess data

dta_psypy

# dta_psypy <- rbindlist(sapply(tmp_files, fread, simplify = FALSE), use.names = TRUE, idcol = "filename", fill = TRUE) %>%
#     janitor::clean_names()%>%
#   mutate(trial_order = if_else(condition == "Example Stimuli", 
#                               practice_this_trial_n, test_this_trial_n),
#          trial_index = if_else(condition == "Example Stimuli", 
#                                practice_this_index, test_this_index)) %>%
#   select(-matches("this_trial_n|this_index")) %>%
#   select(-matches("v1"), -matches("v2"))%>%
#   filter(!is.na(unixtime_start))

# warnings()
# warning of loosing precision here on unixstart?



# Modify the sapply call to include a function that ensures 'unixtime.Start' is always treated as 'double'
dta_psypy <- rbindlist(sapply(tmp_files, function(file) {
  dt <- fread(file, colClasses = list(double = "unixtime.Start")) # Ensure unixtime.Start is read as double
  return(dt)
}, simplify = FALSE), use.names = TRUE, idcol = "filename", fill = TRUE) %>%
  janitor::clean_names() %>%
  mutate(trial_order = if_else(condition == "Example Stimuli", 
                               practice_this_trial_n, test_this_trial_n),
         trial_index = if_else(condition == "Example Stimuli", 
                               practice_this_index, test_this_index)) %>%
  select(-matches("this_trial_n|this_index")) %>%
  select(-matches("v1"), -matches("v2")) %>%
  filter(!is.na(unixtime_start))



# now selct the columsn that we need
colnames(dta_psypy)



    # any_of(
range(dta_psypy$unixtime_start)
dta_psypy

dta_psypy1<- dta_psypy%>%
  select(c(
      "filename", "participant", "session", "date", "exp_name",
      "condition", "emotion", "stim_iaps", "stim_description",
      "valence_mean", "arousal_mean", 
      "emotioncategory",
      "trial_order", "trial_index", 
      # "practice_this_trial_n", 
      # "practice_this_n",
      # "test_this_trial_n", "test_this_n",
      "et_start_started", "unixtime_start",
      "rest_started", "unixtime_end",
      "et_stop_started", "et_stop_stopped",
      "fixation_jit_started", "fixation_jit_stopped",
      "fixation_fix_p_started", "image_p_started",
      "fixation_fix_t_started", "image_t_started",
      "val_slider_response", "val_slider_rt",
      "int_slider_response", "int_slider_rt",
      "happy_slide_response", "happy_slide_rt",
      "sad_slide_response", "sad_slide_rt",
      "fear_slide_response", "fear_slide_rt",
      "disgust_slide_response", "disgust_slide_rt",
      "anger_slide_response", "anger_slide_rt",
      "obs_slider_response", "obs_slider_rt",
      
      "psychopy_version", "frame_rate"
    ))


colnames(dta_psypy1)

dta_psypy1$social_nonsocial<- if_else(dta_psypy1$participant<200,"nonsocial", "social")


dta_psypy1$condition<- if_else(!is.na(dta_psypy1$rest_started), "rest_started",
                                        dta_psypy1$condition)

# unique(dta_psypy1$condition)
# table(is.na(dta_psypy1$condition))

dta_psypy1<- dta_psypy1%>%
  subset(!is.na(participant))



dta_psypy1$participant<- sub("_.*", "", dta_psypy1$filename)

table(dta_psypy1$participant)
# 65


# avoid gaps
dta_psypy1$stim_iaps<- if_else(dta_psypy1$condition == "rest_started", "rest_started",
                                dta_psypy1$stim_iaps)

dta_psypy1$emotioncategory<- if_else(dta_psypy1$condition == "rest_started", "rest_started",
                                      if_else(dta_psypy1$condition == "Example Stimuli", dta_psypy1$emotion,
                                dta_psypy1$emotioncategory))

table(is.na(dta_psypy1$stim_iaps))


  
# #so that zero is rest, so 1 to 4 is pratice
# dta_psypy1$test_this_n+5 #so that it doesn't overlap with pratice

########################################
# here let's make sure the trial start at 1 and not zero, because we will need 0 as trigger for trial off in ledalab
#######################################
dta_psypy1$trial_no_all<- if_else(dta_psypy1$condition == "rest_started", 1,
                                      if_else(dta_psypy1$condition == "Example Stimuli",
                                              dta_psypy1$trial_order+2,
                                              dta_psypy1$trial_order+6))

unique(dta_psypy1$trial_no_all)




# Split the data frame by the specified column and then iterate over the list to write each


```



```{r}
# fix unix start and end fir rest period
# <115 and < 211
range(dta_psypy1$unixtime_start)

# 170652740900

# tmp_test<- dta_psypy1%>%
#   subset(unixtime_start< 170652740900)

unique(tmp_test$participant)
unique(tmp_test$condition)
range(dta_psypy1$unixtime_start)

# dta_psypy1$unixtime_start*1000
# run pnly once
# dta_gsr$gsr_pulse_timestamp_sync_unix_cal_ms
# 
# dta_psypy1$unixtime_start<- if_else(dta_psypy1$unixtime_start< 170652740900,
#                                            round(dta_psypy1$unixtime_start*1000),
#                                            dta_psypy1$unixtime_start)

range(dta_psypy1$unixtime_start)
dta_psypy1$unixtime_end

# tmp_test<- dta_psypy1%>%
#   subset(unixtime_end< 170652753000)

# dta_psypy1$unixtime_end<- if_else(dta_psypy1$unixtime_end< 170652753000,
#                                            round(dta_psypy1$unixtime_end*1000),
#                                            dta_psypy1$unixtime_end)


range(dta_psypy1$unixtime_end)
unique(tmp_test$participant)
unique(tmp_test$condition)


```


```{r}
# write out psypy clean files per person
setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/behavioural/preprocessed")

# Create a unique identifier for each combination of ssid and screencontent
dta_psypy1 <- dta_psypy1 %>%
  mutate(split_column = participant)

# Split the data frame into a list of data frames based on the unique combinations
tmp_split_df <- split(dta_psypy1, dta_psypy1$split_column)

# Iterate over the list of split data frames and write each to a CSV file
walk(names(tmp_split_df), function(tmp_splitcol) {
  write_csv(tmp_split_df[[tmp_splitcol]], paste0('dta_psypy_', tmp_splitcol, ".csv"))
})


```