---
title: "preprocess_quest"
author: "Helio"
date: "2024-03-11"
output: html_document
---






AQ
IAS
Demographics
START
DASS
TAS
SLEEP

AQ_50



```{r}

# Load necessary library
library(readr)

setwd("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/Questionnaires/for analysis")

# Assuming your working directory is already set to where the files are
# For AQ files
aq_files <- list.files(pattern = "AQ")
tas_files <- list.files(pattern = "TAS")
dass_files <- list.files(pattern = "DASS")
ias_files <- list.files(pattern = "IAS")
dmg_files <- list.files(pattern = "DEMOG")
sleep_files <- list.files(pattern = "SLEEP")


# Read and combine AQ files
dta_aq28 <- do.call(rbind, lapply(aq_files, read_csv))%>%
  janitor::clean_names()

dta_tas21 <- do.call(rbind, lapply(tas_files, read_csv))%>%
  janitor::clean_names()

dta_dass <- do.call(rbind, lapply(dass_files, read_csv))%>%
  janitor::clean_names()

dta_ias <- do.call(rbind, lapply(ias_files, read_csv))%>%
  janitor::clean_names()


dta_sleep <- do.call(rbind, lapply(sleep_files, read_csv))%>%
  janitor::clean_names()

dta_demg <- do.call(rbind, lapply(dmg_files, read_csv))%>%
  janitor::clean_names()



library(readr)
library(dplyr)
library(janitor)
```
# Function to read files and harmonize columns
read_and_harmonize <- function(file_names) {
  # Read all files into a list of data frames
  list_of_dfs <- lapply(file_names, read_csv, col_types = cols())

  # Clean names immediately after reading
  list_of_dfs <- lapply(list_of_dfs, janitor::clean_names)

  # Identify all unique column names across all data frames
  all_columns <- unique(unlist(lapply(list_of_dfs, names)))

  # Ensure each data frame has all columns, fill missing ones with NA
  list_of_dfs <- lapply(list_of_dfs, function(df) {
    missing_cols <- setdiff(all_columns, names(df))
    df[missing_cols] <- NA
    # Optionally, order columns to match the first dataframe for consistency
    df <- df[, all_columns]
    return(df)
  })

  # Combine all data frames into one
  combined_df <- do.call(rbind, list_of_dfs)
  return(combined_df)
}



```{r}

unique(dta_aq28$participant_public_id)
# colnames(dta_aq28)
library(data.table)


dta_aq28_1<- dta_aq28%>%
  select(participant_public_id, participant_completion_code, experiment_version, 
          task_name, task_version,question_key, response)%>%
  subset(!is.na(response))%>%
  mutate(aq28grep_sup = grepl("AQ28_", question_key))%>%
  subset(aq28grep_sup == TRUE)%>%
  select(-aq28grep_sup)%>%
  setDT()%>%
    dcast(participant_public_id+participant_completion_code + experiment_version+ 
          task_name+ task_version~ question_key, value.var = "response")%>%
  janitor::clean_names()%>%
   mutate(participant = participant_public_id)%>%
   select(-participant_public_id,-experiment_version,-task_name,
          -task_version)
  
dta_aq28_1


# lets manuallys core aq


colnames(dta_aq28_1)

```


demog


```{r}

colnames(dta_demg)
# delete unecessary columns
# dta_demg1<- dta_demg[,c(8,12,16,27,28,32,34:35,38)]
# 
# colnames(dta_demg1)
# 
# # an issue with other?
# dta_demg1<- dta_demg1[, c(1:5,7:9)]%>%

dta_demg1<- dta_demg%>%
  subset(!is.na(key) & key== "value")%>%
  select(participant_public_id,participant_completion_code, experiment_version, 
          task_name, task_version,key, object_name, response)%>%
  setDT()%>%
  dcast(participant_public_id+participant_completion_code + experiment_version+ 
          task_name+ task_version+key~ object_name, value.var = "response")%>%
     mutate(participant = participant_public_id)%>%
   select(-participant_public_id,-experiment_version,-task_name,
          -task_version)
  


```

TAS
```{r}
colnames(dta_tas21)
dta_tas21_1


dta_tas21_1<- dta_tas21%>%
  select(participant_public_id, participant_completion_code, experiment_version,
         question_key, response)%>%
  subset(!is.na(response))%>%
  mutate(tas_grep_sup = grepl("TAS_", question_key))%>%
  subset(tas_grep_sup == FALSE & grepl("QUESTIONNAIRE", question_key) == FALSE) %>%
  select(-tas_grep_sup) %>%
  setDT()%>%
    dcast(participant_public_id+participant_completion_code + experiment_version 
           ~ question_key, value.var = "response")%>%
  janitor::clean_names()%>%
   mutate(participant = participant_public_id)%>%
   select(-participant_public_id,-experiment_version)
  
```

TAS AQ merge

```{r}
cor(dta_tas21_1$tas20_total, dta_aq28_1$aq28_total_cont)
as.tibble(as.matrix(dta_tas21_1))

left_join(dta_tas21_1, dta_aq28_1)%>%
  ggplot(aes(as.numeric(aq28_total_cont), as.numeric(tas20_total)))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()


```

DASS

```{r}
colnames(dta_dass)

dta_dass_1<- dta_dass%>%
  janitor::clean_names()%>%
  select(participant_public_id, participant_completion_code,question_key, response)%>%
  subset(!is.na(response))%>%
  mutate(dass_grep_sup = grepl("DASS21_", question_key))%>%
  subset(dass_grep_sup == TRUE) %>%
  select(-dass_grep_sup) %>%
  setDT()%>%
    dcast(participant_public_id+participant_completion_code 
           ~ question_key, value.var = "response")%>%
  janitor::clean_names()%>%
   mutate(participant = participant_public_id)%>%
   select(-participant_public_id)

dta_dass_1

left_join(dta_tas21_1, dta_dass_1)%>%
  ggplot(aes(as.numeric(tas20_total), as.numeric(dass21_total)))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()





```
sleep

```{r}
colnames(dta_sleep)
dta_sleep_1

dta_sleep_1


test_sleep <- dta_sleep%>%
  janitor::clean_names()%>%
  select(participant_public_id, participant_completion_code, 
          question, page, object_name,key, response)%>%
  subset(!is.na(response) & !is.na(object_name) )%>%

  # subset(key == "value") %>%
  mutate(key_new = paste0(object_name,paste0("_", key)))%>%
  subset(key!= "quantised")%>%
  select(-key,-object_name)
  setDT()%>%
    dcast(participant_public_id+participant_completion_code  +
           page ~ question, value.var = "response")%>%
  janitor::clean_names()

write_csv(test_sleep, "test_sleep.csv")




library(readr)
dta_sleep_1 <- read_csv("structured_sleep_data_with_scores.csv")%>%
    janitor::clean_names()%>%
   mutate(participant= participant_id)%>%
  select(-participant_id, -completion_code)

dta_sleep_1

colnames(dta_sleep_1)

left_join(dta_sleep_1, dta_dass_1)%>%
  ggplot(aes(total_sleep_score, as.numeric(dass21_total)))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()
```



final files
```{r}
dta_demg1
dta_tas21_1
dta_aq28_1
dta_dass_1
dta_sleep_1



dta_quest<- left_join(dta_demg1, dta_tas21_1) %>%
                left_join(., dta_aq28_1) %>%
                left_join(., dta_dass_1) %>%
    left_join(., dta_sleep_1) %>%
   left_join(., dta_sleep_1) 



dta_quest
```

