---
title: "r2_cortex_social_emophys"
author: "helio"
date: "2026-07-30"
output: html_document
---


related data: load("/Users/pw22812/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/JD_EmotionPhysio/Mixed Models Analysis/Mixed_models_output.RData")
related script: Mixed_models_analysis_JD.Rmd


```{r}
library(ggeffects)
library(emmeans)

time_seq <- seq(
  min(face_time_z_scored$timestamp_z, na.rm = TRUE),
  max(face_time_z_scored$timestamp_z, na.rm = TRUE),
  length.out = 100
)

emotion_AU_time <- emmeans(
  face_time_results$,
  ~ subj_emo_lab_no_amb | social_nonsocial * timestamp_z,
  at = list(timestamp_z = time_seq)
) |>
  confint() |>
  as.data.frame()

emotion_AU_time
# 
require(tidyverse)
ggplot(
  emotion_AU_time,
  aes(
    x = timestamp_z,
    y = emmean,
    colour = subj_emo_lab_no_amb,
    fill = subj_emo_lab_no_amb
  )
) +
  # geom_ribbon(
  #   aes(
  #     ymin = lower.CL,
  #     ymax = upper.CL
  #   ),
  #   alpha = .12,
  #   colour = NA
  # ) +
  stat_summary(geom = "line")+
  # geom_line(linewidth = 1) +
  # facet_wrap(~ social_nonsocial) +
  labs(
    x = "Time",
    y = "Estimated AU45 activity",
    colour = "Emotion",
    fill = "Emotion"
  ) +
  theme_classic()

```



Predict AU data directly 
```{r}
face_time_pred <- face_time_z_scored |>
  mutate(
    pred_AU45 = predict(
      face_time_results$eye_blink,
      newdata = face_time_z_scored,
      re.form = NULL
    )
  )
  
  pred_plot <- face_time_pred |>
  group_by(subj_emo_lab_no_amb, timestamp_z) |>
  summarise(
    pred_AU45 = mean(pred_AU45, na.rm = TRUE),
    .groups = "drop"
  )
  
  ggplot(
  pred_plot,
  aes(
    x = timestamp_z,
    y = pred_AU45,
    colour = subj_emo_lab_no_amb
  )
) +
  geom_line(linewidth = 1) +
  labs(
    x = "Time",
    y = "Predicted AU45",
    colour = "Emotion"
  ) +
  theme_classic()
  
  
  

```

raw data

```{r}
colnames(face_time_z_scored)
face_time_results$Brow_lower #au4
# au7 eyelid_tighten
face_time_results$eyelid_tighten 

face_time_z_scored$au04_r_smt_fitted <- fitted(
  face_time_results$Brow_lower
)

face_time_z_scored$au07_r_smt_fitted <- fitted(
  face_time_results$eyelid_tighten
)


face_time_z_scored$au07_r_smt_fitted <- fitted(
  face_time_results$eyelid_tighten
)

face_time_z_scored$au25_r_smt_fitted <- fitted(
  face_time_results$lips_apart
)


face_time_z_scored$au45_r_smt_fitted <- fitted(
  face_time_results$eye_blink
)

table(face_time_z_scored$participant)

# names(face_time_results)
# [1] "Inner_brow"         "Outer_brow"         "Brow_lower"         "eyelid_raise"       "cheek_raise"        "eyelid_tighten"     "nose_wrinkle"      
#  [8] "upper_lip_raise"    "lip_corner_pull"    "dimpler"            "lip_corner_depress" "chin_raise"         "lip_stretch"        "lip_tighten"       
# [15] "lips_apart"         "jaw_drop"           "eye_blink"  
colnames(face_time_z_scored)

# frame"               "timestamp"           "confidence"          "success"             "filename"            "au01_r_smt"         
#  [7] "au02_r_smt"          "au04_r_smt"          "au05_r_smt"          "au06_r_smt"          "au07_r_smt"          "au09_r_smt"         
# [13] "au10_r_smt"          "au12_r_smt"          "au14_r_smt"          "au15_r_smt"          "au17_r_smt"          "au20_r_smt"         
# [19] "au23_r_smt"          "au25_r_smt"          "au26_r_smt"          "au45_r_smt"          "stim_iaps"           "participant"        
# [25] "social_nonsocial"    "subj_emo_lab_no_amb" "timestamp_z"

# store the fitted au value
# e.g.
face_time_z_scored$au04_r_smt_fitted <- fitted(
  face_time_results$Brow_lower
)


face_time_z_scored%>%
  group_by(face_time_z_scored$participant, subj_emo_lab_no_amb, timestamp_z)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(timestamp_z, au45_r_smt,colour = subj_emo_lab_no_amb))+
  # stat_smooth()
  stat_summary(geom = "pointrange",size = .1)


face_time_z_scored%>%
  group_by(face_time_z_scored$participant, subj_emo_lab_no_amb, timestamp_z)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(timestamp_z, au45_r_smt_fitted, colour = subj_emo_lab_no_amb))+
  # stat_smooth()
  stat_summary(geom = "pointrange",size = .1)




```



```{r}
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(stringr)

# Labels corresponding to the names of face_time_results
au_labels <- c(
  Inner_brow         = "AU01 — Inner brow raiser",
  Outer_brow         = "AU02 — Outer brow raiser",
  Brow_lower         = "AU04 — Brow lowerer",
  eyelid_raise       = "AU05 — Upper-lid raiser",
  cheek_raise        = "AU06 — Cheek raiser",
  eyelid_tighten     = "AU07 — Lid tightener",
  nose_wrinkle       = "AU09 — Nose wrinkler",
  upper_lip_raise    = "AU10 — Upper-lip raiser",
  lip_corner_pull    = "AU12 — Lip-corner puller",
  dimpler            = "AU14 — Dimpler",
  lip_corner_depress = "AU15 — Lip-corner depressor",
  chin_raise         = "AU17 — Chin raiser",
  lip_stretch        = "AU20 — Lip stretcher",
  lip_tighten        = "AU23 — Lip tightener",
  lips_apart         = "AU25 — Lips apart",
  jaw_drop           = "AU26 — Jaw drop",
  eye_blink          = "AU45 — Eye blink"
)

# Check that all model names have a corresponding label
missing_labels <- setdiff(names(face_time_results), names(au_labels))

if (length(missing_labels) > 0) {
  stop(
    "Missing AU labels for: ",
    paste(missing_labels, collapse = ", ")
  )
}

# Extract observed and fitted values from every model
au_time_long <- imap_dfr(
  face_time_results,
  function(model, model_name) {

    # Contains exactly the observations used by this model
    model_data <- model.frame(model)

    # Outcome variable from the left-hand side of the formula
    outcome <- all.vars(formula(model))[1]

    tibble(
      participant = model_data$participant,
      emotion = model_data$subj_emo_lab_no_amb,
      timestamp_z = model_data$timestamp_z,

      au_name = model_name,
      au_label = unname(au_labels[model_name]),

      observed = model_data[[outcome]],
      fitted = unname(fitted(model))
    )
  }
) %>%
  pivot_longer(
    cols = c(observed, fitted),
    names_to = "series",
    values_to = "au_value"
  ) %>%
  mutate(
    series = recode(
      series,
      observed = "Observed AU activity",
      fitted = "Model-fitted AU activity"
    ),
    series = factor(
      series,
      levels = c(
        "Observed AU activity",
        "Model-fitted AU activity"
      )
    )
  )

# Calculate clean participant-level trajectories
# 
# This first averages across trials within each participant, emotion and time point. It then calculates the group mean and 95% confidence interval across participants.
au_time_summary <- au_time_long %>%
  group_by(
    au_name,
    au_label,
    series,
    participant,
    emotion,
    timestamp_z
  ) %>%
  summarise(
    au_value = mean(au_value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(
    au_name,
    au_label,
    series,
    emotion,
    timestamp_z
  ) %>%
  summarise(
    mean_au = mean(au_value, na.rm = TRUE),
    n_participants = sum(is.finite(au_value)),
    se = sd(au_value, na.rm = TRUE) / sqrt(n_participants),
    lower_ci = mean_au - 1.96 * se,
    upper_ci = mean_au + 1.96 * se,
    .groups = "drop"
  )
au_time_summary
plot_one_au <- function(selected_au) {

  plot_data <- au_time_summary %>%
    filter(au_name == selected_au)

  ggplot(
    plot_data,
    aes(
      x = timestamp_z,
      y = mean_au,
      colour = emotion,
      fill = emotion,
      group = emotion
    )
  ) +
    geom_ribbon(
      aes(
        ymin = lower_ci,
        ymax = upper_ci
      ),
      alpha = 0.12,
      colour = NA
    ) +
    geom_line(
      linewidth = 0.65,
      na.rm = TRUE
    ) +
    facet_wrap(
      ~series,
      nrow = 1,
      scales = "fixed"
    ) +
    labs(
      title = unique(plot_data$au_label),
      x = "Time (z-scored)",
      y = "AU intensity",
      colour = "Emotion",
      fill = "Emotion"
    ) +
    theme_classic(base_size = 11) +
    theme(
      plot.title = element_text(face = "bold"),
      strip.background = element_blank(),
      strip.text = element_text(face = "bold"),
       legend.position = "none"
      # legend.position = "bottom"
    )
}

plot_one_au("Brow_lower")
plot_one_au("eye_blink")


au_plots <- names(face_time_results) %>%
  set_names() %>%
  map(plot_one_au)

pdf(
  file = "AU_timecourses_observed_and_fitted.pdf",
  width = 8,
  height = 5,
  onefile = TRUE
)

walk(au_plots, print)

dev.off()


library(purrr)
library(stringr)

# Create an output folder
dir.create(
  "AU_timecourse_plots",
  showWarnings = FALSE,
  recursive = TRUE
)

iwalk(
  au_plots,
  function(plot_object, au_name) {

    # Make the filename safe
    safe_name <- au_name %>%
      str_replace_all("[^A-Za-z0-9_-]", "_")

    ggsave(
      filename = file.path(
        "AU_timecourse_plots",
        paste0(safe_name, "_timecourse.png")
      ),
      plot = plot_object,
      width = 8,
      height = 8.5,
      units = "in",
      dpi = 300,
      bg = "white"
    )
  }
)

# in order
library(purrr)
library(stringr)

dir.create(
  "AU_timecourse_plots",
  showWarnings = FALSE,
  recursive = TRUE
)

walk2(
  au_plots,
  seq_along(au_plots),
  function(plot_object, plot_number) {

    au_name <- names(au_plots)[plot_number]

    safe_name <- au_name %>%
      str_replace_all("[^A-Za-z0-9_-]", "_")

    ggsave(
      filename = file.path(
        "AU_timecourse_plots",
        sprintf(
          "%02d_%s_timecourse.png",
          plot_number,
          safe_name
        )
      ),
      plot = plot_object,
      width = 8,
      height = 5,
      units = "in",
      dpi = 300,
      bg = "white"
    )
  }
)
```


Pairwise

```{r}
emotion_pairwise_overall <- imap_dfr(
  face_time_results,
  function(model, model_name) {

    emm <- emmeans(
      model,
      ~ subj_emo_lab_no_amb,
      at = list(timestamp_z = 0),
      weights = "equal",
      lmer.df = "satterthwaite"
    )

    pairs(
      emm,
      adjust = "tukey"
    ) %>%
      as.data.frame() %>%
      mutate(
        au_name = model_name,
        au_label = unname(au_labels[model_name]),
        .before = 1
      )
  }
) %>%
  mutate(
    au_name = factor(
      au_name,
      levels = names(face_time_results)
    )
  ) %>%
  arrange(
    au_name,
    contrast
  )
emotion_pairwise <- emotion_pairwise_overall %>%
  mutate(
    significance = case_when(
      p.value < .001 ~ "***",
      p.value < .01  ~ "**",
      p.value < .05  ~ "*",
      TRUE           ~ "ns"
    )
  )

emotion_pairwise
```
NOW DOES UPPER FACE ACTIVITY DECREASES OR I9NCREASES IN SOCIAL CONDITION

```{r}

face_time_z_scored%>%
  group_by(participant, social_nonsocial, subj_emo_lab_no_amb, timestamp_z)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(timestamp_z, au04_r_smt_fitted+au07_r_smt_fitted, colour = social_nonsocial))+
    stat_summary(geom = "pointrange")+
  facet_grid(~subj_emo_lab_no_amb)
  


face_time_z_scored%>%
  group_by(participant, social_nonsocial, timestamp_z)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  mutate(upper_face_aus = (au04_r_smt+au07_r_smt)/2)%>%
  ggplot(aes(timestamp_z, upper_face_aus, colour = social_nonsocial))+
    stat_summary(geom = "pointrange")+
  facet_grid(~subj_emo_lab_no_amb)
  
```