---
title: "s4sn cleaner models"
author: "Helio"
date: "2025-09-11"
output: html_document
---

Valence and Intensity


```{r}
mod_res$val_subj<- lmer(val_slider_response ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$val_subj)


```


```{r}

mod_res$int_subj<- lmer(int_slider_response ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)
 # data = dta_emo%>%subset(participant!=235)%>%
 # subset(participant!=245)) #it remains sigmificant with those

anova(mod_res$int_subj)

emmeans::emmeans(mod_res$int_subj, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")


library(dplyr)
library(ggplot2)

# 1. Compute means by emotion × condition
unique(dta_emo$condition)
emo_diffs <- dta_emo %>%
  group_by(subj_emo_lab_no_amb, condition) %>%
  summarise(int_mean = mean(int_slider_response, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = condition, values_from = int_mean) %>%
  mutate(diff = `social` - `control`)   # adjust if your condition labels differ

# 2. Reorder factor levels by size of difference
order_levels <- emo_diffs %>%
  arrange(desc(diff)) %>%
  pull(subj_emo_lab_no_amb)


plts$s4sn_int<-
dta_emo %>%
  # subset(participant!= 235)%>%
  # subset(participant!= 245)%>%
  mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, int_slider_response, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("intensity (au)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plts$s4sn_int

ggsave("s4sn_int.png", plts$s4sn_int,  dpi = 300, width = 10, height = 6,  units = "in",
       device = "png")

 
 ggsave("s4sn_int.png", plts$s4sn_int, device = "png", width = 10, height = 6, dpi = 300)

```


testign individual emotion ratings
```{r}


mod_res$slid_hap<- lmer(happy_slide_response ~ 1+ social_nonsocial + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)


anova(mod_res$slid_hap)

mod_res$slid_sad<- lmer(sad_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)




mod_res$slid_fear<- lmer(fear_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)



mod_res$slid_disg<- lmer(disgust_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)



mod_res$slid_ang<- lmer(anger_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)




# 0) ANOVAs (unchanged)
anova(mod_res$slid_hap)
anova(mod_res$slid_ang)
anova(mod_res$slid_fear)
anova(mod_res$slid_disg)
anova(mod_res$slid_sad)

# 1) Collect models
mod_list_emo_slid <- list(
  slid_ang  = mod_res$slid_ang,
  slid_hap  = mod_res$slid_hap,
  slid_fear = mod_res$slid_fear,
  slid_disg = mod_res$slid_disg,
  slid_sad  = mod_res$slid_sad
)

# Optional tidy-up of workspace, safely
rm(list = intersect(c("betas","beta_pool"), ls()))

# 2) Extract betas/SEs for a term, with missing-term safety
get_beta_se <- function(term, models = mod_list_emo_slid) {
  pull_one <- function(m) {
    coefs <- summary(m)$coefficients
    if (!term %in% rownames(coefs)) return(c(beta = NA_real_, se = NA_real_))
    c(beta = coefs[term, "Estimate"], se = coefs[term, "Std. Error"])
  }
  mat <- sapply(models, pull_one)
  list(
    betas = as.numeric(mat["beta", ]),
    ses   = as.numeric(mat["se",   ])
  )
}

# Example correct call (for a quick check):
# get_beta_se("social_nonsocialsocial")

# 3) Pooling + Z-test with NA/zero checks
pool_effect <- function(betas, ses) {
  keep <- is.finite(betas) & is.finite(ses)
  if (!any(keep)) return(c(beta = NA_real_, se = NA_real_, Z = NA_real_, p = NA_real_))

  beta_pool <- sqrt(sum(betas[keep]^2, na.rm = TRUE))
  se_pool   <- sqrt(sum(ses[keep]^2,   na.rm = TRUE))

  if (!is.finite(se_pool) || se_pool == 0) {
    return(c(beta = beta_pool, se = se_pool, Z = NA_real_, p = NA_real_))
  }

  Z_stat  <- beta_pool / se_pool
  p_value <- 2 * pnorm(-abs(Z_stat))
  c(beta = beta_pool, se = se_pool, Z = Z_stat, p = p_value)
}

# 4) Run omnibus for your term
term_social <- "social_nonsocialsocial"

omnibus <- t(sapply(term_social, function(term) {
  dat <- get_beta_se(term)
  pool_effect(dat$betas, dat$ses)
}))

omnibus


```

autonomic


```{r}
# outliers
# 142
# 129
# 235

mod_res$hr_mean_diff_2 <- lmer(hr_mean_diff ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)
#  data = dta_emo%>%subset(participant!=235)%>%
# subset(participant!=142)) #results remain the same withouth these

anova(mod_res$hr_mean_diff_2)

dta_emo%>%
  group_by(participant,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  # subset(hr_mean_diff <20)%>%
  ggplot(aes(subj_emo_lab_no_amb, hr_mean_diff, colour = subj_emo_lab_no_amb))+
  # geom_smooth(aes(x = as.numeric(as.factor(subj_emo_lab_no_amb))))+
  # geom_jitter(alpha = .2)+
  stat_summary(geom = "pointrange")+
  # ylim(0,10)+
  # facet_grid(~subj_emo_lab_no_amb)+
  ggpubr::stat_compare_means()




emo_diffs_hr <- dta_emo %>%
  group_by(subj_emo_lab_no_amb, condition) %>%
  summarise(hr_mean_diff_mean = mean(hr_mean_diff, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = condition, values_from = hr_mean_diff_mean) %>%
  mutate(diff_hr = `social` - `control`)   # adjust if your condition labels differ

# 2. Reorder factor levels by size of difference
order_levels_hr <- emo_diffs_hr %>%
  arrange(desc(diff_hr)) %>%
  pull(subj_emo_lab_no_amb)

plts$s4sn_hr_diff<-


dta_emo %>%
  subset(participant!= 235)%>%
  subset(participant!= 142)%>%
  # subset(participant!= 142)%>%
  mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_hr))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, hr_mean_diff, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("heart rate (diff)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plts$s4sn_hr_diff

dta_emo %>%
  subset(participant!= 235)%>%
  subset(participant!= 142)%>%
  # subset(participant!= 142)%>%
  # mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels))%>%
  group_by(participant, condition) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, hr_mean_diff, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  # facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("intensity") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plts$s4sn_int

ggsave("s4sn_int.png", plts$s4sn_int,  dpi = 300, width = 10, height = 6,  units = "in",
       device = "png")

 
 ggsave("s4sn_int.png", plts$s4sn_int, device = "png", width = 10, height = 6, dpi = 300)

```

scr
```{r}
range(dta_emo$log_cda_n_scr)
mod_res$scr_cda_phas_2 <- lmer(log_cda_phasic_max ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + # doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)



dta_emo%>%
  subset(participant!= 104)%>%
  subset(participant!= 105)%>%
  subset(participant!= 147)%>%
  subset(participant!= 206)%>%
  subset(participant!= 248)%>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, log_cda_phasic_max, colour = social_nonsocial))+
  geom_jitter(alpha = .2)+
  # geom_boxplot()+
  # geom_text(aes(label = participant))+
  stat_summary(geom = "pointrange", fun.data = mean_se)+
  # ylim(0,10)+
  facet_grid(~subj_emo_lab_no_amb)
  ggpubr::stat_compare_means()
  
  anova(mod_res$scr_cda_phas_2)

  emmeans::emmeans(mod_res$scr_cda_phas_2, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")
  
  emmeans::emmeans(mod_res$scr_cda_phas_2, pairwise ~ social_nonsocial, 
                 adjust = "tukey")
  
  


  
  
  

emo_diffs_scr <- dta_emo %>%
  group_by(subj_emo_lab_no_amb, condition) %>%
  summarise(log_cda_phasic_max_mean = mean(log_cda_phasic_max, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = condition, values_from = log_cda_phasic_max_mean) %>%
  mutate(diff_scr = `social` - `control`)   # adjust if your condition labels differ

# 2. Reorder factor levels by size of difference
order_levels_scr <- emo_diffs_scr %>%
  arrange(desc(diff_scr)) %>%
  pull(subj_emo_lab_no_amb)

plts$s4sn_scr<-
dta_emo %>%
  subset(participant!= 104)%>%
  subset(participant!= 105)%>%
  subset(participant!= 206)%>%
  subset(participant!= 248)%>%
  mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_scr))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, log_cda_phasic_max, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .4) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("scr (log)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


plts$s4sn_scr

```


face
```{r}

dta_emo_face_scale

colnames(dta_emo_4mfa[,c(15:31)])
mod_res$pca_multil_omix_face <- pca(dta_emo_4mfa[,c(15:31)], 
                            scale = TRUE, 
                            center = TRUE, 
                            multilevel = pca_multil_design_face, ncomp = 3)


# interpret the components

 plotVar(mod_res$pca_multil_omix_face , var.names = TRUE, cutoff = 0.4, pch = 16)
 
mod_res$pca_multil_omix_face$loadings
dta_emo_4mfa$pc1_multl_face<-mod_res$pca_multil_omix_face$variates$X[,1] #whole face
dta_emo_4mfa$pc2_multl_face<-mod_res$pca_multil_omix_face$variates$X[,2]#mouth
dta_emo_4mfa$pc3_multl_face<-mod_res$pca_multil_omix_face$variates$X[,3]#eyes

option(scipen = 999)

median(abs(mod_res$pca_multil_omix_face$loadings$X))

 # 0.2048408

abs(mod_res$pca_multil_omix_face$loadings$X)




test1<- afex::aov_ez(data = dta_emo_4mfa,
             id = "participant",
             dv = "pc1_multl_face",
             between = "social_nonsocial",
             within = c("emotioncategory"))



test2<- afex::aov_ez(data = dta_emo_4mfa,
             id = "participant",
             dv = "pc3_multl_face",
             between = "social_nonsocial",
             within = c("emotioncategory"))
emmeans::emmeans(test, pairwise~ social_nonsocial|emotioncategory)
emmeans::emmeans(test, pairwise~ emotioncategory) 

```


```{r}
mod_res$pc1_multl_face <- lmer(pc1_multl_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     # (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)
mod_res$pc2_multl_face <- lmer(pc2_multl_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     # (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)

mod_res$pc3_multl_face <- lmer(pc3_multl_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     # (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)



# anova(mod_res$pc1_trad_face)
anova(mod_res$pc2_multl_face)
anova(mod_res$pc3_multl_face)
anova(mod_res$pc1_multl_face)
# expressivity
emmeans::emmeans(mod_res$pc1_multl_face, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$pc1_multl_face, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "none")


# car::Anova(mod_res$pc1_multl_face, type = 3)
# car::Anova(mod_res$pc2_multl_face, type = 3)
# car::Anova(mod_res$pc3_multl_face, type = 3)

```


mod_res$pc1_trad_face <- lmer(pc1_trad_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)
mod_res$pc2_trad_face <- lmer(pc2_trad_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)

mod_res$pc3_trad_face <- lmer(pc3_trad_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)

??car::Anova

anova(mod_res$pc1_trad_face)
anova(mod_res$pc2_trad_face)
anova(mod_res$pc3_trad_face)

# car::Anova(mod_res$pc1_trad_face, type = 3)
# car::Anova(mod_res$pc2_trad_face, type = 3)
# car::Anova(mod_res$pc3_trad_face, type = 3)


```{r}


plts$s4sn_face <-


dta_emo_4mfa %>%
  # pivot_longer(
  #   cols      = c(pc1_multl_face, pc2_multl_face, pc3_multl_face),
  #   names_to  = "au_pcs",
  #   values_to = "au_pc_scores"
  # ) %>%
  # mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_scr))%>%
  mutate(condition = if_else(social_nonsocial == "social","social", "control"))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, pc1_multl_face, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("face acticity - PC1 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# plts$s4sn_face <-



dta_emo_4mfa %>%
  # pivot_longer(
  #   cols      = c(pc1_multl_face, pc2_multl_face, pc3_multl_face),
  #   names_to  = "au_pcs",
  #   values_to = "au_pc_scores"
  # ) %>%
  # mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_scr))%>%
  mutate(condition = if_else(social_nonsocial == "social","social", "control"))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, pc3_multl_face, colour = condition, fill = condition)) +
  # geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("face acticity - PC3 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


plts$s4sn_face
plts$int_hr_scr <- (plts$s4sn_int+ plts$s4sn_hr_diff+plts$s4sn_scr)



 ggsave("int_hr_scr.png", plts$int_hr_scr, device = "png", width = 14, height = 7, dpi = 300)
 ggsave("int_hr_scr.pdf", plts$int_hr_scr, device = "pdf", width = 18, height = 7, dpi = 400)

 
 
  ggsave("face.pdf", plts$s4sn_face, device = "pdf", width = 10, height = 5, dpi = 400)

ggsave()



```



coherence

```{r}

  ggsave("face.pdf", plts$s4sn_face, device = "pdf", width = 10, height = 5, dpi = 400)




  ggsave("mfa_wide_space.pdf", plts$mfa_wide  , device = "pdf", width = 7, height = 6, dpi = 400)

  ggsave("mfa_wide_ind.pdf", plts$mfa_wide_ind  , device = "pdf", width = 5, height = 5, dpi = 400)



```