---
title: "s4sn abstract-2025"
author: "Helio"
date: "2025-05-30"
output: html_document
---


Plan
- analyse each signal in isolation
- compare is there a social effect of internal vs external signals
- whats the coherence
- use derived emotion


packages
```{r}
require(tidyverse)
require(readr)
require(lmerTest)

```

load datasets


plot settings


```{r}
p$graphstyle_int

sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here

p<- list()

p$graphstyle_int <-  theme(#base plot theme
  
  # axis lines
  axis.line.y = element_line(color="black", size = 1.5),
  axis.line.x = element_line(color="black", size = 1,5),
  
  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
  
  # text
  strip.text.x = element_text(size = 16*(sf+.5),  colour = "black"),
  strip.text.y = element_text(size = 16*(sf+.5),  colour = "black"),
  
  text=element_text(size = 14),
  axis.text.x = element_text(size = 15*(sf+.5), colour = "black",),
  axis.text.y = element_text(size = 15*(sf+.5), colour = "black"),
  
  
  # panel
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  
  # legend
  legend.position = "top",
  legend.key = element_rect(colour = "transparent", fill="transparent"),

  legend.text = element_text(size = 16*(sf+.5)),
  # legend.title= element_text(size = 16*(sf+.5)),
  legend.title = element_blank()
      
  # legend.title = element_text(size = 10*(sf+.3)),
  # legend line tends to be really small in print so adjust here
  # legend.key.height = unit(.5, "cm"),
  # legend.key.width = unit(2, "cm"),
  
  #legend.text = element_text(size = 10*sf),
  # legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)



```

use derived emotion
```{r}
dta_emo <- read_csv("Emotion_full_dataset2.csv")
View(dta_emo)

dta_emo
dta_emo%>%
  group_by(participant,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, obs_slider_response))+
  # geom_point()+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means(method = "t.test")


dta_emo%>%
  group_by(participant,emotioncategory, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(emotioncategory, log_cda_scr))+
  # geom_point()+
  stat_summary(geom = "pointrange")
  ggpubr::stat_compare_means(method = "t.test")

  facet_grid(~social_nonsocial)
  
  
  
  
  dta_emo%>%
  group_by(participant,emotioncategory, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(emotioncategory, log_cda_scr))+
  # geom_point()+
  stat_summary(geom = "pointrange")
  ggpubr::stat_compare_means(method = "t.test")

  facet_grid(~social_nonsocial)
  
  
  
    dta_emo%>%
  group_by(participant,emotioncategory, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  ggplot(aes(emotioncategory, int_slider_response))+
  # geom_point()+
  stat_summary(geom = "pointrange")
  ggpubr::stat_compare_means(method = "t.test")

  facet_grid(~social_nonsocial)



```


lmms
```{r}

colnames(dta_emo)
# Valence

mod_res<- list()

mod_res$val<- lmer(val_slider_response ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + 
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)



dta_emo%>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, val_slider_response, colour = social_nonsocial))+
  geom_jitter(alpha = .2)+
  # geom_dotplot(binaxis='y', stackdir='center',alpha = .2, width = .01, size = .03)+
  # stat_summary(geom = "pointrange")+
  stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
                 geom="pointrange", color="red")+
  # ylim(0,10)+
  facet_grid(~subj_emo_lab_no_amb)+
  ggpubr::stat_compare_means()

anova(mod_res$val)
emmeans::emmeans(mod_res$val, pairwise ~ social_nonsocial|emotioncategory, 
                 adjust = "tukey")
```
Type III Analysis of Variance Table with Satterthwaite's method
                                 Sum Sq Mean Sq NumDF  DenDF F value
social_nonsocial                   0.06   0.056     1   89.2  0.0288
emotioncategory                  463.68  92.737     5   60.0 48.1140
social_nonsocial:emotioncategory  18.00   3.600     5 5251.0  1.8679
                                               Pr(>F)    
social_nonsocial                              0.86554    
emotioncategory                  < 0.0000000000000002 ***
social_nonsocial:emotioncategory              0.09647 .  
arousal
```{r}
mod_res<- list()


# use emotion category

mod_res$int<- lmer(int_slider_response ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$int)
# summary(mod_res$int)

emmeans::emmeans(mod_res$int, pairwise ~ social_nonsocial|emotioncategory, 
                 adjust = "tukey")

report::report(mod_res$int)
report::report(anova(mod_res$int))

# significant for happy

# visualise

dta_emo$pred_int<- predict(mod_res$int)
dta_emo%>%
  ggplot(aes(pred_int, int_slider_response))+
  geom_point()+
  geom_smooth(method = "lm")+
  ylim(0,10)+
  facet_grid(~social_nonsocial)



dta_emo%>%
  group_by(participant,social_nonsocial, emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pred_int, colour = social_nonsocial, fill = social_nonsocial))+
  # geom_jitter(alpha = .2)+
  geom_dotplot(binaxis='y', stackdir='center', alpha = .3)+
stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
                 geom="pointrange", color="red")+
  # ylim(0,10)+
  facet_grid(~emotioncategory)


dta_emo$condition = if_else(dta_emo$social_nonsocial == "social", "social", "control")

dta_emo%>%
  group_by(participant,condition, emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(condition, int_slider_response, colour = condition, fill = condition))+
  # geom_jitter(alpha = .2)+
  
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_dotplot(binaxis = "y", stackdir = "center",
               alpha = .4, dotsize = .6, binwidth = .2) +

  facet_grid(~emotioncategory)+
    xlab("condition")+
     # ylab("transition entropy (bits)")+
  
  # ylab("rating")+
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic()+
  p$graphstyle_int+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))





dta_emo%>%
  group_by(participant,condition, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(condition, int_slider_response, colour = condition, fill = condition))+
  # geom_jitter(alpha = .2)+
  
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_dotplot(binaxis = "y", stackdir = "center",
               alpha = .4, dotsize = .6, binwidth = .2) +

  facet_grid(~subj_emo_lab_no_amb)+
    xlab("condition")+
     # ylab("transition entropy (bits)")+
  
  # ylab("rating")+
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic()+
  p$graphstyle_int+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Type III Analysis of Variance Table with Satterthwaite's method
                                 Sum Sq Mean Sq NumDF  DenDF F value
social_nonsocial                   7.06   7.056     1  90.00  1.7388
emotioncategory                  338.29  67.658     5  59.83 16.6730
social_nonsocial:emotioncategory  78.36  15.672     5 684.01  3.8621
                                          Pr(>F)    
social_nonsocial                        0.190638    
emotioncategory                  0.0000000002763 ***
social_nonsocial:emotioncategory        0.001854 ** 
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
internal


$contrasts
emotioncategory = anger:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.355 0.277 Inf   1.282  0.2000

emotioncategory = disgust:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.165 0.277 Inf   0.596  0.5514

emotioncategory = fear:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.439 0.277 Inf   1.583  0.1135

emotioncategory = happy:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.566 0.277 Inf   2.040  0.0413

emotioncategory = neutral:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.564 0.277 Inf   2.034  0.0419

emotioncategory = sad:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   -0.131 0.277 Inf  -0.474  0.6356

Degrees-of-freedom method: asymptotic 




We fitted a linear mixed model (estimated using ML and nloptwrap optimizer) to
predict int_slider_response with social_nonsocial and emotioncategory (formula:
int_slider_response ~ 1 + social_nonsocial * emotioncategory). The model
included participant as random effects (formula: list(~1 | participant, ~1 |
stim_iaps)). The model's total explanatory power is substantial (conditional R2
= 0.51) and the part related to the fixed effects alone (marginal R2) is of
0.21. The model's intercept, corresponding to social_nonsocial = nonsocial and
emotioncategory = anger, is at 5.68 (95% CI [4.91, 6.46], t(5385) = 14.36, p <
.001). Within this model:

  - The effect of social nonsocial [social] is statistically non-significant and
negative (beta = -0.36, 95% CI [-0.90, 0.19], t(5385) = -1.29, p = 0.198; Std.
beta = -0.12, 95% CI [-0.31, 0.06])
  - The effect of emotioncategory [disgust] is statistically non-significant and
positive (beta = 0.65, 95% CI [-0.35, 1.64], t(5385) = 1.28, p = 0.201; Std.
beta = 0.23, 95% CI [-0.12, 0.57])
  - The effect of emotioncategory [fear] is statistically non-significant and
negative (beta = -0.78, 95% CI [-1.77, 0.22], t(5385) = -1.53, p = 0.126; Std.
beta = -0.27, 95% CI [-0.61, 0.08])
  - The effect of emotioncategory [happy] is statistically non-significant and
negative (beta = -0.34, 95% CI [-1.34, 0.65], t(5385) = -0.68, p = 0.498; Std.
beta = -0.12, 95% CI [-0.46, 0.23])
  - The effect of emotioncategory [neutral] is statistically significant and
negative (beta = -2.86, 95% CI [-3.86, -1.87], t(5385) = -5.64, p < .001; Std.
beta = -0.99, 95% CI [-1.34, -0.65])
  - The effect of emotioncategory [sad] is statistically non-significant and
positive (beta = 0.83, 95% CI [-0.16, 1.83], t(5385) = 1.64, p = 0.100; Std.
beta = 0.29, 95% CI [-0.06, 0.63])
  - The effect of social nonsocial [social] × emotioncategory [disgust] is
statistically non-significant and positive (beta = 0.19, 95% CI [-0.18, 0.56],
t(5385) = 1.00, p = 0.317; Std. beta = 0.07, 95% CI [-0.06, 0.20])
  - The effect of social nonsocial [social] × emotioncategory [fear] is
statistically non-significant and negative (beta = -0.08, 95% CI [-0.46, 0.29],
t(5385) = -0.44, p = 0.661; Std. beta = -0.03, 95% CI [-0.16, 0.10])
  - The effect of social nonsocial [social] × emotioncategory [happy] is
statistically non-significant and negative (beta = -0.21, 95% CI [-0.58, 0.16],
t(5385) = -1.11, p = 0.269; Std. beta = -0.07, 95% CI [-0.20, 0.06])
  - The effect of social nonsocial [social] × emotioncategory [neutral] is
statistically non-significant and negative (beta = -0.21, 95% CI [-0.58, 0.16],
t(5385) = -1.10, p = 0.273; Std. beta = -0.07, 95% CI [-0.20, 0.06])
  - The effect of social nonsocial [social] × emotioncategory [sad] is
statistically significant and positive (beta = 0.49, 95% CI [0.11, 0.86],
t(5385) = 2.56, p = 0.011; Std. beta = 0.17, 95% CI [0.04, 0.30])

Standardized parameters were obtained by fitting the model on a standardized
version of the dataset. 95% Confidence Intervals (CIs) and p-values were
computed using a Wald t-distribution approximation.



Emotion ratings
```{r}

# use emotion category
# "happy_slide_response",
#   "sad_slide_response",
#   "fear_slide_response",
#   "disgust_slide_response",
#   "anger_slide_response"

mod_res$slid_hap<- lmer(happy_slide_response ~ 1+ social_nonsocial + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)



mod_res$slid_hap2<- lmer(happy_slide_response ~ 1+ social_nonsocial + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo%>%
                     subset(emotioncategory == "happy"))

anova(mod_res$slid_hap)

mod_res$slid_sad<- lmer(sad_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

mod_res$slid_sad2<- lmer(sad_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo%>%
                     subset(emotioncategory == "sad"))


mod_res$slid_fear<- lmer(fear_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)
dta_emo$emotioncategory

mod_res$slid_fear2<- lmer(fear_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                 data = dta_emo%>%
                     subset(emotioncategory == "fear"))

mod_res$slid_disg<- lmer(disgust_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)



mod_res$slid_disg2<- lmer(disgust_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                    data = dta_emo%>%
                     subset(emotioncategory == "disgust"))

mod_res$slid_ang<- lmer(anger_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)


mod_res$slid_ang2<- lmer(anger_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                 data = dta_emo%>%
                     subset(emotioncategory == "anger"))


anova(mod_res$slid_hap)
anova(mod_res$slid_ang)
anova(mod_res$slid_fear)
anova(mod_res$slid_disg)
anova(mod_res$slid_sad)


anova(mod_res$slid_hap2)
anova(mod_res$slid_ang2)
anova(mod_res$slid_fear2)
anova(mod_res$slid_disg2)
anova(mod_res$slid_sad2)

summary(mod_res$slid_sad2)


```



```{r}

library(dplyr)
library(tidyr)
library(forcats)
library(ggplot2)

# 1. Pivot and average per participant × condition × slider
summary_df <- dta_emo %>%
  pivot_longer(
    cols      = c(happy_slide_response, sad_slide_response,
                  fear_slide_response, disgust_slide_response,
                  anger_slide_response, int_slider_response,
                  val_slider_response),
    names_to  = "emo_slider",
    values_to = "value"
  ) %>%
  group_by(participant, social_nonsocial, emo_slider) %>%
  summarise(mean_value = mean(value, na.rm = TRUE), .groups = "drop") %>%

  # 2. Label conditions more nicely
  mutate(condition = if_else(social_nonsocial == "social", "social", "control")) %>%

  # 3. Compute per-slider difference
  group_by(emo_slider) %>%
  mutate(
    diff = abs(
      mean(mean_value[condition == "social"]) -
      mean(mean_value[condition == "control"])
    )
  ) %>%
  ungroup() %>%

  # 4. Reorder the factor by that diff (descending)
  mutate(
    emo_slider = fct_reorder(emo_slider, diff, .desc = TRUE)
  )

# 5. Plot
summary_df$emo_slider



summary_df%>%
  group_by(condition,emo_slider )%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  arrange(diff)


plts$subje_affect<-
summary_df%>%
  mutate(emo_slider =str_remove(emo_slider, "_.*$"))%>%
  mutate(emo_slider = factor(emo_slider, levels = c( "int","val","sad", "fear", "anger","disgust", "happy"), labels = c("intensity","valence","sad", "fear", "anger","disgust", "happy")))%>%
ggplot(
       aes(x = condition, y = mean_value,
           colour = condition, fill = condition, shape = condition)) +
  geom_boxplot(alpha = .1, colour = "black", notch = TRUE) +
  geom_dotplot(binaxis = "y", stackdir = "center",
               alpha = .5, dotsize = .6, binwidth = .2, colour = "black") +
  facet_grid(~ emo_slider) +
    xlab("condition")+
     # ylab("transition entropy (bits)")+
  
  ylab("rating")+
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic()+
  p$graphstyle_int+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


plts$subje_affect
```
# summary(mod_res$int)


emmeans::emmeans(mod_res$int, pairwise ~ social_nonsocial|emotioncategory, 
                 adjust = "tukey")

report::report(mod_res$int)
report::report(anova(mod_res$int))

# significant for happy

# visualise

dta_emo$pred_int<- predict(mod_res$int)
dta_emo%>%
  ggplot(aes(pred_int, int_slider_response))+
  geom_point()+
  geom_smooth(method = "lm")+
  ylim(0,10)+
  facet_grid(~social_nonsocial)



dta_emo%>%
  group_by(participant,social_nonsocial, emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pred_int, colour = social_nonsocial))+
  geom_jitter(alpha = .2)+
  stat_summary(geom = "pointrange")+
  # ylim(0,10)+
  facet_grid(~emotioncategory)+
  ggpubr::stat_compare_means()


dta_emo subjective emotion new


```{r}
colnames(dta_emo)

emotion_cols <- c(
  "happy_slide_response",
  "sad_slide_response",
  "fear_slide_response",
  "disgust_slide_response",
  "anger_slide_response"
)

 
dta_emo

dta_emo<-dta_emo %>%
  rowwise() %>%
  mutate(
    # Compute the maximum slider score
    max_score = max(c_across(all_of(emotion_cols))),
    
    # Count how many sliders equal that max
    n_tied = sum(c_across(all_of(emotion_cols)) == max_score),
    
    # Determine label: neutral if < 4.5, “ambiguous” if multiple share max,
    # otherwise pick the single highest
    subj_emotion_label2 = case_when(
      max_score < 4.5      ~ "neutral",
      n_tied > 1           ~ "ambiguous",
      TRUE                 ~ {
        # exactly one winner—find which column it is
        best_idx <- which.max(c_across(all_of(emotion_cols)))
        sub("_slide_response$", "", emotion_cols[best_idx])
      }
    )
  ) %>%
  ungroup() %>%
  select(-max_score, -n_tied)

unique(dta_emo$subj_emotion_label2)

# dta_emo group based emotion category


dta_label_emo <- dta_emo %>%
  group_by(stim_iaps) %>%
  summarise(
    across(all_of(emotion_cols), ~ mean(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    # compute the maximum of the five average scores
    max_avg = max(c_across(all_of(emotion_cols))),
    # count how many sliders tie at that maximum
    n_tied = sum(c_across(all_of(emotion_cols)) == max_avg),
    # assign label (neutral if max_avg < 4.5; “tie” if more than one share max; otherwise pick the one with the single highest mean)
    subj_emo_label_agg = case_when(
      max_avg < 4            ~ "neutral",
      n_tied  >  1             ~ "tie",
      TRUE                     ~ {
        best_idx <- which.max(c_across(all_of(emotion_cols)))
        sub("_slide_response$", "", emotion_cols[best_idx])
      }
    )
  ) %>%
  ungroup() %>%
  select(stim_iaps, subj_emo_label_agg)#emotion_cols


unique(dta_label_emo$subj_emo_label_agg)
dta_label_emo%>%
  
     pivot_longer(
    cols      = emotion_cols,
    names_to  = "emotion",      # name of the new “variable” column
    values_to = "emo_slider"      # name of the new “value” column
  )%>%
  ggplot(aes(emo_slider, colour = emotion))+
  geom_histogram()+
  facet_grid(emotion_label~emotion)+
  geom_vline(xintercept = 4.5)
  


# 2b. Join that label back onto the original dta_emo (so long format is preserved):
dta_emo <- dta_emo %>%
  left_join(dta_label_emo, by = "stim_iaps")

unique(dta_emo$subj_emotion_label2)
dta_emo$subj_emo_lab_no_amb<- if_else(dta_emo$subj_emotion_label2 == "ambiguous", dta_emo$subj_emo_label_agg, dta_emo$subj_emotion_label2)

unique(dta_emo$subj_emo_lab_no_amb)



table(dta_emo$emotioncategory)

table(dta_emo$subj_emo_lab_no_amb)

table(dta_emo$subj_emo_label_agg)


```


subjective based lmms on intensity

```{r}
mod_res$int_subj<- lmer(int_slider_response ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$int_subj)
# summary(mod_res$int)

emmeans::emmeans(mod_res$int_subj, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")


mod_res$int_subj_agg<- lmer(int_slider_response ~ 1+ social_nonsocial * subj_emo_label_agg + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$int_subj_agg)
# summary(mod_res$int)

emmeans::emmeans(mod_res$int_subj_agg, pairwise ~ social_nonsocial|subj_emo_label_agg, 
                 adjust = "tukey")


```





dta_emo%>%
  group_by(participant,condition, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(condition, int_slider_response, colour = condition, fill = condition))+
  # geom_jitter(alpha = .2)+
  
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_dotplot(binaxis = "y", stackdir = "center",
               alpha = .4, dotsize = .6, binwidth = .2) +

  facet_grid(~subj_emo_lab_no_amb)+
    xlab("condition")+
     # ylab("transition entropy (bits)")+
  
  # ylab("rating")+
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic()+
  p$graphstyle_int+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF  F value                Pr(>F)    
social_nonsocial                        4.35    4.35     1   91.8   1.2164              0.272960    
subj_emo_lab_no_amb                  2830.44  566.09     5 5174.5 158.2168 < 0.00000000000000022 ***
social_nonsocial:subj_emo_lab_no_amb   71.90   14.38     5 5284.0   4.0191              0.001216 ** 


subj_emo_lab_no_amb = anger:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.196 0.289 Inf   0.677  0.4983

subj_emo_lab_no_amb = disgust:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.142 0.230 Inf   0.615  0.5384

subj_emo_lab_no_amb = fear:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.368 0.254 Inf   1.449  0.1474

subj_emo_lab_no_amb = happy:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.589 0.227 Inf   2.593  0.0095

subj_emo_lab_no_amb = neutral:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.216 0.247 Inf   0.872  0.3833

subj_emo_lab_no_amb = sad:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   -0.110 0.244 Inf  -0.448  0.6538

lmm s with subjective and ojective are consistent



GSR

```{r}
dta_emo
mod_res$log_cda_phasic_max<- NULL

dta_emo$participant<- factor(dta_emo$participant)

range(dta_emo$log_cda_n_scr)
mod_res$scr_cda_phas <- lmer(log_cda_phasic_max ~ 1+ social_nonsocial * emotioncategory + 
                     (1:emotioncategory|participant) + # doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo %>%subset(log_cda_n_scr>-10))



anova(mod_res$scr_cda_phas)

mod_res$scr_cda_phas_2 <- lmer(log_cda_phasic_max ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + # doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$scr_cda_phas_3 <- lmer(log_cda_phasic_max ~ 1+ social_nonsocial * subj_emo_label_agg + 
                     (1|participant) + # doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)



anova(mod_res$scr_cda_phas)
anova(mod_res$scr_cda_phas_2)
anova(mod_res$scr_cda_phas_3)



summary(mod_res$scr_cda_phas)
??emmeans::emmeans
# emmeans::emmeans(mod_res$scr_cda_phas, pairwise ~ social_nonsocial|subjective_emotion, 
#                  adjust = "tukey")

report::report(mod_res$int)
report::report(anova(mod_res$int))

dta_emo%>%
  group_by(participant,social_nonsocial, subjective_emotion)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, log_cda_phasic_max, colour = social_nonsocial))+
  # geom_jitter(alpha = .2)+
  stat_summary(geom = "pointrange", fun.data = mean_sdl)+
  # ylim(0,10)+
  facet_grid(~subj_emo_lab_no_amb)
  ggpubr::stat_compare_means()


```

Type III Analysis of Variance Table with Satterthwaite's method
                                  Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial                  3.4529  3.4529     1   90.0  2.5802 0.11171  
emotioncategory                  14.3772  2.8754     5   59.1  2.1487 0.07202 .
social_nonsocial:emotioncategory  4.9331  0.9866     5 5251.0  0.7372 0.59545  
---


```{r}
dta_emo

# mod_res$log_cda_phasic_max<- NULL


mod_res$hr_mean_diff <- lmer(hr_mean_diff ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$hr_mean_bpm <- lmer(hr_mean_bpm ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$hr_ibi <- lmer(ibi_mean_s ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$hr_ibi2 <- lmer(ibi_mean_diff ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)




anova(mod_res$hr_mean_diff)
anova(mod_res$hr_ibi2)
anova(mod_res$hr_mean_bpm)
anova(mod_res$hr_ibi)


```



```{r}
mod_res$hr_mean_diff_2 <- lmer(hr_mean_diff ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$hr_mean_diff_3 <- lmer(hr_mean_diff ~ 1+ social_nonsocial * subj_emo_label_agg + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)





anova(mod_res$hr_mean_diff)
anova(mod_res$hr_mean_diff_2)


```



anova(mod_res$hr_mean_diff_3)
summary(mod_res$hr_mean_diff)
??emmeans::emmeans

emmeans::emmeans(mod_res$scr_cda_phas, pairwise ~ social_nonsocial|subjective_emotion, 
                 adjust = "tukey")

report::report(mod_res$int)
report::report(anova(mod_res$int))

emmeans::emmeans(mod_res$hr_mean_diff, pairwise ~ social_nonsocial, 
                 adjust = "tukey")


```{r}
options(scipen = 999)
dta_emo%>%
  group_by(participant,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  subset(hr_mean_diff <20)%>%
  ggplot(aes(subj_emo_lab_no_amb, hr_mean_diff, colour = subj_emo_lab_no_amb))+
  # geom_smooth(aes(x = as.numeric(as.factor(subj_emo_lab_no_amb))))+
  # geom_jitter(alpha = .2)+
  stat_summary(geom = "pointrange")+
  # ylim(0,10)+
  # facet_grid(~subj_emo_lab_no_amb)+
  ggpubr::stat_compare_means()




dta_emo%>%
  group_by(participant,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  # subset(hr_mean_diff <20)%>%
  ggplot(aes(social_nonsocial, hr_mean_diff, colour = social_nonsocial))+
  geom_jitter(alpha = .2)+
  stat_summary(geom = "pointrange")+
  # ylim(0,10)+
  # facet_grid(~subjective_emotion)+
  ggpubr::stat_compare_means()


```




Type III Analysis of Variance Table with Satterthwaite's method
                                 Sum Sq Mean Sq NumDF  DenDF F value   Pr(>F)
social_nonsocial                 154.38 154.381     1   90.0  8.8029 0.003852
emotioncategory                  278.19  55.639     5   59.4  3.1726 0.013232
social_nonsocial:emotioncategory 107.85  21.570     5 5250.8  1.2299 0.292093
                                   
social_nonsocial                 **
emotioncategory                  * 
social_nonsocial:emotioncategory   
external


Fixed effects:
                                                Estimate Std. Error         df t value
(Intercept)                                     -1.30919    0.34221  183.39011  -3.826
social_nonsocialsocial                          -0.85045    0.44847  195.92238  -1.896
emotioncategorydisgust                           0.42686    0.34155  122.78648   1.250
emotioncategoryfear                              0.33980    0.34155  122.78648   0.995
emotioncategoryhappy                             0.34898    0.34155  122.78648   1.022
emotioncategoryneutral                           0.99565    0.34155  122.78648   2.915
emotioncategorysad                               0.02175    0.34155  122.78648   0.064
social_nonsocialsocial:emotioncategorydisgust   -0.81155    0.39522 5250.81865  -2.053
social_nonsocialsocial:emotioncategoryfear      -0.23969    0.39522 5250.81865  -0.606
social_nonsocialsocial:emotioncategoryhappy      0.07001    0.39522 5250.81865   0.177
social_nonsocialsocial:emotioncategoryneutral   -0.24255    0.39522 5250.81865  -0.614
social_nonsocialsocial:emotioncategorysad       -0.23948    0.39522 5250.81865  -0.606
                                              Pr(>|t|)    
(Intercept)                                   0.000179 ***
social_nonsocialsocial                        0.059386 .  
emotioncategorydisgust                        0.213756    
emotioncategoryfear                           0.321761    
emotioncategoryhappy                          0.308905    
emotioncategoryneutral                        0.004228 ** 
emotioncategorysad                            0.949331    
social_nonsocialsocial:emotioncategorydisgust 0.040082 *  
social_nonsocialsocial:emotioncategoryfear    0.544226    
social_nonsocialsocial:emotioncategoryhappy   0.859403    
social_nonsocialsocial:emotioncategoryneutral 0.539426    
social_nonsocialsocial:emotioncategorysad     0.544577    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Correlation of Fixed Effects:
                       (Intr) scl_nn emtnctgryd emtnctgryf emtnctgryh emtnctgryn
scl_nnsclsc            -0.626                                                   
emtnctgryds            -0.499  0.244                                            
emtnctgryfr            -0.499  0.244  0.500                                     
emtnctgryhp            -0.499  0.244  0.500      0.500                          
emtnctgrynt            -0.499  0.244  0.500      0.500      0.500               
emtnctgrysd            -0.499  0.244  0.500      0.500      0.500      0.500    
scl_nnsclscl:mtnctgryd  0.276 -0.441 -0.553     -0.276     -0.276     -0.276    
scl_nnsclscl:mtnctgryf  0.276 -0.441 -0.276     -0.553     -0.276     -0.276    
scl_nnsclscl:mtnctgryh  0.276 -0.441 -0.276     -0.276     -0.553     -0.276    
scl_nnsclscl:mtnctgryn  0.276 -0.441 -0.276     -0.276     -0.276     -0.553    
scl_nnsclscl:mtnctgrys  0.276 -0.441 -0.276     -0.276     -0.276     -0.276    
                       emtnctgrys scl_nnsclscl:mtnctgryd scl_nnsclscl:mtnctgryf
scl_nnsclsc                                                                    
emtnctgryds                                                                    
emtnctgryfr                                                                    
emtnctgryhp                                                                    
emtnctgrynt                                                                    
emtnctgrysd                                                                    
scl_nnsclscl:mtnctgryd -0.276                                                  
scl_nnsclscl:mtnctgryf -0.276      0.500                                       
scl_nnsclscl:mtnctgryh -0.276      0.500                  0.500                
scl_nnsclscl:mtnctgryn -0.276      0.500                  0.500                
scl_nnsclscl:mtnctgrys -0.553      0.500                  0.500                
                       scl_nnsclscl:mtnctgryh scl_nnsclscl:mtnctgryn
scl_nnsclsc                                                         
emtnctgryds                                                         
emtnctgryfr                                                         
emtnctgryhp                                                         
emtnctgrynt                                                         
emtnctgrysd                                                         
scl_nnsclscl:mtnctgryd                                              
scl_nnsclscl:mtnctgryf                                              
scl_nnsclscl:mtnctgryh                                              
scl_nnsclscl:mtnctgryn  0.500                                       
scl_nnsclscl:mtnctgrys  0.500                  0.500 



$emmeans
 social_nonsocial emmean    SE  df asymp.LCL asymp.UCL
 nonsocial        -0.954 0.262 Inf     -1.47    -0.441
 social           -2.048 0.273 Inf     -2.58    -1.513

Results are averaged over the levels of: emotioncategory 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social     1.09 0.369 Inf   2.967  0.0030

Results are averaged over the levels of: emotioncategory 
Degrees-of-freedom method: asymptotic
```{r}


mod_res$entr1 <- lmer(mean_trans_entropy_maxnorm_norm_by_img ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant), #subjective_emotion doesn't converge
                     # (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)
# mod_res$entr2 <- lmer(mean_stat_entropy_maxnorm_norm_by_img ~ 1+ social_nonsocial * subjective_emotion + 
#                      (1|participant), #subjective_emotion doesn't converge
#                      # (1|stim_iaps), #social_nonsocial doesn't converge
#                    REML = FALSE,
#                    data = dta_emo)

dta_emo$rat_fix_dur<- dta_emo$mean_fix_dur_stim_aoi/ (dta_emo$mean_fix_dur_stim_aoi+dta_emo$mean_fix_dur_nonstim_aoi)
dta_emo$mean_fix_dur<- (dta_emo$mean_fix_dur_stim_aoi+dta_emo$mean_fix_dur_nonstim_aoi)/2
dta_emo$mean_sac_amp<- (dta_emo$mean_sac_amp_stim_aoi + dta_emo$mean_sac_amp_nonstim_aoi)/2



mod_res$mean_fix_dur <- lmer(log1p(mean_fix_dur+.1) ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$mean_fix_dur_2 <- lmer(log1p(mean_fix_dur+.1) ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$mean_fix_dur_3 <- lmer(log1p(mean_fix_dur+.1) ~ 1+ social_nonsocial * subj_emo_label_agg + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)


anova(mod_res$mean_fix_dur)
anova(mod_res$mean_fix_dur_2)
anova(mod_res$mean_fix_dur_3)

```

plot(mod_res$mean_fix_dur)



```{r}
mod_res$mean_sac_amp <- lmer(mean_sac_amp ~ 1+ social_nonsocial * emotioncategory + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)


mod_res$mean_sac_amp_2 <- lmer(mean_sac_amp ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$mean_sac_amp_3 <- lmer(mean_sac_amp ~ 1+ social_nonsocial * subj_emo_label_agg + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)



anova(mod_res$mean_sac_amp )
anova(mod_res$mean_sac_amp_2 )
anova(mod_res$mean_sac_amp_3 )


```



mod_res$mean_fix_dur_nonstim_aoi <- lmer(mean_fix_dur_nonstim_aoi ~ 1+ social_nonsocial * subjective_emotion + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)

mod_res$rat_fix_dur <- lmer(rat_fix_dur ~ 1+ social_nonsocial * subjective_emotion + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)


anova(mod_res$entr1)
anova(mod_res$entr2)
```{r}
anova(mod_res$mean_fix_dur_stim_aoi)
anova(mod_res$mean_fix_dur_nonstim_aoi)


```

anova(mod_res$rat_fix_dur)
summary(mod_res$entr1)
??emmeans::emmeans
emmeans::emmeans(mod_res$mean_fix_dur_stim_aoi, pairwise ~ social_nonsocial|emotioncategory, 
                 adjust = "tukey")

report::report(mod_res$int)
report::report(anova(mod_res$int))


PCA first


```{r}
# start with a PCA
options(scipen = 999)
colnames(dta_emo)
dta_emo_face<- dta_emo[,c(1:3,96,97,31:47)]
dta_emo_face_w_subj<- dta_emo[,c(1:3,107,96,97,31:47)]
# PCA first

scale_vars <- names(dta_emo)[31:47]

dta_emo_face_scale<-dta_emo_face%>%
  ungroup()%>%
  # group_by(participant)%>%
  # 1. group by your grouping vars
  
  # 2. for each of the scale_vars, replace with (x - mean)/sd
  mutate(across(
    all_of(scale_vars),
    ~ as.numeric( scale(.x) ),      # scale() returns a 1-column matrix, so we coerce back to numeric
    .names = "{.col}_z"              # optional: give new columns a “_z” suffix
  )) %>%
  # 3. drop the grouping
  ungroup()
  
# gather first
colnames(dta_emo_face_scale)


dta_emo_face_scale




# 1a. PCA on the raw variables, centring & scaling in one go
mod_res$pca <- prcomp(dta_emo_face_scale[, scale_vars],
                  centre = TRUE,    # subtract variable means
                  scale. = TRUE)    # divide by variable sds

mod_res$pca 
dta_emo_face_scale_soc<- dta_emo_face_scale%>%subset(social_nonsocial == "social")
dta_emo_face_scale_nsoc<- dta_emo_face_scale%>%subset(social_nonsocial != "social")

social_nonsocial
mod_res$pca_soc1 <- prcomp(dta_emo_face_scale_soc[, scale_vars],
                  centre = FALSE,    # subtract variable means
                  scale. = FALSE)

mod_res$pca_nsoc1 <- prcomp(dta_emo_face_scale_nsoc[, scale_vars],
                  centre = TRUE,    # subtract variable means
                  scale. = TRUE) 

dta_emo_wide_mfa_nonsocial


get_pca_var(mod_res$pca_soc1)
get_pca_var(mod_res$pca_nsoc1)

summary(mod_res$pca_nsoc1)
summary(mod_res$pca_soc1)


colnames(dta_emo_wide_mfa_nonsocial)

dta_emo_wide_mfa_nonsocial

dta_emo_wide_mfa_soc
  
  17*60
mod_res$pca_nsoc2 <- prcomp(dta_emo_wide_mfa_nonsocial[, 663:1682],
                  centre = TRUE,    # subtract variable means
                  scale. = TRUE) 

mod_res$pca_soc2 <- prcomp(dta_emo_wide_mfa_soc[, 663:1682],
                  centre = TRUE,    # subtract variable means
                  scale. = TRUE)

summary(mod_res$pca_nsoc2)
summary(mod_res$pca_soc2)


(mod_res$pca_nsoc1$sdev)^2
(mod_res$pca_soc1$sdev)^2

# missMDA::



library(dplyr)
library(tidyr)

dta_emo %>%
  select(social_nonsocial, participant,stim_iaps, subj_emo_lab_no_amb, emotioncategory, starts_with("au")) %>%
  pivot_longer(
    cols      = starts_with("au"),
    names_to  = "au_code",
    values_to = "au_value"
  ) %>%
  group_by(participant, au_code)%>%
  mutate(au_value = scale((au_value+.01)))%>%
    group_by(social_nonsocial,subj_emo_lab_no_amb,au_code)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
    #   group_by(au_code)%>%
    # mutate(au_value = scale(au_value))%>%
  ggplot(aes(subj_emo_lab_no_amb,au_code, fill = au_value))+
  geom_tile()+
  scale_fill_viridis_c(option = "inferno")+
  facet_grid(~social_nonsocial)
```




```{r}
 library(MissMDA)
library(dplyr)
library(lme4)

# install.packages("factoextra")

colnames(dta_emo_face_scale)

sd(dta_emo_face_scale$au01_inner_brow_raise)

# ??FactoMineR::PCA


mod_res$pca <- FactoMineR::PCA(dta_emo_face_scale[, c(1:3,6:22)],
                  # centre = TRUE,    # subtract variable means
                  scale.unit = TRUE,
                  graph = TRUE,
                  quali.sup =c(1,2,3))




# # 1a. PCA on the raw variables, centring & scaling in one go
# mod_res$pca <- prcomp(dta_emo_face_scale[, scale_vars],
#                   centre = TRUE,    # subtract variable means
#                   scale. = TRUE)    # divide by variable sds


library(factoextra)

fviz_eig(mod_res$pca, addlabels = TRUE, 
         ylim = c(0, 50), 
         main = "Variance Explained by PCs")

fviz_pca_biplot(mod_res$pca , repel = TRUE,
                geom.ind = "point",
                col.ind = "steelblue",
                col.var = "darkred",
                title = "PCA Biplot")


mod_res$pca$rotation


# get variable information
var_info <- get_pca_var(mod_res$pca)

# % contribution of all variables to PC1
desc(var_info$contrib[, "Dim.1"])

var_info$contrib

mod_res$pca$rotation


fviz_contrib(mod_res$pca, choice = "var", axes = 1,
             top    = 10,
             title  = "Top 10 contributors to PC1")
# pc 1 is mouth nose and eyes (overall facia moveent)

fviz_contrib(mod_res$pca, choice = "var", axes = 2,
             top    = 10,
             title  = "Top 10 contributors to PC2")

# pc 2 mouth

fviz_contrib(mod_res$pca, choice = "var", axes = 3,
             top    = 10,
             title  = "Top 10 contributors to PC3")
# PC3 mostly eye
dta_emo_face_scale<-dta_emo_face


dta_emo_face_scale$PC1<- mod_res$pca$ind$coord[, 1]
dta_emo_face_scale$PC2<- mod_res$pca$ind$coord[, 2]
dta_emo_face_scale$PC3<- mod_res$pca$ind$coord[, 3]


dta_emo_face_scale%>%
   pivot_longer( cols      = c(PC1, PC2, PC3),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores,colour = social_nonsocial))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means()

```


```{r}

dta_emo_face_scale
dta_emo_face_scale_long

dta_emo_face_scale

mod_res$au_pc1 <- lmer(au01_inner_brow_raise ~ 1+ social_nonsocial *emotioncategory+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (0+social_nonsocial|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale)

summary(mod_res$au_pc1)

mod_res$au_pc2 <- lmer(PC2 ~ 1+ social_nonsocial *emotioncategory+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (0+social_nonsocial|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale)

mod_res$au_pc3 <- lmer(PC3 ~ 1+ social_nonsocial *emotioncategory+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (0+social_nonsocial|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale)

anova(mod_res$au_pc1)
anova(mod_res$au_pc2)
anova(mod_res$au_pc3)

```



```{r}

library(lme4)
colnames(dta_emo_face_scale)
# pick out your AU columns in order
au_mat <- with(dta_emo_face_scale,
               cbind(colnames(dta_emo_face_scale[,6:22])))

# fit all seven models at once:

library(lme4)
library(purrr)

# 1. Make a character vector of your AU column-names:
au_vars <- c(colnames(dta_emo_face_scale[,6:22]))

# 2. Write a little function that builds & fits the model for any one AU:


fit_au <- function(dep_var) {
  # construct formula: e.g. au01 ~ social_nonsocial*emotioncategory + (1|participant) + (0+social_nonsocial|stim_iaps)
  fml <- as.formula(
    paste(dep_var, 
          "~ 1 + social_nonsocial * subj_emo_lab_no_amb +",
          "(1 | participant) +",
          "(1 | stim_iaps)")
  )
  lmer(fml, data = dta_emo_face_scale, REML = FALSE)
}

# 3. Fit them all in one go:
mod_list <- map(au_vars, fit_au)
names(mod_list) <- au_vars

# Now mod_list$au01_inner_brow_raise, mod_list$au02_outer_brow_raise, … are your models
```

```{r}

emmeans::emmeans(mod_res$au_pc1, pairwise~social_nonsocial)
emmeans::emmeans(mod_res$au_pc2, pairwise~social_nonsocial)
emmeans::emmeans(mod_res$au_pc3, pairwise~social_nonsocial)

emmeans::emmeans(mod_res$au_pc3, pairwise~social_nonsocial|emotioncategory)

emmeans::emmeans(mod_res$au_pc2, pairwise~social_nonsocial|emotioncategory)

mod_res$au_pc2 



```


```{r}
mod_res$au_pc1_subj <- lmer(PC1 ~ 1+ social_nonsocial *subj_emo_lab_no_amb+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale)


mod_res$au_pc2_subj <- lmer(PC2 ~ 1+ social_nonsocial *subj_emo_lab_no_amb+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale)


mod_res$au_pc3_subj <- lmer(PC3 ~ 1+ social_nonsocial *subj_emo_lab_no_amb+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale)

summary(mod_res$au_pc1_subj)

summary(mod_res$au_pc2_subj)
summary(mod_res$au_pc2_subj)

anova(mod_res$au_pc1_subj)
anova(mod_res$au_pc2_subj)
anova(mod_res$au_pc3_subj)

```


```{r}
dta_emo_face_scale %>%
  select(social_nonsocial, participant,stim_iaps, subj_emo_lab_no_amb, emotioncategory, 
         starts_with("au"), PC1, PC2,PC3) %>%
  pivot_longer(
    cols      = starts_with("PC"),
    names_to  = "pc_code",
    values_to = "pc_value"
  ) %>%
  group_by(participant, pc_code)%>%
  mutate(pc_value = scale((pc_value+.01)))%>%
    group_by(social_nonsocial,subj_emo_lab_no_amb,pc_code)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
    #   group_by(au_code)%>%
    # mutate(au_value = scale(au_value))%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_code, fill = pc_value))+
  geom_tile()+
  scale_fill_viridis_c(option = "inferno")+
  facet_grid(~social_nonsocial)


```

# anova
```{r}
dta_emo_face_scale_agg<- dta_emo_face_scale%>%
      group_by(participant, subj_emo_lab_no_amb,social_nonsocial )%>%
    summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  mutate(PC1_z = scale(PC1),
         PC2_z = scale(PC3),
         PC3_z = scale(PC3))


dta_emo_face_scale_agg1<- dta_emo_face_scale_agg%>%
  pivot_longer(
    cols      = c(PC1,PC2,PC3),
    names_to  = "pc_code",
    values_to = "pc_value"
  ) %>%
 group_by(participant, subj_emo_lab_no_amb,social_nonsocial,pc_code )%>%
    summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()


dta_emo_face_scale_agg1_z<- dta_emo_face_scale_agg%>%
  pivot_longer(
    cols      = c(PC1_z,PC2_z,PC3_z),
    names_to  = "pc_code_z",
    values_to = "pc_value"
  ) %>%
 group_by(participant, subj_emo_lab_no_amb,social_nonsocial,pc_code_z )%>%
    summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()



 afex::aov_ez(data = dta_emo_face_scale_agg1,
             id = "participant",
             dv = "pc_value",
             between = "social_nonsocial",
             within = c("pc_code"))
 



afex::aov_ez(data = dta_emo_face_scale_agg1_z,
             id = "participant",
             dv = "pc_value",
             between = "social_nonsocial",
             within = c("pc_code_z"))


dta_emo_face_scale_agg1_z



```


```{r}


dta_emo_face_scale_agg2<- dta_emo_face_scale_agg%>%
 group_by(participant, subj_emo_lab_no_amb,social_nonsocial )%>%
    summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()




# z 
afex::aov_ez(data = dta_emo_face_scale_agg2,
             id = "participant",
             dv = "PC1_z",
             between = "social_nonsocial")


afex::aov_ez(data = dta_emo_face_scale_agg2,
             id = "participant",
             dv = "PC2_z",
             between = "social_nonsocial")


afex::aov_ez(data = dta_emo_face_scale_agg2,
             id = "participant",
             dv = "PC3_z",
             between = "social_nonsocial")

# orig scale

afex::aov_ez(data = dta_emo_face_scale_agg2,
             id = "participant",
             dv = "PC1",
             between = "social_nonsocial")


afex::aov_ez(data = dta_emo_face_scale_agg2,
             id = "participant",
             dv = "PC2",
             between = "social_nonsocial")


afex::aov_ez(data = dta_emo_face_scale_agg2,
             id = "participant",
             dv = "PC3",
             between = "social_nonsocial")
```


```{r}

dta_emo_face_scale$subj_emo_label_agg<- dta_emo$subj_emo_label_agg

dta_emo_face_scale$subj_emo_lab_no_amb<- dta_emo$subj_emo_lab_no_amb

dta_emo_face_scale_long<- dta_emo_face_scale%>%
   pivot_longer(
    cols      = c(PC1,PC2,PC3),
    names_to  = "au_pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )


dta_emo_face_scale_long%>%
  ggplot(aes(au_pcs, pc_scores,colour = social_nonsocial ))+
  stat_summary(geom = "pointrange")+
  

```


# do MFA or PCA while avoiding violatign the independence of observations assumptions

```{r}

colnames(dta_emo_face_scale)
colnames(dta_emo_face)

options(scipen = 999)
dta_emo_face[,c(1:4,6:22)]%>%
  select(participant, social_nonsocial, stim_iaps, emotioncategory, everything()) %>%
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps, emotioncategory),
    values_from = names(dta_emo_face)[6:22],
    names_sep   = "_"  
  )
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),
    values_from = names(dta_emo_face[,6:22]),
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )

# sd(dta_emo_face$au01_inner_brow_raise)
# sd(dta_emo_face_scale$au01_inner_brow_raise_z)
  
  
  
  dta_emo_face <- dta_emo_face %>%
  mutate(
    emotioncategory = factor(
      emotioncategory
    )
  )

# 2. pivot with emotioncategory first:
wide
dta_emo_face$emotioncategory

library(dplyr); library(tidyr)

dta_emo_face_wide <- dta_emo_face %>%
  select(participant, social_nonsocial, stim_iaps, emotioncategory, everything()) %>%
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),    # ← flip these two
    values_from = names(dta_emo_face)[6:22],
    names_sep   = "_"
  )%>%
  relocate(ends_with("_anger"),  .after = social_nonsocial)%>%
  relocate(ends_with("_fear"),   .after = (ends_with("_anger"))) %>%
  relocate(ends_with("_happy"),  .after = (ends_with("_fear"))) %>%
  relocate(ends_with("_sad"),  .after = (ends_with("_happy"))) %>%  
  relocate(ends_with("_neutral"),.after = (ends_with("_sad")))




dta_emo_face_wide_emo

colnames(dta_emo_face_wide)
# 1a. PCA on the raw variables, centering & scaling in one go
 # divide by variable sds

require(Factoshiny)
require(factoextra)


?FactoMineR::PCA
mod_res$pca_wide <- FactoMineR::PCA(dta_emo_face_wide[, 2:1022],
                  # centre = TRUE,    # subtract variable means
                  scale.unit = FALSE,
                  graph = TRUE,
                  quali.sup =1)   







fviz_screeplot(mod_res$pca_wide)



factoextra::fviz_pca_ind(mod_res$pca_wide )
?factoextra:::fviz_contrib
factoextra:::fviz_contrib(mod_res$pca_wide, choice = "var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$pca_wide, choice = "var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$pca_wide, choice = "var", top = 15, axes = 3)


mod_res$pca_wide$ind$coord

mod_res$pca_wide$var$coord

dta_emo_face_wide$pc1<- mod_res$pca_wide$ind$coord[,1]
dta_emo_face_wide$pc2<- mod_res$pca_wide$ind$coord[,2]
dta_emo_face_wide$pc3<- mod_res$pca_wide$ind$coord[,3]
dta_emo_face_wide$pc4<- mod_res$pca_wide$ind$coord[,4]


```



```{r}

dta_emo_face_wide%>%
  ggplot(aes(social_nonsocial,pc1, fill = social_nonsocial)) +
  geom_dotplot(binaxis='y', stackdir='center', alpha = .3)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means()

dta_emo_face_wide%>%
  ggplot(aes(social_nonsocial,pc2, fill = social_nonsocial)) +
  geom_dotplot(binaxis='y', stackdir='center', alpha = .3)+
  stat_summary(geom = "pointrange")+
    ggpubr::stat_compare_means()


dta_emo_face_wide%>%
  ggplot(aes(social_nonsocial,pc3, fill = social_nonsocial)) +
  geom_dotplot(binaxis='y', stackdir='center', alpha = .3)+
  stat_summary(geom = "pointrange")+
    ggpubr::stat_compare_means()

dta_emo_face_wide%>%
  ggplot(aes(social_nonsocial,pc4, fill = social_nonsocial)) +
  geom_dotplot(binaxis='y', stackdir='center', alpha = .3)+
  stat_summary(geom = "pointrange")+
    ggpubr::stat_compare_means()


```

```{r}
 dta_emo_face_wide%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  # group_by(participant,au_pcs,social_nonsocial)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores,colour = social_nonsocial))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means()
 
```
 # agg emotion
 
 emo wide agg mfa
 
```{r}


# aggregate by emotion


dta_emo_face_wide_emo<- 

dta_emo_face %>%
  select(participant, social_nonsocial, stim_iaps, emotioncategory, everything()) %>%
  ungroup()%>%
  mutate_at(scale_vars, scale)%>%
  group_by(participant,social_nonsocial, emotioncategory)%>%
  
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(emotioncategory),    # ← flip these two
    values_from = names(dta_emo_face)[6:22],
    names_sep   = "_"
  )%>%
  relocate(ends_with("_anger"),  .after = social_nonsocial)%>%
  relocate(ends_with("_fear"),   .after = (ends_with("_anger"))) %>%
  relocate(ends_with("_happy"),  .after = (ends_with("_fear"))) %>%
  relocate(ends_with("_sad"),  .after = (ends_with("_happy"))) %>%  
  relocate(ends_with("_neutral"),.after = (ends_with("_sad")))

colnames(dta_emo_face_wide_emo)

mod_res$pca_wide_emo <- FactoMineR::PCA(dta_emo_face_wide_emo[, 1:104],
                  # centre = TRUE,    # subtract variable means
                  scale.unit = FALSE,
                  graph = FALSE,
                  quali.sup =c(1,2))   



factoextra::fviz_pca_ind(mod_res$pca_wide_emo )

factoextra:::fviz_contrib(mod_res$pca_wide_emo, choice = "var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$pca_wide_emo, choice = "var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$pca_wide_emo, choice = "var", top = 15, axes = 3)



dta_emo_face_wide_emo$pc1<- mod_res$pca_wide_emo$ind$coord[,1]
dta_emo_face_wide_emo$pc2<- mod_res$pca_wide_emo$ind$coord[,2]
dta_emo_face_wide_emo$pc3<- mod_res$pca_wide_emo$ind$coord[,3]
dta_emo_face_wide_emo$pc4<- mod_res$pca_wide_emo$ind$coord[,4]



 dta_emo_face_wide_emo%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  # group_by(participant,au_pcs,social_nonsocial)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores,colour = social_nonsocial))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   geom_boxplot()+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means()
 
 
 
```

 
 # proper MFA
 
```{r}
 dta_emo_face_wide%>%
   select(contains("au01"))
 colnames(dta_emo_face_wide[,3:1022])


 unique(dta_emo$stim_iaps)
 


 mod_res$mfa_face_wide <- MFA(dta_emo_face_wide[,2:1022],
                           group=c(1,170,170,170,170,170,170),
                           type=c("n","s","s","s","s","s", "s"),
                           name.group=c("social_non_soc","anger","fear", "happy","sad","neutral","disgust"),
                           num.group.sup=c(1),
                           graph=TRUE)
 
 
 factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 15, axes = 3)
factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 15, axes = 4)




dta_emo_face_wide$ma_pc1<- mod_res$mfa_face_wide$ind$coord[,1]
dta_emo_face_wide$ma_pc2<- mod_res$mfa_face_wide$ind$coord[,2]
dta_emo_face_wide$ma_pc3<- mod_res$mfa_face_wide$ind$coord[,3]
dta_emo_face_wide$ma_pc4<- mod_res$mfa_face_wide$ind$coord[,4]



 dta_emo_face_wide%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "mfa_pcs",      # name of the new “variable” column
    values_to = "mfa_pc_scores"      # name of the new “value” column
  )%>%
   
  # group_by(participant,au_pcs,social_nonsocial)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc_scores,colour = social_nonsocial))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~mfa_pcs)+
   ggpubr::stat_compare_means()
```


keep emotion as a supplementary as well
dta_emo_face_wide_emo

```{r}

dta_emo_face_w_subj

dta_emo_face_wide_emo2<- 

dta_emo_face %>%
  select(participant, social_nonsocial, stim_iaps, emotioncategory, everything()) %>%
  ungroup()%>%
  # mutate_at(scale_vars, scale)%>%
  group_by(participant,social_nonsocial, emotioncategory)%>%
  
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()

colnames(dta_emo_face_wide_emo2)

mod_res$pca_wide_emo_2 <- FactoMineR::PCA(dta_emo_face_wide_emo2[, 1:20],
                  # centre = TRUE,    # subtract variable means
                  scale.unit = TRUE,
                  graph = TRUE,
                  quali.sup =c(1,2,3))   



factoextra::fviz_pca_ind(mod_res$pca_wide_emo_2 )

factoextra:::fviz_contrib(mod_res$pca_wide_emo_2, choice = "var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$pca_wide_emo_2, choice = "var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$pca_wide_emo_2, choice = "var", top = 15, axes = 3)



dta_emo_face_wide_emo2$pc1<- mod_res$pca_wide_emo_2$ind$coord[,1]
dta_emo_face_wide_emo2$pc2<- mod_res$pca_wide_emo_2$ind$coord[,2]
dta_emo_face_wide_emo2$pc3<- mod_res$pca_wide_emo_2$ind$coord[,3]
dta_emo_face_wide_emo2$pc4<- mod_res$pca_wide_emo_2$ind$coord[,4]


# social vs non social
 dta_emo_face_wide_emo2%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores,colour = social_nonsocial))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(fun.data = mean_se, geom = "pointrange",position = position_dodge(1))+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means(method = "t.test")
 
 # emotion
 
 
 
 dta_emo_face_wide_emo2%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(emotioncategory, pc_scores))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(fun.data = mean_se, geom = "pointrange",position = position_dodge(1))+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means(method = "t.test")
 
 
 
 dta_emo_face_wide_emo2%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,social_nonsocial,emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(fun.data = mean_se, geom = "pointrange",position = position_dodge(1))+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(emotioncategory~pcs)
   ylim(-1,2)+
   ggpubr::stat_compare_means()
   
   
   
   
afex::aov_ez(data = dta_emo_face_wide_emo2,
             id = "participant",
             dv = "pc1",
             between = "social_nonsocial",
             within = c("emotioncategory"))

afex::aov_ez(data = dta_emo_face_wide_emo2,
             id = "participant",
             dv = "pc2",
             between = "social_nonsocial",
             within = c("emotioncategory"))

afex::aov_ez(data = dta_emo_face_wide_emo2,
             id = "participant",
             dv = "pc3",
             between = "social_nonsocial",
             within = c("emotioncategory"))


afex::aov_ez(data = dta_emo_face_wide_emo2,
             id = "participant",
             dv = "pc4",
             between = "social_nonsocial",
             within = c("emotioncategory"))


afex::aov_ez(data = dta_emo_face_wide_emo2,
             id = "participant",
             dv = "pc2",
             between = "social_nonsocial")

```


DONT RUN
emo wide subjective agg
- note we can't have this bevause it will always have some ppts who don't have data due to not having a cateory

```{r}

dta_emo_face_w_subj

dta_emo_face_wide_emo3<- 

dta_emo_face_w_subj %>%
  select(participant, social_nonsocial, stim_iaps, subj_emo_lab_no_amb, everything()) %>%
  ungroup()%>%
  # mutate_at(scale_vars, scale)%>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb)%>%
  
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()

colnames(dta_emo_face_wide_emo3)

mod_res$pca_wide_emo_3 <- FactoMineR::PCA(dta_emo_face_wide_emo3[, 1:20],
                  # centre = TRUE,    # subtract variable means
                  scale.unit = FALSE,
                  graph = FALSE,
                  quali.sup =c(1,2,3))   



factoextra::fviz_pca_ind(mod_res$pca_wide_emo_3 )

factoextra:::fviz_contrib(mod_res$pca_wide_emo_3, choice = "var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$pca_wide_emo_3, choice = "var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$pca_wide_emo_3, choice = "var", top = 15, axes = 3)



dta_emo_face_wide_emo3$pc1<- mod_res$pca_wide_emo_3$ind$coord[,1]
dta_emo_face_wide_emo3$pc2<- mod_res$pca_wide_emo_3$ind$coord[,2]
dta_emo_face_wide_emo3$pc3<- mod_res$pca_wide_emo_3$ind$coord[,3]
dta_emo_face_wide_emo3$pc4<- mod_res$pca_wide_emo_3$ind$coord[,4]


# social vs non social
 dta_emo_face_wide_emo3%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores,colour = social_nonsocial))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(fun.data = mean_se, geom = "pointrange",position = position_dodge(1))+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means(method = "t.test")

 # emotion
 

 dta_emo_face_wide_emo3%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, pc_scores))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(fun.data = mean_se, geom = "pointrange",position = position_dodge(1))+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means()
 
 dta_emo_face_wide_emo3%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,social_nonsocial,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(fun.data = mean_se, geom = "pointrange",position = position_dodge(1))+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(subj_emo_lab_no_amb~pcs)


dta_emo_face_wide_emo3
```
   





```{r}

colnames(dta_emo_face)

options(scipen = 999)

dta_emo_face$subjective_emotion[,c(1:4,6:22)]%>%
  select(participant, social_nonsocial, stim_iaps, subje, everything()) %>%
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps, emotioncategory),
    values_from = names(dta_emo_face)[6:22],
    names_sep   = "_"  
  )
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),
    values_from = names(dta_emo_face[,6:22]),
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )

# sd(dta_emo_face$au01_inner_brow_raise)
# sd(dta_emo_face_scale$au01_inner_brow_raise_z)
  
  
  
  dta_emo_face <- dta_emo_face %>%
  mutate(
    emotioncategory = factor(
      emotioncategory
    )
  )

# 2. pivot with emotioncategory first:
wide
dta_emo_face$emotioncategory

library(dplyr); library(tidyr)

dta_emo_face_wide <- dta_emo_face %>%
  select(participant, social_nonsocial, stim_iaps, emotioncategory, everything()) %>%
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),    # ← flip these two
    values_from = names(dta_emo_face)[6:22],
    names_sep   = "_"
  )%>%
  relocate(ends_with("_anger"),  .after = social_nonsocial)%>%
  relocate(ends_with("_fear"),   .after = (ends_with("_anger"))) %>%
  relocate(ends_with("_happy"),  .after = (ends_with("_fear"))) %>%
  relocate(ends_with("_sad"),  .after = (ends_with("_happy"))) %>%  
  relocate(ends_with("_neutral"),.after = (ends_with("_sad")))



# aggregate by emotion


dta_emo_face_wide_emo<- 

dta_emo_face %>%
  select(participant, social_nonsocial, stim_iaps, emotioncategory, everything()) %>%
  group_by(participant,social_nonsocial, emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(emotioncategory),    # ← flip these two
    values_from = names(dta_emo_face)[6:22],
    names_sep   = "_"
  )%>%
  relocate(ends_with("_anger"),  .after = social_nonsocial)%>%
  relocate(ends_with("_fear"),   .after = (ends_with("_anger"))) %>%
  relocate(ends_with("_happy"),  .after = (ends_with("_fear"))) %>%
  relocate(ends_with("_sad"),  .after = (ends_with("_happy"))) %>%  
  relocate(ends_with("_neutral"),.after = (ends_with("_sad")))


dta_emo_face_wide_emo

colnames(dta_emo_face_wide)
# 1a. PCA on the raw variables, centering & scaling in one go
 # divide by variable sds

require(Factoshiny)
require(factoextra)


?FactoMineR::PCA
mod_res$pca_wide <- FactoMineR::PCA(dta_emo_face_wide[, 2:1022],
                  # centre = TRUE,    # subtract variable means
                  scale.unit = FALSE,
                  graph = TRUE,
                  quali.sup =1)   


fviz_screeplot(mod_res$pca_wide)



factoextra::fviz_pca_ind(mod_res$pca_wide )
?factoextra:::fviz_contrib
factoextra:::fviz_contrib(mod_res$pca_wide, choice = "var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$pca_wide, choice = "var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$pca_wide, choice = "var", top = 15, axes = 3)


mod_res$pca_wide$ind$coord

mod_res$pca_wide$var$coord

dta_emo_face_wide$pc1<- mod_res$pca_wide$ind$coord[,1]
dta_emo_face_wide$pc2<- mod_res$pca_wide$ind$coord[,2]
dta_emo_face_wide$pc3<- mod_res$pca_wide$ind$coord[,3]
dta_emo_face_wide$pc4<- mod_res$pca_wide$ind$coord[,4]





 dta_emo_face_wide%>%
   pivot_longer( cols      = c(pc1, pc2, pc3, pc4),
    names_to  = "pcs",      # name of the new “variable” column
    values_to = "pc_scores"      # name of the new “value” column
  )%>%
   
  group_by(participant,pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(fun.data = mean_se, geom = "pointrange",position = position_dodge(1))+
 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~pcs)+
   ggpubr::stat_compare_means(method = "t.test")
   
   
   
   
afex::aov_ez(data = dta_emo_face_wide,
             id = "participant",
             dv = "pc1",
             between = "social_nonsocial")

afex::aov_ez(data = dta_emo_face_wide,
             id = "participant",
             dv = "pc2",
             between = "social_nonsocial")

afex::aov_ez(data = dta_emo_face_wide,
             id = "participant",
             dv = "pc3",
             between = "social_nonsocial")




```


mfa version
```{r}
 # proper MFA
 dta_emo_face_wide%>%
   select(contains("au01"))
 colnames(dta_emo_face_wide[,3:1022])


 unique(dta_emo$stim_iaps)

 mod_res$mfa_face_wide <- MFA(dta_emo_face_wide[,2:1022],
                           group=c(1,170,170,170,170,170,170),
                           type=c("n","s","s","s","s","s", "s"),
                           name.group=c("social_non_soc","anger","fear", "happy","sad","neutral","disgust"),
                           num.group.sup=c(1),
                           graph=TRUE)
 
 
 factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 15, axes = 3)
factoextra:::fviz_contrib(mod_res$mfa_face_wide, choice = "quanti.var", top = 15, axes = 4)




dta_emo_face_wide$mfa_pc1<- mod_res$mfa_face_wide$ind$coord[,1]
dta_emo_face_wide$mfa_pc2<- mod_res$mfa_face_wide$ind$coord[,2]
dta_emo_face_wide$mfa_pc3<- mod_res$mfa_face_wide$ind$coord[,3]
dta_emo_face_wide$mfa_pc4<- mod_res$mfa_face_wide$ind$coord[,4]



 dta_emo_face_wide%>%
   pivot_longer( cols      = c(mfa_pc1, mfa_pc2, mfa_pc3, mfa_pc4),
    names_to  = "mfa_pcs",      # name of the new “variable” column
    values_to = "mfa_pc_scores"      # name of the new “value” column
  )%>%
   
  # group_by(participant,au_pcs,social_nonsocial)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc_scores,colour = social_nonsocial))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~mfa_pcs)+
   ggpubr::stat_compare_means()


 
```
 
 
 
```{r}
 mod_res$mfa_face_wide_emo <- MFA(dta_emo_face_wide_emo[, 2:104],
                           group=c(1,17,17,17,17,17,17),
                           type=c("n","s","s","s","s","s", "s"),
                           name.group=c("social_non_soc","anger","fear", "happy","sad","neutral","disgust"),
                           num.group.sup=c(1),
                           graph=TRUE)
 
 
 factoextra:::fviz_contrib(mod_res$mfa_face_wide_emo, choice = "quanti.var", top = 10, axes = 1)
factoextra:::fviz_contrib(mod_res$mfa_face_wide_emo, choice = "quanti.var", top = 10, axes = 2)
factoextra:::fviz_contrib(mod_res$mfa_face_wide_emo, choice = "quanti.var", top = 15, axes = 3)
factoextra:::fviz_contrib(mod_res$mfa_face_wide_emo, choice = "quanti.var", top = 15, axes = 4)




dta_emo_face_wide_emo$mfa_pc1<- mod_res$mfa_face_wide_emo$ind$coord[,1]
dta_emo_face_wide_emo$mfa_pc2<- mod_res$mfa_face_wide_emo$ind$coord[,2]
dta_emo_face_wide_emo$mfa_pc3<- mod_res$mfa_face_wide_emo$ind$coord[,3]
dta_emo_face_wide_emo$mfa_pc4<- mod_res$mfa_face_wide_emo$ind$coord[,4]



 dta_emo_face_wide_emo%>%
    pivot_longer( cols      = c(mfa_pc1, mfa_pc2, mfa_pc3, mfa_pc4),
    names_to  = "mfa_pcs",      # name of the new “variable” column
    values_to = "mfa_pc_scores"      # name of the new “value” column
  )%>%
   
  # group_by(participant,au_pcs,social_nonsocial)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc_scores,colour = social_nonsocial))+

  geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~mfa_pcs)+
   ggpubr::stat_compare_means()

 
 
 
```
 
 face pc lmms
 
```{r}

dta_emo_face_scale_long<- dta_emo_face_scale_long%>%
  left_join(dta_emo_agg_demogs)

mod_res$au_pcs_scores <- lmer(pc_scores ~ 1+ social_nonsocial* emotioncategory *au_pcs+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (0+au_pcs|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale_long)



mod_res$au_pcs_scores_subj <- lmer(pc_scores ~ 1+ social_nonsocial* subj_emo_lab_no_amb *au_pcs+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (0+au_pcs|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale_long)


dta_emo_face_scale_long$au_pcs

mod_res$au_pcs_scores1 <- lmer(pc_scores ~ 1+ social_nonsocial* emotioncategory+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale_long%>%subset(au_pcs == "PC1"))


mod_res$au_pcs_scores2 <- lmer(pc_scores ~ 1+ social_nonsocial* emotioncategory+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale_long%>%subset(au_pcs == "PC2"))



mod_res$au_pcs_scores3 <- lmer(pc_scores ~ 1+ social_nonsocial* emotioncategory +
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale_long%>%subset(au_pcs == "PC3"))

summary(mod_res$int )

summary(mod_res$au_pcs_scores )


anova(mod_res$au_pcs_scores )

anova(mod_res$au_pcs_scores_subj )

anova(mod_res$au_pcs_scores1 )
anova(mod_res$au_pcs_scores2 )
anova(mod_res$au_pcs_scores3 )


dta_emo_face_scale_long%>%
  group_by(social_nonsocial,stim_iaps,au_pcs)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores))+
  geom_point()+
  geom_smooth(aes(group = stim_iaps), se = F, method = "lm")+
  facet_grid(~au_pcs)



dta_emo_face_scale_long%>%
  subset(participant != 116)%>%
    subset(participant != 117)%>%
    subset(participant != 242)%>%
    subset(participant != 243)%>%
      subset(participant != 246)%>%
   subset(participant != 228)%>%
   subset(participant != 209)%>%
  group_by(social_nonsocial,participant,au_pcs)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores))+
  # geom_point()+
  # geom_boxplot()+
  # geom_smooth(aes(group = stim_iaps), se = F, method = "lm")+
  facet_grid(~au_pcs)+
  geom_text(aes(label = participant), size = 2)+
  ggpubr::stat_compare_means()




dta_emo_face_scale_long%>%
  # subset(participant != 116)%>%
  #   subset(participant != 117)%>%
  #   subset(participant != 242)%>%
  #   subset(participant != 243)%>%
  #     subset(participant != 246)%>%
  #  subset(participant != 228)%>%
  #  subset(participant != 209)%>%
  group_by(social_nonsocial,participant,au_pcs)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(au_pcs, pc_scores))+
  # geom_point()+
  # geom_boxplot()+
  geom_line(aes(group = participant), se = F, method = "lm")+
  facet_grid(~ social_nonsocial)+
  # geom_text(aes(label = participant), size = 2)+
  ggpubr::stat_compare_means()


```


```{r}
mod_res$au_pcs_scores_2 <- lmer(pc_scores ~ 1+ social_nonsocial* subj_emo_lab_no_amb *au_pcs+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                           # (1|participant)+ #s
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale_long)

mod_res$au_pcs_scores_3 <- lmer(pc_scores ~ 1+ social_nonsocial* subj_emo_label_agg *au_pcs+
                       # social_nonsocial:au_pcs+ social_nonsocial: subjective_emotion+    
                     (1|participant)+ #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_face_scale_long)


summary(mod_res$au_pcs_scores_2)


anova(mod_res$au_pcs_scores_2)



```

```{r}
 anova(mod_res$au_pcs_scores)
 
 
  anova(mod_res$au_pcs_scores_2)
   anova(mod_res$au_pcs_scores_3)
 
   
 emmeans::emmeans(mod_res$au_pcs_scores, pairwise ~ social_nonsocial|au_pcs, adjust = "tukey")
 
 
  emmeans::emmeans(mod_res$au_pcs_scores, pairwise ~ emotioncategory|au_pcs, adjust = "tukey")
 


   
 emmeans::emmeans(mod_res$au_pcs_scores_2, pairwise ~ social_nonsocial|au_pcs, adjust = "tukey")
 
 
  emmeans::emmeans(mod_res$au_pcs_scores_2, pairwise ~ subj_emo_lab_no_amb|au_pcs, adjust = "tukey")
 

  emmeans::emmeans(mod_res$au_pcs_scores_2, pairwise ~ au_pcs|subj_emo_lab_no_amb, adjust = "tukey")
 

 dta_emo_face_scale_long%>%au_pcs_scores2dta_emo_face_scale_long%>%
  group_by(participant,au_pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, pc_scores, colour = social_nonsocial))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   ggpubr::stat_compare_means()+
   facet_grid(~au_pcs)
  # theme(axis.text.x = element_text(hjust = 1,angle = 45))
  
  
  
  
  
  
  dta_emo_face_scale_long%>%
  group_by(participant,au_pcs,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, pc_scores, colour = subj_emo_lab_no_amb))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+

 # geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
   facet_grid(~au_pcs)+
           ggpubr::stat_compare_means()
  
  # ylim(0,10)+
```

Type III Analysis of Variance Table with Satterthwaite's method
                                         Sum Sq Mean Sq NumDF   DenDF F value
social_nonsocial                          0.002   0.002     1    90.0  0.0007
emotioncategory                          19.964   3.993     5    59.3  1.6788
au_pcs                                    0.508   0.254     2 16050.9  0.1069
social_nonsocial:emotioncategory          4.657   0.931     5 16050.9  0.3916
social_nonsocial:au_pcs                 257.365 128.683     2 16050.9 54.1049
emotioncategory:au_pcs                   97.302   9.730    10 16050.9  4.0911
social_nonsocial:emotioncategory:au_pcs  11.737   1.174    10 16050.9  0.4935
                                                       Pr(>F)    
social_nonsocial                                       0.9797    
emotioncategory                                        0.1538    
au_pcs                                                 0.8986    
social_nonsocial:emotioncategory                       0.8549    
social_nonsocial:au_pcs                 < 0.00000000000000022 ***
emotioncategory:au_pcs                              0.0000119 ***
social_nonsocial:emotioncategory:au_pcs                0.8955 


$contrasts
au_pcs = PC1:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.0557 0.128 Inf   0.437  0.6622

au_pcs = PC2:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social  -0.3288 0.128 Inf  -2.579  0.0099

au_pcs = PC3:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.2825 0.128 Inf   2.216  0.0267
 
 
can we check wether the social vs no social affect coherence and divergence



agg subjective is more consistent with emotion category

```{r}

colnames(dta_emo)
dta_emo$mean_stat_entropy_maxnorm_norm_by_img

dta_emo_4mfa<- dta_emo[,c(1:10,13,18,24,52,31:47)]
colnames(dta_emo_4mfa)

install.packages("Factoshiny")
# FactoMineR::MFA()
# factoextra
require(Factoshiny)

Factoshiny::MFAshiny(dta_emo_4mfa)

dta_emo_4mfa

newDF <- dta_emo[,c("val_slider_response","int_slider_response","happy_slide_response","sad_slide_response","fear_slide_response","disgust_slide_response","anger_slide_response","hr_mean_diff","log_cda_phasic_max","mean_fix_dur","mean_sac_amp","au14_dimpler","au12_lip_corner_pull","au_04_brow_lower","au26_jaw_drop","au01_inner_brow_raise","au02_outer_brow_raise","au05_eye_lid_raise","au06_cheek_raise","au07_eye_lid_tighten","au09_nose_wrinkle","au10_upper_lip_raise","au15_lip_corner_depress","au20_lip_stretch","au17_chin_raise","au23_lip_tighten","au25_lips_apart","au45_eye_blink","social_nonsocial","participant","stim_iaps")]
colnames(newDF)

mod_res$mfa_result <- MFA(newDF[,1:29],group=c(7,1,1,2,17,1), type=c("s","s","s","s","s","n"),name.group=c("subj_aff","phys_hr","phys_scr","gaze","face","social_non_soc"),num.group.sup=c(6),graph=FALSE)

plot.MFA(mod_res$mfa_result, choix="ind",lab.par=FALSE,invisible= 'quali',select='cos2  0.25',habillage='social_nonsocial',title="Individual factor map")
# plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
# plot.MFA(res.MFA, choix="group")
# plot.MFA(res.MFA, choix="axes",habillage='group')

mod_res$mfa_result$eig #about 2 or 3 dimensions
fviz_screeplot(mod_res$mfa_result)

mod_res$mfa_result$quanti.var

mod_res$mfa_result$quanti.var

# 
mod_res$mfa_result$quanti.var$contrib


mod_res$mfa_result$group$contrib


# dim 2 is the coerence dimension

# Dimension 1: Cardiac‒Face‒Gaze Intensity
# 	2.	Dimension 2: Subjective‒SCR‒Gaze Coupling
# 	3.	Dimension 3: Phasic SCR (Phasic‐SCR Dominant)

# hierarquical



```


    Dim.1      Dim.2     Dim.3      Dim.4      Dim.5
subj_aff  1.428230 54.2605088 13.698084 17.4047604 12.8463704
phys_hr  37.095963 15.5052843  2.013076  2.3982781 38.0356168
phys_scr  1.347262 16.9088468 77.657241  0.2527347  0.1674103
gaze     15.145339 12.9441659  2.306574 72.9265774  7.6025720
face     44.983206  0.3811942  4.325024  7.0176494 41.3480306
  Dim.1           Dim.2         Dim.3       Dim.4
val_slider_response      0.144929822 10.390056887238  2.8157716824  2.81577114
int_slider_response      0.425686216  4.355168506726  1.5792801419  1.95273366
happy_slide_response     0.014688112  7.227136691208  2.1263357225  1.68919682
sad_slide_response       0.130230099  8.304003125301  1.6254456301  2.64369921
fear_slide_response      0.224494527  7.211935062462  1.6402588003  2.54960759
disgust_slide_response   0.334196432  8.649328528461  2.0707500209  2.83559844
anger_slide_response     0.154004397  8.122879987497  1.8402419763  2.91815353
hr_mean_diff            37.095962664 15.505284295661  2.0130760416  2.39827812
log_cda_phasic_max       1.347262275 16.908846800595 77.6572413790  0.25273474
mean_fix_dur             5.749530171  1.504901933570  1.8237401524 46.61280615
mean_sac_amp             9.395808870 11.439263932984  0.4828339904 26.31377122
au14_dimpler             0.575298149  0.050819445436  0.1308681843  0.25058669
au12_lip_corner_pull     0.823175444  0.031068949081  0.0525393300  0.27690684
au_04_brow_lower         0.002251773  0.000076371102  0.6653145760  0.01252775
au26_jaw_drop            5.913818746  0.101127060323  0.0253927446  0.60223477
au01_inner_brow_raise    2.858645419  0.008600101129  0.5551605863  0.63701110
au02_outer_brow_raise    2.742984002  0.032845208759  0.4446636381  0.39719119
au05_eye_lid_raise       1.527983867  0.036246787748  0.2220348040  0.18760065
au06_cheek_raise         0.519460185  0.044914775957  0.9303877414  0.04981729
au07_eye_lid_tighten     0.170388493  0.017895249357  0.2394942510  0.09959091
au09_nose_wrinkle        3.151913366  0.003108638597  0.3293007593  0.67252248
au10_upper_lip_raise     0.553621891  0.022261584089  0.2404797201  0.33424289
au15_lip_corner_depress  3.799541789  0.000006043545  0.1136853435  0.60215941
au20_lip_stretch         4.660381555  0.022207673026  0.0546703919  0.67841173
au17_chin_raise          6.297064113  0.001810097166  0.0694498595  0.86546655
au23_lip_tighten         4.711374435  0.003781805474  0.0364605357  0.58268333
au25_lips_apart          5.579054672  0.001702147823  0.2142136563  0.70703716
au45_eye_blink           1.096248514  0.002722309683  0.0009083401  0.06165863
                             Dim.5
val_slider_response      2.5576979
int_slider_response      0.5016437
happy_slide_response     1.9414361
sad_slide_response       2.3184011
fear_slide_response      1.5172850
disgust_slide_response   1.2936244
anger_slide_response     2.7162822
hr_mean_diff            38.0356168
log_cda_phasic_max       0.1674103
mean_fix_dur             5.1179634
mean_sac_amp             2.4846086
au14_dimpler             2.5823215
au12_lip_corner_pull     3.7296635
au_04_brow_lower         0.0402684
au26_jaw_drop            2.9633193
au01_inner_brow_raise    2.8395880
au02_outer_brow_raise    2.5858712
au05_eye_lid_raise       1.2309732
au06_cheek_raise         1.5776225
au07_eye_lid_tighten     0.1882272
au09_nose_wrinkle        2.1965405
au10_upper_lip_raise     1.7923782
au15_lip_corner_depress  3.5699602
au20_lip_stretch         3.1618848
au17_chin_raise          4.5329889
au23_lip_tighten         3.4638951
au25_lips_apart          4.2229833
au45_eye_blink           0.6695447

= 

```{r}

# Contribution to the first dimension
fviz_contrib(mod_res$mfa_result, "group", axes = 1)
fviz_contrib(mod_res$mfa_result, "group", axes = 2)
fviz_contrib(mod_res$mfa_result, "group", axes = 3)
# fviz_contrib(mod_res$mfa_result, "group", axes = 4)
# fviz_contrib(mod_res$mfa_result, "group", axes = 5)
# Contribution to the second dimension

mod_res$mfa_result$quanti.var

dta_emo_4mfa$pc1_mfa<- mod_res$mfa_result$ind$coord[, 1]
dta_emo_4mfa$pc2_mfa<- mod_res$mfa_result$ind$coord[, 2]

dta_emo_4mfa$pc3_mfa<- mod_res$mfa_result$ind$coord[, 3]
dta_emo_4mfa$pc4_mfa<- mod_res$mfa_result$ind$coord[, 4]
dta_emo_4mfa$pc5_mfa<- mod_res$mfa_result$ind$coord[, 5]

dta_emo_4mfa%>%
  pivot_longer( cols      = c(pc1_mfa,pc2_mfa,pc3_mfa,pc4_mfa,pc5_mfa),
    names_to  = "mfa_pcs",      # name of the new “variable” column
    values_to = "mfa_pc_scores"      # name of the new “value” column
  )%>%
  subset( mfa_pcs== c("pc1_mfa","pc2_mfa")) %>%
  group_by(participant, social_nonsocial, mfa_pcs)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc_scores, 
             colour = social_nonsocial))+
  geom_point(alpha =.1)+
  stat_summary(geom = "pointrange")+

  facet_grid(~mfa_pcs)+
      ggpubr::stat_compare_means(method = "t.test")


library(dplyr)
library(ggplot2)
library(ggside)
library(ggpubr)

dta_emo_4mfa %>%
  # ── 1. Reshape to long, keep only PC1 & PC2 ───────────────────────────────────
  pivot_longer(
    cols      = c(pc1_mfa, pc2_mfa, pc3_mfa, pc4_mfa, pc5_mfa),
    names_to  = "mfa_pcs",
    values_to = "mfa_pc_scores"
  ) %>%
  filter(mfa_pcs %in% c("pc1_mfa", "pc2_mfa")) %>%
  # ── 2. Summarise per participant × group × PC ─────────────────────────────────
  group_by(participant, social_nonsocial, mfa_pcs) %>%
  summarise(mfa_pc_scores = mean(mfa_pc_scores, na.rm = TRUE), .groups = "drop") %>%
  # ── 3. Plot with ggsides ───────────────────────────────────────────────────────
  ggplot(aes(x = social_nonsocial, y = mfa_pc_scores, colour = social_nonsocial)) +
  geom_boxplot()+
  
  # 3.1 Jittered points to show individual values
  # geom_jitter(
  #   position = position_jitter(width = 0.15),
  #   alpha    = 0.3,
  #   size     = 1.5,
  #   show.legend = FALSE
  # ) +
  
  # 3.2 Mean ± 95% CI for each group
  stat_summary(
    # fun.data = mean_cl_boot,
    geom     = "pointrange",
    size     = 0.8,
    colour   = "black"
  ) +
  
  # 3.3 Side‐boxplots (right margin) for the distribution of scores by group
  # geom_ysidedensity
  # geom_ysidedensity(
  #   aes(fill = social_nonsocial),
  #   orientation   = "y",
  #   # width         = 0.3,
  #   smooth = .2,
  #   # outlier.shape = NA,
  #   alpha         = 0.2,
  #   show.legend   = FALSE
  # )+ 
  
  # 3.4 Facet by which PC we’re plotting
  facet_grid(~ mfa_pcs, scales = "free_y") +
  
  # 3.5 Add p‐values for t‐test between social vs non‐social within each PC
  ggpubr::stat_compare_means(
     aes(label = ..p.signif..),
  method       = "t.test",
  # method.args  = list(alternative = "lesser"),
  label.x.npc  = 0.5,
  label.y.npc  = 0.95,
  size         = 4)
  
  # 3.6 Shared colour/fill scales
  scale_colour_brewer(palette = "Set1", name = "Group") +
  scale_fill_brewer(palette = "Set1", guide = "none") +
  
  # 3.7 Labels and styling
  labs(
    x     = NULL,
    y     = "MFA score",
    title = "PC1 & PC2 Distributions by Social vs Non‐Social",
    subtitle = "Dots = individual participants; bars = mean ± 95% CI; side‐boxplots show full distribution"
  ) +
  theme_minimal() +
  theme(
    panel.grid.minor   = element_blank(),
    panel.grid.major   = element_line(colour = "grey90", size = 0.2),
    strip.background   = element_rect(fill = "grey95", colour = NA),
    strip.text         = element_text(face = "bold"),
    plot.title         = element_text(hjust = 0.5),
    plot.subtitle      = element_text(hjust = 0.5),
    legend.position    = "none"
  ) 
  
  # 3.8 Reserve space for side geoms
  ggside::theme_sides(panel.scale = 0.5)


```


mixed models

```{r}
dta_emo_4mfa

mod_res$lmer_pc1_mfa<- lmer(pc1_mfa ~ 1+ social_nonsocial+ 
                     (1|participant) + 
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo_4mfa)
summary(mod_res$lmer_pc1_mf)

report::report(mod_res$lmer_pc1_mf)


anova(mod_res$lmer_pc1_mf)


anova(mod_res$lmer_pc1_mf)



```
We fitted a linear mixed model (estimated using ML and nloptwrap optimizer) to
predict pc1_mfa with social_nonsocial (formula: pc1_mfa ~ 1 + social_nonsocial).
The model included participant as random effects (formula: list(~1 |
participant, ~1 | stim_iaps)). The model's total explanatory power is moderate
(conditional R2 = 0.23) and the part related to the fixed effects alone
(marginal R2) is of 0.01. The model's intercept, corresponding to
social_nonsocial = nonsocial, is at 0.11 (95% CI [-0.04, 0.26], t(5395) = 1.49,
p = 0.136). Within this model:

  - The effect of social nonsocial [social] is statistically significant and
negative (beta = -0.23, 95% CI [-0.44, -0.03], t(5395) = -2.27, p = 0.023; Std.
beta = -0.22, 95% CI [-0.40, -0.03])



```{r}
mod_res$lmer_pc2_mfa<- lmer(pc2_mfa ~ 1+ social_nonsocial+ 
                     (1|participant) + 
                     (1+social_nonsocial|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo_4mfa)
summary(mod_res$lmer_pc2_mfa)
anova(mod_res$lmer_pc2_mfa)


mod_res$lmer_pc3_mfa<- lmer(pc3_mfa ~ 1+ social_nonsocial+ 
                     (1|participant) + 
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo_4mfa)
summary(mod_res$lmer_pc3_mfa)

anova(mod_res$lmer_pc2_mfa)
anova(mod_res$lmer_pc3_mfa)

# install.packages("MFAmix")   # (do this once)
# library(MFAmix)
ml_mfa_res <- MFAmix::mlMFA(
  data       = list(subj_aff_df, hr_df, scr_df, gaze_df, face_df),
  group      = c(
    ncol(subj_aff_df) - 3,  # 7 subjective‐affect columns
    ncol(hr_df)   - 3,      # 1 HR column
    ncol(scr_df)  - 3,      # 1 SCR column
    ncol(gaze_df) - 3,      # 2 gaze columns
    ncol(face_df) - 3       # 17 face‐AU columns
  ),
  type       = c("s", "s", "s", "s", "s"),
  between    = c("participant", "social_nonsocial"),
  within     = "stim_iaps",
  name.group = c("subj_aff", "phys_hr", "phys_scr", "gaze", "face")
)

```


Type III Analysis of Variance Table with Satterthwaite's method
                  Sum Sq Mean Sq NumDF  DenDF F value Pr(>F)
social_nonsocial 0.53441 0.53441     1 89.456  1.3537 0.2477

Type III Analysis of Variance Table with Satterthwaite's method
                  Sum Sq Mean Sq NumDF  DenDF F value Pr(>F)
social_nonsocial 0.42625 0.42625     1 89.958  1.7357  0.191
aggregated MFA one observation

[1] "val_slider_response"                   
 [2] "int_slider_response"                   
 [3] "happy_slide_response"                  
 [4] "sad_slide_response"                    
 [5] "fear_slide_response"                   
 [6] "disgust_slide_response"                
 [7] "anger_slide_response"                  
 [8] "hr_mean_diff"                          
 [9] "mean_trans_entropy_maxnorm_norm_by_img"
[10] "mean_fix_dur_stim_aoi"                 
[11] "log_cda_phasic_max"                    
[12] "au01_inner_brow_raise"                 
[13] "au02_outer_brow_raise"                 
[14] "au_04_brow_lower"                      
[15] "au05_eye_lid_raise"                    
[16] "au06_cheek_raise"                      
[17] "au07_eye_lid_tighten"                  
[18] "au09_nose_wrinkle"                     
[19] "au10_upper_lip_raise"                  
[20] "au12_lip_corner_pull"                  
[21] "au14_dimpler"                          
[22] "au15_lip_corner_depress"               
[23] "au17_chin_raise"                       
[24] "au20_lip_stretch"                      
[25] "au23_lip_tighten"                      
[26] "au25_lips_apart"                       
[27] "au26_jaw_drop"                         
[28] "au45_eye_blink"                        
[29] "participant"                           
[30] "stim_iaps"                             
[31] "social_nonsocial"                      
[32] "emotioncategory"
```{r}

colnames(newDF)

unique(dta_emo$stim_iaps)

newDF$emotioncategory<- dta_emo$emotioncategory
colnames(newDF)




dta_emo_wide_mfa<- newDF%>%
 pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),
    values_from = names(newDF[,1:28]),
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )


# 

  

dta_emo_wide_mfa
colnames(dta_emo_wide_mfa)
# val_slider_response"                   
#   [5] "int_slider_response"                   
#   [6] "happy_slide_response"                  
#   [7] "sad_slide_response"                    
#   [8] "fear_slide_response"                   
#   [9] "disgust_slide_response"                
#  [10] "anger_slide_response"

60*7 #subjective #420

17*60 #aus #1020
dta_emo_wide_mfa[,422]
dta_emo_wide_mfa
sum(c(420,60,60,120,1020,1))
dta_emo_wide_mfa[,c(3:1682,2)]
?MFA
colnames(dta_emo_wide_mfa)
mod_res$mfa_result_wide <- MFA(dta_emo_wide_mfa[,c(3:1682,2)],
                          group=c(420,60,60,120,1020,1),
                          type=c("s","s","s","s","s","n"),  
                          name.group= c("subj_aff","phys_hr","phys_scr","gaze","face","social_non_soc"),
                          num.group.sup=c(6),#position of group above
                          graph=FALSE)





plot.MFA(mod_res$mfa_result_wide, choix="ind",lab.par=FALSE,invisible= 'quali',select='cos2  0.25',habillage='social_nonsocial',title="Individual factor map")


mod_res$mfa_result_wide$eig #about 2 or 3 dimensions
fviz_screeplot(mod_res$mfa_result_wide)

```

02/7 - coherence operationalisation per subject
```{r}

# ‘inertia’ is a matrix: rows = blocks, cols = dims + “total”


# 2. Inertia on the first axis
# 
# Since MFA is a compromise PCA, you can look at how much of each block’s inertia sits on Dim 1.  If a large proportion of block i’s total inertia is carried by Dim 1, that block is highly “coherent” with the overall structure.


mod_res$mfa_result_wide$inertia.ratio


mod_res$mfa_result_wide$group$correlation


mod_res$mfa_result_wide$ind$within.inertia
dta_emo_wide_mfa$ind_cos2<-mod_res$mfa_result_wide$ind$cos2[,1]
dta_emo_wide_mfa$ind_in<-mod_res$mfa_result_wide$ind$within.inertia[,1]


dta_emo_wide_mfa%>%
  ggplot(aes(social_nonsocial, ind_cos2))+
  geom_jitter(alpha = .1, width = .2)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means()






# choose number of dims to include
K <- 5  


library(dplyr)
library(tidyr)
 
# 1. Pull out the compromise (global) and partial (block) scores
comp  <- mod_res$mfa_result_wide$ind$coord           # n_subjects × K dims
part  <- mod_res$mfa_result_wide$ind$coord.partiel   # (n_subjects × n_blocks) × K dims

# 2. Turn them into “long” tibbles, extracting subject IDs and block names
part_df <- as_tibble(part, rownames = "row") %>% 
  # row looks like "1.subj_aff", "1.phys_hr", etc.
  separate(row, into = c("subject","block"), sep = "\\.", convert = TRUE)

comp_df <- as_tibble(comp, rownames = "subject") %>% 
  mutate(subject = as.integer(subject))

# 3. Nest the K‐dim vectors so we can operate per‐row
part_nest <- part_df %>% 
  nest(part_coord = starts_with("Dim"))

comp_nest <- comp_df %>% 
  nest(comp_coord = starts_with("Dim"))

# 4. Join them back together by subject
joined <- left_join(part_nest, comp_nest, by = "subject")

# 5. Compute, for each (subject, block), the Pearson correlation of the two K‐vectors
coh_df <- joined %>% 
  mutate(
    coherence = map2_dbl(
      comp_coord, part_coord,
      ~ cor(.x[[1]], .y[[1]], use = "pairwise.complete.obs")
    )
  ) %>% 
  select(subject, block, coherence)

# 6. (Optionally) bring back your social vs non-social flag
coh_df <- coh_df %>% 
  left_join(
    dta_emo_agg_wide_mfa %>% select(subject, social_non_soc) %>% distinct(),
    by = "subject"
  )

coh_df

# → coh_df now has one coherence score per subject×block
head(coh_df)
```






```{r}
# Contribution to the first dimension



# 
# fviz_contrib(mod_res$mfa_result, "group", axes = 1)
# fviz_contrib(mod_res$mfa_result, "group", axes = 2)
# fviz_contrib(mod_res$mfa_result, "group", axes = 3)
# fviz_contrib(mod_res$mfa_result, "group", axes = 4)
# fviz_contrib(mod_res$mfa_result, "group", axes = 5)
# Contribution to the second dimension

fviz_contrib(mod_res$mfa_result_wide, "group", axes = 1)
fviz_contrib(mod_res$mfa_result_wide, "group", axes = 2)
fviz_contrib(mod_res$mfa_result_wide, "group", axes = 3)
fviz_contrib(mod_res$mfa_result_wide, "group", axes = 4)
fviz_contrib(mod_res$mfa_result_wide, "group", axes = 5)
# Contribution to the second dimension

mod_res$mfa_result_wide$group

# dim 1 - Cardiac–Face–Gaze Intensity
	# 2.	Dimension 2 (“Phasic-SCR – Gaze – Face Coupling”)
	# 3.	Dimension 3 (“Cardiac – Face – Gaze Blend”)

```






tests of wide mfa with all the stim


```{r}


dta_emo_wide_mfa$pc1_mfa<- mod_res$mfa_result_wide$ind$coord[, 1]
dta_emo_wide_mfa$pc2_mfa<- mod_res$mfa_result_wide$ind$coord[, 2]

dta_emo_wide_mfa$pc3_mfa<- mod_res$mfa_result_wide$ind$coord[, 3]
dta_emo_wide_mfa$pc4_mfa<- mod_res$mfa_result_wide$ind$coord[, 4]
dta_emo_wide_mfa$pc5_mfa<- mod_res$mfa_result_wide$ind$coord[, 5]

mod_res$mfa_result$ind$coord[,1:5]
  
dta_emo_4mfa_coord<-dta_emo_4mfa%>%
  select(participant)


dta_emo_wide_coord1<-  as.data.frame(mod_res$mfa_result_wide$ind$coord[,1:5])
dta_emo_wide_coord1$participant<- dta_emo_wide_mfa$participant





```

```{r}


dta_emo_wide_mfa%>%
  pivot_longer( cols      = c(pc1_mfa,pc2_mfa,pc3_mfa,pc4_mfa,pc5_mfa),
    names_to  = "mfa_pcs",      # name of the new “variable” column
    values_to = "mfa_pc_scores"      # name of the new “value” column
  )%>%
  group_by(participant, social_nonsocial, mfa_pcs)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc_scores, 
             colour = social_nonsocial))+
  geom_point(alpha =.1)+
  stat_summary(geom = "pointrange")+

  facet_grid(~mfa_pcs)+
      ggpubr::stat_compare_means(method = "t.test")

# install.packages("afex")
?afex::aov_ez()

afex::aov_ez(data = dta_emo_wide_mfa,
             id = "participant",
             dv = "pc1_mfa",
             between = "social_nonsocial")

afex::aov_ez(data = dta_emo_wide_mfa,
             id = "participant",
             dv = "pc2_mfa",
             between = "social_nonsocial")

afex::aov_ez(data = dta_emo_wide_mfa,
             id = "participant",
             dv = "pc3_mfa",
             between = "social_nonsocial")

# if coherence is 2 this suggets that difefneces are driven by changes in the signal (1) not cohertence per se?
```
Response: pc1_mfa
            Effect    df  MSE      F  ges p.value
1 social_nonsocial 1, 88 1.54 6.21 * .066    .015

pc2 and pc were no significant
separate MFAs







aggregated by ground truth (iaps)
```{r}
dta_emo_agg<- dta_emo%>%
  group_by(participant,social_nonsocial, emotioncategory)%>%
  summarise_if(is.numeric, mean, na.rm = T)




tmp_var<- c("val_slider_response","int_slider_response","happy_slide_response","sad_slide_response","fear_slide_response","disgust_slide_response","anger_slide_response","hr_mean_diff","log_cda_phasic_max","mean_fix_dur","mean_sac_amp","au14_dimpler","au12_lip_corner_pull","au_04_brow_lower","au26_jaw_drop","au01_inner_brow_raise","au02_outer_brow_raise","au05_eye_lid_raise","au06_cheek_raise","au07_eye_lid_tighten","au09_nose_wrinkle","au10_upper_lip_raise","au15_lip_corner_depress","au20_lip_stretch","au17_chin_raise","au23_lip_tighten","au25_lips_apart","au45_eye_blink","social_nonsocial","participant","emotioncategory")
dta_emo_agg
dta_emo_agg1<- dta_emo_agg[, tmp_var] 

dta_emo_agg_wide_mfa<- dta_emo_agg1 %>%
 pivot_wider(
    id_cols     = c("participant", "social_nonsocial"),
    names_from  = c("emotioncategory"),
    values_from = tmp_var[1:28],
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )


dta_emo_agg_wide_mfa
unique(dta_emo_agg$emotioncategory)
dta_emo_agg

6*7
6*17
colnames(dta_emo_agg_wide_mfa)
?MFA
mod_res$mfa_result_wide_agg <- MFA(dta_emo_agg_wide_mfa[,c(3:170,2)],
                          group=c(42,6,6,12,102,1),
                          type=c("s","s","s","s","s","n"),  
                          name.group= c("subj_aff","phys_hr","phys_scr","gaze","face","social_non_soc"),
                          num.group.sup=c(6),#position of group above
                          graph=FALSE)








fviz_contrib(mod_res$mfa_result_wide_agg, "group", axes = 1)
fviz_contrib(mod_res$mfa_result_wide_agg, "group", axes = 2)
fviz_contrib(mod_res$mfa_result_wide_agg, "group", axes = 3)
fviz_contrib(mod_res$mfa_result_wide_agg, "group", axes = 4)
fviz_contrib(mod_res$mfa_result_wide_agg, "group", axes = 5)


# the first three dimensions are consisetnt with the full stiom mfa


```


```{r}

mod_res$mfa_result_wide$group




dta_emo_agg_wide_mfa$pc1_mfa<- mod_res$mfa_result_wide_agg$ind$coord[, 1]
dta_emo_agg_wide_mfa$pc2_mfa<- mod_res$mfa_result_wide_agg$ind$coord[, 2]

dta_emo_agg_wide_mfa$pc3_mfa<- mod_res$mfa_result_wide_agg$ind$coord[, 3]
dta_emo_agg_wide_mfa$pc4_mfa<- mod_res$mfa_result_wide_agg$ind$coord[, 4]
dta_emo_agg_wide_mfa$pc5_mfa<- mod_res$mfa_result_wide_agg$ind$coord[, 5]


  



dta_emo_agg_wide_mfa_coord1<-  as.data.frame(mod_res$mfa_result_wide_agg$ind$coord[,1:5])
dta_emo_agg_wide_mfa_coord1$participant<- dta_emo_agg_wide_mfa$participant



dta_emo_agg_wide_mfa%>%
  pivot_longer( cols      = c(pc1_mfa,pc2_mfa,pc3_mfa,pc4_mfa,pc5_mfa),
    names_to  = "mfa_pcs",      # name of the new “variable” column
    values_to = "mfa_pc_scores"      # name of the new “value” column
  )%>%
  group_by(participant, social_nonsocial, mfa_pcs)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc_scores, 
             colour = social_nonsocial))+
  geom_point(alpha =.1)+
  stat_summary(geom = "pointrange")+

  facet_grid(~mfa_pcs)+
      ggpubr::stat_compare_means(method = "t.test")



afex::aov_ez(data = dta_emo_agg_wide_mfa,
             id = "participant",
             dv = "pc1_mfa",
             between = "social_nonsocial")


afex::aov_ez(data = dta_emo_agg_wide_mfa,
             id = "participant",
             dv = "pc2_mfa",
             between = "social_nonsocial")

afex::aov_ez(data = dta_emo_agg_wide_mfa,
             id = "participant",
             dv = "pc3_mfa",
             between = "social_nonsocial")
```

now use the wide one for separate MFAS


```{r}
dta_emo_wide_mfa_soc<- dta_emo_wide_mfa%>%
  subset(social_nonsocial != "nonsocial")

dta_emo_wide_mfa_nonsocial<- dta_emo_wide_mfa%>%
  subset(social_nonsocial == "nonsocial")

dta_emo_wide_mfa_nonsocial[,c(1682)]


mod_res$mfa_result_wide_nonsoc <- MFA(dta_emo_wide_mfa_nonsocial[,c(3:1682)],
                                   group=c(420,60,60,120,1020,1),
                              type=c("s","s","s","s","s"),                              name.group=c("subj_aff","phys_hr","phys_scr","gaze","face"),
                               graph=FALSE)



mod_res$mfa_result_wide_soc <- MFA(dta_emo_wide_mfa_soc[,c(3:1682)],
                                   group=c(420,60,60,120,1020,1),
                              type=c("s","s","s","s","s"),                              name.group=c("subj_aff","phys_hr","phys_scr","gaze","face"),
                               graph=FALSE)


mod_res$mfa_result_wide_nonsoc$eig #about 5 dikmension untoil eigen drops
fviz_screeplot(mod_res$mfa_result_wide_nonsoc)

mod_res$mfa_result_wide_soc$eig #about 3
fviz_screeplot(mod_res$mfa_result_wide_soc)
mod_res$mfa_result_wide_soc$eig 
mod_res$mfa_result_nonsoc$eig

```

social
eigenvalue percentage of variance cumulative percentage of variance
comp 1   1.9348631              7.5718543                          7.571854
comp 2   1.7003519              6.6541227                         14.225977
comp 3   1.6256227              6.3616790                         20.587656
comp 4   1.2924545              5.0578654                         25.645521
comp 5   1.1145220              4.3615478                         30.007069
comp 6   1.0111642              3.9570695                         33.964139
comp 7   0.9573629              3.7465245                         37.710663
comp 8   0.9188596              3.5958468                         41.306510
comp 9   0.8654731              3.3869250                         44.693435
comp 10  0.7765796              3.0390509                         47.732486
comp 11  0.7217630              2.8245327                         50.557019

non social:
igenvalue percentage of variance cumulative percentage of variance
comp 1  1.27421561             13.6525348                          13.65253
comp 2  1.17750867             12.6163720                          26.26891
comp 3  1.04457643             11.1920745                          37.46098
comp 4  0.96119879             10.2987280                          47.75971
comp 5  0.85437014              9.1541164                          56.91383
comp 6  0.71734560              7.6859722                          64.59980
comp 7  0.48292949              5.1743297                          69.77413
comp 8  0.34311949              3.6763408                          73.45047
comp 9  0.29180334              3.1265158                          76.57698
comp 10 0.24489453              2.6239131                          79.20090

non social is summarised in fewer dimensions, it means those blocks are more coherent or redundant: they share more common variance, so fewer latent factors are needed.
whereas social needing more dimensions means the blocks are less collinear/coherent and contain more independent sources of variance.



wide aggregared separate MFAS
```{r}

dta_emo_agg_wide_mfa_soc<- dta_emo_agg_wide_mfa%>%
  subset(social_nonsocial != "nonsocial")

dta_emo_agg_wide_mfa_nonsocial<- dta_emo_agg_wide_mfa%>%
  subset(social_nonsocial == "nonsocial")

colnames(dta_emo_agg_wide_mfa_nonsocial)

mod_res$mfa_result_agg_wide_nonsoc <- MFA(dta_emo_agg_wide_mfa_nonsocial[,c(3:170)],
                          group=c(42,6,6,12,102),
                              type=c("s","s","s","s","s"),                              name.group=c("subj_aff","phys_hr","phys_scr","gaze","face"),
                               graph=TRUE)


```


```{r}
mod_res$mfa_result_agg_wide_soc <- MFA(dta_emo_agg_wide_mfa_soc[,c(3:170)],
                          group=c(42,6,6,12,102),
                              type=c("s","s","s","s","s"),                              name.group=c("subj_aff","phys_hr","phys_scr","gaze","face"),
                               graph=TRUE)

mod_res$mfa_result_agg_wide_soc$group$RV


  pivot_longer(
    names_to  = "block",      # name of the new “variable” column
    values_to = "value" 
  )


 as.data.frame(mod_res$mfa_result_agg_wide_nonsoc$group$RV)
  as.data.frame(mod_res$mfa_result_agg_wide_soc$group$RV)
  
  
  
as.data.frame(mod_res$mfa_result_agg_wide_nonsoc$group$RV)%>%
  reshape2::melt(varnames = c("Variable1", "Variable2"), 
                 value.name = "Correlation")%>%
ggplot( aes(x = Variable2, y = Variable1, fill = Correlation)) +
  geom_tile(colour = "white") + 
  # Reverse y-axis so that the first row is at the top
  # scale_y_discrete(limits = rev(levels(mat_long$Variable1))) +
  # Use a diverging colour scale centred at 0.5 (or 0 if you prefer)
  scale_fill_gradient2(
    low = "navy",       # low end of the spectrum
    mid = "white",      # mid-point
    high = "firebrick", # high end of the spectrum
    midpoint = 0.5,     # centre of the scale
    name = "Correlation\nCoefficient"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank()
  ) +
  labs(
    x = NULL,
    y = NULL,
    title = "Heatmap of RV Coefficients")
```


```{r}


mod_res$mfa_result_agg_wide_nonsoc$eig #about 5 dikmension untoil eigen drops
fviz_screeplot(mod_res$mfa_result_agg_wide_nonsoc)

mod_res$mfa_result_agg_wide_soc$eig #about 6
fviz_screeplot(mod_res$mfa_result_agg_wide_soc)
mod_res$mfa_result_agg_wide_soc$eig 
mod_res$mfa_result_agg_wide_nonsoc$eig

```


R Script: Permutation Test for Difference in # of Eigenvalues > 1
#             between Social and Non‐Social MFAs - wide all stim
```{r}
#----------------------------------------------------------
# R Script: Permutation Test for Difference in # of Eigenvalues > 1
#             between Social and Non‐Social MFAs
#----------------------------------------------------------

# 0. PREAMBLE: Install & load necessary packages
#    (Uncomment the install.packages lines if you don’t already have them.)
# install.packages("FactoMineR")
# install.packages("dplyr")
# install.packages("pbapply")   # for a progress bar (optional but helpful)
library(FactoMineR)
library(dplyr)
# install.packages("pbapply")
library(pbapply)

# 1. ASSUMPTIONS ABOUT YOUR DATA FRAME `dta_emo_wide_mfa`
#    - Column 1: participant (not needed for MFA itself)
#    - Column 2: social_nonsocial  (factor with exactly two levels: "social" and "nonsocial")
#    - Columns  3:1682 (inclusive) are your measurement columns, in this order:
#        * subj_aff block:   cols  3 :   422  (count = 420)
#        * phys_hr block:    cols 423 :   482  (count =  60)
#        * phys_scr block:   cols 483 :   542  (count =  60)
#        * gaze block:       cols 543 :   662  (count = 120)
#        * face block:       cols 663 :  1682  (count =1020)
#    Adjust these indices if your column counts differ.

# 2. FUNCTION TO RUN A “BLOCK‐SPECIFIED” MFA AND RETURN # OF EIGENVALUES > 1
run_mfa_count_dims <- function(df_wide) {
  # df_wide: a data frame with columns 3:1682 = all measurement cols
  # Run MFA on those cols, using the same group/type/name specifications.
  mfa_result <- MFA(
    df_wide, 
    group      = c(420, 60, 60, 120, 1020),
    type       = c("s", "s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "gaze", "face"),
    graph      = FALSE
  )
  eig_vals <- mfa_result$eig[ , "eigenvalue"]
  # Count how many eigenvalues exceed 1.0
  sum(eig_vals > 1.0)
}

# 3. COMPUTE THE OBSERVED DIFFERENCE D_obs
#    3a. Subset the data frame into true social vs non‐social
dta_emo_wide_mfa_soc    
dta_emo_wide_mfa_nonsocial 

#    3b. Take only the measurement columns (3:1682) for each subset
meas_cols <- 3:1682
mst_social    <- dta_emo_wide_mfa_soc   [ , meas_cols ]
mst_nonsocial <- dta_emo_wide_mfa_nonsocial[ , meas_cols ]

#    3c. Run MFAs on each subset and count dims>1
dims_social_obs   <- run_mfa_count_dims(mst_social)
dims_nonsocial_obs<- run_mfa_count_dims(mst_nonsocial)

#    3d. Observed difference
D_obs <- dims_social_obs - dims_nonsocial_obs

cat("Observed #dims >1:\n",
    "  Social:    ", dims_social_obs, "\n",
    "  Non-social:", dims_nonsocial_obs, "\n",
    "Observed difference (Social – Non-social) = ", D_obs, "\n\n")

# 4. PERMUTATION TEST
#    4a. Parameters for permutation
set.seed(2025)
B <- 1000  # number of permutations (adjust to taste; 1000–2000 is common)

#    4b. Vector to store differences under the null
null_diffs <- integer(B)

#    4c. Original “social_nonsocial” labels
orig_labels <- dta_emo_wide_mfa$social_nonsocial

#    4d. Measurement‐only matrix for convenience
all_meas_mat <- dta_emo_wide_mfa[ , meas_cols ]

#    4e. Permutation loop (with a progress bar)
null_diffs <- pbapply::pblapply(seq_len(B), function(b) {
  # 1) Permute the social/non‐social labels
  perm_labels <- sample(orig_labels)

  # 2) Split the measurement matrix according to permuted labels
  is_soc_perm   <- perm_labels == "social"
  is_nons_perm  <- perm_labels == "nonsocial"
  mat_soc_perm  <- all_meas_mat[is_soc_perm,   ]
  mat_nons_perm <- all_meas_mat[is_nons_perm, ]

  # 3) Run MFA on each permuted subset and count dims>1
  dims_soc_b   <- run_mfa_count_dims(mat_soc_perm)
  dims_nons_b  <- run_mfa_count_dims(mat_nons_perm)

  # 4) Return the difference (Social – Non‐social) for this permutation
  dims_soc_b - dims_nons_b
}, cl = 1)  # cl = 1 means run sequentially; remove cl arg for defaults

null_diffs <- unlist(null_diffs)

# 5. CALCULATE EMPIRICAL P‐VALUE
#    Two‐sided test: how often does |D_b| >= |D_obs| ?
p_emp <- (sum(abs(null_diffs) >= abs(D_obs)) + 1) / (B + 1)

cat("Permutation test results:\n",
    "  Number of permutations  = ", B, "\n",
    "  Observed difference     = ", D_obs, "\n",
    "  Proportion |D_b| ≥ |D_obs|  = ", signif(p_emp, 3), "\n\n")

# 6. INTERPRETATION MESSAGE
if (p_emp < 0.05) {
  cat("Conclusion: The observed difference in the number of dimensions > 1\n",
      "between social and non‐social is statistically significant (p =", signif(p_emp, 3), ").\n",
      "This suggests that the intrinsic dimensionality (and thus block coherence)\n",
      "differs between the two conditions.\n")
} else {
  cat("Conclusion: The observed difference in the number of dimensions > 1\n",
      "between social and non‐social is NOT statistically significant (p =", signif(p_emp, 3), ").\n",
      "There is insufficient evidence to claim that one group truly needs\n",
      "more dimensions (lower coherence) than the other.\n")
}

# END OF SCRIPT

```
Conclusion: The observed difference in the number of dimensions > 1
 between social and non‐social is NOT statistically significant (p = 0.783 ).
 There is insufficient evidence to claim that one group truly needs
 more dimensions (lower coherence) than the other.
 
 
 
 R Script: Permutation Test for Difference in # of Eigenvalues > 1
#             between Social and Non‐Social MFAs - wide - aggregated by emotion
```{r}
#----------------------------------------------------------
# R Script: Permutation Test for Difference in # of Eigenvalues > 1
#             between Social and Non‐Social MFAs
#----------------------------------------------------------


# FUNCTION TO RUN A “BLOCK‐SPECIFIED” MFA AND RETURN # OF EIGENVALUES > 1
run_mfa_count_dims <- function(df_wide) {
  # df_wide: a data frame with columns 3:1682 = all measurement cols
  # Run MFA on those cols, using the same group/type/name specifications.
  mfa_result <- MFA(
    df_wide, 
    group      = c(420, 60, 60, 120, 1020),
    type       = c("s", "s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "gaze", "face"),
    graph      = FALSE
  )
  eig_vals <- mfa_result$eig[ , "eigenvalue"]
  # Count how many eigenvalues exceed 1.0
  sum(eig_vals > 1.0)
}

# 3. COMPUTE THE OBSERVED DIFFERENCE D_obs
#    3a. Subset the data frame into true social vs non‐social
dta_emo_wide_mfa_soc    
dta_emo_wide_mfa_nonsocial 

#    3b. Take only the measurement columns (3:1682) for each subset
meas_cols <- 3:1682
mst_social    <- dta_emo_wide_mfa_soc   [ , meas_cols ]
mst_nonsocial <- dta_emo_wide_mfa_nonsocial[ , meas_cols ]

#    3c. Run MFAs on each subset and count dims>1
dims_social_obs   <- run_mfa_count_dims(mst_social)
dims_nonsocial_obs<- run_mfa_count_dims(mst_nonsocial)

#    3d. Observed difference
D_obs <- dims_social_obs - dims_nonsocial_obs

cat("Observed #dims >1:\n",
    "  Social:    ", dims_social_obs, "\n",
    "  Non-social:", dims_nonsocial_obs, "\n",
    "Observed difference (Social – Non-social) = ", D_obs, "\n\n")

# 4. PERMUTATION TEST
#    4a. Parameters for permutation
set.seed(2025)
B <- 1000  # number of permutations (adjust to taste; 1000–2000 is common)

#    4b. Vector to store differences under the null
null_diffs <- integer(B)

#    4c. Original “social_nonsocial” labels
orig_labels <- dta_emo_wide_mfa$social_nonsocial

#    4d. Measurement‐only matrix for convenience
all_meas_mat <- dta_emo_wide_mfa[ , meas_cols ]

#    4e. Permutation loop (with a progress bar)
null_diffs <- pbapply::pblapply(seq_len(B), function(b) {
  # 1) Permute the social/non‐social labels
  perm_labels <- sample(orig_labels)

  # 2) Split the measurement matrix according to permuted labels
  is_soc_perm   <- perm_labels == "social"
  is_nons_perm  <- perm_labels == "nonsocial"
  mat_soc_perm  <- all_meas_mat[is_soc_perm,   ]
  mat_nons_perm <- all_meas_mat[is_nons_perm, ]

  # 3) Run MFA on each permuted subset and count dims>1
  dims_soc_b   <- run_mfa_count_dims(mat_soc_perm)
  dims_nons_b  <- run_mfa_count_dims(mat_nons_perm)

  # 4) Return the difference (Social – Non‐social) for this permutation
  dims_soc_b - dims_nons_b
}, cl = 1)  # cl = 1 means run sequentially; remove cl arg for defaults

null_diffs <- unlist(null_diffs)

# 5. CALCULATE EMPIRICAL P‐VALUE
#    Two‐sided test: how often does |D_b| >= |D_obs| ?
p_emp <- (sum(abs(null_diffs) >= abs(D_obs)) + 1) / (B + 1)

cat("Permutation test results:\n",
    "  Number of permutations  = ", B, "\n",
    "  Observed difference     = ", D_obs, "\n",
    "  Proportion |D_b| ≥ |D_obs|  = ", signif(p_emp, 3), "\n\n")

# 6. INTERPRETATION MESSAGE
if (p_emp < 0.05) {
  cat("Conclusion: The observed difference in the number of dimensions > 1\n",
      "between social and non‐social is statistically significant (p =", signif(p_emp, 3), ").\n",
      "This suggests that the intrinsic dimensionality (and thus block coherence)\n",
      "differs between the two conditions.\n")
} else {
  cat("Conclusion: The observed difference in the number of dimensions > 1\n",
      "between social and non‐social is NOT statistically significant (p =", signif(p_emp, 3), ").\n",
      "There is insufficient evidence to claim that one group truly needs\n",
      "more dimensions (lower coherence) than the other.\n")
}

# END OF SCRIPT

```
 
test coherence explicitly - wide mfa with ind stimuli

```{r}
# Example (adjust column ranges to match your actual column indices):
subj_aff_mat <- dta_emo_wide_mfa[ , 3:(3+419)]       # 420 subj_aff columns
phys_hr_mat  <- dta_emo_wide_mfa[ , 423:(423+59)]    # next 60 HR columns
phys_scr_mat <- dta_emo_wide_mfa[ , 483:(483+59)]    # next 60 SCR columns
gaze_mat     <- dta_emo_wide_mfa[ , 543:(543+119)]   # next 120 gaze columns
face_mat     <- dta_emo_wide_mfa[ , 663:(663+1019)]  # next 1020 face columns

# Centre each matrix to zero‐mean by column (MFA automatically does this internally, but for RV you must replicate it manually):
centre <- function(mat) sweep(mat, 2, colMeans(mat), FUN = "-")
subj_aff_c  <- centre(subj_aff_mat)
phys_hr_c   <- centre(phys_hr_mat)
phys_scr_c  <- centre(phys_scr_mat)
gaze_c      <- centre(gaze_mat)
face_c      <- centre(face_mat)



# Identify rows for social vs non-social:
is_social    <- dta_emo_wide_mfa$social_nonsocial == "social"
is_nonsocial <- dta_emo_wide_mfa$social_nonsocial == "nonsocial"

# Split each centred block‐matrix accordingly:
subj_aff_soc  <- subj_aff_c[ is_social, ]
subj_aff_nons <- subj_aff_c[ is_nonsocial, ]
phys_hr_soc   <- phys_hr_c[  is_social, ]
phys_hr_nons  <- phys_hr_c[  is_nonsocial, ]
phys_scr_soc  <- phys_scr_c[ is_social, ]
phys_scr_nons <- phys_scr_c[ is_nonsocial, ]
gaze_soc      <- gaze_c[     is_social, ]
gaze_nons     <- gaze_c[     is_nonsocial, ]
face_soc      <- face_c[     is_social, ]
face_nons     <- face_c[     is_nonsocial, ]


library(FactoMineR)
# use FactoMineR::RVcoef() function (which expects two matrices with the same number of rows):
# Example: RV between subjective-affect and face in social subset

# FactoMineR::()
RV_subj_face_soc  <- coeffRV(subj_aff_soc, face_soc)
RV_subj_face_nons <- coeffRV(subj_aff_nons, face_nons)

# RV between HR and face:
RV_hr_face_soc    <- coeffRV(phys_hr_soc, face_soc)
RV_hr_face_nons   <- coeffRV(phys_hr_nons, face_nons)

# RV between gaze and SCR:
RV_gaze_scr_soc   <- coeffRV(gaze_soc, phys_scr_soc)
RV_gaze_scr_nons  <- coeffRV(gaze_nons, phys_scr_nons)




# …repeat for each pair of blocks you care about…

set.seed(2025)
B <- 500
rv_diff <- numeric(B)
# Because RV is a statistic you can bootstrap (resampling rows‐with‐replacement within each condition), you can test whether, for example, RV_subj_face_soc significantly exceeds RV_subj_face_nons. A simple permutation test:
for (b in seq_len(B)) {
  # Permute the labels “social” vs “non‐social” among all rows:
  perm_labels <- sample(dta_emo_wide_mfa$social_nonsocial)
  is_soc_perm  <- perm_labels == "social"
  is_non_perm  <- perm_labels == "nonsocial"

  # Centre and split again according to permuted labels:
  subj_aff_perm_soc  <- centre(subj_aff_mat)[is_soc_perm, ]
  face_perm_soc      <- centre(face_mat)[is_soc_perm, ]

  subj_aff_perm_nons  <- centre(subj_aff_mat)[is_non_perm, ]
  face_perm_nons      <- centre(face_mat)[is_non_perm, ]

  # Compute RV for permuted
  rv_perm_soc     <- coeffRV(subj_aff_perm_soc,  face_perm_soc)
  rv_perm_nons    <- coeffRV(subj_aff_perm_nons, face_perm_nons)
  rv_diff[b]      <- rv_perm_soc$rv - rv_perm_nons$rv
}

# Observed difference:
obs_diff <- RV_subj_face_soc$rv - RV_subj_face_nons$rv

# Two‐sided p‐value:
p_value <- mean(abs(rv_diff) >= abs(obs_diff))

p_value #[1] 0.096

# RV measures the overall association between two matrices of variables, say \mathbf{X} and \mathbf{Y}, each having the same number of observations (rows) but potentially a different number of columns (variables).
```



test coherence explicitly - wide mfa wide aggregated by emotion
to work on properly
- complete missing block comparisons

```{r}
colnames(dta_emo_agg_wide_mfa)
# Example (adjust column ranges to mat_aggch your actual column indices):
subj_aff_mat_agg <- dta_emo_agg_wide_mfa[ , 3:(3+41)]       
phys_hr_mat_agg  <- dta_emo_agg_wide_mfa[ , 45:50]    
phys_scr_mat_agg <- dta_emo_agg_wide_mfa[ , 51:56]   
gaze_mat_agg     <- dta_emo_agg_wide_mfa[ , 57:68]   
face_mat_agg     <- dta_emo_agg_wide_mfa[ , 69:170]  

# Centre each mat_aggrix to zero‐mean by column (MFA automat_aggically does this internally, but for RV you must replicate it manually):
centre <- function(mat_agg) sweep(mat_agg, 2, colMeans(mat_agg), FUN = "-")
subj_aff_c_agg  <- centre(subj_aff_mat_agg)
phys_hr_c_agg   <- centre(phys_hr_mat_agg)
phys_scr_c_agg  <- centre(phys_scr_mat_agg)
gaze_c_agg      <- centre(gaze_mat_agg)
face_c_agg      <- centre(face_mat_agg)



# Identify rows for social vs non-social:
is_social_agg    <- dta_emo_agg_wide_mfa$social_nonsocial == "social"
is_nonsocial_agg <- dta_emo_agg_wide_mfa$social_nonsocial == "nonsocial"

# Split each centred block‐mat_aggrix accordingly:
subj_aff_soc_agg <- subj_aff_c_agg[ is_social_agg, ]
subj_aff_nons_agg<- subj_aff_c_agg[ is_nonsocial_agg, ]
phys_hr_soc_agg  <- phys_hr_c_agg[  is_social_agg, ]
phys_hr_nons_agg <- phys_hr_c_agg[  is_nonsocial_agg, ]
phys_scr_soc_agg <- phys_scr_c_agg[ is_social_agg, ]
phys_scr_nons_agg<- phys_scr_c_agg[ is_nonsocial_agg, ]
gaze_soc_agg     <- gaze_c_agg[     is_social_agg, ]
gaze_nons_agg    <- gaze_c_agg[     is_nonsocial_agg, ]
face_soc_agg     <- face_c_agg[     is_social_agg, ]
face_nons_agg    <- face_c_agg[     is_nonsocial_agg, ]


library(FactoMineR)
# use FactoMineR::RVcoef() function (which expects two mat_aggrices with the same number of rows):
# Example: RV between subjective-affect and face in social subset

# FactoMineR::()
RV_subj_face_soc_agg <- coeffRV(subj_aff_soc_agg, face_soc_agg)
RV_subj_face_nons_agg<- coeffRV(subj_aff_nons_agg, face_nons_agg)

# RV between 
RV_hr_face_soc_agg   <- coeffRV(subj_aff_soc_agg, phys_hr_soc_agg)
RV_hr_face_nons_agg  <- coeffRV(subj_aff_nons_agg,phys_hr_nons_agg)

# RV 
RV_gaze_scr_soc_agg  <- coeffRV(subj_aff_soc_agg, gaze_soc_agg)
RV_gaze_scr_nons_agg <- coeffRV(subj_aff_nons_agg, gaze_nons_agg)


# …repeat for each pair of blocks you care about… to do (all block)

set.seed(44)
B <- 500
rv_diff_agg <- numeric(B)
# Because RV is a statistic you can bootstrap (resampling rows‐with‐replacement within each condition), you can test whether, for example, RV_subj_face_soc_aggsignificantly exceeds RV_subj_face_nons. A simple permutation test:
for (b in seq_len(B)) {
  # Permute the labels “social” vs “non‐social” among all rows:
  perm_labels <- sample(dta_emo_agg_wide_mfa$social_nonsocial)
  is_soc_perm  <- perm_labels == "social"
  is_non_perm  <- perm_labels == "nonsocial"

  # Centre and split again according to permuted labels:
  subj_aff_perm_soc_agg <- centre(subj_aff_mat_agg)[is_soc_perm, ]
  face_perm_soc_agg     <- centre(face_mat_agg)[is_soc_perm, ]

  subj_aff_perm_nons_agg <- centre(subj_aff_mat_agg)[is_non_perm, ]
  face_perm_nons_agg     <- centre(face_mat_agg)[is_non_perm, ]

  # Compute RV for permuted
  rv_perm_soc_agg    <- coeffRV(subj_aff_perm_soc_agg,  face_perm_soc_agg)
  rv_perm_nons_agg   <- coeffRV(subj_aff_perm_nons_agg, face_perm_nons_agg)
  rv_diff_agg[b]      <- rv_perm_soc$rv - rv_perm_nons$rv
}

# Observed difference:
obs_diff_agg <- RV_subj_face_soc$rv - RV_subj_face_nons$rv

# Two‐sided p‐value:
p_value <- mean(abs(rv_diff_agg) >= abs(obs_diff_agg))

p_value #[1] 0.096

```



R Script: Bootstrap Stability Check for the First 3 MFA Dimensions (CIs)
```{r}
#----------------------------------------------------------
# R Script: Bootstrap Stability Check for the First 3 MFA Dimensions
#----------------------------------------------------------

# 0. Install & load required packages
#    (Uncomment install.packages lines if not already installed.)
# install.packages("FactoMineR")
# install.packages("pbapply")
library(FactoMineR)
library(pbapply)

# 1. ASSUMPTIONS ABOUT YOUR DATA FRAME `dta_emo_wide_mfa`
# ----------------------------------------------------------------------------
#   - Column 1: participant (not used in MFA)
#   - Column 2: social_nonsocial  (factor; supplementary)
#   - Columns 3:1682: measurement columns, five blocks concatenated in this order:
#       * subj_aff:   420 columns  →  cols  3 : 422
#       * phys_hr:     60 columns  → cols 423 : 482
#       * phys_scr:    60 columns  → cols 483 : 542
#       * gaze:       120 columns  → cols 543 : 662
#       * face:      1020 columns  → cols 663 : 1682
#   Adjust these indices if your block sizes differ.

meas_cols   <- 3:1682
block_groups <- c(420, 60, 60, 120, 1020)
block_names  <- c("subj_aff", "phys_hr", "phys_scr", "gaze", "face")
N            <- nrow(dta_emo_wide_mfa)  # total number of rows

# 2. FUNCTION: Run MFA and extract first k eigenvalues + block contributions
# ----------------------------------------------------------------------------
compute_mfa_metrics <- function(meas_data, k = 3) {
  # meas_data: a data.frame or matrix containing exactly the measurement columns
  # k: number of leading dimensions to track (here, 3)

  mfa_res <- MFA(
    meas_data,
    group      = block_groups,
    type       = rep("s", length(block_groups)),
    name.group = block_names,
    graph      = FALSE
  )

  eig_all    <- mfa_res$eig[, "eigenvalue"]
  if (length(eig_all) < k) {
    stop("Requested k exceeds the number of available dimensions.")
  }
  eig_vals_k <- eig_all[1:k]

  block_contrib_all <- mfa_res$group$contrib  # (n_blocks × n_dims)
  block_contrib_k   <- block_contrib_all[, 1:k]

  return(list(
    eig_vals      = eig_vals_k,
    block_contrib = block_contrib_k
  ))
}

# 3. OBSERVED METRICS ON THE ENTIRE DATA SET (k = 3)
# ----------------------------------------------------------------------------

obs_metrics      <- compute_mfa_metrics(dta_emo_wide_mfa[, meas_cols], k = 3)
obs_eig_vals     <- obs_metrics$eig_vals        # length 3
obs_block_contrib <- obs_metrics$block_contrib  # matrix (5 × 3)

cat("Observed first 3 eigenvalues:\n")
print(round(obs_eig_vals, 4))
cat("\nObserved block contributions (5 blocks × 3 dims):\n")
print(round(obs_block_contrib, 2))
cat("\n")

# 4. BOOTSTRAP SETUP
# ----------------------------------------------------------------------------
set.seed(2025)
B <- 500   # you can increase to 1000 for tighter intervals
k <- 3     # track only the first three dimensions

eig_boot    <- matrix(NA, nrow = B, ncol = k)
contrib_boot <- array(NA, dim = c(length(block_groups), k, B),
                      dimnames = list(block_names, paste0("Dim", 1:k), NULL))

all_meas <- dta_emo_wide_mfa[, meas_cols]  # N × 1680 matrix

# 5. BOOTSTRAP LOOP (resample rows with replacement)
# ----------------------------------------------------------------------------
pbapply::pboptions(type = "timer")
for (b in seq_len(B)) {
  boot_idx      <- sample(seq_len(N), size = N, replace = TRUE)
  boot_meas_mat <- all_meas[boot_idx, ]

  boot_metrics  <- compute_mfa_metrics(boot_meas_mat, k = k)

  eig_boot[b, ]       <- boot_metrics$eig_vals
  contrib_boot[, , b] <- boot_metrics$block_contrib
}

pbapply::pboptions(reset = TRUE)


# 6. SUMMARISE BOOTSTRAP DISTRIBUTIONS
# ----------------------------------------------------------------------------
# 6a. Eigenvalues summary
eig_summary <- data.frame(
  Dim        = paste0("Dim", 1:k),
  Observed   = obs_eig_vals,
  Mean_boot  = apply(eig_boot, 2, mean),
  SD_boot    = apply(eig_boot, 2, sd),
  CI_lower   = apply(eig_boot, 2, quantile, probs = 0.025),
  CI_upper   = apply(eig_boot, 2, quantile, probs = 0.975)
)

# 6b. Block‐contribution summary for dims 1–3
contrib_summary_list <- vector("list", length = k)
names(contrib_summary_list) <- paste0("Dim", 1:k)

for (d in seq_len(k)) {
  block_contrib_dimd <- contrib_boot[, d, ]  # (5 blocks × B replicates)

  summary_df <- data.frame(
    Block     = block_names,
    Observed  = obs_block_contrib[, d],
    Mean_boot = apply(block_contrib_dimd, 1, mean),
    SD_boot   = apply(block_contrib_dimd, 1, sd),
    CI_lower  = apply(block_contrib_dimd, 1, quantile, probs = 0.025),
    CI_upper  = apply(block_contrib_dimd, 1, quantile, probs = 0.975)
  )
  contrib_summary_list[[d]] <- summary_df
}

# 7. PRINT RESULTS
# ----------------------------------------------------------------------------
cat("===== Bootstrap Summary: First 3 Eigenvalues =====\n")
print(eig_summary)
cat("\n")

for (d in seq_len(k)) {
  cat("===== Block Contributions on Dim ", d, " =====\n", sep = "")
  print(contrib_summary_list[[d]])
  cat("\n")
}

# 8. INTERPRETATION GUIDELINES
# ----------------------------------------------------------------------------
# • If obs_eig_vals[d] lies well inside [CI_lower, CI_upper], then Dim d is stable.
# • If obs_block_contrib[b, d] has a narrow CI (e.g. Observed ± 1–2 %) then block b’s
#   contribution to dimension d is robust.
# • If either CI dips below 1.0 (for an eigenvalue) or a block’s CI is extremely wide,
#   treat that dimension/block loading with caution.

```

```{r}

# Extract all bootstrap eigenvalues for Dim1:
boot_dim1 <- eig_boot[, 1]

# Compute one-sided p-value:
p_dim1_gt1 <- ( sum(boot_dim1 >= obs_eig_vals[1]) + 1 ) / (B + 1)

# Print:
cat(
  "Dim1 observed λ =", round(obs_eig_vals[1], 3),
  "| bootstrap p(λ ≥ obs) =", signif(p_dim1_gt1, 3), "\n"
)

```

p values ro wether the dolutionni sstable (complemets the abive CIs)
```{r}
#----------------------------------------------------------
# R Script: MFA Bootstrap with Empirical p‐Values for Eigenvalues
#           and Block Contributions (First 3 Dimensions)
#----------------------------------------------------------

# 0. Install & load required packages (if not already installed)
# ---------------------------------------------------------------
# install.packages("FactoMineR")
# install.packages("pbapply")
library(FactoMineR)
library(pbapply)

# 1. DATA ASSUMPTIONS
# ---------------------------------------------------------------
#   - dta_emo_wide_mfa: a data frame with:
#       Column 1: participant (not used in MFA)
#       Column 2: social_nonsocial (factor; supplementary)
#       Columns 3:1682: measurement columns, five blocks concatenated:
#         subj_aff: cols  3 :  422   (420 columns)
#         phys_hr:  cols 423 :  482   ( 60 columns)
#         phys_scr: cols 483 :  542   ( 60 columns)
#         gaze:     cols 543 :  662   (120 columns)
#         face:     cols 663 : 1682   (1020 columns)
#
#    Adjust `meas_cols`, `block_groups`, and `block_names` if your column ranges differ.

meas_cols    <- 3:1682
block_groups <- c(420, 60, 60, 120, 1020)
block_names  <- c("subj_aff", "phys_hr", "phys_scr", "gaze", "face")
N            <- nrow(dta_emo_wide_mfa)   # total number of rows (cases)

# 2. FUNCTION: Run MFA and return first k eigenvalues + block contributions
# ---------------------------------------------------------------
compute_mfa_metrics <- function(meas_data, k = 3) {
  # meas_data: matrix/data.frame containing exactly the measurement columns
  # k: number of leading dimensions to extract
  mfa_res <- MFA(
    meas_data,
    group      = block_groups,
    type       = rep("s", length(block_groups)),
    name.group = block_names,
    graph      = FALSE
  )
  eig_all <- mfa_res$eig[, "eigenvalue"]
  if (length(eig_all) < k) {
    stop("Requested k exceeds available dimensions.")
  }
  eig_vals_k     <- eig_all[1:k]                 # first k eigenvalues
  contrib_all     <- mfa_res$group$contrib        # block × dims matrix
  contrib_vals_k  <- contrib_all[, 1:k]           # first k columns
  return(list(
    eig_vals      = eig_vals_k, 
    block_contrib = contrib_vals_k
  ))
}

# 3. RUN MFA ON FULL DATASET (OBSERVED METRICS)
# ---------------------------------------------------------------
obs_metrics       <- compute_mfa_metrics(dta_emo_wide_mfa[, meas_cols], k = 3)
obs_eig_vals      <- obs_metrics$eig_vals         # length-3 vector
obs_block_contrib <- obs_metrics$block_contrib    # 5 × 3 matrix

cat("Observed eigenvalues (Dim 1–3):\n")
print(round(obs_eig_vals, 4))
cat("\nObserved block contributions (5 blocks × 3 dims):\n")
print(round(obs_block_contrib, 2))
cat("\n")

# 4. BOOTSTRAP SETUP
# ---------------------------------------------------------------
set.seed(2025)

B        <- 500   # number of bootstrap replicates
k        <- 3     # how many dimensions to track
eig_boot <- matrix(NA, nrow = B, ncol = k)
# dims: bootstrap replicate × dimension
contrib_boot <- array(NA, dim = c(length(block_groups), k, B),
                      dimnames = list(block_names, paste0("Dim", 1:k), NULL))
# dims: block × dimension × replicate

all_meas <- dta_emo_wide_mfa[, meas_cols]  # N × 1680 measurement matrix

# 5. BOOTSTRAP LOOP (RESAMPLE ROWS WITH REPLACEMENT)
# ---------------------------------------------------------------
pbapply::pboptions(type = "timer")
for (b in seq_len(B)) {
  boot_idx      <- sample(seq_len(N), size = N, replace = TRUE)
  boot_meas_mat <- all_meas[boot_idx, ]
  boot_metrics  <- compute_mfa_metrics(boot_meas_mat, k = k)
  eig_boot[b, ]       <- boot_metrics$eig_vals
  contrib_boot[, , b] <- boot_metrics$block_contrib
}
pbapply::pboptions(reset = TRUE)

# 6. COMPUTE EMPIRICAL p‐VALUES FOR EIGENVALUES
# ---------------------------------------------------------------
# Test: H0: eigenvalue_d ≤ 1 (Kaiser threshold)  vs  H1: > 1
p_eig_gt1 <- numeric(k)
for (d in 1:k) {
  # Count how many bootstrap λ_d ≤ 1
  count_leq1          <- sum(eig_boot[, d] <= 1.0)
  p_eig_gt1[d]        <- (count_leq1 + 1) / (B + 1) 
  # one-sided p-value: probability λ_d ≤ 1 by chance
}

# Optionally, test H0: λ_d = 1 vs H1: λ_d ≠ 1 (two‐sided around 1)
p_eig_two_sided <- numeric(k)
for (d in 1:k) {
  obs_dev   <- abs(obs_eig_vals[d] - 1.0)
  boot_dev  <- abs(eig_boot[, d] - 1.0)
  count_big <- sum(boot_dev >= obs_dev)
  p_eig_two_sided[d] <- (count_big + 1) / (B + 1)
}

# 7. COMPUTE EMPIRICAL p‐VALUES FOR BLOCK CONTRIBUTIONS
# ---------------------------------------------------------------
# Example test: H0: block contribution ≤ 0  vs  H1: > 0
# (In practice, almost all contributions will exceed 0, but you can test > threshold τ)
threshold_contrib <- 0.05
p_block_contrib_gt0 <- matrix(NA, nrow = length(block_names), ncol = k,
                              dimnames = list(block_names, paste0("Dim", 1:k)))
for (d in 1:k) {
  for (b_idx in seq_along(block_names)) {
    boot_vals_bc <- contrib_boot[b_idx, d, ]  # length B
    # One-sided p-value: probability that bootstrap ≤ threshold
    count_leq_thresh <- sum(boot_vals_bc <= threshold_contrib)
    p_block_contrib_gt0[b_idx, d] <- (count_leq_thresh + 1) / (B + 1)
  }
}

# Another test: H0: block contribution =  observed value (two‐sided)
p_block_two_sided <- matrix(NA, nrow = length(block_names), ncol = k,
                            dimnames = list(block_names, paste0("Dim", 1:k)))
for (d in 1:k) {
  for (b_idx in seq_along(block_names)) {
    obs_bc    <- obs_block_contrib[b_idx, d]
    boot_dev_bc <- abs(contrib_boot[b_idx, d, ] - obs_bc)
    obs_dev_bc  <- 0  # distance from itself
    count_big_bc <- sum(boot_dev_bc >= obs_dev_bc)
    p_block_two_sided[b_idx, d] <- (count_big_bc + 1) / (B + 1)
  }
}

# 8. DISPLAY RESULTS
# ---------------------------------------------------------------
cat("===== Eigenvalue p‐values (one‐sided H0: λ ≤ 1) =====\n")
for (d in 1:k) {
  cat("Dim", d, ": observed λ =", round(obs_eig_vals[d], 3),
      "| p(λ ≤ 1) =", signif(p_eig_gt1[d], 3), 
      "| p_two_sided(λ ≠ 1) =", signif(p_eig_two_sided[d], 3), "\n")
}
cat("\n")

cat("===== Block Contribution p‐values (one‐sided H0: ≤ 0) =====\n")

for (d in 1:k) {
  cat("Dimension", d, ":\n")
  print(
    data.frame(
      Block       = block_names,
      Observed    = obs_block_contrib[, d],
      p_gt0       = round(p_block_contrib_gt0[, d], 3)
    )
  )
  cat("\n")
}

# If you want to test “observed contribution differs from its own bootstrap”:
# (This test is trivial because |boot_dev| ≥ 0 always, so p_two_sided = 1)
cat("===== Block Contribution p‐values (two‐sided around observed) =====\n")

for (d in 1:k) {
  cat("Dimension", d, ":\n")
  print(
    data.frame(
      Block          = block_names,
      Observed       = obs_block_contrib[, d],
      p_two_sided_bc = round(p_block_two_sided[, d], 3)
    )
  )
  cat("\n")
}

# 9. INTERPRETATION GUIDELINES
# ---------------------------------------------------------------
#  - If p_eig_gt1[d] < 0.05: eigenvalue of Dim d is significantly > 1 (robust).
#  - If p_eig_two_sided[d] < 0.05: eigenvalue of Dim d differs from 1 in either direction.
#  - If p_block_contrib_gt0[b, d] < 0.05: block b’s contribution to Dim d is significantly > 0.
#  - Typically, you’d test whether each block’s contribution exceeds a non‐zero threshold
#    (e.g. > 5 %), by setting threshold_contrib = 0.05 and recalculating p_block_contrib_gt0.

# End of script
p_eig_gt1[1]
p_eig_gt1[2]
p_eig_gt1[3]

p_eig_gt1
# overakl thsi is significant? [1] 0.001996008 0.001996008 0.001996008

p_eig_two_sided

p_block_contrib_gt0


as.data.frame(eig_boot)%>%
  ggplot(aes(x = V1))+
  geom_histogram()
```


library(FactoMineR)
sig test for null ([arallell analyssi)])

```{r}

N      <- nrow(all_meas)
p      <- ncol(all_meas)    # here p = sum(block_groups)
M      <- 500               # number of Monte Carlo replicates
k      <- 3                 # how many leading dimensions to compare

# Storage for null eigenvalues
null_eig <- matrix(NA, nrow = M, ncol = k)

for (m in seq_len(M)) {
  # 1) Generate random noise data: N × p matrix, independent columns
  #    Option A: Gaussian null
  # null_data <- matrix(rnorm(N * p), nrow = N, ncol = p)
  
  #    Option B (nonparametric): sample each column with replacement
  null_data <- apply(all_meas, 2, sample, size = N, replace = TRUE)
  
  # 2) Run MFA on null_data
  mfa_null <- MFA(
    null_data,
    group      = block_groups,
    type       = rep("s", length(block_groups)),
    name.group = block_names,
    graph      = FALSE
  )
  
  # 3) Record the first k eigenvalues
  null_eig[m, ] <- mfa_null$eig[1:k, "eigenvalue"]
}

# 4) Compute, for each dimension d=1..k, the 95th percentile of null_eig[,d]
null_cutoffs <- apply(null_eig, 2, quantile, probs = 0.95)

# 5) Compare to observed
obs_metrics  <- compute_mfa_metrics(all_meas, k = k)
obs_eig_vals <- obs_metrics$eig_vals

# Print results
for (d in 1:k) {
  cat(sprintf(
    "Dim %d: observed λ = %.3f, 95%% null cutoff = %.3f → %s\n",
    d,
    obs_eig_vals[d],
    null_cutoffs[d],
    if (obs_eig_vals[d] > null_cutoffs[d]) "significant" else "n.s."
  ))
}

```


d <- 1
hist(null_eig_perm[, d],
     breaks = 30,
     col    = "grey80",
     main   = paste("Null Distribution: Dim", d, "Eigenvalue"),
     xlab   = paste("Permuted λ (Dim", d, ")"))
abline(v = obs_eig_vals[d], col = "red", lwd = 2)
text(
  x = obs_eig_vals[d], 
  y = max(table(cut(null_eig_perm[, d], breaks = 30))) * 0.9,
  labels = paste0("Obs λ = ", round(obs_eig_vals[d], 3)),
  pos    = 4, 
  col    = "red"
)
p_emp <- mean(null_eig_perm[, d] >= obs_eig_vals[d])
mtext(side = 3, text = paste0("Empirical p ≈ ", signif(p_emp, 3)))


t tst or chance under null
```{r}
library(FactoMineR)

M <- 500
k <- 3
p <- sum(block_groups)
null_eig_perm <- matrix(NA, nrow = M, ncol = k)

for (m in seq_len(M)) {
  perm_data <- all_meas  # copy original
  start_col <- 1
  for (b_idx in seq_along(block_groups)) {
    cols_b <- start_col:(start_col + block_groups[b_idx] - 1)
    perm_data[, cols_b] <- all_meas[sample(N), cols_b]
    start_col <- start_col + block_groups[b_idx]
  }
  mfa_p <- MFA(
    perm_data,
    group      = block_groups,
    type       = rep("s", length(block_groups)),
    name.group = block_names,
    graph      = FALSE
  )
  null_eig_perm[m, ] <- mfa_p$eig[1:k, "eigenvalue"]
}

# 95th‐percentile cutoffs:
perm_cutoffs <- apply(null_eig_perm, 2, quantile, probs = 0.95)

# Compare to observed as before:
for (d in 1:k) {
  cat(sprintf(
    "Dim %d: observed λ = %.3f, 95%% perm cutoff = %.3f → %s\n",
    d,
    obs_eig_vals[d],
    perm_cutoffs[d],
    if (obs_eig_vals[d] > perm_cutoffs[d]) "significant" else "n.s."
  ))
}

# Empirical p-value for each d:
p_perm_d <- sapply(1:k, function(d) mean(null_eig_perm[, d] >= obs_eig_vals[d]))
print(p_perm_d)



d <- 1
hist(null_eig_perm[, 3],
     breaks = 30,
     col    = "grey80",
     main   = paste("Null Distribution: Dim", d, "Eigenvalue"),
     xlab   = paste("Permuted λ (Dim", d, ")"))
abline(v = obs_eig_vals[2], col = "red", lwd = 2)
text(
  x = obs_eig_vals[3], 
  y = max(table(cut(null_eig_perm[, 3], breaks = 30))) * 0.9,
  labels = paste0("Obs λ = ", round(obs_eig_vals[3], 3)),
  pos    = 4, 
  col    = "red"
)
p_emp <- mean(null_eig_perm[, d] >= obs_eig_vals[d])
mtext(side = 3, text = paste0("Empirical p ≈ ", signif(p_emp, 3)))

p_emp
```

Permutation Test for Difference in # of Dimensions
#             Needed to Explain ≥50% Inertia (Variance)
#             between Social and Non‐Social MFAs





Conclusion: The observed difference in the number of dimensions
 needed to explain ≥50% inertia between social and non‐social is
 statistically significant (p = 0.000999 ).
 This suggests that, to reach half of the total variance,
 one condition genuinely requires more factors (lower coherence)
 than the other.
```{r}
#----------------------------------------------------------
# R Script: Permutation Test for Difference in # of Dimensions
#             Needed to Explain ≥50% Inertia (Variance)
#             between Social and Non‐Social MFAs
#----------------------------------------------------------

# 0. PREAMBLE: Install & load necessary packages
#    (Uncomment the install.packages lines if needed.)
# install.packages("FactoMineR")
# install.packages("dplyr")
# install.packages("pbapply")   # for a progress bar (optional but helpful)
library(FactoMineR)
library(dplyr)
library(pbapply)

# 1. ASSUMPTIONS ABOUT YOUR DATA FRAME `dta_emo_wide_mfa`
#    - Column 1: participant (not used directly in MFA)
#    - Column 2: social_nonsocial  (factor with exactly two levels: "social" and "nonsocial")
#    - Columns  3:1682 (inclusive) are measurement columns, ordered as:
#        * subj_aff block:   cols  3 :   422   (count = 420)
#        * phys_hr block:    cols 423 :   482   (count =  60)
#        * phys_scr block:   cols 483 :   542   (count =  60)
#        * gaze block:       cols 543 :   662   (count = 120)
#        * face block:       cols 663 :  1682   (count =1020)
#    Adjust these indices if your column counts differ.

meas_cols <- 3:1682

# 2. FUNCTION TO RUN MFA AND RETURN THE MINIMAL NUMBER OF DIMENSIONS
#    REQUIRED TO EXPLAIN ≥50% OF TOTAL INERTIA
run_mfa_count_to_50 <- function(meas_data) {
  # meas_data: data frame or matrix with exactly measurement columns 3:1682
  # Returns the smallest integer k such that the first k dimensions'
  # cumulative "% of variance" ≥ 50.0
  
  mfa_res <- MFA(
    meas_data,
    group      = c(420, 60, 60, 120, 1020),
    type       = c("s", "s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "gaze", "face"),
    graph      = FALSE
  )
  
  # Extract the "% of variance" column from the eigen table
  pct_var <- mfa_res$eig[, "percentage of variance"]
  cum_pct  <- cumsum(pct_var)
  
  # Find the smallest k where cumulative percentage ≥ 50
  k_needed <- which(cum_pct >= 50)[1]
  return(k_needed)
}

# 3. PREPARE OBSERVED COUNTS FOR SOCIAL VS NON-SOCIAL
# ----------------------------------------------------------------------------
# Subset the main data frame into social vs non‐social:
# dta_emo_wide_mfa_soc    <- dta_emo_wide_mfa %>% filter(social_nonsocial == "social")
# dta_emo_wide_mfa_nonsoc <- dta_emo_wide_mfa %>% filter(social_nonsocial == "nonsocial")

# Extract only the measurement columns (3:1682) for each subset
mst_social    <- dta_emo_wide_mfa_soc   [ , meas_cols ]
mst_nonsocial <- dta_emo_wide_mfa_nonsoc[ , meas_cols ]

# Compute how many dimensions are needed to reach ≥50% for each subset
dims_social_obs   <- run_mfa_count_to_50(mst_social)
dims_nonsocial_obs<- run_mfa_count_to_50(mst_nonsocial)

# Observed difference
D_obs <- dims_social_obs - dims_nonsocial_obs

cat("Observed #dims to reach ≥50% inertia:\n",
    "  Social:    ", dims_social_obs, "\n",
    "  Non-social:", dims_nonsocial_obs, "\n",
    "Observed difference (Social – Non-social) = ", D_obs, "\n\n")

# 4. PERMUTATION TEST
# ----------------------------------------------------------------------------
set.seed(2025)
B <- 1000  # number of permutations

# Vector to store differences under the null
null_diffs <- integer(B)

# Original “social_nonsocial” labels (length = total rows)
orig_labels <- dta_emo_wide_mfa$social_nonsocial

# Measurement‐only matrix for convenience (all rows × 1680 cols)
all_meas_mat <- dta_emo_wide_mfa[ , meas_cols ]

# Permutation loop (with progress bar)
null_diffs <- pbapply::pblapply(seq_len(B), function(b) {
  # 1) Permute the social/non‐social labels
  perm_labels <- sample(orig_labels)
  
  # 2) Split the measurement matrix according to permuted labels
  is_soc_perm   <- perm_labels == "social"
  is_nons_perm  <- perm_labels == "nonsocial"
  
  # When permuted labels happen to create an empty group, skip this replicate
  if (sum(is_soc_perm) == 0 || sum(is_nons_perm) == 0) {
    return(NA_integer_)
  }
  
  mat_soc_perm  <- all_meas_mat[is_soc_perm,   ]
  mat_nons_perm <- all_meas_mat[is_nons_perm, ]
  
  # 3) Run MFA on each permuted subset and count dims needed for ≥50%
  dims_soc_b   <- run_mfa_count_to_50(mat_soc_perm)
  dims_nons_b  <- run_mfa_count_to_50(mat_nons_perm)
  
  # 4) Return the difference (Social – Non‐social) for this permutation
  return(dims_soc_b - dims_nons_b)
}, cl = 1)  # cl = 1 means sequential; remove cl argument for defaults

# Convert to integer vector, omitting any NA replicates
null_diffs <- unlist(null_diffs)
null_diffs <- null_diffs[!is.na(null_diffs)]

# 5. CALCULATE EMPIRICAL P‐VALUE
#    Two‐sided test: proportion of |D_b| ≥ |D_obs|
p_emp <- (sum(abs(null_diffs) >= abs(D_obs)) + 1) / (length(null_diffs) + 1)

cat("Permutation test results:\n",
    "  Number of (valid) permutations  = ", length(null_diffs), "\n",
    "  Observed difference             = ", D_obs, "\n",
    "  Proportion |D_b| ≥ |D_obs|      = ", signif(p_emp, 3), "\n\n")

# Permutation test results:
#    Number of (valid) permutations  =  1000 
#    Observed difference             =  4 
#    Proportion |D_b| ≥ |D_obs|      =  0.000999 

# 6. INTERPRETATION MESSAGE
if (p_emp < 0.05) {
  cat("Conclusion: The observed difference in the number of dimensions\n",
      "needed to explain ≥50% inertia between social and non‐social is\n",
      "statistically significant (p =", signif(p_emp, 3), ").\n",
      "This suggests that, to reach half of the total variance,\n",
      "one condition genuinely requires more factors (lower coherence)\n",
      "than the other.\n")
} else {
  cat("Conclusion: The observed difference in the number of dimensions\n",
      "needed to explain ≥50% inertia between social and non‐social is NOT\n",
      "statistically significant (p =", signif(p_emp, 3), ").\n",
      "There is insufficient evidence to claim that one group truly needs\n",
      "more dimensions to explain the same amount of variance.\n")
}


as.data.frame(null_diffs)%>%
  ggplot(aes(null_diffs))+
  geom_density(fill = "gray30")+
  # geom_histogram(bins = 300)+
  geom_vline(xintercept = D_obs)+
  xlim(-3,5)



fviz_mfa_var(mod_res$mfa_result_wide)


fviz_mfa_var(mod_res$mfa_result_wide,
             # highlight variables by group (block)
             habillage = "group",
             # label only those with cos² > 0.3
             select.var = list(cos2 = 0.2),
             # colour‐gradient by cos² (you can drop this if you want pure block colours)
             # col.var = "cos2",
             # gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             # repel = TRUE,       # avoid overlaps in texts
             labelsize = 0) +
  ggtitle("MFA – Variable Correlation Circle (Dim 1 & Dim 2)")
```



Make a plot that shows the results of the dimensions
```{r}

# 2.1 Get the coordinate matrix (variables × dimensions)
mod_res$mfa_result_wide$quanti.var$coord
coords_mat <- mod_res$mfa_result_wide$quanti.var$coord[, 1:2]  # first 5 axes



 # 2.2 Build a data.frame that also stores “which block” each variable belongs to
var_names   <- rownames(coords_mat)                      # e.g. “Age”, “BP”, etc.
block_labels <- rep(block_names, times = block_groups) 
#   – i.e. “Block1” repeated ncol(df1) times, then “Block2” repeated ncol(df2), etc.

df_plot <- data.frame(
  Variable = var_names,
  Block    = block_labels,
  Dim1     = coords_mat[, 1],
  Dim2     = coords_mat[, 2],
  row.names = NULL,
  stringsAsFactors = FALSE
)

# ─── 3. Plain ggplot2 scatter of Dim 1 vs Dim 2, coloured by block ──────────────

# Load ggplot2 (if not already)
library(ggplot2)

mod_res$mfa_result_wide$quanti.var$cos2[, 1:2]
df_plot$dim_1_cos<- mod_res$mfa_result_wide$quanti.var$cos2[, 1]
df_plot$dim_2_cos<- mod_res$mfa_result_wide$quanti.var$cos2[, 2]

df_plot$dim_1_cont<- mod_res$mfa_result_wide$quanti.var$contrib[, 1]
df_plot$dim_2_cont<- mod_res$mfa_result_wide$quanti.var$contrib[, 2]

df_plot$dim_1_2_ratio<- df_plot$dim_1_cos/(df_plot$dim_1_cos+df_plot$dim_2_cos)
df_plot$dim_1_2_ratio_cont<- df_plot$dim_1_cont/(df_plot$dim_1_cont+df_plot$dim_2_cont)



df_plot <- df_plot %>% 
  # (no scaling of Dim1/Dim2 here) 
  mutate(
    cos12_total    = dim_1_cos + dim_2_cos,
    cos12_ratio    = dim_1_cos / (dim_1_cos + dim_2_cos),
    # optionally cap or filter out very low cos² if you only want well-represented vars:
    cos12_total2   = if_else(cos12_total < 0.05, NA_real_, cos12_total)
  )


plts<- list()



plts$mfa_wide<-


df_plot%>%
  # group_by(Block,stim_iaps_emo)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot( aes(x = Dim1, y = Dim2)) +

  # 2) scatter, mapping:
  #    - point size to total cos² (bigger = better captured by Dims 1 & 2)
  #    - point colour (hue) to cos² ratio (red = more Dim1, blue = more Dim2
  
  
  # (after computing df_plot$cos12_total = dim_1_cos + dim_2_cos)

geom_point(
  aes(
    colour = Block,
    shape  = Block,
    size   = cos12_total
  ),
  alpha = 0.3
) +
scale_size_continuous(
  range = c(1, 6),
  name  = "Total cos²\n(Dim1 + Dim2)"
)+
  # 3) shared axes
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # coord_fixed(
  #   xlim = c(-1.1, 1.1),
  #   ylim = c(-1.1, 1.1)
  # ) 
  # 4) scales & legends
  scale_colour_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
  # scale_colour_viridis_c(option = "inferno")+
  # scale_colour_gradient2(
  #   low      = "blue",
  #   mid      = "grey90",
  #   high     = "red",
  #   midpoint = 0.5,
  #   name     = "cos² ratio\n(Dim1 vs Dim2)"
  # ) +
  scale_size_continuous(
    range = c(1, 6),
    name  = "Total cos² (Dim1+2)"
  ) +
  ggside::geom_xsidedensity(
    aes(y = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  )+ 
    ggside::geom_ysidedensity(
    aes(x = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE)+
  # )+ 
  labs(
    x     = "MFA PC1",
    y     = "MFA PC2",
    title = "Shared axes: size = quality of rep."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", size = 0.2)
  )+
  guides(size = FALSE)



plts$mfa_wide+
  p$graphstyle_int
  
    
```




```{r}

mod_res$mfa_result_wide_nonsoc



df_plot_ind <- data.frame(
  social_non = var_names,
  Block    = block_labels,
  Dim1     = coords_mat[, 1],
  Dim2     = coords_mat[, 2],
  row.names = NULL,
  stringsAsFactors = FALSE
)


dta_emo_wide_mfa
dta_emo_wide_coord1$social_nonsocial <- dta_emo_wide_mfa$social_nonsocial


dta_emo_wide_mfa%>%
  # mutate(pc1_mfa = scale(pc1_mfa),
  #        pc2_mfa = scale(pc2_mfa))%>%
  ggplot(aes(abs(pc1_mfa), abs(pc2_mfa), colour =social_nonsocial ))+
  geom_point()


dta_emo_wide_mfa%>%
  # mutate(pc1_mfa = scale(pc1_mfa),
  #        pc2_mfa = scale(pc2_mfa))%>%
  ggplot(aes(abs(pc1_mfa), abs(pc2_mfa), colour =social_nonsocial ))+
  geom_point()



library(ggplot2)

colnames(dta_emo_agg)
dta_emo_agg_demogs<-dta_emo_agg%>%
  group_by(participant, social_nonsocial)%>%
  select(60:76)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()



```


```{r}

dta_emo_agg_demogs


dta_emo_wide_mfa<- dta_emo_wide_mfa%>%
  left_join(dta_emo_agg_demogs)

plts$mfa_wide_ind <- ggplot(dta_emo_wide_mfa, aes(x = pc1_mfa, y = pc2_mfa, colour = social_nonsocial,
                             shape = social_nonsocial)) +
  # 1) Draw a 95% ellipse around each group’s points
  stat_ellipse(
    aes(fill = social_nonsocial),
    type   = "norm",
    level  = 0.95,
    geom   = "polygon",
    alpha  = 0.1,
    colour = NA
  ) +
  # 2) Plot the points themselves
  geom_point(
    alpha = 0.7,
    size  = 2
  ) +
  # 3) Zero lines for reference
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # 4) Facet so that “social” and “non-social” appear in separate panels
  # facet_wrap(~ social_nonsocial) +
  # 5) Shared colour/fill scales (choose a palette you like)
  scale_colour_brewer(palette = "Set1", name = "Group") +
  scale_fill_brewer(palette = "Set1", guide = "none") +
  # 6) Labels and theme tweaks
  labs(
    x     = "PC1 (MFA)",
    y     = "PC2 (MFA)",
    title = "MFA: Individuals on PC1 vs PC2, by Social vs Non-Social"
  ) +
  theme_minimal() +
  theme(
    legend.position   = "top",
    legend.title = element_blank(),
    panel.grid.minor  = element_blank(),
    panel.grid.major  = element_line(colour = "grey90", size = 0.2),
    strip.background  = element_rect(fill = "grey95", colour = NA),
    strip.text        = element_text(face = "bold")
  )+
   # ggside::geom_ysidedensity(aes(y =pc2_mfa, fill = social_nonsocial, alpha = .0001),orientation = "y")+
  
    ggside::geom_ysidedensity(
    aes(x = after_stat(density),fill = social_nonsocial),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  ) +
  
  ggside::geom_xsidedensity(
    aes(y = after_stat(density),fill = social_nonsocial),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  ) +
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")

plts$mfa_wide

plts$mfa_wide_ind+
  p$graphstyle_int+
   scale_xsidey_continuous(breaks = NULL) +
  scale_ysidex_continuous(breaks = NULL) 



dta_emo_wide_mfa%>%
  ggplot(aes(social_nonsocial, pc1_mfa ))+
  geom_point(alpha = .1)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means(method = "t.test")


```


```{r}



dta_emo_wide_mfa%>%
  ggplot(aes(tas20_total, pc1_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
  ggpubr::stat_cor()


dta_emo_wide_mfa%>%
  ggplot(aes(tas20_total, pc2_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
  ggpubr::stat_cor()


dta_emo_wide_mfa%>%
  ggplot(aes(tas20_total, pc3_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
  ylim(-2,4)+
  ggpubr::stat_cor()



dta_emo_wide_mfa%>%
  ggplot(aes(aq28_total_cont, pc1_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
  ggpubr::stat_cor()


dta_emo_wide_mfa%>%
  ggplot(aes(aq28_total_cont, pc2_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
    ylim(-3,4)+
  ggpubr::stat_cor()


dta_emo_wide_mfa%>%
  ggplot(aes(aq28_total_cont, pc3_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+

  ggpubr::stat_cor()


  # anxiety

dta_emo_wide_mfa%>%
  ggplot(aes(dass21_dep, pc1_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
  ggpubr::stat_cor()


dta_emo_wide_mfa%>%
  ggplot(aes(dass21_dep, pc2_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
    # ylim(-3,4)+
  ggpubr::stat_cor()


dta_emo_wide_mfa%>%
  ggplot(aes(dass21_dep, pc3_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+

  ggpubr::stat_cor()
  
```





Make a plot that shows the results of the dimensions
```{r}

# 2.1 Get the coordinate matrix (variables × dimensions)
mod_res$mfa_result_wide_agg$quanti.var$coord
coords_mat_wide_agg <- mod_res$mfa_result_wide_agg$quanti.var$coord[, 1:2]  # first 5 axes



 # 2.2 Build a data.frame that also stores “which block” each variable belongs to
var_names   <- rownames(coords_mat_wide_agg)                      # e.g. “Age”, “BP”, etc.
block_labels_2 <- rep(block_names, times = c(42,6,6,12,102)) 
#   – i.e. “Block1” repeated ncol(df1) times, then “Block2” repeated ncol(df2), etc.

df_plot_agg <- data.frame(
  Variable = var_names,
  Block    = block_labels_2,
  Dim1     = coords_mat_wide_agg[, 1],
  Dim2     = coords_mat_wide_agg[, 2],
  row.names = NULL,
  stringsAsFactors = FALSE
)

# ─── 3. Plain ggplot2 scatter of Dim 1 vs Dim 2, coloured by block ──────────────

# Load ggplot2 (if not already)
library(ggplot2)

mod_res$mfa_result_wide_agg$quanti.var$cos2[, 1:2]

df_plot_agg$dim_1_cos <- mod_res$mfa_result_wide_agg$quanti.var$cos2[, 1]
df_plot_agg$dim_2_cos<- mod_res$mfa_result_wide_agg$quanti.var$cos2[, 2]

df_plot_agg$dim_1_cont<- mod_res$mfa_result_wide_agg$quanti.var$contrib[, 1]
df_plot_agg$dim_2_cont<- mod_res$mfa_result_wide_agg$quanti.var$contrib[, 2]

# df_plot_agg$dim_1_2_ratio<- df_plot_agg$dim_1_cos/(df_plot_agg$dim_1_cos+df_plot_agg$dim_2_cos)
# 
# df_plot_agg$dim_1_2_ratio_cont<- df_plot_agg$dim_1_cont/(df_plot_agg$dim_1_cont+df_plot_agg$dim_2_cont)

df_plot_agg

df_plot_agg <- df_plot_agg %>% 
  # (no scaling of Dim1/Dim2 here) 
  mutate(
    cos12_total    = dim_1_cos + dim_2_cos,
    cos12_ratio    = dim_1_cos / (dim_1_cos + dim_2_cos),
    # optionally cap or filter out very low cos² if you only want well-represented vars:
    cos12_total2   = if_else(cos12_total < 0.05, NA_real_, cos12_total)
  )

# df_plot_agg$df_plot_agg<-NULL

as.data.frame(df_plot_agg)%>%

  # summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot( aes(x = Dim1, y = Dim2*-1)) +

  # 2) scatter, mapping:
  #    - point size to total cos² (bigger = better captured by Dims 1 & 2)
  #    - point colour (hue) to cos² ratio (red = more Dim1, blue = more Dim2
  
  
  # (after computing df_plot_agg$cos12_total = dim_1_cos + dim_2_cos)

geom_point(
  aes(
    colour = Block,
    shape  = Block,
    size   = cos12_total
  ),
  alpha = 0.4
) +
    scale_color_brewer(palette = "Dark2")+
scale_size_continuous(
  range = c(1, 6),
  name  = "Total cos²\n(Dim1 + Dim2)"
)+
  # 3) shared axes
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # coord_fixed(
  #   xlim = c(-1.1, 1.1),
  #   ylim = c(-1.1, 1.1)
  # ) 
  # 4) scales & legends

  # scale_colour_viridis_d(option = "inferno")+
  # scale_colour_gradient2(
  #   low      = "blue",
  #   mid      = "grey90",
  #   high     = "red",
  #   midpoint = 0.5,
  #   name     = "cos² ratio\n(Dim1 vs Dim2)"
  # ) +
  scale_size_continuous(
    range = c(1, 6),
    name  = "Total cos² (Dim1+2)"
  ) +
  # scale_fill_brewer(
  #   palette = "Dark2",
  #   name    = "Block"
  # ) +
  labs(
    x     = "Dimension 1",
    y     = "Dimension 2",
    title = "MFA variables (shared axes): colour = Dim1 vs Dim2, size = quality of rep."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "right",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", size = 0.2)
  )



```




```{r}


dta_emo_agg_wide_mfa
ggplot(dta_emo_agg_wide_mfa, aes(x = pc1_mfa, y = pc2_mfa, colour = social_nonsocial,
                             shape = social_nonsocial)) +
  # 1) Draw a 95% ellipse around each group’s points
  stat_ellipse(
    aes(fill = social_nonsocial),
    type   = "norm",
    level  = 0.95,
    geom   = "polygon",
    alpha  = 0.1,
    colour = NA
  ) +
  # 2) Plot the points themselves
  geom_point(
    alpha = 0.7,
    size  = 2
  ) +
  # 3) Zero lines for reference
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # 4) Facet so that “social” and “non-social” appear in separate panels
  # facet_wrap(~ social_nonsocial) +
  # 5) Shared colour/fill scales (choose a palette you like)
  scale_colour_brewer(palette = "Set1", name = "Group") +
  scale_fill_brewer(palette = "Set1", guide = "none") +
  # 6) Labels and theme tweaks
  labs(
    x     = "PC1 (MFA)",
    y     = "PC2 (MFA)",
    title = "MFA: Individuals on PC1 vs PC2, by Social vs Non-Social"
  ) +
  theme_minimal() +
  theme(
    legend.position   = "none",
    panel.grid.minor  = element_blank(),
    panel.grid.major  = element_line(colour = "grey90", size = 0.2),
    strip.background  = element_rect(fill = "grey95", colour = NA),
    strip.text        = element_text(face = "bold")
  )+
   # ggside::geom_ysidedensity(aes(y =pc2_mfa, fill = social_nonsocial, alpha = .0001),orientation = "y")+
  
    ggside::geom_ysidedensity(
    aes(x = after_stat(density),fill = social_nonsocial),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  ) +
  
  ggside::geom_xsidedensity(
    aes(y = after_stat(density),fill = social_nonsocial),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  ) +
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")


dta_emo_agg_wide_mfa

dta_emo_agg_wide_mfa%>%
  ggplot(aes(social_nonsocial, pc1_mfa ))+
  geom_point(alpha = .1)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means(method = "t.test")

```




```{r}


dta_emo_agg_wide_mfa<- dta_emo_agg_wide_mfa%>%
  left_join(dta_emo_agg_demogs)




```

```{r}

make_df_plot <- function(mfa_res, blocks) {
  # 1.1 Extract Dim1, Dim2 coords for each variable
  coords_12 <- mfa_res$quanti.var$coord[, 1:2]       # matrix (n_vars × 2)
  cos2_mat  <- mfa_res$quanti.var$cos2[, 1:2]        # matrix of cos² on Dim1 & Dim2
  var_names <- rownames(coords_12)
  
  # 1.2 Build ‘Block’ labels (must match the MFA’s `group` argument)
  group_sizes <- sapply(blocks, ncol)
  block_labels <- rep(names(blocks), times = group_sizes)
  
  # 1.3 Assemble a data.frame
  df <- data.frame(
    Variable    = var_names,
    Block       = factor(block_labels, levels = names(blocks)),
    Dim1        = coords_12[, 1],
    Dim2        = coords_12[, 2],
    dim_1_cos   = cos2_mat[, 1],
    dim_2_cos   = cos2_mat[, 2],
    stringsAsFactors = FALSE
  )
  
  # 1.4 Compute total & ratio of cos² on Dim1+Dim2
  df <- df %>%
    mutate(
      cos12_total = dim_1_cos + dim_2_cos,
      cos12_ratio = dim_1_cos / (dim_1_cos + dim_2_cos)
    )
  
  return(df)
}

# ─── 2. Define your ‘blocks’ list exactly as used in the two MFA calls ─────────

blocks <- list(
  subj_aff = NULL,   # placeholder, we only need the ncol counts
  phys_hr  = NULL,
  phys_scr = NULL,
  gaze     = NULL,
  face     = NULL
)
# Replace NULL with the actual data.frames or simply set group sizes manually:
# e.g. blocks <- list(subj_aff = df_subj_aff, phys_hr = df_phys_hr, …)
# The important part is that names(blocks) and sapply(blocks,ncol) match your MFA’s group= argument.

# If you don’t have the original data.frames here, just set:
group_sizes <- c(420, 60, 60, 120, 1020)
names(group_sizes) <- c("subj_aff","phys_hr","phys_scr","gaze","face")
# then do:
blocks <- lapply(group_sizes, function(k) matrix(nrow = k, ncol = 1))
# (we only care about the lengths; the actual contents don’t matter for labeling)

# ─── 3. Build df_plot for non-social and for social ─────────────────────────────

df_plot_nonsoc <- make_df_plot(mod_res$mfa_result_wide_nonsoc, blocks)
df_plot_soc    <- make_df_plot(mod_res$mfa_result_wide_soc,    blocks)

# ─── 4. Plot: non-social MFA variables ──────────────────────────────────────────

p_nonsoc <- df_plot_nonsoc %>%
  ggplot(aes(x = Dim1, y = Dim2)) +
  
  # 4.1 Scatter: size ∝ total cos², colour ∝ cos² ratio, shape ∝ Block
  geom_point(
    aes(
      colour =cos12_ratio  ,#cos12_ratio
      shape  = Block,
      size   = cos12_total
    ),
    alpha = 0.4
  ) +
  
  # 4.2 Zero‐lines
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  
   # scale_colour_viridis_c(option = "inferno")+
  # scale_colour_gradient2(
  #   low      = "blue",
  #   mid      = "grey90",
  #   high     = "red",
  #   midpoint = 0.5,
  #   name     = "cos² ratio\n(Dim1 vs Dim2)"
  # ) +
  # scale_size_continuous(
  #   range = c(1, 6),
  #   name  = "Total cos² (Dim1+2)"
  # ) +
  # scale_fill_brewer(
  #   palette = "Dark2",
  #   name    = "Block"
  # ) +
  # labs(
  #   x     = "Dimension 1",
  #   y     = "Dimension 2",
  #   title = "MFA variables (shared axes): colour = Dim1 vs Dim2, size = quality of rep."
  # ) +
  theme_minimal() +
  theme(
    legend.position  = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", size = 0.2)
  )+
  xlim(-1,1)+
    ylim(-1,1)+
    scale_colour_viridis_c(option = "inferno")

# ─── 5. Plot: social MFA variables ──────────────────────────────────────────────

p_soc <- df_plot_soc %>%
  ggplot(aes(x = Dim1* (-1), y = Dim2*(-1))) +
  
  # 5.1 Scatter: same aesthetics
  geom_point(
    aes(
      colour = cos12_ratio,
      shape  = Block,
      size   = cos12_total
    ),
    alpha = 0.4
  ) +
  
  # 5.2 Zero‐lines
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # scale_colour_gradient2(
  #   low      = "blue",
  #   mid      = "grey90",
  #   high     = "red",
  #   midpoint = 0.5,
  #   name     = "cos² ratio\n(Dim1 vs Dim2)"
  # ) +
  # scale_size_continuous(
  #   range = c(1, 6),
  #   name  = "Total cos² (Dim1+2)"
  # ) +
  # scale_fill_brewer(
  #   palette = "Dark2",
  #   name    = "Block"
  # ) +
  # labs(
  #   x     = "Dimension 1",
  #   y     = "Dimension 2",
  #   title = "MFA variables (shared axes): colour = Dim1 vs Dim2, size = quality of rep."
  # ) +
  theme_minimal() +
  theme(
    legend.position  = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", size = 0.2)
  )+
  xlim(-1,1)+
    ylim(-1,1)+
    scale_colour_viridis_c(option = "inferno")

# ─── 6. Print plots ─────────────────────────────────────────────────────────────

print(p_nonsoc)
print(p_soc)
p_nonsoc+guides(size = FALSE, shape = FALSE)
p_soc+
guides(size = FALSE,shape = FALSE)
```



```{r}
dta_emo_4mfa$social_nonsocial

dta_emo_4mfa_social<- dta_emo_4mfa%>%
  subset(social_nonsocial != "nonsocial")

dta_emo_4mfa_nonsocial<- dta_emo_4mfa%>%
  subset(social_nonsocial == "nonsocial")


colnames(dta_emo_4mfa_social)

mod_res$mfa_result_soc <- MFA(dta_emo_4mfa_social[,c(4:31)],
                              group=c(7,1,1,2,17), 
                              type=c("s","s","s","s","s"),                              name.group=c("subj_aff","phys_hr","phys_scr","gaze","face"),
                              # num.group.sup=c(6),
                              graph=FALSE)


```



```{r}


mod_res$mfa_result_soc$eig #about 2 or 3 dimensions
fviz_screeplot(mod_res$mfa_result_soc)

# Contribution to the first dimension
fviz_contrib(mod_res$mfa_result_soc, "group", axes = 1)
fviz_contrib(mod_res$mfa_result_soc, "group", axes = 2)
fviz_contrib(mod_res$mfa_result_soc, "group", axes = 3)
fviz_contrib(mod_res$mfa_result_soc, "group", axes = 4)
fviz_contrib(mod_res$mfa_result_soc, "group", axes = 5)
# Contribution to the second dimension




```


Alexithymia and autism analysis


```{r}


dta_emo$tas20_total_z<- scale(dta_emo$tas20_total)

dta_emo$aq28_total_cont<- scale(dta_emo$aq28_total_cont)

mod_res$val_tas<- lmer(val_slider_response ~ 1+ social_nonsocial+ tas20_total_z+social_nonsocial+
                         social_nonsocial:tas20_total_z+ social_nonsocial:emotioncategory + 
                     (1|participant) + 
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

mod_res$val_aq<- lmer(val_slider_response ~ 1+ social_nonsocial+ aq28_total_cont+social_nonsocial+
                         social_nonsocial:aq28_total_cont+ social_nonsocial:emotioncategory + 
                     (1|participant) + 
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$val_tas)
anova(mod_res$val_aq)




mod_res$int_tas<- lmer(int_slider_response ~ 1+ social_nonsocial+ emotioncategory + tas20_total_z+
                        social_nonsocial:tas20_total_z+ social_nonsocial: emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$int_tas)



mod_res$int_aq<- lmer(int_slider_response ~ 1+ social_nonsocial+ emotioncategory + aq28_total_cont+
                        social_nonsocial:aq28_total_cont+ social_nonsocial: emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$int_aq)


mod_res$scr_cda_phas_1_tas<- lmer(log_cda_phasic_max ~ 1+ social_nonsocial+ emotioncategory + tas20_total_z+
                        social_nonsocial:tas20_total_z+ social_nonsocial: emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)


mod_res$scr_cda_phas_1_aq<- lmer(log_cda_phasic_max ~ 1+ social_nonsocial+ emotioncategory + aq28_total_cont+
                        social_nonsocial:aq28_total_cont+ social_nonsocial: emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$scr_cda_phas_1_tas)
anova(mod_res$scr_cda_phas_1_aq)



mod_res$hr_mean_diff_1_tas<- lmer(hr_mean_diff ~ 1+ social_nonsocial+ emotioncategory + tas20_total_z+
                        social_nonsocial:tas20_total_z+ social_nonsocial: emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)


mod_res$hr_mean_diff_1_aq<- lmer(hr_mean_diff ~ 1+ social_nonsocial+ emotioncategory + aq28_total_cont+
                        social_nonsocial:aq28_total_cont+ social_nonsocial: emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$hr_mean_diff_1_tas)
anova(mod_res$hr_mean_diff_1_aq)




dta_emo_face_scale_long$tas20_total_z<- scale(dta_emo_face_scale_long$tas20_total)
dta_emo_face_scale_long$aq28_total_cont_z<- scale(dta_emo_face_scale_long$aq28_total_cont)


mod_res$au_pcs_scores_tas<- lmer(pc_scores ~ 1+ social_nonsocial* au_pcs* tas20_total_z* emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo_face_scale_long)


mod_res$au_pcs_scores_aq<- lmer(pc_scores ~ 1+ social_nonsocial* au_pcs* aq28_total_cont_z* emotioncategory+
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo_face_scale_long)


anova(mod_res$au_pcs_scores_tas)

anova(mod_res$au_pcs_scores_aq)





   dta_emo_face_scale_long%>%
  group_by(participant,au_pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(tas20_total_z, pc_scores, colour = social_nonsocial))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
     geom_smooth(method = "lm", se = F)+
   facet_grid(social_nonsocial~au_pcs)+
     ggpubr::stat_cor()
  
   
   
    dta_emo_face_scale_long%>%
  group_by(participant,au_pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(aq28_total_cont_z, pc_scores, colour = social_nonsocial))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
     geom_smooth(method = "lm", se = F)+
   facet_grid(social_nonsocial~au_pcs)+
     ggpubr::stat_cor()
    
    
    
        dta_emo_face_scale_long%>%
  group_by(participant,au_pcs,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(aq28_total_cont, tas20_total, colour = social_nonsocial))+

  # geom_jitter(alpha = .2, position = position_dodge(1))+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
 geom_smooth(aes(group = participant), method = 'lm',se = F, size = .5)+
     geom_smooth(method = "lm", se = F)+
   facet_grid(~social_nonsocial)+
     ggpubr::stat_cor()


        
        
dta_emo_agg_wide_mfa%>%
  subset(pc1_mfa> -3)%>%
  ggplot(aes(tas20_total, pc1_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
  # ylim(-3,4)+
  ggpubr::stat_cor()



dta_emo_agg_wide_mfa%>%
  ggplot(aes(tas20_total, pc2_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+
  ggpubr::stat_cor()


dta_emo_agg_wide_mfa%>%
    subset(pc3_mfa> -3)%>%
  # subset( )
  ggplot(aes(tas20_total, pc3_mfa ))+
  geom_point()+
  facet_grid(~social_nonsocial)+
  geom_smooth(method = "lm")+

  ggpubr::stat_cor()

```







