---
title: "s4sn cleaner models"
author: "Helio"
date: "2025-09-11"
output: html_document
---

Valence and Intensity


```{r}
mod_res$val_subj<- lmer(val_slider_response ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)

anova(mod_res$val_subj)




```


```{r}

mod_res$int_subj<- lmer(int_slider_response ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)
 # data = dta_emo%>%subset(participant!=235)%>%
 # subset(participant!=245)) #it remains sigmificant with those

anova(mod_res$int_subj)

emmeans::emmeans(mod_res$int_subj, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")


library(dplyr)
library(ggplot2)

# 1. Compute means by emotion × condition
unique(dta_emo$condition)
emo_diffs <- dta_emo %>%
  group_by(subj_emo_lab_no_amb, condition) %>%
  summarise(int_mean = mean(int_slider_response, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = condition, values_from = int_mean) %>%
  mutate(diff = `social` - `control`)   # adjust if your condition labels differ

# 2. Reorder factor levels by size of difference
order_levels <- emo_diffs %>%
  arrange(desc(diff)) %>%
  pull(subj_emo_lab_no_amb)




plts$s4sn_int<-
dta_emo %>%
  # subset(participant!= 235)%>%
  # subset(participant!= 245)%>%
  mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, int_slider_response, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("intensity (au)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plts$s4sn_int

ggsave("s4sn_int.png", plts$s4sn_int,  dpi = 300, width = 10, height = 6,  units = "in",
       device = "png")

 
 ggsave("s4sn_int.png", plts$s4sn_int, device = "png", width = 10, height = 6, dpi = 300)

```


testign individual emotion ratings
```{r}


mod_res$slid_hap<- lmer(happy_slide_response ~ 1+ social_nonsocial + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)


anova(mod_res$slid_hap)

mod_res$slid_sad<- lmer(sad_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)




mod_res$slid_fear<- lmer(fear_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)



mod_res$slid_disg<- lmer(disgust_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)



mod_res$slid_ang<- lmer(anger_slide_response ~ 1+ social_nonsocial  + 
                     (1|participant) + #subjective_emotion doesn't coverge
                     (1|stim_iaps), 
                   REML = FALSE,
                   data = dta_emo)




# 0) ANOVAs (unchanged)
anova(mod_res$slid_hap)
anova(mod_res$slid_ang)
anova(mod_res$slid_fear)
anova(mod_res$slid_disg)
anova(mod_res$slid_sad)

# 1) Collect models
mod_list_emo_slid <- list(
  slid_ang  = mod_res$slid_ang,
  slid_hap  = mod_res$slid_hap,
  slid_fear = mod_res$slid_fear,
  slid_disg = mod_res$slid_disg,
  slid_sad  = mod_res$slid_sad
)



# Optional tidy-up of workspace, safely
rm(list = intersect(c("betas","beta_pool"), ls()))

# 2) Extract betas/SEs for a term, with missing-term safety
get_beta_se <- function(term, models = mod_list_emo_slid) {
  pull_one <- function(m) {
    coefs <- summary(m)$coefficients
    if (!term %in% rownames(coefs)) return(c(beta = NA_real_, se = NA_real_))
    c(beta = coefs[term, "Estimate"], se = coefs[term, "Std. Error"])
  }
  mat <- sapply(models, pull_one)
  list(
    betas = as.numeric(mat["beta", ]),
    ses   = as.numeric(mat["se",   ])
  )
}

# Example correct call (for a quick check):
# get_beta_se("social_nonsocialsocial")

# 3) Pooling + Z-test with NA/zero checks
pool_effect <- function(betas, ses) {
  keep <- is.finite(betas) & is.finite(ses)
  if (!any(keep)) return(c(beta = NA_real_, se = NA_real_, Z = NA_real_, p = NA_real_))

  beta_pool <- sqrt(sum(betas[keep]^2, na.rm = TRUE))
  se_pool   <- sqrt(sum(ses[keep]^2,   na.rm = TRUE))

  if (!is.finite(se_pool) || se_pool == 0) {
    return(c(beta = beta_pool, se = se_pool, Z = NA_real_, p = NA_real_))
  }

  Z_stat  <- beta_pool / se_pool
  p_value <- 2 * pnorm(-abs(Z_stat))
  c(beta = beta_pool, se = se_pool, Z = Z_stat, p = p_value)
}

# 4) Run omnibus for your term
term_social <- "social_nonsocialsocial"

omnibus <- t(sapply(term_social, function(term) {
  dat <- get_beta_se(term)
  pool_effect(dat$betas, dat$ses)
}))

omnibus



```

autonomic


```{r}
# outliers
# 142
# 129
# 235

mod_res$hr_mean_diff_2 <- lmer(hr_mean_diff ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)


mod_res$hr_mean_diff_2.tas <- lmer(hr_mean_diff ~ 1+ social_nonsocial * subj_emo_lab_no_amb *tas20_total_z+
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)
#  data = dta_emo%>%subset(participant!=235)%>%
# subset(participant!=142)) #results remain the same withouth these

anova(mod_res$hr_mean_diff_2)

anova(mod_res$hr_mean_diff_2.tas)

dta_emo%>%
  group_by(participant,subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  # subset(hr_mean_diff <20)%>%
  ggplot(aes(subj_emo_lab_no_amb, hr_mean_diff, colour = subj_emo_lab_no_amb))+
  # geom_smooth(aes(x = as.numeric(as.factor(subj_emo_lab_no_amb))))+
  # geom_jitter(alpha = .2)+
  stat_summary(geom = "pointrange")+
  # ylim(0,10)+
  # facet_grid(~subj_emo_lab_no_amb)+
  ggpubr::stat_compare_means()




emo_diffs_hr <- dta_emo %>%
  group_by(subj_emo_lab_no_amb, condition) %>%
  summarise(hr_mean_diff_mean = mean(hr_mean_diff, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = condition, values_from = hr_mean_diff_mean) %>%
  mutate(diff_hr = `social` - `control`)   # adjust if your condition labels differ

# 2. Reorder factor levels by size of difference
order_levels_hr <- emo_diffs_hr %>%
  arrange(desc(diff_hr)) %>%
  pull(subj_emo_lab_no_amb)

plts$s4sn_hr_diff<-


dta_emo %>%
  subset(participant!= 235)%>%
  subset(participant!= 142)%>%
  # subset(participant!= 142)%>%
  mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_hr))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, hr_mean_diff, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("heart rate (diff)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plts$s4sn_hr_diff

dta_emo %>%
  subset(participant!= 235)%>%
  subset(participant!= 142)%>%
  # subset(participant!= 142)%>%
  # mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels))%>%
  group_by(participant, condition) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, hr_mean_diff, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  # facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("intensity") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plts$s4sn_int

ggsave("s4sn_int.png", plts$s4sn_int,  dpi = 300, width = 10, height = 6,  units = "in",
       device = "png")

 
 ggsave("s4sn_int.png", plts$s4sn_int, device = "png", width = 10, height = 6, dpi = 300)

```

scr
```{r}
range(dta_emo$log_cda_n_scr)
mod_res$scr_cda_phas_2 <- lmer(log_cda_phasic_max ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + # doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo)



dta_emo%>%
  subset(participant!= 104)%>%
  subset(participant!= 105)%>%
  subset(participant!= 147)%>%
  subset(participant!= 206)%>%
  subset(participant!= 248)%>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, log_cda_phasic_max, colour = social_nonsocial))+
  geom_jitter(alpha = .2)+
  # geom_boxplot()+
  # geom_text(aes(label = participant))+
  stat_summary(geom = "pointrange", fun.data = mean_se)+
  # ylim(0,10)+
  facet_grid(~subj_emo_lab_no_amb)
  ggpubr::stat_compare_means()
  
  anova(mod_res$scr_cda_phas_2)

  emmeans::emmeans(mod_res$scr_cda_phas_2, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")
  
  emmeans::emmeans(mod_res$scr_cda_phas_2, pairwise ~ social_nonsocial, 
                 adjust = "tukey")
  
  


  
  
  

emo_diffs_scr <- dta_emo %>%
  group_by(subj_emo_lab_no_amb, condition) %>%
  summarise(log_cda_phasic_max_mean = mean(log_cda_phasic_max, na.rm = TRUE), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = condition, values_from = log_cda_phasic_max_mean) %>%
  mutate(diff_scr = `social` - `control`)   # adjust if your condition labels differ

# 2. Reorder factor levels by size of difference
order_levels_scr <- emo_diffs_scr %>%
  arrange(desc(diff_scr)) %>%
  pull(subj_emo_lab_no_amb)

plts$s4sn_scr<-
dta_emo %>%
  subset(participant!= 104)%>%
  subset(participant!= 105)%>%
  subset(participant!= 206)%>%
  subset(participant!= 248)%>%
  mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_scr))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, log_cda_phasic_max, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .4) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("scr (log)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


plts$s4sn_scr

```


face
```{r}

dta_emo_face_scale



colnames(dta_emo_4mfa[,c(15:31)])
mod_res$pca_multil_omix_face <- pca(dta_emo_4mfa[,c(15:31)], 
                            scale = TRUE, 
                            center = TRUE, 
                            multilevel = pca_multil_design_face, ncomp = 3)


# interpret the components

 plotVar(mod_res$pca_multil_omix_face , var.names = TRUE, cutoff = 0.4, pch = 16)
 
mod_res$pca_multil_omix_face$loadings
dta_emo_4mfa$pc1_multl_face<-mod_res$pca_multil_omix_face$variates$X[,1] #whole face
dta_emo_4mfa$pc2_multl_face<-mod_res$pca_multil_omix_face$variates$X[,2]#mouth
dta_emo_4mfa$pc3_multl_face<-mod_res$pca_multil_omix_face$variates$X[,3]#eyes

option(scipen = 999)

median(abs(mod_res$pca_multil_omix_face$loadings$X))

 # 0.2048408

abs(mod_res$pca_multil_omix_face$loadings$X)




test1<- afex::aov_ez(data = dta_emo_4mfa,
             id = "participant",
             dv = "pc1_multl_face",
             between = "social_nonsocial",
             within = c("emotioncategory"))



test2<- afex::aov_ez(data = dta_emo_4mfa,
             id = "participant",
             dv = "pc3_multl_face",
             between = "social_nonsocial",
             within = c("emotioncategory"))
emmeans::emmeans(test, pairwise~ social_nonsocial|emotioncategory)
emmeans::emmeans(test, pairwise~ emotioncategory) 

```


```{r}
mod_res$pc1_multl_face <- lmer(pc1_multl_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     # (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)
mod_res$pc2_multl_face <- lmer(pc2_multl_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     # (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)

mod_res$pc3_multl_face <- lmer(pc3_multl_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     # (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)



# anova(mod_res$pc1_trad_face)
anova(mod_res$pc2_multl_face)
anova(mod_res$pc3_multl_face)
anova(mod_res$pc1_multl_face)
# expressivity
emmeans::emmeans(mod_res$pc1_multl_face, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$pc1_multl_face, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "none")


# car::Anova(mod_res$pc1_multl_face, type = 3)
# car::Anova(mod_res$pc2_multl_face, type = 3)
# car::Anova(mod_res$pc3_multl_face, type = 3)

```


mod_res$pc1_trad_face <- lmer(pc1_trad_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)
mod_res$pc2_trad_face <- lmer(pc2_trad_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)

mod_res$pc3_trad_face <- lmer(pc3_trad_face ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_emo_4mfa)

??car::Anova

anova(mod_res$pc1_trad_face)
anova(mod_res$pc2_trad_face)
anova(mod_res$pc3_trad_face)

# car::Anova(mod_res$pc1_trad_face, type = 3)
# car::Anova(mod_res$pc2_trad_face, type = 3)
# car::Anova(mod_res$pc3_trad_face, type = 3)


```{r}


plts$s4sn_face <-


dta_emo_4mfa %>%
  # pivot_longer(
  #   cols      = c(pc1_multl_face, pc2_multl_face, pc3_multl_face),
  #   names_to  = "au_pcs",
  #   values_to = "au_pc_scores"
  # ) %>%
  # mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_scr))%>%
  mutate(condition = if_else(social_nonsocial == "social","social", "control"))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, pc1_multl_face, colour = condition, fill = condition)) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("face acticity - PC1 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# plts$s4sn_face <-



dta_emo_4mfa %>%
  # pivot_longer(
  #   cols      = c(pc1_multl_face, pc2_multl_face, pc3_multl_face),
  #   names_to  = "au_pcs",
  #   values_to = "au_pc_scores"
  # ) %>%
  # mutate(subj_emo_lab_no_amb = factor(subj_emo_lab_no_amb, levels = order_levels_scr))%>%
  mutate(condition = if_else(social_nonsocial == "social","social", "control"))%>%
  group_by(participant, condition, subj_emo_lab_no_amb) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(condition, pc3_multl_face, colour = condition, fill = condition)) +
  # geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("face acticity - PC3 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


plts$s4sn_face
plts$int_hr_scr <- (plts$s4sn_int+ plts$s4sn_hr_diff+plts$s4sn_scr)



 ggsave("int_hr_scr.png", plts$int_hr_scr, device = "png", width = 14, height = 7, dpi = 300)
 ggsave("int_hr_scr.pdf", plts$int_hr_scr, device = "pdf", width = 18, height = 7, dpi = 400)

 
 
  ggsave("face.pdf", plts$s4sn_face, device = "pdf", width = 10, height = 5, dpi = 400)

ggsave()


```



coherence

```{r}

  ggsave("face.pdf", plts$s4sn_face, device = "pdf", width = 10, height = 5, dpi = 400)




  ggsave("mfa_wide_space.pdf", plts$mfa_wide  , device = "pdf", width = 7, height = 6, dpi = 400)

  ggsave("mfa_wide_ind.pdf", plts$mfa_wide_ind  , device = "pdf", width = 5, height = 5, dpi = 400)



```





```{r}

unique(dta_emo$participant)


# unique(dta_emo_wide_mfa$)
dta_emo_wide_mfa<- newDF%>%
 pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),
    values_from = names(newDF[,1:28]),
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )


# 

  

dta_emo_wide_mfa
colnames(dta_emo_wide_mfa)
# val_slider_response"                   
#   [5] "int_slider_response"                   
#   [6] "happy_slide_response"                  
#   [7] "sad_slide_response"                    
#   [8] "fear_slide_response"                   
#   [9] "disgust_slide_response"                
#  [10] "anger_slide_response"

60*7 #subjective #420

17*60 #aus #1020
dta_emo_wide_mfa[,422]
dta_emo_wide_mfa
sum(c(420,60,60,120,1020,1))
dta_emo_wide_mfa[,c(3:1682,2)]
?MFA
colnames(dta_emo_wide_mfa)
mod_res$mfa_result_wide <- MFA(dta_emo_wide_mfa[,c(3:1682,2)],
                          group=c(420,60,60,120,1020,1),
                          type=c("s","s","s","s","s","n"),  
                          name.group= c("subj_aff","phys_hr","phys_scr","gaze","face","social_non_soc"),
                          num.group.sup=c(6),#position of group above
                          graph=FALSE)





plot.MFA(mod_res$mfa_result_wide, choix="ind",lab.par=FALSE,invisible= 'quali',select='cos2  0.25',habillage='social_nonsocial',title="Individual factor map")


mod_res$mfa_result_wide$eig #about 2 or 3 dimensions
fviz_screeplot(mod_res$mfa_result_wide)

```

Make a plot that shows the results of the dimensions
```{r}

# 2.1 Get the coordinate matrix (variables × dimensions)
mod_res$mfa_result_wide$quanti.var$coord
coords_mat <- mod_res$mfa_result_wide$quanti.var$coord[, 1:2]  # first 5 axes



 # 2.2 Build a data.frame that also stores “which block” each variable belongs to
var_names   <- rownames(coords_mat)                      # e.g. “Age”, “BP”, etc.
block_labels <- rep(block_names, times = block_groups) 
#   – i.e. “Block1” repeated ncol(df1) times, then “Block2” repeated ncol(df2), etc.

df_plot <- data.frame(
  Variable = var_names,
  Block    = block_labels,
  Dim1     = coords_mat[, 1],
  Dim2     = coords_mat[, 2],
  row.names = NULL,
  stringsAsFactors = FALSE
)

# ─── 3. Plain ggplot2 scatter of Dim 1 vs Dim 2, coloured by block ──────────────

# Load ggplot2 (if not already)
library(ggplot2)

mod_res$mfa_result_wide$quanti.var$cos2[, 1:2]
df_plot$dim_1_cos<- mod_res$mfa_result_wide$quanti.var$cos2[, 1]
df_plot$dim_2_cos<- mod_res$mfa_result_wide$quanti.var$cos2[, 2]

df_plot$dim_1_cont<- mod_res$mfa_result_wide$quanti.var$contrib[, 1]
df_plot$dim_2_cont<- mod_res$mfa_result_wide$quanti.var$contrib[, 2]

df_plot$dim_1_2_ratio<- df_plot$dim_1_cos/(df_plot$dim_1_cos+df_plot$dim_2_cos)
df_plot$dim_1_2_ratio_cont<- df_plot$dim_1_cont/(df_plot$dim_1_cont+df_plot$dim_2_cont)



df_plot <- df_plot %>% 
  # (no scaling of Dim1/Dim2 here) 
  mutate(
    cos12_total    = dim_1_cos + dim_2_cos,
    cos12_ratio    = dim_1_cos / (dim_1_cos + dim_2_cos),
    # optionally cap or filter out very low cos² if you only want well-represented vars:
    cos12_total2   = if_else(cos12_total < 0.05, NA_real_, cos12_total)
  )


plts<- list()



plts$mfa_wide<-


df_plot%>%
  # group_by(Block,stim_iaps_emo)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot( aes(x = Dim1, y = Dim2)) +

  # 2) scatter, mapping:
  #    - point size to total cos² (bigger = better captured by Dims 1 & 2)
  #    - point colour (hue) to cos² ratio (red = more Dim1, blue = more Dim2
  
  
  # (after computing df_plot$cos12_total = dim_1_cos + dim_2_cos)

geom_point(
  aes(
    colour = Block,
    shape  = Block,
    size   = cos12_total
  ),
  alpha = 0.3
) +
scale_size_continuous(
  range = c(1, 6),
  name  = "Total cos²\n(Dim1 + Dim2)"
)+
  # 3) shared axes
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # coord_fixed(
  #   xlim = c(-1.1, 1.1),
  #   ylim = c(-1.1, 1.1)
  # ) 
  # 4) scales & legends
  scale_colour_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
  # scale_colour_viridis_c(option = "inferno")+
  # scale_colour_gradient2(
  #   low      = "blue",
  #   mid      = "grey90",
  #   high     = "red",
  #   midpoint = 0.5,
  #   name     = "cos² ratio\n(Dim1 vs Dim2)"
  # ) +
  scale_size_continuous(
    range = c(1, 6),
    name  = "Total cos² (Dim1+2)"
  ) +
  ggside::geom_xsidedensity(
    aes(y = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  )+ 
    ggside::geom_ysidedensity(
    aes(x = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE)+
  # )+ 
  labs(
    x     = "MFA PC1",
    y     = "MFA PC2",
    title = "Shared axes: size = quality of rep."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", size = 0.2)
  )+
  guides(size = FALSE)



plts$mfa_wide+
  p$graphstyle_int
  
    
```

plot ind

```{r}


dta_emo_wide_mfa<- dta_emo_wide_mfa%>%
  left_join(dta_emo_agg_demogs)

plts$mfa_wide_ind <-


ggplot(dta_emo_wide_mfa, aes(x = pc1_mfa, y = pc3_mfa, colour = social_nonsocial,
                             shape = social_nonsocial)) +
  # 1) Draw a 95% ellipse around each group’s points
  stat_ellipse(
    aes(fill = social_nonsocial),
    type   = "norm",
    level  = 0.95,
    geom   = "polygon",
    alpha  = 0.1,
    colour = NA
  ) +
  # 2) Plot the points themselves
  geom_point(
    alpha = 0.7,
    size  = 2
  ) +
  # 3) Zero lines for reference
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # 4) Facet so that “social” and “non-social” appear in separate panels
  # facet_wrap(~ social_nonsocial) +
  # 5) Shared colour/fill scales (choose a palette you like)
  scale_colour_brewer(palette = "Set1", name = "Group") +
  scale_fill_brewer(palette = "Set1", guide = "none") +
  # 6) Labels and theme tweaks
  labs(
    x     = "PC1 (MFA)",
    y     = "PC2 (MFA)",
    title = "MFA: Individuals on PC1 vs PC2, by Social vs Non-Social"
  ) +
  theme_minimal() +
  theme(
    legend.position   = "top",
    legend.title = element_blank(),
    panel.grid.minor  = element_blank(),
    panel.grid.major  = element_line(colour = "grey90", size = 0.2),
    strip.background  = element_rect(fill = "grey95", colour = NA),
    strip.text        = element_text(face = "bold")
  )+
   # ggside::geom_ysidedensity(aes(y =pc2_mfa, fill = social_nonsocial, alpha = .0001),orientation = "y")+
  
    ggside::geom_ysidedensity(
    aes(x = after_stat(density),fill = social_nonsocial),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  ) +
  
  ggside::geom_xsidedensity(
    aes(y = after_stat(density),fill = social_nonsocial),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  ) +
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")



plts$mfa_wide_ind

dta_emo_wide_mfa

dta_emo_wide_mfa%>%
  ggplot(aes(social_nonsocial, pc1_mfa ))+
  geom_point(alpha = .1)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means(method = "t.test")

dta_emo_wide_mfa%>%
  ggplot(aes(social_nonsocial, pc2_mfa ))+
  geom_point(alpha = .1)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means(method = "t.test")


dta_emo_wide_mfa$ind_cos2_mfa1<-mod_res[["mfa_face_wide"]][["ind"]][["cos2"]][,1]

dta_emo_wide_mfa$ind_contrb_mfa1<-mod_res[["mfa_face_wide"]][["ind"]][["contrib"]][,1]


dta_emo_wide_mfa%>%
  ggplot(aes(social_nonsocial, log1p(ind_contrb_mfa1+.1 )))+
  geom_point(alpha = .1)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means(method = "t.test")

```


permutation


```{r}
#----------------------------------------------------------
# R Script: Permutation Test for Difference in # of Dimensions
#             Needed to Explain ≥50% Inertia (Variance)
#             between Social and Non‐Social MFAs
#----------------------------------------------------------

# 0. PREAMBLE: Install & load necessary packages
#    (Uncomment the install.packages lines if needed.)
# install.packages("FactoMineR")
# install.packages("dplyr")
# install.packages("pbapply")   # for a progress bar (optional but helpful)
library(FactoMineR)
library(dplyr)
library(pbapply)

# 1. ASSUMPTIONS ABOUT YOUR DATA FRAME `dta_emo_wide_mfa`
#    - Column 1: participant (not used directly in MFA)
#    - Column 2: social_nonsocial  (factor with exactly two levels: "social" and "nonsocial")
#    - Columns  3:1682 (inclusive) are measurement columns, ordered as:
#        * subj_aff block:   cols  3 :   422   (count = 420)
#        * phys_hr block:    cols 423 :   482   (count =  60)
#        * phys_scr block:   cols 483 :   542   (count =  60)
#        * gaze block:       cols 543 :   662   (count = 120)
#        * face block:       cols 663 :  1682   (count =1020)
#    Adjust these indices if your column counts differ.

meas_cols <- 3:1682

# 2. FUNCTION TO RUN MFA AND RETURN THE MINIMAL NUMBER OF DIMENSIONS
#    REQUIRED TO EXPLAIN ≥50% OF TOTAL INERTIA
run_mfa_count_to_50 <- function(meas_data) {
  # meas_data: data frame or matrix with exactly measurement columns 3:1682
  # Returns the smallest integer k such that the first k dimensions'
  # cumulative "% of variance" ≥ 50.0
  
  mfa_res <- MFA(
    meas_data,
    group      = c(420, 60, 60, 120, 1020),
    type       = c("s", "s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "gaze", "face"),
    graph      = FALSE
  )
  
  # Extract the "% of variance" column from the eigen table
  pct_var <- mfa_res$eig[, "percentage of variance"]
  cum_pct  <- cumsum(pct_var)
  
  # Find the smallest k where cumulative percentage ≥ 50
  k_needed <- which(cum_pct >= 50)[1]
  return(k_needed)
}

# 3. PREPARE OBSERVED COUNTS FOR SOCIAL VS NON-SOCIAL
# ----------------------------------------------------------------------------
# Subset the main data frame into social vs non‐social:
# dta_emo_wide_mfa_soc    <- dta_emo_wide_mfa %>% filter(social_nonsocial == "social")
# dta_emo_wide_mfa_nonsoc <- dta_emo_wide_mfa %>% filter(social_nonsocial == "nonsocial")

# Extract only the measurement columns (3:1682) for each subset
mst_social    <- dta_emo_wide_mfa_soc   [ , meas_cols ]
mst_nonsocial <- dta_emo_wide_mfa_nonsoc[ , meas_cols ]

# Compute how many dimensions are needed to reach ≥50% for each subset
dims_social_obs   <- run_mfa_count_to_50(mst_social)
dims_nonsocial_obs<- run_mfa_count_to_50(mst_nonsocial)

# Observed difference
D_obs <- dims_social_obs - dims_nonsocial_obs

cat("Observed #dims to reach ≥50% inertia:\n",
    "  Social:    ", dims_social_obs, "\n",
    "  Non-social:", dims_nonsocial_obs, "\n",
    "Observed difference (Social – Non-social) = ", D_obs, "\n\n")

# 4. PERMUTATION TEST
# ----------------------------------------------------------------------------
set.seed(2025)
B <- 1000  # number of permutations

# Vector to store differences under the null
null_diffs <- integer(B)

# Original “social_nonsocial” labels (length = total rows)
orig_labels <- dta_emo_wide_mfa$social_nonsocial

# Measurement‐only matrix for convenience (all rows × 1680 cols)
all_meas_mat <- dta_emo_wide_mfa[ , meas_cols ]

# Permutation loop (with progress bar)
null_diffs <- pbapply::pblapply(seq_len(B), function(b) {
  # 1) Permute the social/non‐social labels
  perm_labels <- sample(orig_labels)
  
  # 2) Split the measurement matrix according to permuted labels
  is_soc_perm   <- perm_labels == "social"
  is_nons_perm  <- perm_labels == "nonsocial"
  
  # When permuted labels happen to create an empty group, skip this replicate
  if (sum(is_soc_perm) == 0 || sum(is_nons_perm) == 0) {
    return(NA_integer_)
  }
  
  mat_soc_perm  <- all_meas_mat[is_soc_perm,   ]
  mat_nons_perm <- all_meas_mat[is_nons_perm, ]
  
  # 3) Run MFA on each permuted subset and count dims needed for ≥50%
  dims_soc_b   <- run_mfa_count_to_50(mat_soc_perm)
  dims_nons_b  <- run_mfa_count_to_50(mat_nons_perm)
  
  # 4) Return the difference (Social – Non‐social) for this permutation
  return(dims_soc_b - dims_nons_b)
}, cl = 1)  # cl = 1 means sequential; remove cl argument for defaults

# Convert to integer vector, omitting any NA replicates
null_diffs <- unlist(null_diffs)
null_diffs <- null_diffs[!is.na(null_diffs)]

# 5. CALCULATE EMPIRICAL P‐VALUE
#    Two‐sided test: proportion of |D_b| ≥ |D_obs|
p_emp <- (sum(abs(null_diffs) >= abs(D_obs)) + 1) / (length(null_diffs) + 1)

cat("Permutation test results:\n",
    "  Number of (valid) permutations  = ", length(null_diffs), "\n",
    "  Observed difference             = ", D_obs, "\n",
    "  Proportion |D_b| ≥ |D_obs|      = ", signif(p_emp, 3), "\n\n")

# Permutation test results:
#    Number of (valid) permutations  =  1000 
#    Observed difference             =  4 
#    Proportion |D_b| ≥ |D_obs|      =  0.000999 

# 6. INTERPRETATION MESSAGE
if (p_emp < 0.05) {
  cat("Conclusion: The observed difference in the number of dimensions\n",
      "needed to explain ≥50% inertia between social and non‐social is\n",
      "statistically significant (p =", signif(p_emp, 3), ").\n",
      "This suggests that, to reach half of the total variance,\n",
      "one condition genuinely requires more factors (lower coherence)\n",
      "than the other.\n")
} else {
  cat("Conclusion: The observed difference in the number of dimensions\n",
      "needed to explain ≥50% inertia between social and non‐social is NOT\n",
      "statistically significant (p =", signif(p_emp, 3), ").\n",
      "There is insufficient evidence to claim that one group truly needs\n",
      "more dimensions to explain the same amount of variance.\n")
}


as.data.frame(null_diffs)%>%
  ggplot(aes(null_diffs))+
  geom_density(fill = "gray30")+
  # geom_histogram(bins = 300)+
  geom_vline(xintercept = D_obs)+
  xlim(-3,5)



```

the eigen value tets needs to. beredone the abstract s4ssn might have an issue

```{r}
# save.image("s4sndata_select.RData", c(dta_emo,dta_emo_4mfa,dta_emo_face_wide_emo, mod_res,emo_diffs, order_levels, order_levels_hr, order_levels_scr,
#                                       mod_list_emo_slid,get_beta_se,pool_effect, term_social, omnibus,
#                                       dta_emo_face_scale ))

save(
  dta_emo,
  dta_emo_4mfa,
  dta_emo_face_wide_emo,
  mod_res,
  emo_diffs,
  order_levels,
  order_levels_hr,
  order_levels_scr,
  mod_list_emo_slid,
  get_beta_se,
  pool_effect,
  term_social,
  omnibus,
  dta_emo_face_scale,
  file = "s4sndata_select.RData"
)
# use this and s4sn submission 2025

```



