---
title: "social_emophys_facenmfs"
author: "helio"
date: "2026-01-13"
output: html_document
---

```{r}
rm(`face_time_z_scored 1`)

dta_face_z_scored <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/s4sn2025plots/face_time_z_scored 1.rds")

save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/social_emophys_facenmfs.RData")



```


```{r}
# check the validity. of the data
require(tidyverse)
colnames(dta_face_z_scored)
options(scipen = 999)
dta_face_z_scored
dta_face_z_scored<- dta_face_z_scored%>%
  group_by(participant)%>%
  mutate(confidence_ppt = mean(confidence, na.rm = T))%>%
  group_by(filename)%>%
  mutate(confidence_p_trial = mean(confidence, na.rm = T))%>%
  ungroup()
  
  
  # ggplot(aes(confidence))+
  # geom_histogram()


dta_face_z_scored_1<- dta_face_z_scored%>%
  subset(confidence_ppt>0)

length(unique(dta_face_z_scored$participant))
dta_face_z_scored_1%>%
  group_by(participant)%>%
  summarise_if(is.numeric,mean, n.rm = T)%>%
    ggplot(aes(confidence))+
  geom_histogram()

dta_face_z_scored

dta_face_z_scored_1%>%
  mutate


# 
au_cols <- c("au01_r_smt","au02_r_smt","au04_r_smt","au05_r_smt",
             "au06_r_smt","au07_r_smt","au09_r_smt","au10_r_smt",
             "au12_r_smt","au14_r_smt","au15_r_smt","au17_r_smt",
             "au20_r_smt","au23_r_smt","au25_r_smt","au26_r_smt",
             "au45_r_smt")

# Extract the matrix (still z-scored at this point)
temp <- as.matrix(dta_face_z_scored_1[ , au_cols])

# Small epsilon to avoid exact zeros if you want (optional)
eps <- 1e-6

# Per-AU shift: subtract min of each column
X_shifted <- apply(temp, 2, function(col) {
  col - min(col) 
})



# Put shifted data back in the original data frame if needed
dta_face_z_shift_1 <- dta_face_z_scored_1
dta_face_z_shift_1[ , au_cols] <- X_shifted
  
range(dta_face_z_shift_1$au09_r_smt)
range(dta_face_z_shift_1$au01_r_smt)

range(dta_face_z_scored_1$au09_r_smt)
range(dta_face_z_scored_1$au01_r_smt)


dta_face_z_shift_1%>%
  group_by(participant)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(au09_r_smt))+
  geom_histogram()


dta_face_z_scored_1%>%
   group_by(participant)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(au09_r_smt))+
  geom_histogram()
```

make it positive to satisfy the non-negativity constraint
```{r}

dta_face_z_shift_1

# to improve computation lets resample
table(dta_face_z_shift_1$participant)

dta_face_z_shift_1%>%
  group_by(participant,stim_iaps)%>%
  mutate(n_count = n())%>%
    group_by(participant)%>%
  summarise_at(c("n_count"), mean)

dta_face_z_shift_1%>%
  group_by(participant,stim_iaps)%>%
  mutate(n_count = n())%>%
  summarise_at(c("frame"), max)%>%
  ggplot(aes(frame))+
  geom_histogram()

```


```{r}
dta_face_z_shift_1
saveRDS(dta_face_z_shift_1, "dta_face_z_shift_1.Rds")
```
# 108 below have 77 frames in average for some reason same as 205

```{r}
dta_face_z_shift_2<- dta_face_z_shift_1%>%
  subset(as.numeric(participant)> 108)%>%
    subset(participant!= "205")

sort(unique(as.numeric(dta_face_z_shift_2$participant)))

max(dta_face_z_shift_2$frame)
# now downsampel for computational efficiency
dta_face_z_shift_2


rm(N)

K <- 74
# indices <- floor(seq(1, N, length.out = K))

dta_face_z_shift_2_subs <-

dta_face_z_shift_2 %>%
  group_by(participant,filename)%>%
  arrange(frame,.by_group = TRUE) %>%
  group_modify(~ {
    N <- nrow(.x)                         # .x is the data for this group only
    idx <- floor(seq(1, N, length.out = K))
    .x[idx, ]                             # return the selected rows
  }) %>%
  ungroup()
unique(dta_face_z_shift_2$stim_iaps)

dta_face_z_shift_2$participant

dta_face_z_shift_2%>%
  filter(participant == "222",
         stim_iaps == "4617.jpg")%>%
  ggplot(aes(frame, au09_r_smt))+
  geom_line()


dta_face_z_shift_2_subs%>%
  filter(participant == "222",
         stim_iaps == "4617.jpg")%>%
  ggplot(aes(frame, au09_r_smt))+
  geom_line()

colnames(dta_face_z_shift_2_subs)


table(dta_face_z_shift_2_subs$participant, dta_face_z_shift_2_subs$stim_iaps)

unique(dta_face_z_shift_2_subs$frame)
```
# apply NMF
install.packages("NMF")
require(NMF)


What do we want to do

1. Some preprocessing fit an NMF
2. derive temporal features 
- do some visualisation on specfic features

3. use MFA to group fatues by components, and take the first 3 components
4. use PCA to run each compoennt separatelly and take the first component


```{r}
# colnames(df_OF_output_AUsW_unblind_posed_binned)
require(NMF)
require(tidyverse)
# install.packages("NMF")
# install.packages("Biobase")
# single run and single numeric seed for reproducibility

# run overnight
res_find_k <- nmf(dta_face_z_shift_2_subs[,7:23], 2:6, 
                      seed=123456,
                      nrun = 100,
                       .options = 'v')


NMF::plot(res_find_k)
  geom_vline(xintercept = 3)
  NMF::consensusmap(res_find_k)
  

```


```{r}
unique(dta_face_z_shift_2_subs$participant)
# actually fit()
res_k3 <- NMF::nmf(dta_face_z_shift_2_subs[,7:23], r = 3, 
                  nrun = 50, 
                  seed=123456,
                 .options = list( 'v')) 

# some checks

# FactoMineR::PCA(dta_face_z_shift_2_subs[,7:23], k = 3,
#                                         scale.unit = TRUE,
#                   graph = TRUE) 


# store components

coefmap(res_k3)


```


```{r}
basismap(res_k3)

dta_face_z_shift_2_subs$nmf_comp1<- as.data.frame(res_k3@fit@W)[,1]
dta_face_z_shift_2_subs$nmf_comp2<- as.data.frame(res_k3@fit@W)[,2]
dta_face_z_shift_2_subs$nmf_comp3<- as.data.frame(res_k3@fit@W)[,3]

# some vis
# k 1 mouth/smiles
# k2 2. eyes
# k3 = mix,mosly eyes

unique(dta_face_z_shift_2_subs$timestamp)
dta_face_z_shift_2_subs$frame


dta_face_z_shift_2_subs<- dta_face_z_shift_2_subs%>%
  arrange(filename, frame)%>%
  group_by(filename)%>%
  mutate(bin_frame = 1:n())

unique(dta_face_z_shift_2_subs$bin_frame)
```


```{r}
dta_face_z_shift_2_subs%>%
  group_by(participant, frame,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ggplot(aes(bin_frame, nmf_comp1, colour = subj_emo_lab_no_amb))+
  geom_smooth()+
  facet_grid(~social_nonsocial)

dta_face_z_shift_2_subs%>%
  group_by(participant, frame,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ggplot(aes(bin_frame, nmf_comp2, colour = subj_emo_lab_no_amb))+
  geom_smooth()+
  facet_grid(~social_nonsocial)


dta_face_z_shift_2_subs%>%
  group_by(participant, frame,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ggplot(aes(bin_frame, nmf_comp3, colour = subj_emo_lab_no_amb))+
  geom_smooth()+
  facet_grid(~social_nonsocial)
  
```



```{r}

dta_face_z_shift_2_subs%>%
  group_by(participant,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, nmf_comp1, colour = subj_emo_lab_no_amb))+
  geom_jitter(width = .1, alpha = .1)+
 stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)

dta_face_z_shift_2_subs%>%
  group_by(participant,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, log1p(nmf_comp2), colour = subj_emo_lab_no_amb))+
  geom_jitter(width = .1, alpha = .1)+
   stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)


dta_face_z_shift_2_subs%>%
  group_by(participant,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, nmf_comp3, colour = subj_emo_lab_no_amb))+
    geom_jitter(width = .1, alpha = .1)+
   stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)
unique(dta_face_z_shift_2_subs$participant)
# 103, 104, 105, 106, 107, 108, 201, 202, 203, 204, 205
```


```{r}
mod_res<- list()

mod_res
require(lmerTest)
dta_face_z_shift_2_subs_agg <- dta_face_z_shift_2_subs%>%
  group_by(participant,stim_iaps, subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)


dta_face_z_shift_2_subs_agg <- dta_face_z_shift_2_subs%>%
  group_by(participant,stim_iaps, subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)

dta_face_z_shift_2_subs_agg

mod_res$nmf_comp1 <- lmer(log1p(nmf_comp1+.1) ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_face_z_shift_2_subs_agg)


mod_res$nmf_comp2 <- lmer(log1p(nmf_comp2+.1) ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_face_z_shift_2_subs_agg)




mod_res$nmf_comp3 <- lmer(log1p(nmf_comp3+.1)  ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_face_z_shift_2_subs_agg)




mod_res$nmf_comp2.2 <- lmer(nmf_comp2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb +
                     (1+|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), # social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_face_z_shift_2_subs_agg)

# singular
# relgrad <- with(mod_res$nmf_comp2.2@optinfo$derivs,solve(Hessian,gradient))
# max(abs(relgrad))

# check is more maxima moel is needed
anova(mod_res$nmf_comp2.2,mod_res$nmf_comp2)

anova(mod_res$nmf_comp1)
anova(mod_res$nmf_comp2)
anova(mod_res$nmf_comp3)

emmeans::emmeans(mod_res$nmf_comp2, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$nmf_comp2, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "none")

```


```{r}

dta_face_z_shift_2_subs_agg <- dta_face_z_shift_2_subs%>%
  group_by(participant,stim_iaps, subj_emo_lab_no_amb,social_nonsocial)%>%
  mutate(nmf_comp1_max= max(nmf_comp1),
         nmf_comp2_max= max(nmf_comp2),
         nmf_comp3_max= max(nmf_comp3)
         )%>%
 summarise_if(is.numeric, max,na.rm = T)

mod_res$nmf_comp1_max <- lmer(log1p(nmf_comp1_max+.1) ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_face_z_shift_2_subs_agg)


mod_res$nmf_comp2_max <- lmer(log1p(nmf_comp2_max+.1) ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_face_z_shift_2_subs_agg)




mod_res$nmf_comp3_max <- lmer(log1p(nmf_comp3_max+.1)  ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_face_z_shift_2_subs_agg)

anova(mod_res$nmf_comp1_max)
anova(mod_res$nmf_comp2_max)
anova(mod_res$nmf_comp3_max)




emmeans::emmeans(mod_res$nmf_comp2_max, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$nmf_comp2_max, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "none")

```

aggregate features just slight differences 

2. derive temporal features 
```{r}
# cmfts
# pivot longer
colnames(dta_face_z_shift_2_subs)

dta_face_z_shift_2_subs_long <- dta_face_z_shift_2_subs %>%
  pivot_longer(
    cols = nmf_comp1:nmf_comp3,      
    names_to  = "nmf_component",     
    values_to = "nmf_value"          
  )%>%
  select(participant,
         timestamp,
         filename,
         stim_iaps,
         frame,
         bin_frame,
         social_nonsocial,
         subj_emo_lab_no_amb,
         nmf_component,
         nmf_value)

dta_face_z_shift_2_subs_long
```

# create unique timeseries IDs


```{r}


# CREATE a t for frame to avoid number only name columns
  dta_face_z_shift_2_subs_long

dta_face_z_shift_2_subs_long<-  dta_face_z_shift_2_subs_long%>%
  arrange(filename,nmf_component,frame)%>%
  group_by(filename,nmf_component) %>%
  mutate(bin_frame2 = paste0("t_", paste0(bin_frame)))%>%
  ungroup()
 
unique(dta_face_z_shift_2_subs_long$bin_frame)

dta_face_z_shift_2_subs_wid<- dta_face_z_shift_2_subs_long%>%
pivot_wider(
    id_cols    = c(participant,
                  filename,
                  stim_iaps,
                  nmf_component,
                  social_nonsocial,
                  subj_emo_lab_no_amb),
    names_from  = bin_frame2,
    values_from = nmf_value
  )


colnames(dta_face_z_shift_2_subs_wid)

dta_face_z_shift_2_subs_wid
```
  
  
calculate multivariate timeseries features

```{r}
colnames(dta_face_z_shift_2_subs_wid)
require(CMFMTS)

?CMFMTS::cmfmts
dta_face_z_shift_2_subs_wid$filename[300:310]
dta_cmfsts$filename[300:310]

dta_face_z_shift_2_subs_wid$mean_feat <- rowMeans(dta_face_z_shift_2_subs_wid[,7: 80], na.rm = TRUE)
dta_face_z_shift_2_subs_wid$max_feat <- apply(dta_face_z_shift_2_subs_wid[, 7:80], 1, max, na.rm = TRUE)

colnames(dta_face_z_shift_2_subs_wid)
dta_cmfsts<- CMFMTS::cmfmts(dataset = dta_face_z_shift_2_subs_wid[,6:79],
                               scale = F,
               na = T 
               # n_cores = 6
               )

dta_face_z_shift_2_subs_wid


dta_cmfsts<- bind_cols(dta_face_z_shift_2_subs_wid[,1:6], dta_cmfsts[,6:46])

dta_cmfsts$

# drop uninformative timeseries
colnames(dta_cmfsts)

sd_values_pos <- apply(dta_cmfsts[, 7:47], 
                   MARGIN = 2, sd, na.rm = T) # 2 chooses columns and 2 chooses rows


# Identify the columns with a standard deviation of zero
zero_sd_cols_pos <- names(which(sd_values_pos == 0))

# [1] "length"          "nperiods"        "seasonal_period" s

# Drop the columns with a standard deviation of zero
dta_cmfsts2 <- dta_cmfsts%>%select(-zero_sd_cols_pos)

dta_cmfsts2$mean_feat<- dta_face_z_shift_2_subs_wid$mean_feat 
dta_cmfsts2$max_feat<- dta_face_z_shift_2_subs_wid$max_feat 
dta_cmfsts2

all_na <- sapply(dta_cmfsts2[, 7:44], function(x) all(is.na(x)))
all_na_names<- names(all_na)[all_na]
# "max_kl_shift"  "time_kl_shift"
dta_cmfsts2 <- dta_cmfsts2%>%select(-all_na_names)
all_na_names


colnames(dta_cmfsts2)

corr_mat <- dta_cmfsts2[,7:44] %>%
  cor(use = "pairwise.complete.obs", method = "pearson")

dta_cmfsts2$nonlinearity
# library(ggplot2)
# library(reshape2)

corr_df <- melt(corr_mat, varnames = c("var1", "var2"), value.name = "cor")

ggplot(corr_df, aes(x = var1, y = var2, fill = cor)) +
  geom_tile() +
  scale_fill_gradient2(
    limits = c(-1, 1),
    midpoint = 0,
    name = "r"
  ) +
  coord_fixed() +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1, size = 7),
    axis.text.y = element_text(size = 7),
    axis.title = element_blank(),
    panel.grid = element_blank()
  )


# therenis evidence that mean and max of component is embeded somehow in the other features, as many if the otehr features correlate to some degree and some stringly with mean and max feature so, a model with mean or max features is probably redundant
```


just soem visualisations
```{r}
dta_cmfsts2
dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, diff1_acf1, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)

dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, diff1_acf10, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)

dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, entropy, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)

# spike is floored
dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,log1p(time_level_shift+.1), colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)


social_nonsocial
  

```



```{r}
dta_cmfsts2


colnames(dta_cmfsts2)




# 35 featureleft_join(
dta_cmfsts3_wid<- dta_cmfsts2 %>%  
  arrange(nmf_component) %>%
  pivot_wider(
    id_cols = c(participant,
                filename,
                stim_iaps,
                social_nonsocial,
                subj_emo_lab_no_amb),
    names_from  = nmf_component,              # values in this col become suffixes
    values_from = c(lempel_ziv:max_feat),  # c
    names_glue = "{nmf_component}_{.value}"   # e.g. lempel_ziv_comp1
  )

colnames(dta_cmfsts3_wid)
id_cols <- c("participant",
             "filename",
             "stim_iaps",
             "social_nonsocial",
             "subj_emo_lab_no_amb")

# get component levels in the order you want
comp_levels <- sort(unique(dta_cmfsts2$nmf_component))
# e.g. c("nmf_comp1", "nmf_comp2", "nmf_comp3")

# build column order: comp1_* then comp2_* then comp3_*, etc.
feature_cols_ordered <- unlist(
  lapply(comp_levels, function(comp) {
    prefix <- paste0(comp, "_")
    grep(paste0("^", prefix), names(dta_cmfsts3_wid), value = TRUE)
  })
)

# reorder columns
dta_cmfsts3_wid <- dta_cmfsts3_wid[, c(id_cols, feature_cols_ordered)]

colnames(dta_cmfsts3_wid)
```
first approach MFA with 
group by AUS
```{r}

# 35 features left
colnames(dta_cmfsts3_wid)
# ?FactoMineR::MFA()
require(FactoMineR)
35+35+35
table(is.na(dta_cmfsts3_wid[, 6:113]))

dta_cmfsts3_wid_complete<- as.data.frame(dta_cmfsts3_wid)
# table(is.na(dta_cmfsts3_wid$nmf_comp3_max_feat))

# dta_cmfsts3_wid_complete<- as_tibble(dta_cmfsts3_wid_complete)


dta_cmfsts3_wid_complete<- dta_cmfsts3_wid_complete %>%
  mutate(across(6:119, ~ if(is.numeric(.)) replace(., !is.finite(.), NA) else .))


dta_cmfsts3_wid_complete2 <- missMDA::imputeMFA(dta_cmfsts3_wid_complete[,6:119],
                                               ncp=2,
                                                group=c(38, 38, 38),
                          type=c("s","s","s"))

# withouth mean and max features
mod_res$mfa_cmfts_face <- MFA(dta_cmfsts3_wid_complete2$completeObs,
                              # tab.comp = dta_cmfsts3_wid_complete2$completeObs,
                          group=c(36, 36, 36),
                          type=c("s","s","s"),
                          ncp = 3,
                          name.group= c("comp1","comp2", "comp3"),
                          # num.group.sup=c(6),
                          graph=TRUE)


```
```{r}
require(factoextra)

fviz_contrib(mod_res$mfa_cmfts_face, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_cmfts_face, "quanti.var", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_cmfts_face, "quanti.var", axes = 3,top = 10)


fviz_contrib(mod_res$mfa_cmfts_face, "group", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_cmfts_face, "group", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_cmfts_face, "group", axes = 3,top = 10)
# factoextra::fviz_mfa_axes(mod_mfa$mfa_wide)
```


```{r}
dta_cmfsts3_wid$mfa1<- mod_res$mfa_cmfts_face$ind$coord[,1]
dta_cmfsts3_wid$mfa2<- mod_res$mfa_cmfts_face$ind$coord[,2]
dta_cmfsts3_wid$mfa3<- mod_res$mfa_cmfts_face$ind$coord[,3]

```

```{r}
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,mfa1, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  # facet_grid(~social_nonsocial)

dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,mfa2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,mfa3, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
```






```{r}



mod_res$mfa1 <- lmer(mfa1 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)


mod_res$mfa2 <- lmer(mfa2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)




mod_res$mfa3 <- lmer(mfa3  ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)

anova(mod_res$mfa1)
anova(mod_res$mfa2)
anova(mod_res$mfa3)


emmeans::emmeans(mod_res$mfa1, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$mfa2, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")


emmeans::emmeans(mod_res$mfa3, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "none")

emmeans::emmeans(mod_res$mfa2, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$mfa3, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")

```





```{r}

comp1_idx <- 1:36
comp2_idx <- 37:72
comp3_idx <- 73:108

# PCA for each component block (on imputed data)
dta_cmfsts3_wid_complete2$completeObs
mod_res$pca_comp1 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp1_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp2 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp2_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp3 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp3_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)


dta_cmfsts3_wid$pc_comp1<- mod_res$pca_comp1$ind$coord[,1]
dta_cmfsts3_wid$pc_comp2<- mod_res$pca_comp2$ind$coord[,1]
dta_cmfsts3_wid$pc_comp3<- mod_res$pca_comp3$ind$coord[,1]

```


```{r}
fviz_contrib(mod_res$pca_comp1, "var", axes = 1, top = 5)
fviz_contrib(mod_res$pca_comp2, "var", axes = 1,top = 5)# 
fviz_contrib(mod_res$pca_comp3, "var", axes = 1,top = 5)
```

```{r}
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp1, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)

dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp3, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")

```

```{r}

mod_res$pc_comp1 <- lmer(pc_comp1 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)


mod_res$pc_comp2 <- lmer(pc_comp2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)




mod_res$pc_comp3 <- lmer(pc_comp3  ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)

anova(mod_res$pc_comp1)
anova(mod_res$pc_comp2)
anova(mod_res$pc_comp3)

# singular
# relgrad <- with(mod_res$nmf_comp2.2@optinfo$derivs,solve(Hessian,gradient))
# max(abs(relgrad))

# check is more maxima moel is needed
anova(mod_res$nmf_comp2.2,mod_res$nmf_comp2)

emmeans::emmeans(mod_res$pc_comp1, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$pc_comp2, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")


emmeans::emmeans(mod_res$pc_comp3, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "none")

emmeans::emmeans(mod_res$pc_comp2, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$pc_comp3, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")

```

Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value   Pr(>F)   
social_nonsocial                       0.067  0.0666     1   85.6  0.0093 0.923499   
subj_emo_lab_no_amb                  146.598 29.3195     5  390.8  4.0820 0.001266 **
social_nonsocial:subj_emo_lab_no_amb  40.919  8.1838     5 5000.8  1.1394 0.336999   
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Warning: The working directory was changed to /Users/pw22812 inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value    Pr(>F)    
social_nonsocial                       9.852  9.8522     1   85.7  1.7662 0.1873802    
subj_emo_lab_no_amb                   91.065 18.2130     5  601.3  3.2651 0.0064347 ** 
social_nonsocial:subj_emo_lab_no_amb 124.561 24.9123     5 4991.6  4.4661 0.0004617 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial                       2.436  2.4357     1   88.9  0.3270 0.56885  
subj_emo_lab_no_amb                  103.004 20.6009     5  430.3  2.7661 0.01792 *
social_nonsocial:subj_emo_lab_no_amb  44.488  8.8976     5 5032.6  1.1947 0.30899  
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

mfa with mean nd max as additional features
```{r}
colnames(dta_cmfsts3_wid_complete2$completeObs)

mod_res$mfa_cmfts_face_2 <- MFA(dta_cmfsts3_wid_complete2$completeObs,
                              # tab.comp = dta_cmfsts3_wid_complete2$completeObs,
                          group=c(38, 38, 38),
                          type=c("s","s","s"),
                          ncp = 3,
                          name.group= c("comp1","comp2", "comp3"),
                          # num.group.sup=c(6),
                          graph=TRUE)


```

```{r}
require(factoextra)

fviz_contrib(mod_res$mfa_cmfts_face_2, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_cmfts_face_2, "quanti.var", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_cmfts_face_2, "quanti.var", axes = 3,top = 10)


fviz_contrib(mod_res$mfa_cmfts_face_2, "group", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_cmfts_face_2, "group", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_cmfts_face_2, "group", axes = 3,top = 10)
```
interestingy mean and max features arent sper prominent
```{r}

dta_cmfsts3_wid$mfa1.2<- mod_res$mfa_cmfts_face_2$ind$coord[,1]
dta_cmfsts3_wid$mfa2.2<- mod_res$mfa_cmfts_face_2$ind$coord[,2]
dta_cmfsts3_wid$mfa3.2<- mod_res$mfa_cmfts_face_2$ind$coord[,3]

```

```{r}
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,mfa1.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)

dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,mfa2.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,mfa3.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
```

largely similar to models withoth max or mean




```{r}

mod_res$mfa1.2 <- lmer(mfa1.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)


mod_res$mfa2.2 <- lmer(mfa2.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)




mod_res$mfa3.2 <- lmer(mfa3.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)


anova(mod_res$mfa1)
anova(mod_res$mfa2)
anova(mod_res$mfa3)
anova(mod_res$mfa1.2)
anova(mod_res$mfa2.2)
anova(mod_res$mfa3.2)

```
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value    Pr(>F)    
social_nonsocial                      0.0010  0.0010     1   86.2  0.0012 0.9724260    
subj_emo_lab_no_amb                  18.8187  3.7637     5  493.0  4.6987 0.0003345 ***
social_nonsocial:subj_emo_lab_no_amb  1.9676  0.3935     5 5000.0  0.4913 0.7830340    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Warning: The working directory was changed to /Users/pw22812 inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value   Pr(>F)   
social_nonsocial                      0.8667 0.86671     1   85.8  1.6260 0.205701   
subj_emo_lab_no_amb                  10.9154 2.18309     5  677.1  4.0956 0.001137 **
social_nonsocial:subj_emo_lab_no_amb 10.5539 2.11078     5 4990.8  3.9600 0.001382 **
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                     Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial                     0.0565 0.05654     1   86.5  0.1072 0.74410  
subj_emo_lab_no_amb                  3.7689 0.75378     5 5033.8  1.4298 0.20999  
social_nonsocial:subj_emo_lab_no_amb 5.4531 1.09061     5 5033.8  2.0688 0.06625 .
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value    Pr(>F)    
social_nonsocial                      0.0006  0.0006     1   86.2  0.0007 0.9786603    
subj_emo_lab_no_amb                  19.5350  3.9070     5  496.3  4.8271 0.0002548 ***
social_nonsocial:subj_emo_lab_no_amb  1.8299  0.3660     5 4999.9  0.4522 0.8119691    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value   Pr(>F)    
social_nonsocial                      1.0036  1.0036     1   85.7  2.0147 0.159407    
subj_emo_lab_no_amb                  10.4740  2.0948     5  692.7  4.2052 0.000900 ***
social_nonsocial:subj_emo_lab_no_amb  9.5727  1.9145     5 4989.4  3.8433 0.001775 ** 
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                     Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial                     0.2583 0.25830     1   86.0  0.5567 0.45762  
subj_emo_lab_no_amb                  2.4916 0.49832     5  368.0  1.0740 0.37432  
social_nonsocial:subj_emo_lab_no_amb 4.8408 0.96817     5 5007.9  2.0867 0.06403 .
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

results are essentially thes same?


```{r}
emmeans::emmeans(mod_res$mfa1.2, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$mfa2.2, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")


emmeans::emmeans(mod_res$mfa2.2, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")


```

$emmeans
 subj_emo_lab_no_amb  emmean     SE  df asymp.LCL asymp.UCL
 anger               -0.0421 0.0917 Inf   -0.2217    0.1376
 disgust              0.1265 0.0802 Inf   -0.0307    0.2837
 fear                -0.0120 0.0843 Inf   -0.1772    0.1532
 happy               -0.0392 0.0795 Inf   -0.1950    0.1166
 neutral             -0.0642 0.0828 Inf   -0.2265    0.0981
 sad                 -0.0353 0.0826 Inf   -0.1973    0.1267

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate     SE  df z.ratio p.value
 anger - disgust   -0.16857 0.0606 Inf  -2.783  0.0603
 anger - fear      -0.03005 0.0652 Inf  -0.461  0.9974
 anger - happy     -0.00287 0.0609 Inf  -0.047  1.0000
 anger - neutral    0.02213 0.0650 Inf   0.340  0.9994
 anger - sad       -0.00677 0.0628 Inf  -0.108  1.0000
 disgust - fear     0.13853 0.0494 Inf   2.804  0.0568
 disgust - happy    0.16570 0.0416 Inf   3.980  0.0010
 disgust - neutral  0.19070 0.0475 Inf   4.011  0.0009
 disgust - sad      0.16180 0.0465 Inf   3.483  0.0066
 fear - happy       0.02718 0.0485 Inf   0.560  0.9935
 fear - neutral     0.05218 0.0534 Inf   0.977  0.9253
 fear - sad         0.02327 0.0529 Inf   0.440  0.9979
 happy - neutral    0.02500 0.0451 Inf   0.555  0.9938
 happy - sad       -0.00390 0.0461 Inf  -0.085  1.0000
 neutral - sad     -0.02890 0.0510 Inf  -0.567  0.9931

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
P value adjustment: tukey method for comparing a family of 6 estimates 

Warning: The working directory was changed to /Users/pw22812 inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5100' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5100' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
NOTE: Results may be misleading due to involvement in interactions
$emmeans
 subj_emo_lab_no_amb   emmean     SE  df asymp.LCL asymp.UCL
 anger                0.01769 0.0901 Inf   -0.1589     0.194
 disgust              0.09079 0.0831 Inf   -0.0721     0.254
 fear                 0.02115 0.0855 Inf   -0.1464     0.189
 happy               -0.05276 0.0826 Inf   -0.2147     0.109
 neutral             -0.05588 0.0845 Inf   -0.2214     0.110
 sad                 -0.00274 0.0846 Inf   -0.1685     0.163

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate     SE  df z.ratio p.value
 anger - disgust   -0.07311 0.0486 Inf  -1.504  0.6617
 anger - fear      -0.00346 0.0518 Inf  -0.067  1.0000
 anger - happy      0.07044 0.0494 Inf   1.427  0.7105
 anger - neutral    0.07357 0.0518 Inf   1.420  0.7151
 anger - sad        0.02043 0.0500 Inf   0.409  0.9985
 disgust - fear     0.06964 0.0403 Inf   1.729  0.5126
 disgust - happy    0.14355 0.0350 Inf   4.103  0.0006
 disgust - neutral  0.14668 0.0387 Inf   3.787  0.0021
 disgust - sad      0.09353 0.0381 Inf   2.457  0.1372
 fear - happy       0.07391 0.0396 Inf   1.867  0.4228
 fear - neutral     0.07703 0.0424 Inf   1.815  0.4559
 fear - sad         0.02389 0.0426 Inf   0.561  0.9935
 happy - neutral    0.00313 0.0360 Inf   0.087  1.0000
 happy - sad       -0.05002 0.0381 Inf  -1.312  0.7788
 neutral - sad     -0.05314 0.0411 Inf  -1.293  0.7889

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
P value adjustment: tukey method for comparing a family of 6 estimates 

Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5100' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5100' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
$emmeans
subj_emo_lab_no_amb = anger:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.1714 0.126 Inf   -0.0748    0.4176
 social           -0.1360 0.127 Inf   -0.3851    0.1130

subj_emo_lab_no_amb = disgust:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.1578 0.117 Inf   -0.0715    0.3870
 social            0.0238 0.116 Inf   -0.2032    0.2508

subj_emo_lab_no_amb = fear:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.0578 0.120 Inf   -0.1776    0.2932
 social           -0.0155 0.120 Inf   -0.2500    0.2191

subj_emo_lab_no_amb = happy:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.1032 0.116 Inf   -0.1250    0.3315
 social           -0.2087 0.115 Inf   -0.4346    0.0172

subj_emo_lab_no_amb = neutral:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.0715 0.120 Inf   -0.1640    0.3070
 social           -0.1832 0.117 Inf   -0.4133    0.0468

subj_emo_lab_no_amb = sad:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.1351 0.119 Inf   -0.0987    0.3689
 social           -0.1406 0.118 Inf   -0.3711    0.0899

Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
subj_emo_lab_no_amb = anger:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.3075 0.177 Inf   1.735  0.0827

subj_emo_lab_no_amb = disgust:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.1340 0.163 Inf   0.822  0.4111

subj_emo_lab_no_amb = fear:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.0733 0.168 Inf   0.436  0.6629

subj_emo_lab_no_amb = happy:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.3120 0.162 Inf   1.921  0.0547

subj_emo_lab_no_amb = neutral:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.2547 0.167 Inf   1.525  0.1273

subj_emo_lab_no_amb = sad:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.2757 0.166 Inf   1.662  0.0965

Degrees-of-freedom method: asymptotic 

overall similar, but mean and max nmf analysis seem to pickup clearer differences?

pca version inclding man and max features


```{r}
length(39:76)
colnames(dta_cmfsts3_wid_complete2$completeObs)
comp1_idx <- 1:38
comp2_idx <- 39:76
comp3_idx <- 77:114

# PCA for each component block (on imputed data)
dta_cmfsts3_wid_complete2$completeObs
```

```{r}
mod_res$pca_comp1.2 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp1_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp2.2 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp2_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp3.2 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp3_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)


dta_cmfsts3_wid$pc_comp1.2<- mod_res$pca_comp1.2$ind$coord[,1]
dta_cmfsts3_wid$pc_comp2.2<- mod_res$pca_comp2.2$ind$coord[,1]
dta_cmfsts3_wid$pc_comp3.2<- mod_res$pca_comp3.2$ind$coord[,1]

```


```{r}
fviz_contrib(mod_res$pca_comp1.2, "var", axes = 1, top = 5)
fviz_contrib(mod_res$pca_comp2.2, "var", axes = 1,top = 5)# 
fviz_contrib(mod_res$pca_comp3.2, "var", axes = 1,top = 5)
```

```{r}
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp1.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)

dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp2.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp3.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")

```


lmer modles on pca with mean and max features
```{r}

mod_res$pc_comp1.2.lmer <- lmer(pc_comp1.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)


mod_res$pc_comp2.2.lmer <- lmer(pc_comp2.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)




mod_res$pc_comp3.2.lmer <- lmer(pc_comp3.2  ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)


```

```{r}

anova(mod_res$pc_comp1.2.lmer)
anova(mod_res$pc_comp2.2.lmer)
anova(mod_res$pc_comp3.2.lmer)

```

Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value    Pr(>F)    
social_nonsocial                       0.021  0.0208     1   85.6  0.0029 0.9571273    
subj_emo_lab_no_amb                  152.756 30.5512     5  412.7  4.2800 0.0008318 ***
social_nonsocial:subj_emo_lab_no_amb  43.056  8.6112     5 4999.1  1.2064 0.3033058    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Warning: The working directory was changed to /Users/pw22812 inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value    Pr(>F)    
social_nonsocial                      12.286  12.286     1   85.6  2.2736 0.1352740    
subj_emo_lab_no_amb                   96.286  19.257     5  638.3  3.5637 0.0034693 ** 
social_nonsocial:subj_emo_lab_no_amb 116.717  23.343     5 4989.4  4.3198 0.0006349 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial                       2.054  2.0541     1   88.7  0.2504 0.61806  
subj_emo_lab_no_amb                  107.221 21.4443     5  414.1  2.6136 0.02421 *
social_nonsocial:subj_emo_lab_no_amb  42.105  8.4210     5 5032.5  1.0263 0.40014 

generally similar to before?

```{r}

emmeans::emmeans(mod_res$pc_comp1, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$pc_comp2, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")


emmeans::emmeans(mod_res$pc_comp3, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "none")

emmeans::emmeans(mod_res$pc_comp2, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$pc_comp3, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")
```

$emmeans
 subj_emo_lab_no_amb   emmean    SE  df asymp.LCL asymp.UCL
 anger               -0.22836 0.346 Inf    -0.907     0.450
 disgust              0.30314 0.320 Inf    -0.324     0.931
 fear                -0.14522 0.330 Inf    -0.791     0.501
 happy                0.00991 0.319 Inf    -0.615     0.635
 neutral             -0.10057 0.327 Inf    -0.741     0.540
 sad                 -0.15713 0.326 Inf    -0.795     0.481

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate    SE  df z.ratio p.value
 anger - disgust    -0.5315 0.176 Inf  -3.026  0.0299
 anger - fear       -0.0831 0.191 Inf  -0.435  0.9980
 anger - happy      -0.2383 0.175 Inf  -1.361  0.7502
 anger - neutral    -0.1278 0.190 Inf  -0.671  0.9851
 anger - sad        -0.0712 0.184 Inf  -0.387  0.9989
 disgust - fear      0.4484 0.140 Inf   3.193  0.0177
 disgust - happy     0.2932 0.114 Inf   2.563  0.1066
 disgust - neutral   0.4037 0.136 Inf   2.972  0.0351
 disgust - sad       0.4603 0.131 Inf   3.509  0.0060
 fear - happy       -0.1551 0.138 Inf  -1.126  0.8707
 fear - neutral     -0.0447 0.157 Inf  -0.285  0.9997
 fear - sad          0.0119 0.152 Inf   0.078  1.0000
 happy - neutral     0.1105 0.132 Inf   0.839  0.9603
 happy - sad         0.1670 0.129 Inf   1.298  0.7866
 neutral - sad       0.0566 0.147 Inf   0.384  0.9989

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
P value adjustment: tukey method for comparing a family of 6 estimates 

Warning: The working directory was changed to /Users/pw22812 inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5100' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5100' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
NOTE: Results may be misleading due to involvement in interactions
$emmeans
 subj_emo_lab_no_amb  emmean    SE  df asymp.LCL asymp.UCL
 anger                0.0327 0.304 Inf    -0.563     0.629
 disgust              0.2772 0.281 Inf    -0.273     0.828
 fear                 0.0198 0.289 Inf    -0.547     0.586
 happy               -0.1281 0.279 Inf    -0.676     0.420
 neutral             -0.1574 0.286 Inf    -0.717     0.403
 sad                 -0.0217 0.286 Inf    -0.582     0.538

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate    SE  df z.ratio p.value
 anger - disgust    -0.2445 0.161 Inf  -1.518  0.6527
 anger - fear        0.0130 0.172 Inf   0.075  1.0000
 anger - happy       0.1608 0.163 Inf   0.987  0.9221
 anger - neutral     0.1902 0.172 Inf   1.104  0.8800
 anger - sad         0.0544 0.166 Inf   0.328  0.9995
 disgust - fear      0.2574 0.133 Inf   1.943  0.3760
 disgust - happy     0.4053 0.114 Inf   3.570  0.0048
 disgust - neutral   0.4346 0.127 Inf   3.409  0.0085
 disgust - sad       0.2989 0.125 Inf   2.392  0.1589
 fear - happy        0.1478 0.130 Inf   1.136  0.8665
 fear - neutral      0.1772 0.141 Inf   1.254  0.8097
 fear - sad          0.0415 0.141 Inf   0.294  0.9997
 happy - neutral     0.0293 0.120 Inf   0.245  0.9999
 happy - sad        -0.1064 0.125 Inf  -0.854  0.9572
 neutral - sad      -0.1357 0.136 Inf  -0.999  0.9185

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
P value adjustment: tukey method for comparing a family of 6 estimates 

Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5100' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5100' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
NOTE: Results may be misleading due to involvement in interactions
$emmeans
 subj_emo_lab_no_amb  emmean    SE  df asymp.LCL asymp.UCL
 anger               -0.0327 0.200 Inf   -0.4247    0.3592
 disgust             -0.2318 0.148 Inf   -0.5222    0.0586
 fear                -0.0862 0.168 Inf   -0.4154    0.2430
 happy                0.1039 0.145 Inf   -0.1804    0.3881
 neutral              0.2377 0.162 Inf   -0.0792    0.5547
 sad                  0.0323 0.160 Inf   -0.2813    0.3459

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate    SE  df z.ratio p.value
 anger - disgust     0.1990 0.180 Inf   1.103  0.2701
 anger - fear        0.0535 0.196 Inf   0.273  0.7845
 anger - happy      -0.1366 0.180 Inf  -0.757  0.4488
 anger - neutral    -0.2705 0.194 Inf  -1.392  0.1640
 anger - sad        -0.0651 0.188 Inf  -0.345  0.7298
 disgust - fear     -0.1456 0.145 Inf  -1.001  0.3168
 disgust - happy    -0.3357 0.120 Inf  -2.796  0.0052
 disgust - neutral  -0.4695 0.140 Inf  -3.357  0.0008
 disgust - sad      -0.2641 0.136 Inf  -1.939  0.0525
 fear - happy       -0.1901 0.143 Inf  -1.332  0.1827
 fear - neutral     -0.3239 0.160 Inf  -2.029  0.0425
 fear - sad         -0.1185 0.157 Inf  -0.756  0.4498
 happy - neutral    -0.1338 0.134 Inf  -0.996  0.3191
 happy - sad         0.0716 0.134 Inf   0.533  0.5939
 neutral - sad       0.2054 0.151 Inf   1.359  0.1740

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 

Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5100' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5100' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
$emmeans
subj_emo_lab_no_amb = anger:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.4170 0.425 Inf    -0.416     1.250
 social           -0.3516 0.429 Inf    -1.193     0.490

subj_emo_lab_no_amb = disgust:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.4563 0.396 Inf    -0.320     1.233
 social            0.0981 0.392 Inf    -0.671     0.867

subj_emo_lab_no_amb = fear:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.1524 0.407 Inf    -0.645     0.949
 social           -0.1129 0.405 Inf    -0.907     0.681

subj_emo_lab_no_amb = happy:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.4046 0.394 Inf    -0.369     1.178
 social           -0.6608 0.390 Inf    -1.426     0.104

subj_emo_lab_no_amb = neutral:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.3138 0.407 Inf    -0.484     1.111
 social           -0.6287 0.398 Inf    -1.408     0.151

subj_emo_lab_no_amb = sad:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.4353 0.404 Inf    -0.356     1.227
 social           -0.4787 0.398 Inf    -1.259     0.302

Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
subj_emo_lab_no_amb = anger:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.769 0.600 Inf   1.281  0.2001

subj_emo_lab_no_amb = disgust:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.358 0.553 Inf   0.648  0.5172

subj_emo_lab_no_amb = fear:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.265 0.570 Inf   0.466  0.6415

subj_emo_lab_no_amb = happy:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    1.065 0.551 Inf   1.933  0.0532

subj_emo_lab_no_amb = neutral:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.943 0.566 Inf   1.664  0.0961

subj_emo_lab_no_amb = sad:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.914 0.563 Inf   1.625  0.1042

Degrees-of-freedom method: asymptotic 

Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5100' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5100' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5100)' or larger];
but be warned that this may result in large computation time and memory use.
$emmeans
subj_emo_lab_no_amb = anger:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial        -0.4257 0.272 Inf    -0.959     0.107
 social            0.3603 0.287 Inf    -0.203     0.924

subj_emo_lab_no_amb = disgust:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial        -0.2465 0.206 Inf    -0.651     0.158
 social           -0.2170 0.205 Inf    -0.619     0.185

subj_emo_lab_no_amb = fear:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial        -0.0544 0.232 Inf    -0.510     0.401
 social           -0.1180 0.236 Inf    -0.581     0.345

subj_emo_lab_no_amb = happy:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.0844 0.202 Inf    -0.312     0.481
 social            0.1233 0.201 Inf    -0.271     0.518

subj_emo_lab_no_amb = neutral:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.2488 0.233 Inf    -0.209     0.706
 social            0.2266 0.220 Inf    -0.204     0.657

subj_emo_lab_no_amb = sad:
 social_nonsocial  emmean    SE  df asymp.LCL asymp.UCL
 nonsocial        -0.0177 0.225 Inf    -0.459     0.424
 social            0.0824 0.220 Inf    -0.349     0.514

Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
subj_emo_lab_no_amb = anger:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social  -0.7860 0.391 Inf  -2.008  0.0446

subj_emo_lab_no_amb = disgust:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social  -0.0295 0.286 Inf  -0.103  0.9177

subj_emo_lab_no_amb = fear:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.0637 0.327 Inf   0.195  0.8455

subj_emo_lab_no_amb = happy:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social  -0.0389 0.281 Inf  -0.139  0.8898

subj_emo_lab_no_amb = neutral:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social   0.0222 0.318 Inf   0.070  0.9443

subj_emo_lab_no_amb = sad:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social  -0.1001 0.309 Inf  -0.323  0.7463

Degrees-of-freedom method: asymptotic 


NEXT do a model where we include the 77 sample people
put on a separate script

```{r}
save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/social_emophys_facenmfs.RData")
```

