---
title: "social_emophys_face_visualisations"
author: "helio"
date: "2026-02-19"
output: html_document
---


data: save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/social_emophys_facenmfs_77frames.RData")

relsted analysis code: social_emophys_facenmfs_77frames
visualisations of face responses

```{r}

sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here

p<- list()

p$graphstyle_int <-  theme(#base plot theme
  
  # axis lines
  axis.line.y = element_line(color="black", size = 1.5),
  axis.line.x = element_line(color="black", size = 1,5),
  
  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
  
  # text
  strip.text.x = element_text(size = 16*(sf+.5),  colour = "black"),
  strip.text.y = element_text(size = 16*(sf+.5),  colour = "black"),
  
  text=element_text(size = 14),
  axis.text.x = element_text(size = 15*(sf+.5), colour = "black",),
  axis.text.y = element_text(size = 15*(sf+.5), colour = "black"),
  
  
  # panel
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  # panel.background = element_rect(fill="transparent"),
  # panel.border = element_rect(fill="transparent"),
  # strip shades (reco rectagles)
   # strip.background = element_blank(),
  
  # legend
  # legend.position = "top",
  legend.key = element_rect(colour = "transparent", fill="transparent"),
  # axis.ticks = element_blank(),
  # legend.k
  #legend.direction = "horizontal",

  legend.text = element_text(size = 16*(sf+.5)),
  legend.title= element_text(size = 16*(sf+.5)),
  # legend.title = element_text(size = 10*(sf+.3)),
  # legend line tends to be really small in print so adjust here
  # legend.key.height = unit(.5, "cm"),
  # legend.key.width = unit(2, "cm"),
  
  #legend.text = element_text(size = 10*sf),
  # legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)


```
raw face pc models
face comp 1
```{r}

df_plot_face_pc1 <- dta_cmfsts_aus3_wid %>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup() %>%
  mutate(pca_comp1_au = scale(pca_comp1_au)[, 1])

x_levels_fpc1 <- levels(factor(df_plot_face_pc1$subj_emo_lab_no_amb))
y_lim_fpc1 <- range(df_plot_face_pc1$pca_comp1_au, na.rm = TRUE)

plts$face_pc1 <- df_plot_face_pc1 %>%
  ggplot(aes(social_nonsocial, pca_comp1_au,
             colour = social_nonsocial, shape = social_nonsocial)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
  geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  stat_summary(geom ="pointrange", fun.data = "mean_se") +
  facet_grid(~subj_emo_lab_no_amb) +
  xlab("condition") + ylab("comp1 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  coord_cartesian(ylim = y_lim_fpc1) +
  theme_classic() +
  p$graphstyle_int +
  theme(
    # axis.text.x = element_text(angle = 45, hjust = 1),
    
        legend.position = "none", #because this might be the top plot
        legend.title = element_blank(),
        axis.title.x = element_blank(), #remove the repeated social and non social just on the top plos
        axis.text.x = element_blank(),
        strip.text.x = element_text(size = 12*(sf+.5), colour = "black"))

plts$face_pc1 

plts$face_pc1_soc_dens <- ggplot(df_plot_face_pc1,
                                 aes(y = pca_comp1_au, fill = social_nonsocial)) +
  geom_density(aes(x = after_stat(density)), orientation = "y",
               alpha = 0.25, colour = NA) +
  scale_fill_brewer(palette = "Dark2") +
  coord_cartesian(ylim = y_lim_fpc1) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")


plts$face_pc1_emo_top <- df_plot_face_pc1 %>%
  group_by(subj_emo_lab_no_amb) %>%
  summarise(mean = mean(pca_comp1_au, na.rm = TRUE),
            se = sd(pca_comp1_au, na.rm = TRUE) / sqrt(n()),
            .groups = "drop") %>%
  ggplot(aes(subj_emo_lab_no_amb, mean)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
  geom_pointrange(aes(ymin = mean - se, ymax = mean + se), linewidth = 1) +
  scale_x_discrete(limits = x_levels_fpc1) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

plts$face_pc1_p1 <- (plts$face_pc1_emo_top | plot_spacer()) +
  plot_layout(widths = c(5, 1))

plts$face_pc1_p2 <- (plts$face_pc1 | plts$face_pc1_soc_dens) +
  plot_layout(widths = c(5, 1))

plts$face_pc1_ptchw <- (plts$face_pc1_p1 / plts$face_pc1_p2) +
  plot_layout(heights = c(1.5, 5))

plts$face_pc1_ptchw 

library(cowplot)

# # extract legend from main plot only
# social_non_soc_leg <- get_legend(plts$face_pc1 + theme(legend.position = "top"))
# 
# 
# 
#  
# 
# 
# 
# base_pc1 <- (plts$face_pc1_p1 / plts$face_pc1_p2) +
#   plot_layout(heights = c(1.5, 5))
# 
# library(cowplot)
# 
# leg <- get_legend(plts$face_pc1 + theme(legend.position = "top"))
# 
# plts$face_pc1_ptchw  <- wrap_elements(social_non_soc_leg) / base_pc1 +
#   plot_layout(heights = c(0.4, 5))

plts$face_pc1_final
```

 plts$face_pc1<-
dta_cmfsts_aus3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  mutate(pca_comp1_au = scale(pca_comp1_au)[,1])%>%
  ggplot(aes(social_nonsocial,pca_comp1_au, colour = social_nonsocial, shape = social_nonsocial))+
 geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("comp1 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top", legend.title = element_blank(), strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )

plts$face_pc1




face comp 2
```{r}

library(dplyr)
library(ggplot2)
library(patchwork)


plts$face_pc2<-dta_cmfsts_aus3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  mutate(pca_comp2_au = scale(pca_comp2_au)[,1])%>%
  ggplot(aes(social_nonsocial,pca_comp2_au, colour = social_nonsocial, shape = social_nonsocial))+
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
 geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(label = participant))+
  xlab("condition") +
  ylab("comp2 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
 theme(
    # axis.text.x = element_text(angle = 45, hjust = 1),
    
        legend.position = "none", #because this might be the top plot
        legend.title = element_blank(),
        axis.title.x = element_blank(), #remove the repeated social and non social just on the top plos
        axis.text.x = element_blank(),
        strip.text.x = element_text(size = 12*(sf+.5), colour = "black"))




df_plot_face_pc2 <- dta_cmfsts_aus3_wid %>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup() %>%
  mutate(pca_comp2_au = scale(pca_comp2_au)[, 1])

# shared ranges
x_levels_fpc2 <- levels(factor(df_plot_face_pc2$subj_emo_lab_no_amb))
y_lim_fpc2 <- range(df_plot_face_pc2$pca_comp2_au, na.rm = TRUE)




plts$face_pc2_soc_dens <- ggplot(df_plot_face_pc2, aes(y = pca_comp2_au, fill = social_nonsocial)) +
  geom_density(aes(x = after_stat(density)), orientation = "y",
               alpha = 0.25, colour = NA) +
  scale_fill_brewer(palette = "Dark2") +
  coord_cartesian(ylim = y_lim_fpc2) +
  theme_classic() +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    legend.position = "none"
    # plot.margin = margin(0, 0, 0, 0)
  )

plts$face_pc2_soc_dens

plts$face_pc2_emo_top <- df_plot_face_pc2 %>%
  group_by(subj_emo_lab_no_amb) %>%
  summarise(mean = mean(pca_comp2_au, na.rm = TRUE),
            se = sd(pca_comp2_au, na.rm = TRUE) / sqrt(n()),
            .groups = "drop") %>%
  ggplot(aes(subj_emo_lab_no_amb, mean)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted", colour = "gray50", linewidth = .8)+
  geom_pointrange(aes(ymin = mean - se, ymax = mean + se), linewidth = 1) +
  scale_x_discrete(limits = x_levels_fpc2) +
  
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())




plts$face_pc2_p1<- (plts$face_pc2_emo_top  | plot_spacer())+plot_layout(widths = c(5, 1))

plts$face_pc2_p2<- (plts$face_pc2 |  plts$face_pc2_soc_dens)+plot_layout(widths = c(5, 1))

plts$face_pc2_ptchw<- (plts$face_pc2_p1/plts$face_pc2_p2)+plot_layout(heights = c(1.5, 5))
plts$face_pc2_ptchw




```

comp 3




plts$face_pc3<-dta_cmfsts_aus3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ungroup()%>%
  mutate(pca_comp3_au = scale(pca_comp3_au)[,1])%>%
  ggplot(aes(social_nonsocial,pca_comp3_au, colour = social_nonsocial, shape = social_nonsocial))+
 geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
   geom_point(size = 1.5, position = position_dodge(width = 0.4)) +
  # geom_dotplot(binaxis = "y", stackdir = "center",
  #              alpha = .4, dotsize = .6, binwidth = .2) +
  stat_summary(geom ="pointrange", fun.data  = "mean_se")+
  facet_grid(~subj_emo_lab_no_amb) +
  # geom_text(aes(labelcomp1_pyfeat = participant))+
  xlab("condition") +
  ylab("comp3 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none", legend.title = element_blank(),  
         strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )
 


```{r}
 plts$face_pc1
 plts$face_pc2
 plts$face_pc3
 
 
df_plot_face_pc3 <- dta_cmfsts_aus3_wid %>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup() %>%
  mutate(pca_comp3_au = scale(pca_comp3_au)[, 1])

x_levels_fpc3 <- levels(factor(df_plot_face_pc3$subj_emo_lab_no_amb))
y_lim_fpc3 <- range(df_plot_face_pc3$pca_comp3_au, na.rm = TRUE)

plts$face_pc3 <- ggplot(df_plot_face_pc3,
                        aes(social_nonsocial, pca_comp3_au,
                            colour = social_nonsocial, shape = social_nonsocial)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
   geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_jitter(width = .2, size = 2, alpha = .2) +
  # geom_point(size = 1.5, position = position_dodge(width = 0.4)) +
  stat_summary(geom ="pointrange", fun.data = "mean_se") +
  facet_grid(~subj_emo_lab_no_amb) +
  xlab("condition") +
  ylab("comp3 (z)") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  coord_cartesian(ylim = y_lim_fpc3) +
  theme_classic() +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        strip.text.x = element_text(size = 12*(sf+.5), colour = "black"))

plts$face_pc3_soc_dens <- ggplot(df_plot_face_pc3,
                                 aes(y = pca_comp3_au, fill = social_nonsocial)) +
  geom_density(aes(x = after_stat(density)), orientation = "y",
               alpha = 0.25, colour = NA) +
  scale_fill_brewer(palette = "Dark2") +
  coord_cartesian(ylim = y_lim_fpc3) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")

plts$face_pc3_emo_top <- df_plot_face_pc3 %>%
  group_by(subj_emo_lab_no_amb) %>%
  summarise(mean = mean(pca_comp3_au, na.rm = TRUE),
            se = sd(pca_comp3_au, na.rm = TRUE) / sqrt(n()),
            .groups = "drop") %>%
  ggplot(aes(subj_emo_lab_no_amb, mean)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
  geom_pointrange(aes(ymin = mean - se, ymax = mean + se), linewidth = 1) +
  scale_x_discrete(limits = x_levels_fpc3) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

plts$face_pc3_p1 <- (plts$face_pc3_emo_top | plot_spacer()) +
  plot_layout(widths = c(5, 1))

plts$face_pc3_p2 <- (plts$face_pc3 | plts$face_pc3_soc_dens) +
  plot_layout(widths = c(5, 1))

plts$face_pc3_ptchw <- (plts$face_pc3_p1 / plts$face_pc3_p2) +
  plot_layout(heights = c(1.5, 5))

plts$face_pc3_ptchw 

```


timeseries component plots


```{r}

plts$face_nmf_tims1<-
dta_face_z_shift_3%>%
  group_by(participant, bin_frame,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ungroup()%>%
  mutate(nmf_comp1 = scale(nmf_comp1)[,1])%>%
ggplot( aes(as.numeric(bin_frame), nmf_comp1,
               colour = subj_emo_lab_no_amb,
               fill   = subj_emo_lab_no_amb,
             linetype = subj_emo_lab_no_amb,
               group  = subj_emo_lab_no_amb)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun.data = mean_se, geom = "ribbon",
               alpha = .20, colour = NA) +
  facet_grid(~social_nonsocial) +
  ylab("comp 1 (z)")+
  xlab("bin frame")+
  p$graphstyle_int+ guides(fill = "none")+
  guides(fill = "none")+  theme(
        legend.position = "none", legend.title = element_blank(), axis.title.x = element_blank())
# gather legends separtelly
  # 
  #  p$graphstyle_int+ guides(fill = "none")+
  # guides(fill = "none")+  theme(
  #       legend.position = "top", legend.title = element_blank())

plts$face_nmf_tims1
plts$face_nmf_tims2<- dta_face_z_shift_3%>%
  group_by(participant, bin_frame,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ungroup()%>%
  mutate(nmf_comp2 = scale(nmf_comp2)[,1])%>%
  # ggplot(aes(bin_frame, nmf_comp2, colour = subj_emo_lab_no_amb))+
  ggplot( aes(as.numeric(bin_frame), nmf_comp2,
               colour = subj_emo_lab_no_amb,
               fill   = subj_emo_lab_no_amb,
                linetype = subj_emo_lab_no_amb,
               group  = subj_emo_lab_no_amb)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun.data = mean_se, geom = "ribbon",
               alpha = .20, colour = NA) +
  facet_grid(~social_nonsocial) +
   ylab("comp 2 (z)")+
  xlab("bin frame")+
   p$graphstyle_int+ guides(fill = "none")+
  guides(fill = "none")+  theme(
        legend.position = "none", legend.title = element_blank(), axis.title.x = element_blank())
  # geom_smooth()+
  # facet_grid(~social_nonsocial)

plts$face_nmf_tims3<-
dta_face_z_shift_3%>%
  group_by(participant, bin_frame,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%ungroup()%>%
  mutate(nmf_comp3 = scale(nmf_comp3)[,1])%>%
  # ggplot(aes(bin_frame, nmf_comp3, colour = subj_emo_lab_no_amb))+
   ggplot( aes(as.numeric(bin_frame), nmf_comp3,
               colour = subj_emo_lab_no_amb,
               fill   = subj_emo_lab_no_amb,
                linetype = subj_emo_lab_no_amb,
               group  = subj_emo_lab_no_amb)) +
  geom_hline(aes(yintercept = 0), linetype = "dotted",
             colour = "gray50", linewidth = .8) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun.data = mean_se, geom = "ribbon",
               alpha = .20, colour = NA) +
  facet_grid(~social_nonsocial) +
   ylab("comp 3 (z)")+
  xlab("bin frame")+
   p$graphstyle_int+ guides(fill = "none")+
  guides(fill = "none")+  theme(
        legend.position = "none", legend.title = element_blank())

plts$face_nmf_tims1

plts$face_nmf_tims2
plts$face_nmf_tims3
```

combine
```{r}

# how to load local plots (comp1_pyfeat.png, comp2_pyfeat.png, comp3_pyfeat.png) andf combine with below

setwd("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/Figures")
library(png)
library(grid)
library(ggplot2)
library(patchwork)

# helper: read PNG and wrap as a ggplot object
png_plot <- function(path) {
  img <- png::readPNG(path)
  ggplot() +
    annotation_custom(rasterGrob(img, width = unit(1, "npc"), height = unit(1, "npc"))) +
    coord_cartesian(expand = FALSE) +
    theme_void()
}
# avoid streching
png_plot <- function(path) {
  img <- png::readPNG(path)
  h <- dim(img)[1]
  w <- dim(img)[2]

  ggplot() +
    annotation_custom(
      rasterGrob(img, width = unit(1, "npc"), height = unit(1, "npc"))
    ) +
    coord_fixed(ratio = h / w, expand = FALSE) +   # <- prevents stretching
    theme_void()
}

comp1_pyfeat <- png_plot("comp1_pyfeat.png")
comp2_pyfeat <- png_plot("comp2_pyfeat.png")
comp3_pyfeat <- png_plot("comp3_pyfeat.png")

# combine: top row = your NMF faces, middle row = your PC faces, bottom row = pyfeat PNGs

library(magick)
library(ggplot2)
library(grid)
install.packages("magick")
png_plot <- function(path) {

  img <- image_read(path) |>
         image_trim()      # <- removes empty margins automatically

  # get dimensions AFTER trimming
  info <- image_info(img)
  w <- info$width
  h <- info$height

  img <- as.raster(img)

  ggplot() +
    annotation_custom(
      rasterGrob(img, width = unit(1, "npc"), height = unit(1, "npc"))
    ) +
    coord_fixed(ratio = h / w, expand = FALSE) +
    theme_void()
}

comp1_pyfeat <- png_plot("comp1_pyfeat.png")
comp2_pyfeat <- png_plot("comp2_pyfeat.png")
comp3_pyfeat <- png_plot("comp3_pyfeat.png")


plts$face_ks <- (comp1_pyfeat | comp2_pyfeat | comp3_pyfeat) /
    # (comp1_pyfeat        | comp2_pyfeat        | comp3_pyfeat)/
  (plts$face_nmf_tims1 | plts$face_nmf_tims2 | plts$face_nmf_tims3) /
  ( plts$face_pc1       | plts$face_pc2       | plts$face_pc3) 


plts$face_ks 


```

each column is a type of plot
```{r}
plts$face_ks2 

(wrap_plots(comp1_pyfeat) / wrap_plots(comp2_pyfeat) / wrap_plots(comp3_pyfeat) )|
    # (comp1_pyfeat        | comp2_pyfeat        | comp3_pyfeat)/
  (plts$face_nmf_tims1 / plts$face_nmf_tims2 / plts$face_nmf_tims3) |
  ( patchwork::wrap_plots(plts$face_pc1_ptchw)       / 
      wrap_plots(plts$face_pc2_ptchw)       / 
      wrap_plots(plts$face_pc3_ptchw) )

plts$face_ks2+plot_layout(heights = c(1,1,1), widths = c(.5,1,1))



library(cowplot)
library(patchwork)

# pick which plots supply the legends
plts$face_nmf_leg <- get_legend(plts$face_nmf_tims1 + theme(legend.position = "top"))
plts$face_pc_leg <- get_legend(plts$face_pc1       + theme(legend.position = "top"))

# 
# title plot for column 1
plts$pyfeat_title<- ggplot() +
  annotate("text", x = 0, y = 0, label = "Facial response components", hjust = 0, size = 5) +
  theme_void()







col_pyfeat <-
  (plts$pyfeat_title / comp1_pyfeat / comp2_pyfeat / comp3_pyfeat) +
  plot_layout(heights = c(0.1, 1, 1, 1))

col_nmf <-
  (wrap_elements(plts$face_nmf_leg) / plts$face_nmf_tims1 / plts$face_nmf_tims2 / plts$face_nmf_tims3) +
  plot_layout(heights = c(0.1, 1, 1, 1))

col_pc <-
  (wrap_elements(plts$face_pc_leg) / plts$face_pc1_ptchw / plts$face_pc2_ptchw / plts$face_pc3_ptchw) +
  plot_layout(heights = c(0.1, 1, 1, 1))

(col_pyfeat | col_nmf | col_pc) +
  plot_layout(widths = c(0.5, 1, 1.5))
```



# try rowwise
# centered title panel
plts$pyfeat_title <- ggplot() +
  annotate("text", x = 0.5, y = 0.5,
           label = "Facial response components",
           hjust = 0, vjust = 0.5, size = 12) +
  xlim(0, 1) + ylim(0, 1) +
  theme_void()

row1 <- (plts$pyfeat_title | wrap_elements(plts$face_nmf_leg) | wrap_elements(plts$face_pc_leg))
row2 <- (comp1_pyfeat | plts$face_nmf_tims1 | plts$face_pc1_ptchw)
row3 <- (comp2_pyfeat | plts$face_nmf_tims2 | plts$face_pc2_ptchw)
row4 <- (comp3_pyfeat | plts$face_nmf_tims3 | plts$face_pc3_ptchw)

Main solution
```{r}
# remove legends from all body plots
# plts$face_nmf_tims1 <- plts$face_nmf_tims1 + theme(legend.position = "none")
# plts$face_nmf_tims2 <- plts$face_nmf_tims2 + theme(legend.position = "none")
# plts$face_nmf_tims3 <- plts$face_nmf_tims3 + theme(legend.position = "none")
# 
plts$face_pc1_ptchw <- plts$face_pc1_ptchw + theme(legend.position = "none")
# plts$face_pc2 <- plts$face_pc2 + theme(legend.position = "none")
# plts$face_pc3 <- plts$face_pc3 + theme(legend.position = "none")


center_grob <- function(g) {
  ggplot() +
    annotation_custom(grob = g) +
    theme_void()
}

row1 <- (
  plts$pyfeat_title  |
  center_grob(plts$face_nmf_leg) |
  center_grob(plts$face_pc_leg)
)

row2 <- (comp1_pyfeat | plts$face_nmf_tims1 | plts$face_pc1_ptchw)
row3 <- (comp2_pyfeat | plts$face_nmf_tims2 | plts$face_pc2_ptchw)
row4 <- (comp3_pyfeat | plts$face_nmf_tims3 | plts$face_pc3_ptchw)

plts$face_panel<- (row1 / row2 / row3 / row4) +
  plot_layout(heights = c(0.25, 1, 1, 1), widths = c(0.5, 1, 1.7))




 
ggsave("plts_face_panel.png",plts$face_panel,  dpi = 300, width = 22, height = 17,  units = "in",
       device = "png")


ggsave("plts_face_panel.tiff",plts$face_panel,  dpi = 300, width = 22, height = 17,  units = "in",
       device = "tiff", compression = "lzw")
```




```{r}
save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/social_emophys_facenmfs_77frames.RData")

```