---
title: "social empophys coherence"
author: "helio"
date: "2026-01-15"
output: html_document
---

build on s4sn
mfa
consider including one component per face

consider reducing dimensionality of subjective ratings into one compoentn as well

just subjective, scr, hr, and face



```{r}
# vis preferences 

sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here

p<- list()

p$graphstyle_int <-  theme(#base plot theme
  
  # axis lines
  axis.line.y = element_line(color="black", size = 1.5),
  axis.line.x = element_line(color="black", size = 1,5),
  
  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
  
  # text
  strip.text.x = element_text(size = 16*(sf+.5),  colour = "black"),
  strip.text.y = element_text(size = 16*(sf+.5),  colour = "black"),
  
  text=element_text(size = 14),
  axis.text.x = element_text(size = 15*(sf+.5), colour = "black",),
  axis.text.y = element_text(size = 15*(sf+.5), colour = "black"),
  
  
  # panel
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  # panel.background = element_rect(fill="transparent"),
  # panel.border = element_rect(fill="transparent"),
  # strip shades (reco rectagles)
   # strip.background = element_blank(),
  
  # legend
  # legend.position = "top",
  legend.key = element_rect(colour = "transparent", fill="transparent"),
  # axis.ticks = element_blank(),
  # legend.k
  #legend.direction = "horizontal",

  legend.text = element_text(size = 16*(sf+.5)),
  legend.title= element_text(size = 16*(sf+.5)),
  # legend.title = element_text(size = 10*(sf+.3)),
  # legend line tends to be really small in print so adjust here
  # legend.key.height = unit(.5, "cm"),
  # legend.key.width = unit(2, "cm"),
  
  #legend.text = element_text(size = 10*sf),
  # legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)

```

```{r}


dta_pca1_3_face_92 <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/dta_pca1_3_face_92.rds")



dta_mfa_part1<- dta_emo[,c("val_slider_response","int_slider_response","happy_slide_response","sad_slide_response","fear_slide_response","disgust_slide_response","anger_slide_response","hr_mean_diff","log_cda_iscr","social_nonsocial","participant","stim_iaps",
                           "social_nonsocial", "emotioncategory", "subj_emo_lab_no_amb")]

colnames(dta_pca1_3_face_92)
dta_pca1_3_face_92$social_nonsocial<- NULL
dta_pca1_3_face_92

dta_mfa_part1$social_nonsocial<- NULL

dta_mfa_part2<- left_join(dta_mfa_part1, dta_pca1_3_face_92, 
                          by = c("participant", "stim_iaps", "subj_emo_lab_no_amb"))


dta_emo
dta_mfa_part2$social_nonsocial<- dta_emo$social_nonsocial
colnames(dta_mfa_part2)

dta_mfa_part3<- dta_mfa_part2[,c(10:15,1:9,130:132, 16:129)]

colnames(dta_mfa_part3)
dta_mfa_part4<- dta_mfa_part3[,1:18]

colnames(dta_emo)

dta_emo
dta_emo_dmg<- dta_emo%>%
  group_by(participant,diagnosis,asd)%>%
  summarise_at(c("tas20_total","dass21_total","dass21_dep", "dass21_anx","dass21_total","obs_slider_response","belief_slider_response","aq28_scale_sum_cont"),
               mean, na.rm = T)

dta_emo_dmg
```

first MFA
keep ratings, summairse face into PCs

```{r}
# cast to wide
colnames(dta_mfa_part4)

dta_mfa_part4_wide<- dta_mfa_part4%>%
  select(-filename, subj_emo_lab_no_amb)%>%
 pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),
    values_from = names(dta_mfa_part4[,7:18]),
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )
# rm(dta_emo_wide_mfa)
colnames(dta_mfa_part4_wide[,3:722])

dta_mfa_part4_wide
table(is.na(dta_mfa_part4_wide))
# complete

dta_mfa_part4_wide


# 420+60+60+(60*3)
# 
# 
# 541:600

imputedmfa <- missMDA::imputeMFA(dta_mfa_part4_wide[,3:722],
                                               ncp=2,
                                                group=c(420, 60, 60, 180),
                          type=c("s","s","s", "s"))


dta_mfa_part4_wide_complete<- imputedmfa$completeObs


# just the hr, scr, subje, face components
mod_res$mfa_result_wide_new <- MFA(dta_mfa_part4_wide_complete,
                         group=c(420, 60, 60, 180),
                         type=c("s","s","s", "s"),
                          name.group= c("subj_aff","phys_hr","phys_scr","face"),
                          # num.group.sup=c(6),#position of group above
                          graph=TRUE)
dta_mfa_part4_wide_complete

mod_res$mfa_result_wide_new$global.pca$var

```

some vis

```{r}
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 3,top = 10)




fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 1,sort.val = "none",ylim = c(0, 60))
fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 2,sort.val = "none",ylim = c(0, 60))
fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 3,sort.val = "none",ylim = c(0, 60))


fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 1, top= 80)
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 2)# 
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 3)

```

```{r}
dta_mfa_part4_wide$mfa_pc1<- mod_res$mfa_result_wide_new$ind$coord[,1]
dta_mfa_part4_wide$mfa_pc2<- mod_res$mfa_result_wide_new$ind$coord[,2]
dta_mfa_part4_wide$mfa_pc3<- mod_res$mfa_result_wide_new$ind$coord[,3]

dta_mfa_part4_wide$mfa_pc1_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,1]
dta_mfa_part4_wide$mfa_pc2_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,2]
dta_mfa_part4_wide$mfa_pc3_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,3]
# dta_mfa_part4_wide$ma_pc4<- mod_res$mfa_result_wide_new$ind$coord[,4]

mod_res$mfa_result_wide_new$quanti.var$coord
```


```{r}

dta_mfa_part4_wide%>%
  # mutate(social_nonsocial = ifelse(partic >199, "social", "nonsocial"))%>%
  # group_by(particpant, social,nonsocial)%>%
  # summairse_if(is.numeric, mean, na.rm = T)%>%
   # subset(participant!= 105)%>%#doesnt change significance
  ggplot(aes(social_nonsocial, mfa_pc1,colour = social_nonsocial))+
  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means(method = "t.test")
  # geom_text(aes(label = participant))

dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, mfa_pc2,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, mfa_pc3,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means(".test")





dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc2_contrib+.1),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc3_contrib+.1),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()



dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc3_contrib+ mfa_pc3_contrib),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()

dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, (mfa_pc1_contrib+mfa_pc2_contrib+mfa_pc3_contrib),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()+
  geom_text(aes(label = participant))

```







```{r}
mod_res$mfa_result_wide_new$group$contrib
mod_res$mfa_result_wide_new$group$coord

mod_res$mfa_result_wide_new$quanti.var$contrib[, 1]
mod_res$mfa_result_wide_new$quanti.var$coord[, 1]
range(mod_res$mfa_result_wide_new$quanti.var$contrib[, 1])
range(mod_res$mfa_result_wide_new$quanti.var$contrib[, 2])


df_plot%>%
  group_by(Block)%>%
  mutate(Dim1_z_cont= scale(log1p(dim_1_cont+.1)),
         Dim2_z_cont =scale(log1p(dim_2_cont+.1)))%>%
  # subset(!is.na(cos12_total2))%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot( aes(x = log1p(dim_1_cont+.01), y = log1p(dim_2_cont+.01))) +

geom_point(
  aes(
    colour = Block,
    shape  = Block,
    size   = dim_1_cos
  ),
  alpha = 0.3
) +
  # geom_line(aes(group = stim_iaps), colour = "grey60", alpha = 0.7) + 
  # 3) shared axes
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # coord_fixed(

  scale_colour_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
  # scale_colour_viridis_c(option = "inferno")+
 
  # scale_size_continuous(
  #   range = c(1, 6),
  #   name  = "Total cos² (Dim1+2)"
  # ) +
  ggside::geom_xsidedensity(
    aes(y = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  )+ 
    ggside::geom_ysidedensity(
    aes(x = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE)+
  # )+ 
  labs(
    x     = "MFA PC1",
    y     = "MFA PC2",
    title = "Shared axes: size = quality of rep."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", size = 0.2)
  )+
  guides(size = FALSE)


```

PCA version with equal weight to grouos
Weighted PCA
Give each block equal weight manually:
```{r}

# scale each block so blocks have unit variance contribution
dta_mfa_part4_wide_complete_z <- dta_mfa_part4_wide_complete
blocks <- list(1:420, 421:480, 481:540, 541:720)

for (blk in blocks) {
  # divide by sqrt of mean variance within block
  s <- sqrt(mean(apply(dta_mfa_part4_wide_complete[, blk], 2, var)))
  dta_mfa_part4_wide_complete_z[, blk] <- dta_mfa_part4_wide_complete[, blk] / s
}

mod_res$pca_res <- PCA(dta_mfa_part4_wide_complete_z, scale.unit = TRUE, graph = TRUE)
```

```{r}
fviz_contrib(mod_res$pca_res, "var", axes = 1, top = 15)
fviz_contrib(mod_res$pca_res, "var", axes = 2,top = 10)# 
fviz_contrib(mod_res$pca_res, "var", axes = 3,top = 10)


```





Randomly permute the rows of the dataset within each group (preserving group structure), recompute MFA, and record the eigenvalues. If the observed eigenvalue for dimension 1 exceeds the distribution of permuted eigenvalues, it is unlikely to arise by chance.

library(FactoMineR)
```{r eval=FALSE, include=FALSE}

mod_res$mfa_result_wide_new <- MFA(dta_mfa_part4_wide_complete,
                         group=c(420, 60, 60, 180),
                         type=c("s","s","s", "s"),
                          name.group= c("subj_aff","phys_hr","phys_scr","face"),
                          # num.group.sup=c(6),#position of group above
                          graph=TRUE)
obs <- mod_res$mfa_result_wide_new$eig[1,1]  # eigenvalue of dim 1
B <- 500
sim <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  # permute rows within each group
  g <- list(1:420, 421:480, 481:540, 541:720)
  for (i in seq_along(g)) {
    dta_perm[g[[i]], ] <- dta_perm[sample(g[[i]]), ]
  }
  mfa_b <- MFA(dta_perm,
               group=c(420,60,60,180),
               type=c("s","s","s","s"),
               name.group=c("subj_aff","phys_hr","phys_scr","face"),
               graph=FALSE)
  sim[b] <- mfa_b$eig[1,1]
}

p_value <- mean(sim >= obs)

p_value

# too consevative as it just shuffles blocks, but structure also comes from variables
```
Test gaps between dimension instead
<!-- Sometimes it’s nicer to use a ratio instead of a raw difference, because overall scale of eigenvalues can shift under permutations. -->

Row-within-block null: “blocks have structure, but no cross-block alignment”

Goal: preserve within-block variable structure, break alignment across blocks.

Here we shuffle rows separately within each block of columns.
note its conservative because it ignores the variable influence on global dimensions

too conservative don't report this
```{r}
eig_obs <- mod_res$mfa_result_wide_new$eig[, 1]

ratio1_obs <- eig_obs[1] / eig_obs[2]    # λ1 / λ2
ratio2_obs <- eig_obs[2] / eig_obs[3]    # λ2 / λ3, etc.


# permutation ratios

# dta_perm <- dta_mfa_part4_wide_complete

mfa_b <- MFA(dta_perm,
             group = c(420,60,60,180),
             type  = c("s","s","s","s"),
             name.group = c("subj_aff","phys_hr","phys_scr","face"),
             ncp = 2,       # <<--- crucial
             graph = FALSE)

B <- 500
ratio1_sim <- numeric(B)
g <- list(1:420, 421:480, 481:540, 541:720)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  for (i in seq_along(g)) {
    dta_perm[g[[i]], ] <- dta_perm[sample(g[[i]]), ]
  }
  
  mfa_b <- MFA(dta_perm,
               group = c(420,60,60,180),
               type  = c("s","s","s","s"),
               name.group = c("subj_aff","phys_hr","phys_scr","face"),
               ncp = 2,
               graph = FALSE)
  
  eig_b <- mfa_b$eig[,1]
  ratio1_sim[b] <- eig_b[1] / eig_b[2]
}

p_ratio1 <- mean(ratio1_sim >= ratio1_obs)
p_ratio1

# same as before too cosnervative
```
Column-wise null: “no structure at all” (everything is independent)

Goal: test whether there is any real multivariate structure (sanity check).

Here we shuffle rows independently within each column, then compare the λ₁/λ₂ ratio.

this is the permutation test
```{r}
set.seed(123)
# mod_res$mfa_result_wide_new
eig_obs  <- mod_res$mfa_result_wide_new$eig[, 1]
ratio1_obs <- eig_obs[1] / eig_obs[2]

B <- 1000
sim_eig1 <- numeric(B)          # <-- ADD THIS
ratio1_sim_indep <- numeric(B)

for (b in 1:B) {

  dta_perm <- dta_mfa_part4_wide_complete[, 1:720]

  # shuffle each column independently across participants
  for (j in seq_len(ncol(dta_perm))) {
    dta_perm[, j] <- dta_perm[sample(nrow(dta_perm)), j]
  }

  mfa_b <- FactoMineR::MFA(
    dta_perm,
    group      = c(420, 60, 60, 180),
    type       = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    ncp        = 2,
    graph      = FALSE
  )

  eig_b <- mfa_b$eig[, 1]
  sim_eig1[b] <- eig_b[1]                 # <-- STORE EIG1
  ratio1_sim_indep[b] <- eig_b[1] / eig_b[2]
}

p_eig1 <- mean(sim_eig1 >= eig_obs[1])

(sum(sim_eig1 >= eig_obs[1]) + 1) / (B + 1)
p_ratio1_indep <- mean(ratio1_sim_indep >= ratio1_obs)

range(sim_eig1)
p_eig1
p_ratio1_indep


ggplot()+
# ggplot(
  geom_histogram(aes(x = ratio1_sim_indep))+
   geom_vline(xintercept = ratio1_obs[1],
             linetype = "dashed",
             linewidth = 1)



library(ggplot2)
alpha <- 0.05

crit_ratio <- quantile(ratio1_sim_indep, 1 - alpha)

df_ratio <- data.frame(sim = ratio1_sim_indep)

df_ratio$region <- ifelse(df_ratio$sim >= crit_ratio,
                          "α = .05 region", "null")





```

pca sanity check (not for reporting)
```{r}
eig_obs_pca <-mod_res$pca_res$eig[, 1]      # eigenvalues
ratio_obs_pca <- eig_obs[1] / eig_obs[2]   # optional λ1/λ2 ratio


set.seed(123)

B <- 500
sim_eig1_pca  <- numeric(B)
sim_ratio_pca <- numeric(B)

dta_mfa_part4_wide_complete_z

for (b in 1:B) {
  X_perm <- dta_mfa_part4_wide_complete_z
  
  # shuffle each column independently
  for (j in seq_len(ncol(X_perm))) {
    X_perm[, j] <- X_perm[sample(nrow(X_perm)), j]
  }
  
  pca_b <- PCA(X_perm, scale.unit = TRUE, ncp = 2, graph = FALSE)
  eig_b <- pca_b$eig[, 1]
  
  sim_eig1_pca[b]  <- eig_b[1]
  sim_ratio_pca[b] <- eig_b[1] / eig_b[2]
}

p_eig1_pca <- mean(sim_eig1_pca >= eig_obs_pca[1])

p_ratio_pca <- mean(sim_ratio_pca >= ratio_obs_pca)

p_eig1_pca
p_ratio_pca
# consistent with MFA

ggplot()+
# ggplot(
  geom_histogram(aes(x = log(sim_eig1_pca)))+
   geom_vline(xintercept = log(eig_obs_pca[1]),
             linetype = "dashed",
             linewidth = 1)


ggplot()+
# ggplot(
  geom_histogram(aes(x = log(sim_ratio_pca)))+
   geom_vline(xintercept = log(ratio_obs_pca[1]),
             linetype = "dashed",
             linewidth = 1)
  




```

loadings
Compare to a “no structure at all” null (column-wise shuffle)


“Are loadings on Dim 1 more ‘spread out’ / larger than I’d see if all variables were independent noise?”
```{r}

 mod_res$mfa_result_wide_new$quanti.var$coord
# observed statistics
loadings1 <- mod_res$mfa_result_wide_new$quanti.var$coord[, 1]
thr <- 0.3

mean_sq_loading_obs <- mean(loadings1^2)
prop_large_obs      <- mean(abs(loadings1) >= thr)

# permutation under "independent variables" null
set.seed(123)
B <- 500
mean_sq_sim <- numeric(B)
prop_large_sim <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  # shuffle each column independently
  for (j in seq_len(ncol(dta_perm))) {
    dta_perm[, j] <- dta_perm[sample(nrow(dta_perm)), j]
  }
  
  mfa_b <- MFA(dta_perm,
               group      = c(420, 60, 60, 180),
               type       = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               ncp        = 2,
               graph      = FALSE)
  
  load_b <- mfa_b$quanti.var$coord[, 1]
  mean_sq_sim[b]   <- mean(load_b^2)
  prop_large_sim[b] <- mean(abs(load_b) >= thr)
}

# one-sided p-values: is observed larger than null?
p_mean_sq   <- mean(mean_sq_sim   >= mean_sq_loading_obs)
p_prop_large <- mean(prop_large_sim >= prop_large_obs)
range(mean_sq_sim)
range(mean_sq_loading_obs)
range(prop_large_sim)
prop_large_obs
p_mean_sq
p_prop_large

# both alright
# 0
```

Compare to a “no cross-block alignment” null (row-per-block shuffle)

This one keeps within-block structure as signal and only kills cross-block alignment:

i.e. Are the loadings on Dim 1 stronger than I’d expect if blocks had structure but were unrelated”
a bit more conservative because it ignores that structure comes mostly from the variables, the block stuff is for normalisation

not for reporting
```{r}

# observed stats again
# loadings1 <- mod_res$quanti.var$coord[, 1]
# thr <- 0.3

# mean_sq_loading_obs <- mean(loadings1^2)
# prop_large_obs      <- mean(abs(loadings1) >= thr)

# column indices per block
block_cols <- list(
  subj_aff = 1:420,
  phys_hr  = 421:480,
  phys_scr = 481:540,
  face     = 541:720
)

set.seed(123)
B <- 500
mean_sq_sim_block   <- numeric(B)
prop_large_sim_block <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  # shuffle rows separately within each block of columns
  for (blk in block_cols) {
    idx_rows <- sample(nrow(dta_perm))
    dta_perm[, blk] <- dta_perm[idx_rows, blk]
  }
  
  mfa_b <- MFA(dta_perm,
               group      = c(420, 60, 60, 180),
               type       = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               ncp        = 2,
               graph      = FALSE)
  
  load_b <- mfa_b$quanti.var$coord[, 1]
  mean_sq_sim_block[b]    <- mean(load_b^2)
  prop_large_sim_block[b] <- mean(abs(load_b) >= thr)
}

p_mean_sq_block   <- mean(mean_sq_sim_block    >= mean_sq_loading_obs)
p_prop_large_block <- mean(prop_large_sim_block >= prop_large_obs)

p_mean_sq_block
p_prop_large_block

```
1] 0.516
[1] 0.288

as discussed above this is conservative



#############
Stability
#############
This checks stability of loadings and factor scores.

Idea:
Resample rows with replacement, rerun MFA, and assess:
	•	correlation between bootstrapped and original axes
	•	confidence intervals for contributions or loadings

bootMFA (from ExPosition) do this directly but exposition its deprecated;

so I will do manual bootstrapping:

 stability of the latent dimension, i.e. how reproducible is Dim 1 as a participant-level score?

```{r}
B <- 1000
corrs <- matrix(NA, B, 1)
require(FactoMineR)
colnames(dta_mfa_part4_wide_complete)


for (b in 1:B) {
  idx <- sample(nrow(dta_mfa_part4_wide_complete), replace=TRUE)
  mfa_b <- MFA(dta_mfa_part4_wide_complete[idx,1:720],
               group=c(420,60,60,180),
               type=c("s","s","s","s"),
               name.group=c("subj_aff","phys_hr","phys_scr","face"),
               graph=FALSE)
  corrs[b] <- cor(mfa_b$ind$coord[,1], mod_res$mfa_result_wide_new$ind$coord[idx,1])
}



mean_abs_corr <- mean(abs(corrs))
corrs
mean_abs_corr #0.8157963




 sample(nrow(dta_mfa_part4_wide_complete), replace=TRUE)
```


CIs in case we need them at some point
library(FactoMineR)
```{r}
n       <- nrow(dta_mfa_part4_wide_complete)
B_boot  <- 500

# original MFA
mfa_orig      <- mod_res$mfa_result_wide_new
loadings_orig <- mfa_orig$quanti.var$coord[, 1]
eig_orig      <- mfa_orig$eig[, 1]
gap1_orig     <- eig_orig[1] - eig_orig[2]
ratio1_orig   <- eig_orig[1] / eig_orig[2]

# storage
loadings_boot <- matrix(NA, nrow = length(loadings_orig), ncol = B_boot)
eig1_boot     <- numeric(B_boot)
eig2_boot     <- numeric(B_boot)
gap1_boot     <- numeric(B_boot)
ratio1_boot   <- numeric(B_boot)

set.seed(123)

for (b in 1:B_boot) {
  idx <- sample.int(n, size = n, replace = TRUE)
  dta_boot <- dta_mfa_part4_wide_complete[idx, ]

  mfa_b <- MFA(dta_boot,
               group      = c(420, 60, 60, 180),
               type       = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               ncp        = 2,     # we only need first 2 dims for gaps
               graph      = FALSE)

  ## eigenvalues + gap/ratio
  eig_b         <- mfa_b$eig[, 1]
  eig1_boot[b]  <- eig_b[1]
  eig2_boot[b]  <- eig_b[2]
  gap1_boot[b]  <- eig_b[1] - eig_b[2]
  ratio1_boot[b] <- eig_b[1] / eig_b[2]

  ## loadings on Dim 1 with sign alignment
  load_b    <- mfa_b$quanti.var$coord[, 1]
  sign_flip <- sign(sum(load_b * loadings_orig, na.rm = TRUE))
  loadings_boot[, b] <- load_b * sign_flip
}

## 95% bootstrap CIs for loadings
load_ci_low  <- apply(loadings_boot, 1, quantile, probs = 0.025, na.rm = TRUE)
load_ci_high <- apply(loadings_boot, 1, quantile, probs = 0.975, na.rm = TRUE)

## 95% CIs for eigenvalue 1, and gap/ratio
eig1_ci    <- quantile(eig1_boot,  probs = c(0.025, 0.975), na.rm = TRUE)
gap1_ci    <- quantile(gap1_boot,  probs = c(0.025, 0.975), na.rm = TRUE)
ratio1_ci  <- quantile(ratio1_boot, probs = c(0.025, 0.975), na.rm = TRUE)

eig_orig[1]
ratio1_orig
eig1_ci
# gap1_ci
ratio1_ci
```



<!-- so in summary the diemnsions are valid -->
social vs non social


```{r}

library(FactoMineR)
dta_mfa_part4_wide_complete$social_nonsocial <- dta_mfa_part4_wide$social_nonsocial
# ---- run MFA once ----
idx_grp <- which(names(dta_mfa_part4_wide_complete) == "social_nonsocial")
X       <- dta_mfa_part4_wide_complete[, -idx_grp]
grp     <- dta_mfa_part4_wide_complete[[idx_grp]]

mfa_res <- MFA(X,
               group      = c(420, 60, 60, 180),
               type       = c("s","s","s","s"),
               name.group = c("subj_aff","phys_hr","phys_scr","face"),
               graph      = FALSE)



# ---- extract quantities ----
coord1 <- mod_res$mfa_result_wide_new$ind$coord[, 1]      # Dim 1 scores
contrib1 <- mod_res$mfa_result_wide_new$ind$contrib[, 1]  # Dim 1 contributions

# ---- observed statistics ----
# mean difference in scores

# note permutation tests  require an explicit absolute value for two-sided logic, whereas the standard t-test already comes with that logic built in.
T_coord_obs <- abs(mean(coord1[grp == "social"]) - 
                   mean(coord1[grp == "nonsocial"]))

# median difference in contributions (more robust)
T_contrib_obs <- abs(median(contrib1[grp == "social"]) - 
                     median(contrib1[grp == "nonsocial"]))

# ---- permutation test (integrated) ----
set.seed(1)

B <- 5000
T_coord_sim   <- numeric(B)
T_contrib_sim <- numeric(B)

for (b in 1:B) {
  grp_perm <- sample(grp)

  # recompute both statistics under permuted labels not removed abs in coord
  T_coord_sim[b] <- abs(mean(coord1[grp_perm == "social"]) -
                        mean(coord1[grp_perm == "nonsocial"]))

  T_contrib_sim[b] <- abs(median(contrib1[grp_perm == "social"]) -
                          median(contrib1[grp_perm == "nonsocial"]))
}

# ---- p-values (two-sided via permutation) ----
p_coord   <- mean(T_coord_sim   >= T_coord_obs)
p_contrib <- mean(T_contrib_sim >= T_contrib_obs)

list(
  p_value_coord   = p_coord,
  p_value_contrib = p_contrib
)

# $p_value_coord
# [1] 0.0006
# 
# $p_value_contrib
# [1] 0.421

t.test(coord1 ~ grp)

t.test(dta_mfa_part4_wide$mfa_pc1_contrib ~ dta_mfa_part4_wide$social_nonsocial)
```

Welch Two Sample t-test

data:  coord1 by grp
t = 3.638, df = 84.185, p-value = 0.0004727
alternative hypothesis: true difference in means between group nonsocial and group social is not equal to 0
95 percent confidence interval:
 0.3975154 1.3560049
sample estimates:
mean in group nonsocial    mean in group social 
              0.4188965              -0.4578636 
              
we see differences in dimensions but not in other metrics, contrib, cons, etc



note  shuffling the columns address  structure not group differences. the later needs shufflig labels

USING EIGENVUALUES REQUIRES REFIITING

```{r}


## -----------------------------
## 1. Prepare data and grouping
## -----------------------------
idx_grp <- which(names(dta_mfa_part4_wide_complete) == "social_nonsocial")

# all MFA variables (no group column)
X   <- dta_mfa_part4_wide_complete[, -idx_grp]

# grouping factor: "social" / "nonsocial"
grp <- dta_mfa_part4_wide_complete[[idx_grp]]

## --------------------------------------
## 2. Helper: % variance on first dim
## --------------------------------------
get_dim1_pct <- function(X_sub) {
  mfa_res <- MFA(
    X_sub,
    group      = c(420, 60, 60, 180),
    type       = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    graph      = FALSE
  )
  # column 2 in $eig is % of inertia in FactoMineR
  mfa_res$eig[1, 2]
}

## --------------------------------------
## 3. Observed difference (social vs nonsocial)
## --------------------------------------
dim1_soc_obs <- get_dim1_pct(X[grp == "social", ])
dim1_non_obs <- get_dim1_pct(X[grp == "nonsocial", ])

diff_obs <- abs(dim1_soc_obs - dim1_non_obs)

dim1_soc_obs
dim1_non_obs
diff_obs

## --------------------------------------
## 4. Permutation test: shuffle labels, refit MFA
## --------------------------------------
set.seed(1)
B <- 500

diff_sim <- numeric(B)

for (b in seq_len(B)) {
  # permute social / nonsocial labels
  grp_perm <- sample(grp)

  # permuted groups
  X_soc_b <- X[grp_perm == "social", , drop = FALSE]
  X_non_b <- X[grp_perm == "nonsocial", , drop = FALSE]

  # refit MFA in each permuted group
  dim1_soc_b <- get_dim1_pct(X_soc_b)
  dim1_non_b <- get_dim1_pct(X_non_b)

  # store absolute difference
  diff_sim[b] <- abs(dim1_soc_b - dim1_non_b)
}

## --------------------------------------
## 5. Permutation p-value
## --------------------------------------
p_perm <- mean(diff_sim >= diff_obs)

result_mfa_perm <- list(
  dim1_social_obs     = dim1_soc_obs,
  dim1_nonsocial_obs  = dim1_non_obs,
  diff_obs            = diff_obs,
  p_value_perm        = p_perm,
  diff_sim_range      = range(diff_sim)
)

result_mfa_perm

# SO THE ABSOLUTE EIGEN VALUE DOESNt DIFFER
# perhaps the best way to capture coherence is to see how much of all variables and groups from MFA is acounted by dimension 1, rather than looking at absolute eigenvalues
```

$dim1_social_obs
[1] 10.01993

$dim1_nonsocial_obs
[1] 8.194522

$diff_obs
[1] 1.825403

$p_value_perm
[1] 0.212

$diff_sim_range
[1] 0.0001709709 4.0902212746

lets try co conceptualise coherebnce as the degree to which most variables and blocks allign with the dominant dimenhsion, dim 1
```{r}
 mod_res$mfa_result_wide_new$quanti.var
 mod_res$mfa_result_wide_new$group$


```


```{r}
get_coherence <- function(X_sub) {
  mfa_res <- MFA(
    X_sub,
    group      = c(420, 60, 60, 180),
    type       = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    graph      = FALSE
  )
  
  # variable-level alignment with Dim 1
  cos2_dim1 <- mfa_res$quanti.var$cos2[, 1]
  coh_var   <- mean(cos2_dim1, na.rm = TRUE)  # overall variable–Dim1 coherence
  
  # block-level info (not collapsed, but useful for interpretation)
  block_contrib_dim1 <- mfa_res$group$contrib[, 1]
  
  list(
    coherence_var_dim1   = coh_var,             # main scalar index (0–1)
    block_contrib_dim1   = block_contrib_dim1, # per-block contributions
    dim1_pct_inertia     = mfa_res$eig[1, 2]   # % total inertia on Dim 1 (for context)
  )
}

# observed
idx_grp <- which(names(dta_mfa_part4_wide_complete) == "social_nonsocial")
X   <- dta_mfa_part4_wide_complete[, -idx_grp]
grp <- dta_mfa_part4_wide_complete[[idx_grp]]  # factor: social / nonsocial

# coherence for each group
coh_soc <- get_coherence(X[grp == "social", ]) 
coh_non <- get_coherence(X[grp == "nonsocial", ])

coh_soc$coherence_var_dim1
coh_non$coherence_var_dim1

coh_diff_obs <- abs(coh_soc$coherence_var_dim1 - coh_non$coherence_var_dim1)
coh_diff_obs

# permutation test
set.seed(1)
B <- 500
coh_diff_sim <- numeric(B)

for (b in seq_len(B)) {
  grp_perm <- sample(grp)  # permute social / nonsocial labels
  
  coh_soc_b <- get_coherence(X[grp_perm == "social", ])
  coh_non_b <- get_coherence(X[grp_perm == "nonsocial", ])
  
  coh_diff_sim[b] <- abs(coh_soc_b$coherence_var_dim1 - coh_non_b$coherence_var_dim1)
}

p_coh <- mean(coh_diff_sim >= coh_diff_obs)

result_coherence <- list(
  social_coherence_var_dim1    = coh_soc$coherence_var_dim1,
  nonsocial_coherence_var_dim1 = coh_non$coherence_var_dim1,
  diff_obs                     = coh_diff_obs,
  p_value_perm                 = p_coh,
  sim_diff_range               = range(coh_diff_sim),
  social_block_contrib_dim1    = coh_soc$block_contrib_dim1,
  nonsocial_block_contrib_dim1 = coh_non$block_contrib_dim1,
  social_dim1_pct_inertia      = coh_soc$dim1_pct_inertia,
  nonsocial_dim1_pct_inertia   = coh_non$dim1_pct_inertia
)

result_coherence

```


also no differences, so we don't have structural differences in the degree to which responses are more or less captured by cohrence dimension between social and non social, just that they differ in their location in this dimension (work put the interpretation of locations)

Long format sanity check below, where number of observations will be greater than variables
- we get the same as above, so it's unlikely that our findings above are driven by instability arising from number of varuables > then subjects.


```{r}

 dta_mfa_part4
colnames(dta_mfa_part4)



dta_mfa_part4_imptd <- missMDA::imputeMFA(dta_mfa_part4[,7:18],
                                               ncp=2,
                                                group=c(7, 1, 1, 3),
                          type=c("s","s","s", "s"))


dta_mfa_part4_imptd_cmplt<- dta_mfa_part4_imptd$completeObs


# just the hr, scr, subje, face components
mod_res$mfa_result_long_new <- MFA(dta_mfa_part4_imptd_cmplt,
                         group=c(7, 1, 1, 3),
                         type=c("s","s","s", "s"),
                          name.group= c("subj_aff","phys_hr","phys_scr","face"),
                          # num.group.sup=c(6),#position of group above
                          graph=TRUE)




fviz_contrib(mod_res$mfa_result_long_new, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_long_new, "quanti.var", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_long_new, "quanti.var", axes = 3,top = 10)


fviz_contrib(mod_res$mfa_result_long_new, "group", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_long_new, "group", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_long_new, "group", axes = 3,top = 10)

```



```{r}
dta_mfa_part4$mfa_pc1<- mod_res$mfa_result_long_new$ind$coord[,1]
dta_mfa_part4$mfa_pc2<- mod_res$mfa_result_long_new$ind$coord[,2]
dta_mfa_part4$mfa_pc3<- mod_res$mfa_result_long_new$ind$coord[,3]

dta_mfa_part4$mfa_pc1_contrib<- mod_res$mfa_result_long_new$ind$contrib[,1]
dta_mfa_part4$mfa_pc2_contrib<- mod_res$mfa_result_long_new$ind$contrib[,2]
dta_mfa_part4$mfa_pc3_contrib<- mod_res$mfa_result_long_new$ind$contrib[,3]
# dta_mfa_part4_wide$ma_pc4<- mod_res$mfa_result_wide_new$ind$coord[,4]


dta_mfa_part4$mfa_pc1_cos2 <- mod_res$mfa_result_long_new$ind$cos2[,1]

mod_res$mfa_pc1_lmer <- lmer(mfa_pc1 ~ 1+ social_nonsocial +  
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)


mod_res$mfa_pc1_contrib <- lmer(mfa_pc1_contrib ~ 1+ social_nonsocial +  
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)


mod_res$mfa_pc1_cos2 <- lmer(mfa_pc1_cos2 ~ 1+ social_nonsocial +  
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)

anova(mod_res$mfa_pc1_lmer)
anova(mod_res$mfa_pc1_contrib)

anova(mod_res$mfa_pc1_cos2)
```


```{r}

dta_mfa_part4%>%
  group_by(participant)%>%
  mutate(mfa_pc1 = scale(mfa_pc1))%>%
  group_by(participant, social_nonsocial)%>%
 
  summarise_if(is.numeric, mean, na.rm = T)%>%
   
  ggplot(aes(social_nonsocial, mfa_pc1,colour = social_nonsocial))+
  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


```

dta_mfa_part4%>%
     group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc2,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


```{r}


dta_mfa_part4%>%
     group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc3,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()

```

```{r}

dta_mfa_part4%>%
  # subset(participant!= 105)%>%
  # subset(participant!= 104)%>%
 
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
   
  ggplot(aes(social_nonsocial, mfa_pc1_contrib,colour = social_nonsocial))+
  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()+
  geom_text(aes(label = participant))

dta_mfa_part4%>%
     group_by(participant,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc2_contrib,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4%>%
     group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc3_contrib,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()
```



```{r}

var_names2   <- rownames(mod_res$mfa_result_long_new$quanti.var$coord[,1:2])        


block_groups2 <- c(7, 1, 1, 3)
block_names2  <- c("subj_aff","phys_hr","phys_scr","face")


block_labels2 <- rep(block_names2, times = block_groups2) 

df_plot2 <- data.frame(
  Variable = var_names2,
  Block    = block_labels2,
  Dim1     = mod_res$mfa_result_long_new$quanti.var$coord[,1],
  Dim2     = mod_res$mfa_result_long_new$quanti.var$coord[,2],
  row.names = NULL,
  stringsAsFactors = FALSE
)
df_plot2

# Load ggplot2 (if not already)
library(ggplot2)



df_plot2$dim_1_cos<- mod_res$mfa_result_long_new$quanti.var$cos2[, 1]
df_plot2$dim_2_cos<- mod_res$mfa_result_long_new$quanti.var$cos2[, 2]

df_plot2$dim_1_cont<- mod_res$mfa_result_long_new$quanti.var$contrib[, 1]
df_plot2$dim_2_cont<- mod_res$mfa_result_long_new$quanti.var$contrib[, 2]


df_plot2 <- df_plot2 %>% 
  # (no scaling of Dim1/Dim2 here) 
  mutate(
    cos12_total    = dim_1_cos + dim_2_cos,
    
    # optionally cap or filter out very low cos² if you only want well-represented vars:
    cos12_total2   = if_else(cos12_total < 0.05, NA_real_, cos12_total)
  )


plts<- list()




df_plot2%>%
  # group_by(Block)%>%
  # mutate(Dim1_z = scale(Dim1),
  #        Dim2_z =scale(Dim2))%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot( aes(x = Dim1, y = Dim2)) +

geom_point(
  aes(
    colour = Block,
    shape  = Block,
    size   = cos12_total
  ),
  alpha = 0.3
) +
  # 3) shared axes
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  # coord_fixed(

  scale_colour_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
  # scale_colour_viridis_c(option = "inferno")+
 
  scale_size_continuous(
    range = c(1, 6),
    name  = "Total cos² (Dim1+2)"
  ) +
  ggside::geom_xsidedensity(
    aes(y = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,                       
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE
  )+ 
    ggside::geom_ysidedensity(
    aes(x = after_stat(density),fill = Block),       # density of PC1
    position = "identity",
    alpha    = 0.3,
    size     = 0,
    adjust   = 1.2,                     # smoothing
    show.legend = FALSE)+
  # )+ 
  labs(
    x     = "MFA PC1",
    y     = "MFA PC2",
    title = "Shared axes: size = quality of rep."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", size = 0.2)
  )+
  guides(size = FALSE)

```

note social vs non social differences will allways liely disapear when mfa is fittes separtelly per person, due to normalisatio of between subject differences



```{r}
save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/s4sndata_select.RData")

```