---
title: "social empophys coherence"
author: "helio"
date: "2026-01-15"
output: html_document
---

Prep


```{r}


dta_pca1_3_face_92 <- readRDS(soc_emophys_paths$backup_rdata, "/dta_pca1_3_face_92.rds")

dta_mfa_part1<- dta_emo[,c("val_slider_response","int_slider_response","happy_slide_response","sad_slide_response","fear_slide_response","disgust_slide_response","anger_slide_response","hr_mean_diff","log_cda_iscr","social_nonsocial","participant","stim_iaps",
                           "social_nonsocial", "emotioncategory", "subj_emo_lab_no_amb")]

# colnames(dta_pca1_3_face_92)
dta_pca1_3_face_92$social_nonsocial<- NULL
dta_pca1_3_face_92

dta_mfa_part1$social_nonsocial<- NULL

dta_mfa_part2<- left_join(dta_mfa_part1, dta_pca1_3_face_92, 
                          by = c("participant", "stim_iaps", "subj_emo_lab_no_amb"))


dta_mfa_part2$social_nonsocial<- dta_emo$social_nonsocial
colnames(dta_mfa_part2)

dta_mfa_part3<- dta_mfa_part2[,c(10:15,1:9,130:132, 16:129)]

colnames(dta_mfa_part3)
dta_mfa_part4<- dta_mfa_part3[,1:18]

colnames(dta_emo)

dta_emo_dmg<- dta_emo%>%
  group_by(participant,diagnosis,asd)%>%
  summarise_at(c("tas20_total","dass21_total","dass21_dep", "dass21_anx","dass21_total","obs_slider_response","belief_slider_response","aq28_scale_sum_cont"),
               mean, na.rm = T)

dta_emo_dmg
```

MFA coherence analyes

```{r}
# cast to wide
colnames(dta_mfa_part4)

dta_mfa_part4_wide<- dta_mfa_part4%>%
  select(-filename, subj_emo_lab_no_amb)%>%
 pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),
    values_from = names(dta_mfa_part4[,7:18]),
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )
# rm(dta_emo_wide_mfa)
colnames(dta_mfa_part4_wide[,3:722])

dta_mfa_part4_wide
table(is.na(dta_mfa_part4_wide))
# complete

dta_mfa_part4_wide

# 420+60+60+(60*3)
# 
# 
# 541:600

# imputation
imputedmfa <- missMDA::imputeMFA(dta_mfa_part4_wide[,3:722],
                                               ncp=2,
                                                group=c(420, 60, 60, 180),
                          type=c("s","s","s", "s"))


dta_mfa_part4_wide_complete<- imputedmfa$completeObs

# fit the MFA
# just the hr, scr, subje, face components
mod_res$mfa_result_wide_new <- MFA(dta_mfa_part4_wide_complete,
                         group=c(420, 60, 60, 180),
                         type=c("s","s","s", "s"),
                          name.group= c("subj_aff","phys_hr","phys_scr","face"),
                          # num.group.sup=c(6),#position of group above
                          graph=TRUE)
dta_mfa_part4_wide_complete

mod_res$mfa_result_wide_new$global.pca$var

```

some preliminary visualisations

```{r}
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 3,top = 10)

fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 1,sort.val = "none",ylim = c(0, 60))
fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 2,sort.val = "none",ylim = c(0, 60))
fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 3,sort.val = "none",ylim = c(0, 60))


fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 1, top= 80)
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 2)# 
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 3)

```

store component scores
```{r}
dta_mfa_part4_wide$mfa_pc1<- mod_res$mfa_result_wide_new$ind$coord[,1]
dta_mfa_part4_wide$mfa_pc2<- mod_res$mfa_result_wide_new$ind$coord[,2]
dta_mfa_part4_wide$mfa_pc3<- mod_res$mfa_result_wide_new$ind$coord[,3]

dta_mfa_part4_wide$mfa_pc1_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,1]
dta_mfa_part4_wide$mfa_pc2_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,2]
dta_mfa_part4_wide$mfa_pc3_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,3]
# dta_mfa_part4_wide$ma_pc4<- mod_res$mfa_result_wide_new$ind$coord[,4]

mod_res$mfa_result_wide_new$quanti.var$coord
```

quick prelim vis
```{r}

dta_mfa_part4_wide%>%
  ggplot(aes(social_nonsocial, mfa_pc1,colour = social_nonsocial))+
  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means(method = "t.test")
  # geom_text(aes(label = participant))

dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, mfa_pc2,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, mfa_pc3,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means(".test")





dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc2_contrib+.1),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc3_contrib+.1),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()





```


sanity check - PCA version with equal weight to grupos
Weighted PCA
Give each block equal weight manually:
```{r}

# scale each block so blocks have unit variance contribution
dta_mfa_part4_wide_complete_z <- dta_mfa_part4_wide_complete
blocks <- list(1:420, 421:480, 481:540, 541:720)

for (blk in blocks) {
  # divide by sqrt of mean variance within block
  s <- sqrt(mean(apply(dta_mfa_part4_wide_complete[, blk], 2, var)))
  dta_mfa_part4_wide_complete_z[, blk] <- dta_mfa_part4_wide_complete[, blk] / s
}

mod_res$pca_res <- PCA(dta_mfa_part4_wide_complete_z, scale.unit = TRUE, graph = TRUE)
```

```{r}
fviz_contrib(mod_res$pca_res, "var", axes = 1, top = 15)
fviz_contrib(mod_res$pca_res, "var", axes = 2,top = 10)# 
fviz_contrib(mod_res$pca_res, "var", axes = 3,top = 10)

```


Validation

Randomly permute the rows of the dataset within each group (preserving group structure), recompute MFA, and record the eigenvalues. If the observed eigenvalue for dimension 1 exceeds the distribution of permuted eigenvalues, it is unlikely to arise by chance.


Column-wise null: “no structure at all” (everything is independent)

Goal: test whether there is any real multivariate structure (sanity check).

Here we shuffle rows independently within each column, then compare the λ₁/λ₂ ratio.

this is the permutation test
```{r}
set.seed(123)
# mod_res$mfa_result_wide_new
eig_obs  <- mod_res$mfa_result_wide_new$eig[, 1]
ratio1_obs <- eig_obs[1] / eig_obs[2]

B <- 1000
sim_eig1 <- numeric(B)          # <-- ADD THIS
ratio1_sim_indep <- numeric(B)

for (b in 1:B) {

  dta_perm <- dta_mfa_part4_wide_complete[, 1:720]

  # shuffle each column independently across participants
  for (j in seq_len(ncol(dta_perm))) {
    dta_perm[, j] <- dta_perm[sample(nrow(dta_perm)), j]
  }

  mfa_b <- FactoMineR::MFA(
    dta_perm,
    group      = c(420, 60, 60, 180),
    type       = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    ncp        = 2,
    graph      = FALSE
  )

  eig_b <- mfa_b$eig[, 1]
  sim_eig1[b] <- eig_b[1]                 # <-- STORE EIG1
  ratio1_sim_indep[b] <- eig_b[1] / eig_b[2]
}

p_eig1 <- mean(sim_eig1 >= eig_obs[1])

(sum(sim_eig1 >= eig_obs[1]) + 1) / (B + 1)
p_ratio1_indep <- mean(ratio1_sim_indep >= ratio1_obs)

range(sim_eig1)
p_eig1
p_ratio1_indep


ggplot()+
# ggplot(
  geom_histogram(aes(x = ratio1_sim_indep))+
   geom_vline(xintercept = ratio1_obs[1],
             linetype = "dashed",
             linewidth = 1)



library(ggplot2)
alpha <- 0.05

crit_ratio <- quantile(ratio1_sim_indep, 1 - alpha)

df_ratio <- data.frame(sim = ratio1_sim_indep)

df_ratio$region <- ifelse(df_ratio$sim >= crit_ratio,
                          "α = .05 region", "null")





```

pca sanity check (not for reporting)
```{r}
eig_obs_pca <-mod_res$pca_res$eig[, 1]      # eigenvalues
ratio_obs_pca <- eig_obs[1] / eig_obs[2]   # optional λ1/λ2 ratio


set.seed(123)

B <- 500
sim_eig1_pca  <- numeric(B)
sim_ratio_pca <- numeric(B)

dta_mfa_part4_wide_complete_z

for (b in 1:B) {
  X_perm <- dta_mfa_part4_wide_complete_z
  
  # shuffle each column independently
  for (j in seq_len(ncol(X_perm))) {
    X_perm[, j] <- X_perm[sample(nrow(X_perm)), j]
  }
  
  pca_b <- PCA(X_perm, scale.unit = TRUE, ncp = 2, graph = FALSE)
  eig_b <- pca_b$eig[, 1]
  
  sim_eig1_pca[b]  <- eig_b[1]
  sim_ratio_pca[b] <- eig_b[1] / eig_b[2]
}

p_eig1_pca <- mean(sim_eig1_pca >= eig_obs_pca[1])

p_ratio_pca <- mean(sim_ratio_pca >= ratio_obs_pca)

p_eig1_pca
p_ratio_pca
# consistent with MFA

ggplot()+
# ggplot(
  geom_histogram(aes(x = log(sim_eig1_pca)))+
   geom_vline(xintercept = log(eig_obs_pca[1]),
             linetype = "dashed",
             linewidth = 1)


ggplot()+
# ggplot(
  geom_histogram(aes(x = log(sim_ratio_pca)))+
   geom_vline(xintercept = log(ratio_obs_pca[1]),
             linetype = "dashed",
             linewidth = 1)
  




```


loadings
Compare to a “no structure at all” null (column-wise shuffle)

```{r}

 mod_res$mfa_result_wide_new$quanti.var$coord
# observed statistics
loadings1 <- mod_res$mfa_result_wide_new$quanti.var$coord[, 1]
thr <- 0.3

mean_sq_loading_obs <- mean(loadings1^2)
prop_large_obs      <- mean(abs(loadings1) >= thr)

# permutation under "independent variables" null
set.seed(123)
B <- 500
mean_sq_sim <- numeric(B)
prop_large_sim <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  # shuffle each column independently
  for (j in seq_len(ncol(dta_perm))) {
    dta_perm[, j] <- dta_perm[sample(nrow(dta_perm)), j]
  }
  
  mfa_b <- MFA(dta_perm,
               group      = c(420, 60, 60, 180),
               type       = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               ncp        = 2,
               graph      = FALSE)
  
  load_b <- mfa_b$quanti.var$coord[, 1]
  mean_sq_sim[b]   <- mean(load_b^2)
  prop_large_sim[b] <- mean(abs(load_b) >= thr)
}

# one-sided p-values: is observed larger than null?
p_mean_sq   <- mean(mean_sq_sim   >= mean_sq_loading_obs)
p_prop_large <- mean(prop_large_sim >= prop_large_obs)
range(mean_sq_sim)
range(mean_sq_loading_obs)
range(prop_large_sim)
prop_large_obs
p_mean_sq
p_prop_large

# both alright
# 0
```


#############
Stability
#############
This checks stability of loadings and factor scores.

Idea:
- stability of the latent dimension, i.e. how reproducible is Dim 1 as a participant-level score?
Resample rows with replacement, rerun MFA, and assess:
- correlation between bootstrapped and original axes, same for loadings
- bootMFA (from ExPosition) does this directly but exposition its deprecated;
- so I will do manual bootstrapping:


Issues and fixes

Sign indeterminacy of MFA dimensions
Issue: Bootstrap dimensions can flip sign, lowering correlations.
Fix: Align the sign of the bootstrap Dimension 1 with the original before computing correlations.

Bootstrap duplicates participants
Issue: Correlating bootstrap scores with obs_scores[idx] compares duplicated rows rather than a clean one-to-one mapping.
Fix: Project the full original dataset onto the bootstrap solution and correlate those scores with the original scores.

Score stability ≠ dimension stability
Issue: Correlating individual scores alone does not test whether the dimension structure (variable loadings) is stable.
Fix: Also bootstrap Dimension 1 loadings and correlate bootstrap vs. observed loadings.


loading stability (structure of the dimension) and
score stability (reliability of individual differences).

```{r}

library(FactoMineR)

# loadings stability
library(FactoMineR)

B <- 1000
boot_corrs <- numeric(B)

# Original MFA
mfa_obs <- MFA(
  dta_mfa_part4_wide_complete[, 1:720],
  group = c(420, 60, 60, 180),
  type = c("s", "s", "s", "s"),
  name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
  graph = FALSE
)

# Variable coordinates/loadings for Dimension 1 in the observed solution
obs_loadings <- mfa_obs$quanti.var$coord[, 1]

n <- nrow(dta_mfa_part4_wide_complete)

for (b in seq_len(B)) {
  idx <- sample(seq_len(n), size = n, replace = TRUE)

  mfa_b <- MFA(
    dta_mfa_part4_wide_complete[idx, 1:720],
    group = c(420, 60, 60, 180),
    type = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    graph = FALSE
  )

  boot_loadings <- mfa_b$quanti.var$coord[, 1]

  # Align sign to observed solution
  if (cor(boot_loadings, obs_loadings, use = "pairwise.complete.obs") < 0) {
    boot_loadings <- -boot_loadings
  }

  boot_corrs[b] <- cor(
    boot_loadings,
    obs_loadings,
    use = "pairwise.complete.obs"
  )
}

mean_corr <- mean(boot_corrs, na.rm = TRUE)
ci_corr <- quantile(boot_corrs, probs = c(.025, .975), na.rm = TRUE)

mean_corr
ci_corr



#  participants core stability
B <- 1000
boot_score_corrs <- numeric(B)

X <- scale(dta_mfa_part4_wide_complete[, 1:720])

mfa_obs <- MFA(
  X,
  group = c(420, 60, 60, 180),
  type = c("s", "s", "s", "s"),
  name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
  graph = FALSE
)

obs_scores <- mfa_obs$ind$coord[, 1]
n <- nrow(X)

for (b in seq_len(B)) {
  idx <- sample(seq_len(n), size = n, replace = TRUE)

  mfa_b <- MFA(
    X[idx, ],
    group = c(420, 60, 60, 180),
    type = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    graph = FALSE
  )

  # Use variable coordinates on Dim 1 as weights to score all original cases
  w <- mfa_b$quanti.var$coord[, 1]
  boot_scores_full <- as.numeric(X %*% w)

  # Align sign
  if (cor(boot_scores_full, obs_scores, use = "pairwise.complete.obs") < 0) {
    boot_scores_full <- -boot_scores_full
  }

  boot_score_corrs[b] <- cor(
    boot_scores_full,
    obs_scores,
    use = "pairwise.complete.obs"
  )
}

mean_score_corr <- mean(boot_score_corrs, na.rm = TRUE)
ci_score_corr <- quantile(boot_score_corrs, c(.025, .975), na.rm = TRUE)

mean_score_corr
ci_score_corr

# loadings stability: 
  mean_corr
  # 0.6856942
#   score stability (individuals)
mean_score_corr
# 0.7381403




mean_corr <- mean(boot_corrs, na.rm = TRUE)
ci_corr <- quantile(boot_corrs, probs = c(.025, .975), na.rm = TRUE)

# one-sided p: H0 <= 0, H1 > 0
p_one_sided <- mean(boot_corrs <= 0, na.rm = TRUE)

# two-sided empirical p around 0
p_two_sided <- 2 * min(
  mean(boot_corrs <= 0, na.rm = TRUE),
  mean(boot_corrs >= 0, na.rm = TRUE)
)

mean_corr
ci_corr
p_one_sided
p_two_sided


mean(boot_corrs)
mean(boot_score_corrs)
mean(boot_corrs <= .3, na.rm = TRUE)

mean(boot_score_corrs <= .50, na.rm = TRUE)
```



<!-- so in summary the dimensions are valid, robust and reliable-->
social vs non social


```{r}

library(FactoMineR)
dta_mfa_part4_wide_complete$social_nonsocial <- dta_mfa_part4_wide$social_nonsocial
# ---- run MFA once ----
idx_grp <- which(names(dta_mfa_part4_wide_complete) == "social_nonsocial")
X       <- dta_mfa_part4_wide_complete[, -idx_grp]
grp     <- dta_mfa_part4_wide_complete[[idx_grp]]

mfa_res <- MFA(X,
               group      = c(420, 60, 60, 180),
               type       = c("s","s","s","s"),
               name.group = c("subj_aff","phys_hr","phys_scr","face"),
               graph      = FALSE)



# ---- extract quantities ----
coord1 <- mod_res$mfa_result_wide_new$ind$coord[, 1]      # Dim 1 scores
contrib1 <- mod_res$mfa_result_wide_new$ind$contrib[, 1]  # Dim 1 contributions

# ---- observed statistics ----
# mean difference in scores

# note permutation tests  require an explicit absolute value for two-sided logic, whereas the standard t-test already comes with that logic built in.
T_coord_obs <- abs(mean(coord1[grp == "social"]) - 
                   mean(coord1[grp == "nonsocial"]))

# median difference in contributions (more robust)
T_contrib_obs <- abs(median(contrib1[grp == "social"]) - 
                     median(contrib1[grp == "nonsocial"]))

# ---- permutation test (integrated) ----
set.seed(1)

B <- 5000
T_coord_sim   <- numeric(B)
T_contrib_sim <- numeric(B)

for (b in 1:B) {
  grp_perm <- sample(grp)

  # recompute both statistics under permuted labels not removed abs in coord
  T_coord_sim[b] <- abs(mean(coord1[grp_perm == "social"]) -
                        mean(coord1[grp_perm == "nonsocial"]))

  T_contrib_sim[b] <- abs(median(contrib1[grp_perm == "social"]) -
                          median(contrib1[grp_perm == "nonsocial"]))
}

# ---- p-values (two-sided via permutation) ----
p_coord   <- mean(T_coord_sim   >= T_coord_obs)
p_contrib <- mean(T_contrib_sim >= T_contrib_obs)

list(
  p_value_coord   = p_coord,
  p_value_contrib = p_contrib
)

# $p_value_coord
# [1] 0.0006
# 
# $p_value_contrib
# [1] 0.421

t.test(coord1 ~ grp)

t.test(dta_mfa_part4_wide$mfa_pc1_contrib ~ grp)

install.packages("effectsize")
library(effectsize)

cohens_d(mfa_pc1 ~ grp, data = dta_mfa_part4_wide)
# Cohen's d |       95% CI
# ------------------------
# 0.77      | [0.34, 1.20]
cohens_d(mfa_pc1_contrib ~ grp, data = dta_mfa_part4_wide)
```

Welch Two Sample t-test

data:  coord1 by grp
t = 3.638, df = 84.185, p-value = 0.0004727
alternative hypothesis: true difference in means between group nonsocial and group social is not equal to 0
95 percent confidence interval:
 0.3975154 1.3560049
sample estimates:
mean in group nonsocial    mean in group social 
              0.4188965              -0.4578636 
              
we see differences in dimensions but not in other metrics, contrib, cons, etc





USING EIGENVUALUES REQUIRES REFIITING

```{r}


## -----------------------------
## 1. Prepare data and grouping
## -----------------------------
idx_grp <- which(names(dta_mfa_part4_wide_complete) == "social_nonsocial")

# all MFA variables (no group column)
X   <- dta_mfa_part4_wide_complete[, -idx_grp]

# grouping factor: "social" / "nonsocial"
grp <- dta_mfa_part4_wide_complete[[idx_grp]]

## --------------------------------------
## 2. Helper: % variance on first dim
## --------------------------------------
get_dim1_pct <- function(X_sub) {
  mfa_res <- MFA(
    X_sub,
    group      = c(420, 60, 60, 180),
    type       = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    graph      = FALSE
  )
  # column 2 in $eig is % of inertia in FactoMineR
  mfa_res$eig[1, 2]
}

## --------------------------------------
## 3. Observed difference (social vs nonsocial)
## --------------------------------------
dim1_soc_obs <- get_dim1_pct(X[grp == "social", ])
dim1_non_obs <- get_dim1_pct(X[grp == "nonsocial", ])

diff_obs <- abs(dim1_soc_obs - dim1_non_obs)

dim1_soc_obs
dim1_non_obs
diff_obs

## --------------------------------------
## 4. Permutation test: shuffle labels, refit MFA
## --------------------------------------
set.seed(1)
B <- 500

diff_sim <- numeric(B)

for (b in seq_len(B)) {
  # permute social / nonsocial labels
  grp_perm <- sample(grp)

  # permuted groups
  X_soc_b <- X[grp_perm == "social", , drop = FALSE]
  X_non_b <- X[grp_perm == "nonsocial", , drop = FALSE]

  # refit MFA in each permuted group
  dim1_soc_b <- get_dim1_pct(X_soc_b)
  dim1_non_b <- get_dim1_pct(X_non_b)

  # store absolute difference
  diff_sim[b] <- abs(dim1_soc_b - dim1_non_b)
}

## --------------------------------------
## 5. Permutation p-value
## --------------------------------------
p_perm <- mean(diff_sim >= diff_obs)

result_mfa_perm <- list(
  dim1_social_obs     = dim1_soc_obs,
  dim1_nonsocial_obs  = dim1_non_obs,
  diff_obs            = diff_obs,
  p_value_perm        = p_perm,
  diff_sim_range      = range(diff_sim)
)

result_mfa_perm

# SO THE ABSOLUTE EIGEN VALUE DOESNt DIFFER
# perhaps the best way to capture coherence is to see how much of all variables and groups from MFA is acounted by dimension 1, rather than looking at absolute eigenvalues
```

$dim1_social_obs
[1] 10.01993

$dim1_nonsocial_obs
[1] 8.194522

$diff_obs
[1] 1.825403

$p_value_perm
[1] 0.212

$diff_sim_range
[1] 0.0001709709 4.0902212746

whats the degree  to which most variables and blocks align with the dominant dimenhsion, dim 1 (i.e. is there a diference in quality if representation?)
```{r}
 mod_res$mfa_result_wide_new$quanti.var
 mod_res$mfa_result_wide_new$group$


```


```{r}
get_coherence <- function(X_sub) {
  mfa_res <- MFA(
    X_sub,
    group      = c(420, 60, 60, 180),
    type       = c("s", "s", "s", "s"),
    name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
    graph      = FALSE
  )
  
  # variable-level alignment with Dim 1
  cos2_dim1 <- mfa_res$quanti.var$cos2[, 1]
  coh_var   <- mean(cos2_dim1, na.rm = TRUE)  # overall variable–Dim1 coherence
  
  # block-level info (not collapsed, but useful for interpretation)
  block_contrib_dim1 <- mfa_res$group$contrib[, 1]
  
  list(
    coherence_var_dim1   = coh_var,             # main scalar index (0–1)
    block_contrib_dim1   = block_contrib_dim1, # per-block contributions
    dim1_pct_inertia     = mfa_res$eig[1, 2]   # % total inertia on Dim 1 (for context)
  )
}

# observed
idx_grp <- which(names(dta_mfa_part4_wide_complete) == "social_nonsocial")
X   <- dta_mfa_part4_wide_complete[, -idx_grp]
grp <- dta_mfa_part4_wide_complete[[idx_grp]]  # factor: social / nonsocial

# coherence for each group
coh_soc <- get_coherence(X[grp == "social", ]) 
coh_non <- get_coherence(X[grp == "nonsocial", ])

coh_soc$coherence_var_dim1
coh_non$coherence_var_dim1

coh_diff_obs <- abs(coh_soc$coherence_var_dim1 - coh_non$coherence_var_dim1)
coh_diff_obs

# permutation test
set.seed(1)
B <- 500
coh_diff_sim <- numeric(B)

for (b in seq_len(B)) {
  grp_perm <- sample(grp)  # permute social / nonsocial labels
  
  coh_soc_b <- get_coherence(X[grp_perm == "social", ])
  coh_non_b <- get_coherence(X[grp_perm == "nonsocial", ])
  
  coh_diff_sim[b] <- abs(coh_soc_b$coherence_var_dim1 - coh_non_b$coherence_var_dim1)
}

p_coh <- mean(coh_diff_sim >= coh_diff_obs)

result_coherence <- list(
  social_coherence_var_dim1    = coh_soc$coherence_var_dim1,
  nonsocial_coherence_var_dim1 = coh_non$coherence_var_dim1,
  diff_obs                     = coh_diff_obs,
  p_value_perm                 = p_coh,
  sim_diff_range               = range(coh_diff_sim),
  social_block_contrib_dim1    = coh_soc$block_contrib_dim1,
  nonsocial_block_contrib_dim1 = coh_non$block_contrib_dim1,
  social_dim1_pct_inertia      = coh_soc$dim1_pct_inertia,
  nonsocial_dim1_pct_inertia   = coh_non$dim1_pct_inertia
)

result_coherence

```


also no differences, so we don't have structural differences in the degree to which responses are more or less captured by coherence dimension between social and non social, just that they differ in their location in this dimension

Long format sanity check below, where number of observations will be greater than variables (as pre-reg)
- we get the same as above, so it's unlikely that our findings above are driven by instability arising from number of variables > thann subjects.


```{r}

dta_mfa_part4
colnames(dta_mfa_part4)

dta_mfa_part4_imptd <- missMDA::imputeMFA(dta_mfa_part4[,7:18],
                                               ncp=2,
                                                group=c(7, 1, 1, 3),
                          type=c("s","s","s", "s"))


dta_mfa_part4_imptd_cmplt<- dta_mfa_part4_imptd$completeObs


# just the hr, scr, subje, face components
mod_res$mfa_result_long_new <- MFA(dta_mfa_part4_imptd_cmplt,
                         group=c(7, 1, 1, 3),
                         type=c("s","s","s", "s"),
                          name.group= c("subj_aff","phys_hr","phys_scr","face"),
                          # num.group.sup=c(6),#position of group above
                          graph=TRUE)




fviz_contrib(mod_res$mfa_result_long_new, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_long_new, "quanti.var", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_long_new, "quanti.var", axes = 3,top = 10)


fviz_contrib(mod_res$mfa_result_long_new, "group", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_long_new, "group", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_long_new, "group", axes = 3,top = 10)

```



```{r}
dta_mfa_part4$mfa_pc1<- mod_res$mfa_result_long_new$ind$coord[,1]
dta_mfa_part4$mfa_pc2<- mod_res$mfa_result_long_new$ind$coord[,2]
dta_mfa_part4$mfa_pc3<- mod_res$mfa_result_long_new$ind$coord[,3]

dta_mfa_part4$mfa_pc1_contrib<- mod_res$mfa_result_long_new$ind$contrib[,1]
dta_mfa_part4$mfa_pc2_contrib<- mod_res$mfa_result_long_new$ind$contrib[,2]
dta_mfa_part4$mfa_pc3_contrib<- mod_res$mfa_result_long_new$ind$contrib[,3]
# dta_mfa_part4_wide$ma_pc4<- mod_res$mfa_result_wide_new$ind$coord[,4]


dta_mfa_part4$mfa_pc1_cos2 <- mod_res$mfa_result_long_new$ind$cos2[,1]

mod_res$mfa_pc1_lmer <- lmer(mfa_pc1 ~ 1+ social_nonsocial +  
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)


mod_res$mfa_pc1_lmer <- lmer(mfa_pc1 ~ 1+ social_nonsocial +  
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4$subj)


mod_res$mfa_pc1_contrib <- lmer(mfa_pc1_contrib ~ 1+ social_nonsocial +  
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)


mod_res$mfa_pc1_cos2 <- lmer(mfa_pc1_cos2 ~ 1+ social_nonsocial +  
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_mfa_part4)
require(lmerTest)
library(car)
library(afex)
afex::ano(mod_res$mfa_pc1_lmer)
anova(mod_res$mfa_pc1_contrib)

anova(mod_res$mfa_pc1_cos2)
```


```{r}

dta_mfa_part4%>%
  group_by(participant)%>%
  mutate(mfa_pc1 = scale(mfa_pc1))%>%
  group_by(participant, social_nonsocial)%>%
 
  summarise_if(is.numeric, mean, na.rm = T)%>%
   
  ggplot(aes(social_nonsocial, mfa_pc1,colour = social_nonsocial))+
  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


```



```{r}


dta_mfa_part4%>%
     group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc3,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()

```

```{r}

dta_mfa_part4%>%
  # subset(participant!= 105)%>%
  # subset(participant!= 104)%>%
 
  group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
   
  ggplot(aes(social_nonsocial, mfa_pc1_contrib,colour = social_nonsocial))+
  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()+
  geom_text(aes(label = participant))

dta_mfa_part4%>%
     group_by(participant,social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc2_contrib,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4%>%
     group_by(participant, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(social_nonsocial, mfa_pc3_contrib,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()
```







```{r}
save.image(soc_emophys_paths$cohr_rdata)

```