---
title: "social_emophys_facenmfs w 77 frames"
author: "helio"
date: "2026-01-15"
output: html_document
---


```{r}
# pre-processed face data
dta_face_z_shift_1 <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/dta_face_z_shift_1.Rds")
# 108 below have 77 frames in average for some reason same as 205
dta_face_z_shift_1

require(tidyverse)

dta_face_z_shift_2<- dta_face_z_shift_1%>%
  subset(as.numeric(participant)> 108)%>%
    subset(participant!= "205")



K <- 74
# indices <- floor(seq(1, N, length.out = K))

dta_face_z_shift_2_subs <-

dta_face_z_shift_2 %>%
  group_by(participant,filename)%>%
  arrange(frame,.by_group = TRUE) %>%
  group_modify(~ {
    N <- nrow(.x)                         # .x is the data for this group only
    idx <- floor(seq(1, N, length.out = K))
    .x[idx, ]                             # return the selected rows
  }) %>%
  ungroup()

dta_face_z_shift_1.1<- dta_face_z_shift_1%>%
  subset(as.numeric(participant)< 109)%>%
  bind_rows(dta_face_z_shift_1%>%subset(participant== "205"))

unique(dta_face_z_shift_1.1$participant)

range(dta_face_z_shift_1.1$frame)


dta_face_z_shift_1.1_subs<- dta_face_z_shift_1.1%>%
  subset(frame != 26)%>%
  subset(frame != 52)%>%
   subset(frame != 77)

dta_face_z_shift_3<- dta_face_z_shift_2_subs%>%
  bind_rows(dta_face_z_shift_1.1_subs)



table(dta_face_z_shift_3$participant, dta_face_z_shift_3$stim_iaps)

unique(dta_face_z_shift_3$frame)


dta_face_z_shift_3<- dta_face_z_shift_3%>%
  arrange(filename, frame)%>%
  group_by(filename)%>%
  mutate(bin_frame = 1:n())

unique(dta_face_z_shift_3$bin_frame)
```

# apply NMF
install.packages("NMF")
require(NMF)


What do we want to do

1. Some preprocessing and fit an NMF
2. derive temporal features 
- do some visualisation on specfic features
3. use MFA to group feats by components, and take the first 3 components
4. use PCA to run each component features separatelly and take the first component




```{r}
require(NMF)

unique(dta_face_z_shift_3$participant)
res_k3 <- NMF::nmf(dta_face_z_shift_3[,7:23], r = 3, 
                  nrun = 50, 
                  seed=123456,
                 .options = list( 'v')) 

# some checks
# store components

# k1 = mouth
coefmap(res_k3)

# k2 = small eyes/brows


# k3. =mix upper/lower face

require(NMF)
res_k3@fit
```
basismap(res_k3)


```{r}
dta_face_z_shift_3$nmf_comp1<- as.data.frame(res_k3@fit@W)[,1]
dta_face_z_shift_3$nmf_comp2<- as.data.frame(res_k3@fit@W)[,2]
dta_face_z_shift_3$nmf_comp3<- as.data.frame(res_k3@fit@W)[,3]



options(scipen = 999)
H_matrix<- as.data.frame(res_k3@fit@H)/max(res_k3@fit@H)

H_matrix1<- as.data.frame(t(H_matrix))

colnames(H_matrix1)
H_matrix1$au<- rownames(H_matrix1)

colnames(H_matrix1)

names(H_matrix1)<- c("comp1", "comp2", "comp3", "au")

colnames((H_matrix1))

H_matrix2<- H_matrix1%>%
  mutate(comp1 = comp1/max(comp1),
         comp2 = comp2/max(comp2),
         comp3 = comp3/max(comp3)
         
         )


H_matrix2
```

# some vis
mean
```{r}
dta_face_z_shift_3%>%
  group_by(participant, frame,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)%>%
  ggplot(aes(bin_frame, nmf_comp1, colour = subj_emo_lab_no_amb, group = subj_emo_lab_no_amb))+
  # geom_smooth()+
   stat_summary(fun = mean, geom = "line", linewidth = 1) +

  stat_summary(fun.data = mean_se, geom = "ribbon",
               aes(fill = subj_emo_lab_no_amb),
               alpha = .20, colour = NA)+
  facet_grid(~social_nonsocial)



```




max
```{r}

dta_face_z_shift_3%>%
  group_by(participant,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, max,na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, nmf_comp1, colour = subj_emo_lab_no_amb))+
  geom_jitter(width = .1, alpha = .1)+
 stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)

dta_face_z_shift_3%>%
  group_by(participant,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, max,na.rm = T)%>%
  ggplot(aes(social_nonsocial, nmf_comp2, colour = subj_emo_lab_no_amb))+
  geom_jitter(width = .1, alpha = .1)+
 stat_summary(geom = "pointrange")+
  facet_grid(~subj_emo_lab_no_amb)


dta_face_z_shift_3%>%
  group_by(participant,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, max,na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, log1p(nmf_comp2), colour = subj_emo_lab_no_amb))+
  geom_jitter(width = .1, alpha = .1)+
   stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)


dta_face_z_shift_3%>%
  group_by(participant,subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, max,na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, nmf_comp3, colour = subj_emo_lab_no_amb))+
    geom_jitter(width = .1, alpha = .1)+
   stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)
unique(dta_face_z_shift_3$participant)
# 103, 104, 105, 106, 107, 108, 201, 202, 203, 204, 205
```


aggregated lmer models
```{r}
mod_res<- list()

mod_res
require(lmerTest)



dta_face_z_shift_3_agg <- dta_face_z_shift_3%>%
  group_by(participant,stim_iaps, subj_emo_lab_no_amb,social_nonsocial)%>%
 summarise_if(is.numeric, mean,na.rm = T)




dta_face_z_shift_3_agg

```



2. derive temporal features 
```{r}
# cmfts
# pivot longer
# colnames(dta_face_z_shift_3)

dta_face_z_shift_3_long <- dta_face_z_shift_3 %>%
  pivot_longer(
    cols = nmf_comp1:nmf_comp3,      
    names_to  = "nmf_component",     
    values_to = "nmf_value"          
  )%>%
  select(participant,
         timestamp,
         filename,
         stim_iaps,
         frame,
         bin_frame,
         social_nonsocial,
         subj_emo_lab_no_amb,
         nmf_component,
         nmf_value)

dta_face_z_shift_3_long
```

# create unique timeseries IDs


```{r}


# CREATE a t for frame to avoid number only name columns
dta_face_z_shift_3_long
colnames(dta_face_z_shift_3_long)
dta_face_z_shift_3_long<-  dta_face_z_shift_3_long%>%
  arrange(filename,nmf_component,frame)%>%
  group_by(filename,nmf_component) %>%
  mutate(bin_frame2 = paste0("t_", paste0(bin_frame)))%>%
  ungroup()
 
unique(dta_face_z_shift_3_long$bin_frame)

dta_face_z_shift_3_wid<- dta_face_z_shift_3_long%>%
pivot_wider(
    id_cols    = c(participant,
                  filename,
                  stim_iaps,
                  nmf_component,
                  social_nonsocial,
                  subj_emo_lab_no_amb),
    names_from  = bin_frame2,
    values_from = nmf_value
  )


colnames(dta_face_z_shift_3_wid)

dta_face_z_shift_3_wid
```
  
  
calculate multivariate timeseries features

```{r}

require(CMFMTS)

# ?CMFMTS::cmfmts

dta_face_z_shift_3_wid$filename[300:310]
dta_cmfsts$filename[300:310]

dta_face_z_shift_3_wid$mean_feat <- rowMeans(dta_face_z_shift_3_wid[,7: 80], na.rm = TRUE)
dta_face_z_shift_3_wid$max_feat <- apply(dta_face_z_shift_3_wid[, 7:80], 1, max, na.rm = TRUE)

colnames(dta_face_z_shift_3_wid)

table(is.na(dta_face_z_shift_3_wid[,6:79]))

dta_cmfsts<- CMFMTS::cmfmts(dataset = dta_face_z_shift_3_wid[,7:80]+.01,
                               scale = F,
               na = T 
               # n_cores = 6
               )

dta_face_z_shift_3_wid

colnames(dta_cmfsts)
dta_cmfsts

range(dta_cmfsts$diff1x_pacf5, na.rm = T)
range(scale(dta_cmfsts$diff1x_pacf5), na.rm = T)

```


```{r}
dta_cmfsts<- bind_cols(dta_face_z_shift_3_wid[,1:6], dta_cmfsts)



# drop uninformative timeseries
colnames(dta_cmfsts)

sd_values_pos <- apply(dta_cmfsts[, 7:47], 
                   MARGIN = 2, sd, na.rm = T) # 2 chooses columns and 2 chooses rows


# Identify the columns with a standard deviation of zero
zero_sd_cols_pos <- names(which(sd_values_pos == 0))
zero_sd_cols_pos

# [1] "length"          "nperiods"        "seasonal_period" s

# Drop the columns with a standard deviation of zero
dta_cmfsts2 <- dta_cmfsts%>%select(-zero_sd_cols_pos)

dta_cmfsts2$mean_feat<- dta_face_z_shift_3_wid$mean_feat 
dta_cmfsts2$max_feat<- dta_face_z_shift_3_wid$max_feat 

# dta_cmfsts2


all_na <- sapply(dta_cmfsts2[, 7:44], function(x) all(is.na(x)))
all_na_names<- names(all_na)[all_na]
# "max_kl_shift"  "time_kl_shift"
dta_cmfsts2 <- dta_cmfsts2%>%select(-all_na_names)
all_na_names


colnames(dta_cmfsts2)

corr_mat <- dta_cmfsts2[,7:44] %>%
  cor(use = "pairwise.complete.obs", method = "pearson")


# library(ggplot2)
library(reshape2)

corr_df <- melt(corr_mat, varnames = c("var1", "var2"), value.name = "cor")

ggplot(corr_df, aes(x = var1, y = var2, fill = cor)) +
  geom_tile() +
  scale_fill_gradient2(
    limits = c(-1, 1),
    midpoint = 0,
    name = "r"
  ) +
  coord_fixed() +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1, size = 7),
    axis.text.y = element_text(size = 7),
    axis.title = element_blank(),
    panel.grid = element_blank()
  )



```


just some visualisations of features
```{r}
# dta_cmfsts2

dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, diff1_acf1, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)

dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, diff1_acf10, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)

dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb, entropy, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)


dta_cmfsts2%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial, nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,log1p(time_level_shift+.1), colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~nmf_component)


  

```


order features for PCA
```{r}
dta_cmfsts2
colnames(dta_cmfsts2)



# 35 featureleft_join(
dta_cmfsts3_wid<- dta_cmfsts2 %>%  
  arrange(nmf_component) %>%
  pivot_wider(
    id_cols = c(participant,
                filename,
                stim_iaps,
                social_nonsocial,
                subj_emo_lab_no_amb),
    names_from  = nmf_component,              # values in this col become suffixes
    values_from = c(lempel_ziv:max_feat),  # c
    names_glue = "{nmf_component}_{.value}"   # e.g. lempel_ziv_comp1
  )

# colnames(dta_cmfsts3_wid)
id_cols <- c("participant",
             "filename",
             "stim_iaps",
             "social_nonsocial",
             "subj_emo_lab_no_amb")

# get component levels in the order you want
comp_levels <- sort(unique(dta_cmfsts2$nmf_component))
# e.g. c("nmf_comp1", "nmf_comp2", "nmf_comp3")

# build column order: comp1_* then comp2_* then comp3_*, etc.
feature_cols_ordered <- unlist(
  lapply(comp_levels, function(comp) {
    prefix <- paste0(comp, "_")
    grep(paste0("^", prefix), names(dta_cmfsts3_wid), value = TRUE)
  })
)

# reorder columns
dta_cmfsts3_wid <- dta_cmfsts3_wid[, c(id_cols, feature_cols_ordered)]

colnames(dta_cmfsts3_wid)
```



pca models
inlcude min max as additionak features
```{r}
# 35 features left
colnames(dta_cmfsts3_wid)
# ?FactoMineR::MFA()
require(FactoMineR)



dta_cmfsts3_wid_complete<- as.data.frame(dta_cmfsts3_wid)


dta_cmfsts3_wid_complete<- dta_cmfsts3_wid_complete %>%
  mutate(across(6:119, ~ if(is.numeric(.)) replace(., !is.finite(.), NA) else .))


dta_cmfsts3_wid_complete2 <- missMDA::imputeMFA(dta_cmfsts3_wid_complete[,6:119],
                                               ncp=2,
                                                group=c(38, 38, 38),
                          type=c("s","s","s"))




```



pca version inclding man and max features


```{r}
length(39:76)
colnames(dta_cmfsts3_wid_complete2$completeObs)
comp1_idx <- 1:38
comp2_idx <- 39:76
comp3_idx <- 77:114

# PCA for each component block (on imputed data)
dta_cmfsts3_wid_complete2$completeObs
```


```{r}
mod_res$pca_comp1.2 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp1_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp2.2 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp2_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp3.2 <- FactoMineR::PCA(dta_cmfsts3_wid_complete2$completeObs[,comp3_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)


dta_cmfsts3_wid$pc_comp1.2<- mod_res$pca_comp1.2$ind$coord[,1]
dta_cmfsts3_wid$pc_comp2.2<- mod_res$pca_comp2.2$ind$coord[,1]
dta_cmfsts3_wid$pc_comp3.2<- mod_res$pca_comp3.2$ind$coord[,1]

```


```{r}
# require(factoextra)
fviz_contrib(mod_res$pca_comp1.2, "var", axes = 1, top = 5)
fviz_contrib(mod_res$pca_comp2.2, "var", axes = 1,top = 5)# 
fviz_contrib(mod_res$pca_comp3.2, "var", axes = 1,top = 5)
```

```{r}
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp1.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)

dta_cmfsts3_wid %>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,nmf_comp2_shannon_entropy_CS, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")



dta_cmfsts3_wid %>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp1.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")




dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp2.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
dta_cmfsts3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pc_comp3.2, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")

```

looks similar to data w/ the 77 frames folks 
lmer models on pca with mean and max features
```{r}

mod_res$pc_comp1.2.lmer <- lmer(pc_comp1.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)


mod_res$pc_comp2.2.lmer <- lmer(pc_comp2.2 ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)




mod_res$pc_comp3.2.lmer <- lmer(pc_comp3.2  ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid)

colnames(dta_cmfsts3_wid)

```

```{r}

anova(mod_res$pc_comp1.2.lmer)
anova(mod_res$pc_comp2.2.lmer)
anova(mod_res$pc_comp3.2.lmer)

```

Type III Analysis of Variance Table with Satterthwaite's method
                                      Sum Sq Mean Sq NumDF  DenDF F value    Pr(>F)
social_nonsocial                       0.757  0.7572     1   92.7  0.1040 0.7477564
subj_emo_lab_no_amb                  155.544 31.1088     5  493.8  4.2746 0.0008148
social_nonsocial:subj_emo_lab_no_amb  62.519 12.5039     5 5406.8  1.7181 0.1267525
                                        
social_nonsocial                        
subj_emo_lab_no_amb                  ***
social_nonsocial:subj_emo_lab_no_amb    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Warning: The working directory was changed to /Users/pw22812 inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
Type III Analysis of Variance Table with Satterthwaite's method
                                     Sum Sq Mean Sq NumDF  DenDF F value    Pr(>F)    
social_nonsocial                      18.42  18.420     1   92.7  3.3518 0.0703424 .  
subj_emo_lab_no_amb                  121.16  24.232     5  729.3  4.4095 0.0005802 ***
social_nonsocial:subj_emo_lab_no_amb 124.17  24.834     5 5400.8  4.5189 0.0004107 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
Type III Analysis of Variance Table with Satterthwaite's method
                                     Sum Sq Mean Sq NumDF  DenDF F value  Pr(>F)  
social_nonsocial                     18.371 18.3710     1   93.8  2.6917 0.10422  
subj_emo_lab_no_amb                  87.346 17.4692     5  487.8  2.5596 0.02666 *
social_nonsocial:subj_emo_lab_no_amb 33.312  6.6625     5 5419.4  0.9762 0.43069 

similar to data withoith 77 frame folks

```{r}

emmeans::emmeans(mod_res$pc_comp1.2.lmer, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$pc_comp2.2.lmer, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")


emmeans::emmeans(mod_res$pc_comp3.2.lmer, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$pc_comp2.2.lmer, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "tukey")
emmeans::emmeans(mod_res$pc_comp2.2.lmer, pairwise ~ subj_emo_lab_no_amb|social_nonsocial, 
                 adjust = "tukey")
```

$emmeans
 subj_emo_lab_no_amb   emmean    SE  df asymp.LCL asymp.UCL
 anger               -0.18689 0.339 Inf    -0.851     0.477
 disgust              0.33004 0.313 Inf    -0.283     0.943
 fear                -0.13205 0.322 Inf    -0.763     0.499
 happy               -0.00507 0.311 Inf    -0.615     0.605
 neutral             -0.12261 0.318 Inf    -0.747     0.501
 sad                 -0.16117 0.318 Inf    -0.784     0.462

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate    SE  df z.ratio p.value
 anger - disgust   -0.51693 0.176 Inf  -2.933  0.0393
 anger - fear      -0.05484 0.190 Inf  -0.289  0.9997
 anger - happy     -0.18183 0.177 Inf  -1.028  0.9089
 anger - neutral   -0.06428 0.189 Inf  -0.340  0.9994
 anger - sad       -0.02572 0.182 Inf  -0.141  1.0000
 disgust - fear     0.46209 0.142 Inf   3.252  0.0146
 disgust - happy    0.33511 0.119 Inf   2.814  0.0552
 disgust - neutral  0.45265 0.136 Inf   3.322  0.0115
 disgust - sad      0.49121 0.133 Inf   3.701  0.0029
 fear - happy      -0.12698 0.139 Inf  -0.912  0.9437
 fear - neutral    -0.00944 0.154 Inf  -0.061  1.0000
 fear - sad         0.02912 0.152 Inf   0.192  1.0000
 happy - neutral    0.11754 0.130 Inf   0.906  0.9450
 happy - sad        0.15611 0.131 Inf   1.189  0.8425
 neutral - sad      0.03856 0.146 Inf   0.264  0.9998

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
P value adjustment: tukey method for comparing a family of 6 estimates 

Warning: The working directory was changed to /Users/pw22812 inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5520' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5520' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.
NOTE: Results may be misleading due to involvement in interactions
$emmeans
 subj_emo_lab_no_amb  emmean    SE  df asymp.LCL asymp.UCL
 anger                0.0105 0.294 Inf    -0.566     0.588
 disgust              0.2930 0.272 Inf    -0.239     0.825
 fear                -0.0325 0.279 Inf    -0.580     0.515
 happy               -0.1818 0.270 Inf    -0.711     0.348
 neutral             -0.2020 0.276 Inf    -0.742     0.338
 sad                 -0.0276 0.276 Inf    -0.569     0.513

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate    SE  df z.ratio p.value
 anger - disgust   -0.28247 0.158 Inf  -1.793  0.4704
 anger - fear       0.04304 0.168 Inf   0.256  0.9999
 anger - happy      0.19231 0.160 Inf   1.202  0.8362
 anger - neutral    0.21250 0.167 Inf   1.270  0.8016
 anger - sad        0.03818 0.161 Inf   0.237  0.9999
 disgust - fear     0.32551 0.130 Inf   2.509  0.1214
 disgust - happy    0.47478 0.113 Inf   4.207  0.0004
 disgust - neutral  0.49498 0.124 Inf   3.986  0.0010
 disgust - sad      0.32066 0.122 Inf   2.630  0.0902
 fear - happy       0.14927 0.127 Inf   1.174  0.8496
 fear - neutral     0.16947 0.136 Inf   1.246  0.8142
 fear - sad        -0.00485 0.136 Inf  -0.036  1.0000
 happy - neutral    0.02020 0.115 Inf   0.175  1.0000
 happy - sad       -0.15412 0.122 Inf  -1.262  0.8057
 neutral - sad     -0.17432 0.131 Inf  -1.329  0.7689

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
P value adjustment: tukey method for comparing a family of 6 estimates 

Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5520' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5520' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.
NOTE: Results may be misleading due to involvement in interactions
$emmeans
 subj_emo_lab_no_amb   emmean    SE  df asymp.LCL asymp.UCL
 anger                0.00905 0.236 Inf    -0.453     0.471
 disgust             -0.21663 0.199 Inf    -0.606     0.173
 fear                -0.05366 0.212 Inf    -0.469     0.362
 happy                0.11718 0.197 Inf    -0.268     0.503
 neutral              0.19356 0.207 Inf    -0.212     0.599
 sad                  0.05725 0.206 Inf    -0.347     0.461

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
 contrast          estimate    SE  df z.ratio p.value
 anger - disgust     0.2257 0.171 Inf   1.324  0.1857
 anger - fear        0.0627 0.184 Inf   0.341  0.7329
 anger - happy      -0.1081 0.171 Inf  -0.632  0.5276
 anger - neutral    -0.1845 0.183 Inf  -1.011  0.3122
 anger - sad        -0.0482 0.177 Inf  -0.273  0.7848
 disgust - fear     -0.1630 0.137 Inf  -1.185  0.2359
 disgust - happy    -0.3338 0.115 Inf  -2.899  0.0037
 disgust - neutral  -0.4102 0.132 Inf  -3.115  0.0018
 disgust - sad      -0.2739 0.128 Inf  -2.133  0.0329
 fear - happy       -0.1708 0.135 Inf  -1.268  0.2048
 fear - neutral     -0.2472 0.149 Inf  -1.661  0.0968
 fear - sad         -0.1109 0.147 Inf  -0.756  0.4499
 happy - neutral    -0.0764 0.125 Inf  -0.609  0.5422
 happy - sad         0.0599 0.127 Inf   0.472  0.6371
 neutral - sad       0.1363 0.141 Inf   0.966  0.3338

Results are averaged over the levels of: social_nonsocial 
Degrees-of-freedom method: asymptotic 

Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5520' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5520' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.
$emmeans
subj_emo_lab_no_amb = anger:
 social_nonsocial   emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.53022 0.400 Inf    -0.254   1.31425
 social           -0.50915 0.425 Inf    -1.342   0.32409

subj_emo_lab_no_amb = disgust:
 social_nonsocial   emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.58067 0.372 Inf    -0.149   1.31000
 social            0.00535 0.389 Inf    -0.756   0.76716

subj_emo_lab_no_amb = fear:
 social_nonsocial   emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.23576 0.382 Inf    -0.512   0.98388
 social           -0.30076 0.401 Inf    -1.087   0.48530

subj_emo_lab_no_amb = happy:
 social_nonsocial   emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.44740 0.370 Inf    -0.279   1.17336
 social           -0.81094 0.387 Inf    -1.569  -0.05241

subj_emo_lab_no_amb = neutral:
 social_nonsocial   emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.37260 0.381 Inf    -0.374   1.11945
 social           -0.77653 0.394 Inf    -1.549  -0.00416

subj_emo_lab_no_amb = sad:
 social_nonsocial   emmean    SE  df asymp.LCL asymp.UCL
 nonsocial         0.55686 0.379 Inf    -0.185   1.29909
 social           -0.61215 0.394 Inf    -1.385   0.16071

Degrees-of-freedom method: asymptotic 
Confidence level used: 0.95 

$contrasts
subj_emo_lab_no_amb = anger:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    1.039 0.579 Inf   1.796  0.0725

subj_emo_lab_no_amb = disgust:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.575 0.533 Inf   1.080  0.2802

subj_emo_lab_no_amb = fear:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    0.537 0.549 Inf   0.977  0.3284

subj_emo_lab_no_amb = happy:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    1.258 0.531 Inf   2.370  0.0178

subj_emo_lab_no_amb = neutral:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    1.149 0.545 Inf   2.108  0.0350

subj_emo_lab_no_amb = sad:
 contrast           estimate    SE  df z.ratio p.value
 nonsocial - social    1.169 0.541 Inf   2.159  0.0308

Degrees-of-freedom method: asymptotic 

Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'pbkrtest.limit = 5520' (or larger)
[or, globally, 'set emm_options(pbkrtest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.
Note: D.f. calculations have been disabled because the number of observations exceeds 3000.
To enable adjustments, add the argument 'lmerTest.limit = 5520' (or larger)
[or, globally, 'set emm_options(lmerTest.limit = 5520)' or larger];
but be warned that this may result in large computation time and memory use.


```{r}
setwd(soc_emophys_paths$backup_rdata)
save.image("social_emophys_facenmfs_77frames.RData")
saveRDS(dta_cmfsts3_wid, "dta_pca1_3_face_92.rds")
```

can I get a single PCA

 

technical check
use the to derive features directly then average features per NMF group

```{r}
# (dta_face_z_shift_3[,7:23], r = 3, 
 
 colnames(dta_face_z_shift_3)

dta_face_z_shift_3_long_aus <- dta_face_z_shift_3 %>%
  pivot_longer(
    cols = au01_r_smt:au45_r_smt,      
    names_to  = "au_code",     
    values_to = "au_value"          
  )%>%
  select(participant,
         timestamp,
         filename,
         stim_iaps,
         frame,
         bin_frame,
         social_nonsocial,
         subj_emo_lab_no_amb,
         au_code,
         au_value)

dta_face_z_shift_3_long_aus
```

# create unique timeseries IDs


```{r}


# CREATE a t for frame to avoid number only name columns
dta_face_z_shift_3_long_aus

dta_face_z_shift_3_long_aus<-  dta_face_z_shift_3_long_aus%>%
  arrange(filename,au_code,au_value)%>%
  group_by(filename,au_code) %>%
  mutate(bin_frame2 = paste0("t_", paste0(bin_frame)))%>%
  ungroup()
 
unique(dta_face_z_shift_3_long_aus$bin_frame)

dta_face_z_shift_3_wid_aus<- dta_face_z_shift_3_long_aus%>%
pivot_wider(
    id_cols    = c(participant,
                  filename,
                  stim_iaps,
                  au_code,
                  social_nonsocial,
                  subj_emo_lab_no_amb),
    names_from  = bin_frame2,
    values_from = au_value
  )


colnames(dta_face_z_shift_3_wid)

dta_face_z_shift_3_wid_aus
```
  
  
calculate multivariate timeseries features

```{r}

require(CMFMTS)

# ?CMFMTS::cmfmts

dta_face_z_shift_3_wid_aus$filename[300:310]


df <- dta_face_z_shift_3_wid_aus  # rename as needed

# find columns that match "t_<number>"
t_cols <- grep("^t_\\d+$", names(df), value = TRUE)

# extract numbers after "t_"
t_nums <- as.numeric(sub("t_", "", t_cols))

# order t_cols by those numbers
t_cols_sorted <- t_cols[order(t_nums)]

# now rebuild data with sorted t_ columns
other_cols <- setdiff(names(df), t_cols)

dta_face_z_shift_3_wid_aus <- dta_face_z_shift_3_wid_aus[, c(other_cols, t_cols_sorted)]
dta_face_z_shift_3_wid_aus$mean_feat <-NULL

dta_face_z_shift_3_wid_aus$max_feat<- NULL 
colnames(dta_face_z_shift_3_wid_aus)
dta_face_z_shift_3_wid_aus$mean_feat <- rowMeans(dta_face_z_shift_3_wid_aus[,7: 80], na.rm = TRUE)
dta_face_z_shift_3_wid_aus$max_feat <- apply(dta_face_z_shift_3_wid_aus[, 7:80], 1, max, na.rm = TRUE)


dta_face_z_shift_3_wid_aus
colnames(dta_face_z_shift_3_wid_aus)
table(is.na(dta_face_z_shift_3_wid_aus[,7:80]))

dta_cmfsts_aus<- CMFMTS::cmfmts(dataset = dta_face_z_shift_3_wid_aus[,7:80]+.01,
                               scale = F,
               na = T ,
               n_cores = 8
               )



dta_cmfsts_aus
```
```{r}
dta_cmfsts_aus<- bind_cols(dta_face_z_shift_3_wid_aus[,1:6], dta_cmfsts_aus)



# drop uninformative timeseries
colnames(dta_cmfsts_aus)

sd_values_pos <- apply(dta_cmfsts_aus[, 7:47], 
                   MARGIN = 2, sd, na.rm = T) # 2 chooses columns and 2 chooses rows


# Identify the columns with a standard deviation of zero
zero_sd_cols_pos <- names(which(sd_values_pos == 0))
zero_sd_cols_pos

# [1] "length"          "nperiods"        "seasonal_period" s

# Drop the columns with a standard deviation of zero
dta_cmfsts_aus2 <- dta_cmfsts_aus%>%select(-zero_sd_cols_pos)
dta_cmfsts_aus
dta_cmfsts_aus2$mean_feat<- dta_face_z_shift_3_wid_aus$mean_feat 
dta_cmfsts_aus2$max_feat<- dta_face_z_shift_3_wid_aus$max_feat 

# dta_cmfsts2

colnames(dta_cmfsts_aus2)
all_na <- sapply(dta_cmfsts_aus2[, 7:44], function(x) all(is.na(x)))
all_na_names<- names(all_na)[all_na]
all_na_names
# "max_kl_shift"  "time_kl_shift"
dta_cmfsts_aus2 <- dta_cmfsts_aus2%>%select(-all_na_names)


```





```{r}
colnames(dta_cmfsts_aus2)
```
```{r}

corr_mat2 <- dta_cmfsts_aus2[,7:44] %>%
  cor(use = "pairwise.complete.obs", method = "pearson")


# library(ggplot2)
library(reshape2)

corr_df_2 <- melt(corr_mat2, varnames = c("var1", "var2"), value.name = "cor")

ggplot(corr_df_2, aes(x = var1, y = var2, fill = cor)) +
  geom_tile() +
  scale_fill_gradient2(
    limits = c(-1, 1),
    midpoint = 0,
    name = "r"
  ) +
  coord_fixed() +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1, size = 7),
    axis.text.y = element_text(size = 7),
    axis.title = element_blank(),
    panel.grid = element_blank()
  )
  
```


  
AVERAGE FEATURES PER AU GROUP BASED ON NMF

```{r}

coefmap( res_k3)
dta_cmfsts_aus2
options()
res_k3@fit@H
```
```{r}
# lookup table as a named vector
au_to_component <- c(
  "au04_r_smt" = 2,
  "au07_r_smt" = 2,
  "au14_r_smt" = 1,
   "au10_r_smt" = 1,
  "au12_r_smt" = 1,
  "au06_r_smt" = 1,
  "au23_r_smt" = 3,
  "au09_r_smt" = 3,
  "au45_r_smt" = 3,
  "au20_r_smt" = 3,
  "au05_r_smt" = 3,
  "au02_r_smt" = 3,
  "au01_r_smt" = 3,
  "au17_r_smt" = 3,
  "au15_r_smt" = 3,
  "au25_r_smt" = 3,
  "au26_r_smt" = 3
)

dta_cmfsts_aus2$nmf_component <- ifelse(
  dta_cmfsts_aus2$au_code %in% names(au_to_component),
  au_to_component[dta_cmfsts_aus2$au_code],
  NA
)

unique(dta_cmfsts_aus2$nmf_component)

table(is.na(dta_cmfsts_aus2$nmf_component))
dta_cmfsts_aus2$nmf_component<- au_to_component(dta_cmfsts_aus2$au_code)

dta_cmfsts_aus2

dta_cmfsts_aus3<- dta_cmfsts_aus2%>%
  group_by(participant, filename,stim_iaps,social_nonsocial,subj_emo_lab_no_amb,nmf_component)%>%
  summarise_if(is.numeric, mean, na.rm = T)


dta_cmfsts_aus3
colnames(dta_cmfsts_aus3)


```



# now visualise some examples

```{r}
dta_cmfsts_aus3%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(subj_emo_lab_no_amb,log1p(time_level_shift+.1), colour = social_nonsocial))+
   geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")


dta_cmfsts_aus3%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(subj_emo_lab_no_amb,log1p(max_feat+.1), colour = social_nonsocial))+
   geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")


dta_cmfsts_aus3%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
ggplot(aes(subj_emo_lab_no_amb,log1p(curvature+.1), colour = social_nonsocial))+
   geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")


```
# dcast compponents
# pca on each compoennt


  THEN PCA
```{r}

colnames(dta_cmfsts_aus3)

dta_cmfsts_aus3$nmf_component_au<- if_else(dta_cmfsts_aus3$nmf_component ==1, "comp1",
                                        if_else(dta_cmfsts_aus3$nmf_component ==2, "comp2",  
                                           if_else(dta_cmfsts_aus3$nmf_component ==3, "comp3",NA)))

unique(dta_cmfsts_aus3$nmf_component_au)
dta_cmfsts_aus3$nmf_component<- NULL

dta_cmfsts_aus3_wid<- dta_cmfsts_aus3 %>%  
  arrange(nmf_component_au) %>%
  pivot_wider(
    id_cols = c(participant,
                filename,
                stim_iaps,
                social_nonsocial,
                subj_emo_lab_no_amb),
    names_from  = nmf_component_au,              # values in this col become suffixes
    values_from = c(lempel_ziv:max_feat),  # c
    names_glue = "{nmf_component_au}_{.value}"   # e.g. lempel_ziv_comp1
  )

colnames(dta_cmfsts_aus3_wid)

id_cols <- c("participant",
             "filename",
             "stim_iaps",
             "social_nonsocial",
             "subj_emo_lab_no_amb")

# get component levels in the order you want
comp_levels_au <- sort(unique(dta_cmfsts_aus3$nmf_component_au))
# e.g. c("nmf_comp1", "nmf_comp2", "nmf_comp3")

# build column order: comp1_* then comp2_* then comp3_*, etc.
feature_cols_ordered_au <- unlist(
  lapply(comp_levels_au, function(comp) {
    prefix <- paste0(comp, "_")
    grep(paste0("^", prefix), names(dta_cmfsts_aus3_wid), value = TRUE)
  })
)



# reorder columns
dta_cmfsts_aus3_wid <- dta_cmfsts_aus3_wid[, c(id_cols, feature_cols_ordered_au)]

colnames(dta_cmfsts_aus3_wid)
```



pca models

```{r}

colnames(dta_cmfsts_aus3_wid)
# ?FactoMineR::MFA()
require(FactoMineR)



dta_cmfsts_aus3_wid_complete<- as.data.frame(dta_cmfsts_aus3_wid)
colnames(dta_cmfsts_aus3_wid_complete)




dta_cmfsts_aus3_wid_complete<- dta_cmfsts_aus3_wid_complete %>%
  mutate(across(6:119, ~ if(is.numeric(.)) replace(., !is.finite(.), NA) else .))


dta_cmfsts_aus3_wid_complete2 <- missMDA::imputeMFA(dta_cmfsts_aus3_wid_complete[,6:119],
                                               ncp=2,
                                                group=c(38, 38, 38),
                          type=c("s","s","s"))




```



pca version inclding man and max features


```{r}
length(39:76)
colnames(dta_cmfsts_aus3_wid_complete2$completeObs)
comp1_idx <- 1:38
comp2_idx <- 39:76
comp3_idx <- 77:114

# PCA for each component block (on imputed data)
dta_cmfsts_aus3_wid_complete2$completeObs
```


```{r}
mod_res$pca_comp1_au <- FactoMineR::PCA(dta_cmfsts_aus3_wid_complete2$completeObs[,comp1_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp2_au <- FactoMineR::PCA(dta_cmfsts_aus3_wid_complete2$completeObs[,comp2_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)

mod_res$pca_comp3_au <- FactoMineR::PCA(dta_cmfsts_aus3_wid_complete2$completeObs[,comp3_idx],
  scale.unit = TRUE,
  ncp        = 1,
  graph      = TRUE
)


dta_cmfsts_aus3_wid$pca_comp1_au<- mod_res$pca_comp1_au$ind$coord[,1]
dta_cmfsts_aus3_wid$pca_comp2_au<- mod_res$pca_comp2_au$ind$coord[,1]
dta_cmfsts_aus3_wid$pca_comp3_au<- mod_res$pca_comp3_au$ind$coord[,1]

```


```{r}
# require(factoextra)
fviz_contrib(mod_res$pca_comp1.2, "var", axes = 1, top = 5)
fviz_contrib(mod_res$pca_comp2.2, "var", axes = 1,top = 5)# 
fviz_contrib(mod_res$pca_comp3.2, "var", axes = 1,top = 5)

fviz_contrib(mod_res$pca_comp1_au, "var", axes = 1, top = 5)
fviz_contrib(mod_res$pca_comp2_au, "var", axes = 1,top = 5)# 
fviz_contrib(mod_res$pca_comp3_au, "var", axes = 1,top = 5)
```

```{r}
dta_cmfsts_aus3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pca_comp1_au, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)

dta_cmfsts_aus3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pca_comp2_au, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")
  # facet_grid(~social_nonsocial)
dta_cmfsts_aus3_wid%>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(subj_emo_lab_no_amb,pca_comp3_au, colour = social_nonsocial))+
  geom_jitter(width= .1, alpha = .1)+
  stat_summary(geom = "pointrange")

```

looks similar to daat w/ the 77 frames folks 
lmer models on pca with mean and max features
```{r}

mod_res$pca_comp1_au_lmer <- lmer(pca_comp1_au ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts_aus3_wid)


mod_res$pca_comp2_au_lmer <- lmer(pca_comp2_au ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts_aus3_wid)




mod_res$pca_comp3_au_lmer <- lmer(pca_comp3_au  ~ 1+ social_nonsocial * subj_emo_lab_no_amb + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts_aus3_wid)



```

```{r}

anova(mod_res$pca_comp1_au_lmer)
anova(mod_res$pca_comp2_au_lmer)
anova(mod_res$pca_comp3_au_lmer)


```



```{r}

emmeans::emmeans(mod_res$pca_comp1_au_lmer, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$pca_comp2_au_lmer, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")

emmeans::emmeans(mod_res$pca_comp3_au_lmer, pairwise ~ subj_emo_lab_no_amb, 
                 adjust = "tukey")


emmeans::emmeans(mod_res$pca_comp2_au_lmer, pairwise ~ social_nonsocial|subj_emo_lab_no_amb, 
                 adjust = "none")


emmeans::emmeans(mod_res$pca_comp2_au_lmer, pairwise ~ subj_emo_lab_no_amb|social_nonsocial, 
                 adjust = "tukey")


save.image("social_emophys_facenmfs_77frames.RData")

```




