---
title: "subjective affect vis"
author: "helio"
date: "2026-02-19"
output: html_document
---

starting point: jays subjective plots

associated data: load("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/Mixed_models_output_JD.RData")
associated scripts: Mixed_models_Analysis_JD.Rmd

```{r plot}
#combined plots 
#raw data points per ppt
valence_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb) %>%
   summarise(
    mean = mean(val_slider_response, na.rm = TRUE),
    sd   = sd(val_slider_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop"
  )

#summary stats 
valence_agg_means2 <- subjective_data %>%
  group_by(social_nonsocial, subj_emo_lab_no_amb) %>%
  summarise(
    mean = mean(val_slider_response, na.rm = TRUE),
    sd   = sd(val_slider_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)


valence_df2   <- as.data.frame(valence_emm2)   %>% mutate(model = "Valence")
intensity_df2 <- as.data.frame(intensity_emm2) %>% mutate(model = "Intensity")

social_x_valence <- ggplot(valence_agg_means, aes(x = social_nonsocial, y = mean, colour = social_nonsocial, shape = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 2, alpha = 0.15) +
   geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # summary mean points
  geom_point(data = valence_agg_means2, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial),
             size = 2, inherit.aes = FALSE) +
  # summary error bars
  geom_errorbar(data = valence_agg_means2, aes(x = social_nonsocial, y = mean, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial,shape = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ subj_emo_lab_no_amb, nrow = 1) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Valence (Mean)", colour = "") +
  theme_classic(base_size = 14) +
 p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top", legend.title = element_blank() 
         # strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )

  
  

social_x_valence

# side density data
df_plot_valence <- subjective_data %>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise(mean = mean(val_slider_response, na.rm = TRUE), .groups = "drop")

y_lim_valence <- range(df_plot_valence$mean, na.rm = TRUE)

plts$valence_soc_dens <- ggplot(df_plot_valence,
  aes(y = mean, fill = social_nonsocial)) +
  geom_density(aes(x = after_stat(density)), orientation = "y",
               alpha = 0.25, colour = NA) +
  scale_fill_brewer(palette = "Dark2") +
  coord_cartesian(ylim = y_lim_valence) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")

# top emotion summary
plts$valence_emo_top <- df_plot_valence %>%
  group_by(subj_emo_lab_no_amb) %>%
  ggplot(aes(subj_emo_lab_no_amb, mean)) +
  stat_summary(geom = "pointrange", fun.data = mean_se) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

# patchwork
plts$valence_p1 <- (plts$valence_emo_top | plot_spacer()) +
  plot_layout(widths = c(5, 1))

plts$valence_p2 <- (social_x_valence| plts$valence_soc_dens) +
  plot_layout(widths = c(5, 1))

plts$valence_ptchw <- (plts$valence_p1 / plts$valence_p2) +
  plot_layout(heights = c(1.5, 5))


plts$valence_ptchw 

```

ggsave(filename = "valence.tiff", plot = social_x_valence, width = 7, height = 7, dpi = 300, compression = "lzw", bg = "white")
```{r}

intensity_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial, subj_emo_lab_no_amb) %>%
  summarise(mean = mean(int_slider_response, na.rm = TRUE), .groups = "drop")


#summary stats 
intensity_agg_means2 <- subjective_data %>%
  group_by(social_nonsocial, subj_emo_lab_no_amb) %>%
  summarise(
    mean = mean(int_slider_response, na.rm = TRUE),
    sd   = sd(int_slider_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)


social_x_intensity <- ggplot(intensity_agg_means, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 2, alpha = 0.15) +
  # summary mean points
   geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  geom_point(data = intensity_agg_means2, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial),
             size = 2, inherit.aes = FALSE) +
  # summary error bars
  geom_errorbar(data = intensity_agg_means2, aes(x = social_nonsocial, y = mean, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ subj_emo_lab_no_amb, nrow = 1) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Intensity (Mean)", colour = "") +
  theme_classic(base_size = 14) +
 p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
legend.position = "none"
        # legend.position = "top", legend.title = element_blank() 
         # strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )
social_x_intensity

ggsave(filename = "intensity_model.tiff", plot = social_x_intensity, width = 7, height = 7,dpi = 300,compression = "lzw", bg = "white")


# side density
df_plot_intensity <- subjective_data %>%
  group_by(participant, subj_emo_lab_no_amb, social_nonsocial) %>%
  summarise(mean = mean(int_slider_response, na.rm = TRUE), .groups = "drop")

y_lim_intensity <- range(df_plot_intensity$mean, na.rm = TRUE)

plts$intensity_soc_dens <- ggplot(df_plot_intensity,
  aes(y = mean, fill = social_nonsocial)) +
  geom_density(aes(x = after_stat(density)), orientation = "y",
               alpha = 0.25, colour = NA) +
  scale_fill_brewer(palette = "Dark2") +
  coord_cartesian(ylim = y_lim_intensity) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")

# top emotion summary
plts$intensity_emo_top <- df_plot_intensity %>%
  group_by(subj_emo_lab_no_amb) %>%
  ggplot(aes(subj_emo_lab_no_amb, mean)) +
  stat_summary(geom = "pointrange", fun.data = mean_se) +
  theme_classic() +
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

# patchwork like HR/SCR
plts$intensity_p1 <- (plts$intensity_emo_top | plot_spacer()) +
  plot_layout(widths = c(5, 1))

plts$intensity_p2 <- (social_x_intensity | plts$intensity_soc_dens) +
  plot_layout(widths = c(5, 1))

plts$intensity_ptchw <- (plts$intensity_p1 / plts$intensity_p2) +
  plot_layout(heights = c(1.5, 5))

plts$intensity_ptchw 
```


```{r plot emotion ratings x social/nonsocial}
# happy_emm <- emmeans(subjratings_x_social_subjemotion$Happy, ~ social_nonsocial)
# happy_df   <- as.data.frame(happy_emm)   %>% mutate(model = "Happy")
# 
# sad_emm <- emmeans(subjratings_x_social_subjemotion$Sad, ~ social_nonsocial) 
# sad_df   <- as.data.frame(sad_emm)   %>% mutate(model = "Sad")
# 
# anger_emm<- emmeans(subjratings_x_social_subjemotion$Anger, ~ social_nonsocial) 
# anger_df   <- as.data.frame(anger_emm)   %>% mutate(model = "Angry")
# 
# disgust_emm<- emmeans(subjratings_x_social_subjemotion$Disgust, ~ social_nonsocial) 
# disgust_df   <- as.data.frame(disgust_emm)   %>% mutate(model = "Disgust")
# 
# fear_emm<- emmeans(subjratings_x_social_subjemotion$Fear, ~ social_nonsocial) 
# fear_df   <- as.data.frame(fear_emm)   %>% mutate(model = "Fear")


happy_agg_means <- subjective_data %>%
  group_by(participant, social_nonsocial) %>%   
  summarise(
    mean = mean(happy_slide_response),
    .groups = "drop"
  )

#summary stats 
happy_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(happy_slide_response, na.rm = TRUE),
    sd   = sd(happy_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

sad_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(sad_slide_response, , na.rm = TRUE), .groups = "drop")

sad_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(sad_slide_response, na.rm = TRUE),
    sd   = sd(sad_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

anger_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(anger_slide_response, , na.rm = TRUE), .groups = "drop")

anger_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(anger_slide_response, na.rm = TRUE),
    sd   = sd(anger_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

disgust_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(disgust_slide_response, , na.rm = TRUE), .groups = "drop")

disgust_summary <- subjective_data %>%
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(disgust_slide_response, na.rm = TRUE),
    sd   = sd(disgust_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)

fear_agg_means <- subjective_data %>%
  group_by(participant,social_nonsocial) %>%   
  summarise(mean = mean(fear_slide_response, , na.rm = TRUE), .groups = "drop")

fear_summary <- subjective_data %>%  
  group_by(social_nonsocial) %>%
  summarise(
    mean = mean(fear_slide_response, na.rm = TRUE),
    sd   = sd(fear_slide_response, na.rm = TRUE),
    n    = n(),
    se   = sd / sqrt(n),
    .groups = "drop")%>%
    mutate(ci_lower = mean - 1.96*se,
         ci_upper = mean + 1.96*se)


```


```{r}
#plot separately
plot_happy <- ggplot(happy_agg_means %>% mutate(emotion = "Happy"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 2, alpha = 0.15) +
    geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # condition means
  geom_point(data = happy_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial),
             size = 2, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = happy_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (Mean)") +
  theme_classic(base_size = 14) +
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none", legend.title = element_blank() 
         # strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )

plot_happy


plot_sad <- ggplot(sad_agg_means %>% mutate(emotion = "Sad"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 2, alpha = 0.15) +
   geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # condition means
  geom_point(data = sad_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial),
             size = 2, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = sad_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (emm)") +
  theme_classic(base_size = 14) +
  
  p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none", legend.title = element_blank() 
         # strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )
  
  

plot_sad

plot_angry <- ggplot(anger_agg_means %>% mutate(emotion = "Angry"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 2, alpha = 0.15) +
   geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # condition means
  geom_point(data = anger_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial),
             size = 2, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = anger_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (Mean)") +
  theme_classic(base_size = 14) +
   p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none", legend.title = element_blank() 
         # strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )

plot_angry

plot_disgust <- ggplot(disgust_agg_means %>% mutate(emotion = "Disgust"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 2, alpha = 0.15) +
   geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # condition means
  geom_point(data = disgust_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial),
             size = 2, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = disgust_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (emm)") +
  theme_classic(base_size = 14) +
   p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none", legend.title = element_blank() 
         # strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )

plot_disgust

plot_fear <- ggplot(fear_agg_means %>% mutate(emotion = "Fear"),
                     aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial)) +
  # raw participant means (jittered)
  geom_jitter(width = 0.15, size = 2, alpha = 0.15) +
   geom_boxplot(alpha = .01, colour = "black", notch = TRUE) +
  # condition means
  geom_point(data = fear_summary, aes(x = social_nonsocial, y = mean, colour = social_nonsocial,shape = social_nonsocial),
             size = 2, inherit.aes = FALSE) +
  # 95% CI error bars
  geom_errorbar(data = fear_summary,
                aes(x = social_nonsocial, ymin = ci_lower, ymax = ci_upper, colour = social_nonsocial),
                width = 0.15, size = 1, inherit.aes = FALSE) +
  facet_wrap(~ emotion) +
  coord_cartesian(ylim = c(0, 10)) +
  scale_colour_brewer(palette = "Dark2") +
  labs(x = "Condition", y = "Rating (Mean)") +
  theme_classic(base_size = 14) +
   p$graphstyle_int +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none", legend.title = element_blank() 
         # strip.text.x = element_text(size = 12*(sf+.5),  colour = "black")
  # strip.text.y = element_text(size = 12*(sf+.5),  colour = "black")
        )

plot_fear


```

library(patchwork)

```{r}
plot_angry <- plot_angry + labs(x = "")
plot_disgust <- plot_disgust + labs(x = "", y= "")
plot_fear <- plot_fear + labs(x = "Condition", y= "") # Keep label in middle
plot_happy <- plot_happy + labs(x = "", y= "")
plot_sad <- plot_sad + labs(x = "", y= "")
```


# The combined emotion plot gets one tag

```{r}
emotion_x_social <- (plot_angry + plot_disgust + plot_fear + 
                     plot_happy + plot_sad +
                     plot_layout(nrow = 1, guides = "collect"))



#ggsave(filename = "social_x_emotions.tiff",
    #plot = emotion_x_social, width = 15, height = 4,dpi = 300, compression = "lzw", bg = "white")

emotion_x_social
(social_x_valence | social_x_intensity) +  plot_layout(nrow = 1, guides = "collect")

subj_ratings_plot <- (social_x_valence | social_x_intensity) / emotion_x_social+
  plot_layout(heights = c(1.5, 0.5))+plot_annotation(tag_levels = "A")

subj_ratings_plot 

plts$subj_affect<-subj_ratings_plot


ggsave(filename = "plts_subj_affect.png",
    plot = plts$subj_affect, width = 14, height = 10,dpi = 300, 
    device = "png",units = "in",
    bg = "white")


ggsave(filename = "plts_subj_affect.tiff",
    plot = plts$subj_affect, width = 14, height = 10,dpi = 300, compression = "lzw", 
    device = "tiff",
    bg = "white")
```

save
save.image("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/Mixed_models_output_JD.RData")