---
title: "social empophys coherence"
author: "helio"
date: "2026-01-15"
output: html_document
---

build on s4sn
mfa
consider including one component per face

consider reducing dimensionality of subjective ratings into one compoentn as well

just subjective, scr, hr, and face

```{r}
newDF <- dta_emo[,c("val_slider_response","int_slider_response","happy_slide_response","sad_slide_response","fear_slide_response","disgust_slide_response","anger_slide_response","hr_mean_diff","log_cda_phasic_max","mean_fix_dur","mean_sac_amp","au14_dimpler","au12_lip_corner_pull","au_04_brow_lower","au26_jaw_drop","au01_inner_brow_raise","au02_outer_brow_raise","au05_eye_lid_raise","au06_cheek_raise","au07_eye_lid_tighten","au09_nose_wrinkle","au10_upper_lip_raise","au15_lip_corner_depress","au20_lip_stretch","au17_chin_raise","au23_lip_tighten","au25_lips_apart","au45_eye_blink","social_nonsocial","participant","stim_iaps")]
colnames(newDF)


  newDF$emotioncategory<- dta_emo$emotioncategory
newDF$subj_emo_lab_no_amb<- dta_emo$subj_emo_lab_no_amb



dta_emo_wide_mfa

table(is.na(dta_emo_wide_mfa))

colnames(dta_emo_wide_mfa)
colnames(dta_emo)

dta_pca1_3_face_92 <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofBristol/AffexLab/Research Projects/EmotionPhysio2024/2023-24 Project/Data backup/RData/dta_pca1_3_face_92.rds")



dta_mfa_part1<- dta_emo[,c("val_slider_response","int_slider_response","happy_slide_response","sad_slide_response","fear_slide_response","disgust_slide_response","anger_slide_response","hr_mean_diff","log_cda_iscr","social_nonsocial","participant","stim_iaps",
                           "social_nonsocial", "emotioncategory", "subj_emo_lab_no_amb")]

colnames(dta_pca1_3_face_92)
dta_pca1_3_face_92$social_nonsocial<- NULL
dta_pca1_3_face_92

dta_mfa_part1$social_nonsocial<- NULL

dta_mfa_part2<- left_join(dta_mfa_part1, dta_pca1_3_face_92, 
                          by = c("participant", "stim_iaps", "subj_emo_lab_no_amb"))


dta_emo
dta_mfa_part2$social_nonsocial<- dta_emo$social_nonsocial
colnames(dta_mfa_part2)

dta_mfa_part3<- dta_mfa_part2[,c(10:15,1:9,130:132, 16:129)]

colnames(dta_mfa_part3)
dta_mfa_part4<- dta_mfa_part3[,1:18]
```

first MFA
keep ratings, summairse face into PCs

```{r}
# cast to wide
colnames(dta_mfa_part4)

dta_mfa_part4_wide<- dta_mfa_part4%>%
  select(-filename, subj_emo_lab_no_amb)%>%
 pivot_wider(
    id_cols     = c(participant, social_nonsocial),
    names_from  = c(stim_iaps,emotioncategory),
    values_from = names(dta_mfa_part4[,7:18]),
    names_sep   = "_"   # optional: how to separate the original column name from the stimulus ID
  )
# rm(dta_emo_wide_mfa)
colnames(dta_mfa_part4_wide[,3:722])

dta_mfa_part4_wide
table(is.na(dta_mfa_part4_wide))
# complete

dta_mfa_part4_wide


# 420+60+60+(60*3)
# 
# 
# 541:600

imputedmfa <- missMDA::imputeMFA(dta_mfa_part4_wide[,3:722],
                                               ncp=2,
                                                group=c(420, 60, 60, 180),
                          type=c("s","s","s", "s"))


dta_mfa_part4_wide_complete<- imputedmfa$completeObs


# just the hr, scr, subje, face components
mod_res$mfa_result_wide_new <- MFA(dta_mfa_part4_wide_complete,
                         group=c(420, 60, 60, 180),
                         type=c("s","s","s", "s"),
                          name.group= c("subj_aff","phys_hr","phys_scr","face"),
                          # num.group.sup=c(6),#position of group above
                          graph=TRUE)


mod_res$mfa_result_wide_new$global.pca$var

```

some vis

```{r}
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_wide_new, "quanti.var", axes = 3,top = 10)


fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 2,top = 10)# 
fviz_contrib(mod_res$mfa_result_wide_new, "group", axes = 3,top = 10)

```

```{r}
dta_mfa_part4_wide$mfa_pc1<- mod_res$mfa_result_wide_new$ind$coord[,1]
dta_mfa_part4_wide$mfa_pc2<- mod_res$mfa_result_wide_new$ind$coord[,2]
dta_mfa_part4_wide$mfa_pc3<- mod_res$mfa_result_wide_new$ind$coord[,3]

dta_mfa_part4_wide$mfa_pc1_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,1]
dta_mfa_part4_wide$mfa_pc2_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,2]
dta_mfa_part4_wide$mfa_pc3_contrib<- mod_res$mfa_result_wide_new$ind$contrib[,3]
# dta_mfa_part4_wide$ma_pc4<- mod_res$mfa_result_wide_new$ind$coord[,4]

```


```{r}

dta_mfa_part4_wide%>%
  mutate(social_nonsocial = ifelse(partic >199, "social", "nonsocial"))%>%
  group_by(particpant, social,nonsocial)%>%
  summairse_if(is.numeric, mean, na.rm = T)%>%
   
  ggplot(aes(social_nonsocial, mfa_pc1,colour = social_nonsocial))+
  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()

dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, mfa_pc2,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, mfa_pc3,colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()





dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc2_contrib+.1),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()


dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc3_contrib+.1),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()



dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, log1p(mfa_pc3_contrib+ mfa_pc3_contrib),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()



dta_mfa_part4_wide%>%
   
  ggplot(aes(social_nonsocial, (mfa_pc1_contrib+mfa_pc2_contrib+mfa_pc3_contrib),colour = social_nonsocial))+

  geom_jitter(alpha = .2, width = .1)+
  stat_summary(geom = "pointrange",position = position_dodge(1))+
   ggpubr::stat_compare_means()+
  geom_text(aes(label = participant))
```


PCA verison with equal weight to grouos
Weighted PCA
Give each block equal weight manually:
```{r}

# scale each block so blocks have unit variance contribution
dta_mfa_part4_wide_complete_z <- dta_mfa_part4_wide_complete
blocks <- list(1:420, 421:480, 481:540, 541:720)

for (blk in blocks) {
  # divide by sqrt of mean variance within block
  s <- sqrt(mean(apply(dta_mfa_part4_wide_complete[, blk], 2, var)))
  dta_mfa_part4_wide_complete_z[, blk] <- dta_mfa_part4_wide_complete[, blk] / s
}

mod_res$pca_res <- PCA(dta_mfa_part4_wide_complete_z, scale.unit = TRUE, graph = TRUE)
```

```{r}
fviz_contrib(mod_res$pca_res, "var", axes = 1, top = 15)
fviz_contrib(mod_res$pca_res, "var", axes = 2,top = 10)# 
fviz_contrib(mod_res$pca_res, "var", axes = 3,top = 10)


```

Randomly permute the rows of the dataset within each group (preserving group structure), recompute MFA, and record the eigenvalues. If the observed eigenvalue for dimension 1 exceeds the distribution of permuted eigenvalues, it is unlikely to arise by chance.

library(FactoMineR)
```{r}

mod_res$mfa_result_wide_new <- MFA(dta_mfa_part4_wide_complete,
                         group=c(420, 60, 60, 180),
                         type=c("s","s","s", "s"),
                          name.group= c("subj_aff","phys_hr","phys_scr","face"),
                          # num.group.sup=c(6),#position of group above
                          graph=TRUE)
obs <- mod_res$mfa_result_wide_new$eig[1,1]  # eigenvalue of dim 1
B <- 500
sim <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  # permute rows within each group
  g <- list(1:420, 421:480, 481:540, 541:720)
  for (i in seq_along(g)) {
    dta_perm[g[[i]], ] <- dta_perm[sample(g[[i]]), ]
  }
  mfa_b <- MFA(dta_perm,
               group=c(420,60,60,180),
               type=c("s","s","s","s"),
               name.group=c("subj_aff","phys_hr","phys_scr","face"),
               graph=FALSE)
  sim[b] <- mfa_b$eig[1,1]
}

p_value <- mean(sim >= obs)

p_value
```
Test gaps between dimension instead
<!-- Sometimes it’s nicer to use a ratio instead of a raw difference, because overall scale of eigenvalues can shift under permutations. -->

Row-within-block null: “blocks have structure, but no cross-block alignment”

Goal: preserve within-block variable structure, break alignment across blocks.

Here we shuffle rows separately within each block of columns.
conservative becaue it ignores the variable influence on global dimensions

```{r}
eig_obs <- mod_res$mfa_result_wide_new$eig[, 1]

ratio1_obs <- eig_obs[1] / eig_obs[2]    # λ1 / λ2
ratio2_obs <- eig_obs[2] / eig_obs[3]    # λ2 / λ3, etc.


# permutation ratios

# dta_perm <- dta_mfa_part4_wide_complete

mfa_b <- MFA(dta_perm,
             group = c(420,60,60,180),
             type  = c("s","s","s","s"),
             name.group = c("subj_aff","phys_hr","phys_scr","face"),
             ncp = 2,       # <<--- crucial
             graph = FALSE)

B <- 500
ratio1_sim <- numeric(B)
g <- list(1:420, 421:480, 481:540, 541:720)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  for (i in seq_along(g)) {
    dta_perm[g[[i]], ] <- dta_perm[sample(g[[i]]), ]
  }
  
  mfa_b <- MFA(dta_perm,
               group = c(420,60,60,180),
               type  = c("s","s","s","s"),
               name.group = c("subj_aff","phys_hr","phys_scr","face"),
               ncp = 2,
               graph = FALSE)
  
  eig_b <- mfa_b$eig[,1]
  ratio1_sim[b] <- eig_b[1] / eig_b[2]
}

p_ratio1 <- mean(ratio1_sim >= ratio1_obs)
p_ratio1
```
Column-wise null: “no structure at all” (everything is independent)

Goal: test whether there is any real multivariate structure (sanity check).

Here we shuffle rows independently within each column, then compare the λ₁/λ₂ ratio.

```{r}
set.seed(123)
# 
# eig_obs  <- mfa_res$eig[, 1]
# ratio1_obs <- eig_obs[1] / eig_obs[2]

B <- 500
ratio1_sim_indep <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  # shuffle each column independently
  for (j in seq_len(ncol(dta_perm))) {
    dta_perm[, j] <- dta_perm[sample(nrow(dta_perm)), j]
  }
  
  mfa_b <- MFA(dta_perm,
               group      = c(420, 60, 60, 180),
               type       = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               ncp        = 2,   # only need the first 2 components
               graph      = FALSE)
  
  eig_b <- mfa_b$eig[, 1]
  ratio1_sim_indep[b] <- eig_b[1] / eig_b[2]
}

range(ratio1_sim_indep)
ratio1_obs 
p_ratio1_indep <- mean(ratio1_sim_indep >= ratio1_obs)
# p_ratio1_indep = 0


```

```{r}
eig_obs <- pca_res$eig[, 1]      # eigenvalues
ratio_obs <- eig_obs[1] / eig_obs[2]   # optional λ1/λ2 ratio


set.seed(123)

B <- 500
sim_eig1  <- numeric(B)
sim_ratio <- numeric(B)

for (b in 1:B) {
  X_perm <- X
  
  # shuffle each column independently
  for (j in seq_len(ncol(X_perm))) {
    X_perm[, j] <- X_perm[sample(nrow(X_perm)), j]
  }
  
  pca_b <- PCA(X_perm, scale.unit = TRUE, ncp = 2, graph = FALSE)
  eig_b <- pca_b$eig[, 1]
  
  sim_eig1[b]  <- eig_b[1]
  sim_ratio[b] <- eig_b[1] / eig_b[2]
}

```
loadings
Compare to a “no structure at all” null (column-wise shuffle)


“Are loadings on Dim 1 more ‘spread out’ / larger than I’d see if all variables were independent noise?”
```{r}

 mod_res$mfa_result_wide_new$quanti.var$coord
# observed statistics
loadings1 <- mod_res$mfa_result_wide_new$quanti.var$coord[, 1]
thr <- 0.3

mean_sq_loading_obs <- mean(loadings1^2)
prop_large_obs      <- mean(abs(loadings1) >= thr)

# permutation under "independent variables" null
set.seed(123)
B <- 500
mean_sq_sim <- numeric(B)
prop_large_sim <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  # shuffle each column independently
  for (j in seq_len(ncol(dta_perm))) {
    dta_perm[, j] <- dta_perm[sample(nrow(dta_perm)), j]
  }
  
  mfa_b <- MFA(dta_perm,
               group      = c(420, 60, 60, 180),
               type       = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               ncp        = 2,
               graph      = FALSE)
  
  load_b <- mfa_b$quanti.var$coord[, 1]
  mean_sq_sim[b]   <- mean(load_b^2)
  prop_large_sim[b] <- mean(abs(load_b) >= thr)
}

# one-sided p-values: is observed larger than null?
p_mean_sq   <- mean(mean_sq_sim   >= mean_sq_loading_obs)
p_prop_large <- mean(prop_large_sim >= prop_large_obs)
range(mean_sq_sim)
range(mean_sq_loading_obs)
range(prop_large_sim)
prop_large_obs
p_mean_sq
p_prop_large

# both alright
```

Compare to a “no cross-block alignment” null (row-per-block shuffle)

This one keeps within-block structure as signal and only kills cross-block alignment:

i.e. Are the loadings on Dim 1 stronger than I’d expect if blocks had structure but were unrelated”
a bii more conservative because it ignores that structure comes mostly from the variables, the block stuff is for normlaisation


```{r}

# observed stats again
# loadings1 <- mod_res$quanti.var$coord[, 1]
# thr <- 0.3

# mean_sq_loading_obs <- mean(loadings1^2)
# prop_large_obs      <- mean(abs(loadings1) >= thr)

# column indices per block
block_cols <- list(
  subj_aff = 1:420,
  phys_hr  = 421:480,
  phys_scr = 481:540,
  face     = 541:720
)

set.seed(123)
B <- 500
mean_sq_sim_block   <- numeric(B)
prop_large_sim_block <- numeric(B)

for (b in 1:B) {
  dta_perm <- dta_mfa_part4_wide_complete
  
  # shuffle rows separately within each block of columns
  for (blk in block_cols) {
    idx_rows <- sample(nrow(dta_perm))
    dta_perm[, blk] <- dta_perm[idx_rows, blk]
  }
  
  mfa_b <- MFA(dta_perm,
               group      = c(420, 60, 60, 180),
               type       = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               ncp        = 2,
               graph      = FALSE)
  
  load_b <- mfa_b$quanti.var$coord[, 1]
  mean_sq_sim_block[b]    <- mean(load_b^2)
  prop_large_sim_block[b] <- mean(abs(load_b) >= thr)
}

p_mean_sq_block   <- mean(mean_sq_sim_block    >= mean_sq_loading_obs)
p_prop_large_block <- mean(prop_large_sim_block >= prop_large_obs)

p_mean_sq_block
p_prop_large_block

```


This checks stability of loadings and factor scores.

Idea:
Resample rows with replacement, rerun MFA, and assess:
	•	correlation between bootstrapped and original axes
	•	confidence intervals for contributions or loadings

bootMFA (from ExPosition) do this directly 9but its deprecated;

so I will do manual bootstrapping:

 stability of the latent dimension, i.e. how reproducible is Dim 1 as a participant-level score?

```{r}
B <- 200
corrs <- matrix(NA, B, 1)

for (b in 1:B) {
  idx <- sample(nrow(dta_mfa_part4_wide_complete), replace=TRUE)
  mfa_b <- MFA(dta_mfa_part4_wide_complete[idx,],
               group=c(420,60,60,180),
               type=c("s","s","s","s"),
               name.group=c("subj_aff","phys_hr","phys_scr","face"),
               graph=FALSE)
  corrs[b] <- cor(mfa_b$ind$coord[,1], mod_res$mfa_result_wide_new$ind$coord[idx,1])
}

mean_abs_corr <- mean(abs(corrs))

mean_abs_corr
```



loadings_boot <- matrix(NA, nrow = length(loadings_orig), ncol = B_boot)

for (b in 1:B_boot) {
  idx <- sample(1:n, size = n, replace = TRUE)
  dta_boot <- dta_mfa_part4_wide_complete[idx, ]

  mfa_b <- MFA(dta_boot,
               group = c(420, 60, 60, 180),
               type  = c("s", "s", "s", "s"),
               name.group = c("subj_aff", "phys_hr", "phys_scr", "face"),
               graph = FALSE)

  load_b <- mfa_b$quanti.var$coord[, 1]
  # align sign using a global correlation with original loadings
  sign_flip <- sign(sum(load_b * loadings_orig, na.rm = TRUE))
  loadings_boot[, b] <- load_b * sign_flip
}

# e.g. 95% bootstrap interval for each variable’s loading
load_ci_low  <- apply(loadings_boot, 1, quantile, probs = 0.025, na.rm = TRUE)
load_ci_high <- apply(loadings_boot, 1, quantile, probs = 0.975, na.rm = TRUE)
