---
title: "estimating power for depression effects of facial behaviour"
author: "helio"
date: "2026-04-20"
output: html_document
---

setwd(paste0("~",soc_emophys_paths$backup_rdata))


save.image("social_emophys_facenmfs_77frames.RData")
saveRDS(dta_cmfsts3_wid, "dta_pca1_3_face_92.rds")
```{r}
load("social_emophys_facenmfs_77frames.RData")

dta_cmfsts3_wid
colnames(dta_cmfsts3_wid)
require(tidyverse)

dta_cmfsts3_wid_w_dmg<- dta_cmfsts3_wid%>%
  left_join(dta_emo_dmg)

range(dta_cmfsts3_wid_w_dmg$dass21_dep, na.rm = T)

unique(dta_emo_dmg$participant)

dta_emo_dmg%>%
  mutate(participant_numerc=as.numeric(as.character(participant)))%>%
  mutate(social_nonsoc = if_else(participant_numerc < 190, "nonsocial", "social"))%>%
  # group_by(
  ggplot(aes(dass21_dep))+
  geom_histogram()+
  facet_grid(~social_nonsoc)+
  geom_vline(xintercept = 10)+
  geom_vline(xintercept = 14)


```


```{r}
  

unique(dta_cmfsts3_wid_w_dmg$participant)

table(is.na(dta_cmfsts3_wid_w_dmg$tas20_total))


dta_cmfsts3_wid_w_dmg_2<- dta_cmfsts3_wid_w_dmg%>%
  subset(!is.na(dass21_dep))

dta_cmfsts3_wid_w_dmg_2$das_dep_10<- if_else(dta_cmfsts3_wid_w_dmg_2$dass21_dep>=10, "high", "low")


dta_cmfsts3_wid_w_dmg_2$das_dep_14<- if_else(dta_cmfsts3_wid_w_dmg_2$dass21_dep>=14, "high", "low")

table(dta_cmfsts3_wid_w_dmg_2$das_dep_10)/60

table(dta_cmfsts3_wid_w_dmg_2$das_dep_14)/60

dta_cmfsts3_wid_w_dmg_2$das_dep_10_low_14_high<- if_else(dta_cmfsts3_wid_w_dmg_2$das_dep_14 == "high", "high",
                                                         if_else(dta_cmfsts3_wid_w_dmg_2$das_dep_10 == "low", "low", NA))

table(dta_cmfsts3_wid_w_dmg_2$das_dep_10_low_14_high)/60


```


```{r}

# colnames(dta_cmfsts3_wid_w_dmg_2)



dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp2.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()


dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp3.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()

dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp1.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()

dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp1.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  # facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()


# let's put a number
dta_cmfsts3_wid_w_dmg_2_agg<- dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,dass21_dep, das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)



dta_cmfsts3_wid_w_dmg_2_agg%>%
  ggplot(aes(dass21_dep, pc_comp1.2))+
  geom_point()+
  ggpubr::stat_cor()


dta_cmfsts3_wid_w_dmg_2_agg<- dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,dass21_dep, das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)





library(effectsize)
dta_cmfsts3_wid_w_dmg_2_agg$das_dep_10<- factor(dta_cmfsts3_wid_w_dmg_2_agg$das_dep_10)

effectsize::cohens_d(
  pc_comp1.2 ~ das_dep_10,
  data = dta_cmfsts3_wid_w_dmg_2_agg %>% 
           filter(social_nonsocial == "non-social")
)


library(dplyr)
library(tidyr)

dta_cmfsts3_wid_w_dmg_2_agg %>%
  group_by(social_nonsocial, das_dep_10) %>%
  summarise(
    mean = mean(pc_comp1.2, na.rm = TRUE),
    sd = sd(pc_comp1.2, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = das_dep_10,
    values_from = c(mean, sd, n)
  ) %>%
  mutate(
    mean_diff = mean_low - mean_high,
    pooled_sd = sqrt(
      ((n_low - 1) * sd_low^2 + (n_high - 1) * sd_high^2) /
      (n_low + n_high - 2)
    ),
    cohen_d = mean_diff / pooled_sd
  )
```

ocial_nonsocial
<chr>
mean_high
<dbl>
mean_low
<dbl>
sd_high
<dbl>
sd_low
<dbl>
n_high
<int>
n_low
<int>
mean_diff
<dbl>
nonsocial	-0.7492552	0.8259397	2.997052	2.522036	28	19	1.5751948	
social	-0.1646321	0.2906957	3.269751	2.708864	24	19	0.4553278	

estimate a mixed model for high vs low depression

```{r}
# start with continuous depression

dta_cmfsts3_wid_w_dmg_2$dass21_dep_z<- scale(dta_cmfsts3_wid_w_dmg_2$dass21_dep)[,1]
mod_res$power_dep_high_low <- lmer(pc_comp1.2 ~ 1+ social_nonsocial * dass21_dep_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid_w_dmg_2)
summary(mod_res$power_dep_high_low )
anova(mod_res$power_dep_high_low )

# 0.3982/0.4333
#moderate.
report::report(mod_res$power_dep_high_low )


# because in previous visualisations we saw the effect is bigger in non social, likely due to the evaluative nature and restarined nature pof social condition, let's fit a model just. on nosocial 

dta_cmfsts3_wid_w_dmg_2_ns<- dta_cmfsts3_wid_w_dmg_2%>%subset(social_nonsocial!= "social")
dta_cmfsts3_wid_w_dmg_2_ns$dass21_dep_z<- scale(dta_cmfsts3_wid_w_dmg_2_ns$dass21_dep_z)
mod_res$power_dep_high_low_nopnsocial <- lmer(pc_comp1.2 ~ 1+ dass21_dep_z + 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid_w_dmg_2_ns)


summary(mod_res$power_dep_high_low_nopnsocial)
# still moderate

# group comparison categorically by dass cutoofs - across everyone

mod_res$power_dep_high_low_cut_10 <- lmer(pc_comp1.2 ~ 1+ das_dep_10 *social_nonsocial+ 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid_w_dmg_2)

anova(mod_res$power_dep_high_low_cut_10)
emmeans::emmeans(mod_res$power_dep_high_low_cut_10, pairwise~das_dep_10, p.adjust = "none")
summary(mod_res$power_dep_high_low_cut_10)

report::report(mod_res$power_dep_high_low_cut_10)
report::report_effectsize(mod_res$power_dep_high_low_cut_10)
# small


# just looks at the nonsocial
mod_res$power_dep_high_low_cut_10_nons <- lmer(pc_comp1.2 ~ 1+ das_dep_10+ 
                     (1|participant) + #subjective_emotion doesn't converge
                     (1|stim_iaps), #social_nonsocial doesn't converge
                   REML = FALSE,
                   data = dta_cmfsts3_wid_w_dmg_2_ns)

anova(mod_res$power_dep_high_low_cut_10_nons)
summary(mod_res$power_dep_high_low_cut_10_nons)

report::report_effectsize(mod_res$power_dep_high_low_cut_10_nons)
# small

```


based on the vis above we can take c1 

below we take all above 14 (moderate), and mild are considered low
```{r}

dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_14, pc_comp1.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()


dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_14, pc_comp2.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()


dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_14, pc_comp3.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()

```
low vs moderate +, rationale, is to see if the moderate group adds noise


```{r}


dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10_low_14_high, pc_comp1.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()


dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10_low_14_high, pc_comp2.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()


dta_cmfsts3_wid_w_dmg_2%>%
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10_low_14_high, pc_comp3.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()




```


evidence of small to moderate, because we are being conservative, we can probably go for the higher  given that we expect that social interaction task will be more powerful (medium/moderate)

estimate power for a number of designs
- between comparison on aggregated data
- mixed model between subj comparison
- simulation stuff



- simulation stuff
simrmr
```{r}



```

```{r}
dta_cmfsts3_wid_w_dmg_2%>%
#  if das_dep_10  == low, add a gaussian that makes them more high on pc_comp1.2 by up to 2 compared to low group and vice versa
  # mutate(pc_comp1.2_sim = if_else())
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp1.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()

  
  
  library(dplyr)

set.seed(123)

dta_sim_agg <- dta_cmfsts3_wid_w_dmg_2 %>%
  mutate(
    sim_shift = case_when(
      das_dep_10 == "low" ~ pmin(pmax(rnorm(n(), mean = 1,  sd = 0.5), 0), 2),
      das_dep_10 != "low" ~ -pmin(pmax(rnorm(n(), mean = 1, sd = 0.5), 0), 2),
      TRUE ~ NA_real_
    ),
    `pc_comp1.2_sim` = `pc_comp1.2` + sim_shift
  ) %>%
  group_by(participant, social_nonsocial, das_dep_10, das_dep_14, das_dep_10_low_14_high) %>%
  summarise(
    across(where(is.numeric), ~ mean(.x, na.rm = TRUE)),
    .groups = "drop"
  )



dta_cmfsts3_wid_w_dmg_2%>%
#  if das_dep_10  == low, add a gaussian that makes them more high on pc_comp1.2 by up to 2 compared to low group and vice versa
  # mutate(pc_comp1.2_sim = if_else())
  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp1.2))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()
  
  
  dta_sim_agg%>%

  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp1.2_sim))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()
```


```{r}

library(dplyr)

set.seed(123)

dta_sim_low_power <- dta_cmfsts3_wid_w_dmg_2 %>%
  mutate(
    `pc_comp1.2_sim` = `pc_comp1.2` + rnorm(n(), mean = 0, sd = 2)
  ) %>%
  group_by(participant, social_nonsocial, dass21_dep, das_dep_10, das_dep_14, das_dep_10_low_14_high) %>%
  summarise(
    across(where(is.numeric), ~ mean(.x, na.rm = TRUE)),
    .groups = "drop"
  )


table(dta_sim_low_power$das_dep_10, dta_sim_low_power$social_nonsocial)
  dta_sim_low_power%>%

  group_by(participant, social_nonsocial,das_dep_10, das_dep_14, das_dep_10_low_14_high)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(das_dep_10, pc_comp1.2_sim))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  facet_grid(~social_nonsocial)+
  ggpubr::stat_compare_means()

```
